### 2013-06-06 Report/ReportFHE.tex
Report with cost

% THIS IS SIGPROC-SP.TEX - VERSION 3.1
% WORKS WITH V3.2SP OF ACM_PROC_ARTICLE-SP.CLS
% APRIL 2009
%
% It is an example file showing how to use the 'acm_proc_article-sp.cls' V3.2SP
% LaTeX2e document class file for Conference Proceedings submissions.
% ----------------------------------------------------------------------------------------------------------------
% This .tex file (and associated .cls V3.2SP) *DOES NOT* produce:
%       1) The Permission Statement
%       2) The Conference (location) Info information
%       3) The Copyright Line with ACM data
%       4) Page numbering
% ---------------------------------------------------------------------------------------------------------------
% It is an example which *does* use the .bib file (from which the .bbl file
% is produced).
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission,
% you need to 'insert'  your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%
% Questions regarding SIGS should be sent to
% Adrienne Griscti ---> griscti@acm.org
%
% Questions/suggestions regarding the guidelines, .tex and .cls files, etc. to
% Gerald Murray ---> murray@hq.acm.org
%
% For tracking purposes - this is V3.1SP - APRIL 2009
\documentclass{acm_proc_article-sp}

\makeatletter
\newif\if@restonecol
\makeatother
\let\algorithm\relax
\let\endalgorithm\relax
\usepackage{algorithm2e}
\begin{document}

\title{Analysis of Security-Cost Trade-off of Fully Homomorphic Encryption Schemes}

%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{2} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Kais Chaabouni \\
       \affaddr{ENSIMAG}\\
       \affaddr{Grenoble INP}\\
       \affaddr{Grenoble, France}\\
       \email{kais.chaabouni@ensimag.imag.fr}
% 2nd. author
\alignauthor 
Amrit Kumar\\
       \affaddr{ENSIMAG-Ecole Polytechnique}\\
       \affaddr{Grenoble INP}\\
       \affaddr{Grenoble, France}\\
       \email{amrit.kumar@ensimag.imag.fr}
}

% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.

\date{30 July 1999}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

\maketitle
\begin{abstract}
Abstract \\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\
\end{abstract}

\keywords{ Fully Homomorphic Encryption, Security, Cost} % NOT required for Proceedings

\section{Introduction}

Motivation and significance of fully homomorphic encryption scheme such as Gentry's lattice-based scheme.  
This work evaluates the efficiency of FHE implementations for operations varying from XOR to sort on remote machines. Trade-off between cost and security is analyzed. \\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\

\section{Gentry's fully homomorphic scheme}
 FHE\\\\\\\
\subsection{The Framework}
Overview of the algorithm and its complexity. 
 \\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\

\subsection{Example}
Description using a typical operation like modular multiplication of two $n$-bit vectors. Comparison with partial homomorphic encryption scheme such as RSA. \\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\

\section{Experimental Evaluation of Cost}

Describe the FHE algorithm and its corresponding implementation choice. Installation, set-up procedure and usage of the implementation. We detail the measurements to be taken, like Wall time, CPU time and memory usage based on certain security or algorithmic parameters.

Statistical analysis of the measurements using minimum, max, mean and standard deviation. \\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\

\section{Evaluation on Bench Marks}

We describe the system parameters and test vectors. This section also includes description of the process of evaluation for the following operations :

As the \textsc{hCrypt} implementation provides us with the two gates : \texttt{XOR} and \texttt{AND} which form a complete set of functional gates. The $\neg$\texttt{a} is \texttt{XOR(a,1)} while \texttt{OR(a,b)} is \texttt{XOR(XOR(a,b), AND(a,b))}.

\paragraph{ XOR of $n$-bits}

We start with the simplest operations on bits. \texttt{XOR} of $n$-bits requires $n-1$ \texttt{XOR} gates.

\paragraph{Majority of $n$-bits}

Majority bit will be evaluated with the following circuit :

\[\prod_{i=1}^{n}{a_i}+\sum_{i=1}^{n}{(\prod_{j!=i}{a_j}) \neg a_i}\]

Hence it uses $(n^2-1)$ \texttt{AND} gates and $n$ \texttt{OR} gates.

\paragraph{Sum of integers of $n$-bits} Sum of two integers can be performed using an $n$-bit adder based on \texttt{full-adder} circuits. The cost of a full adder circuit is $2$ \texttt{XOR} to calculate the sum and the cost of calculating $3-bit$ majority function for the carry.

\paragraph{Sum of arbtrary integers}

\begin{itemize}
\item Sum of : 
	\begin{itemize}
	\item  bounded integers
	\item unbounded integers
 	\end{itemize}
\item String sorting with the following methods :
	\begin{itemize}
	\item Insertion sort
	\item Merge sort
	\item Quick Sort
	\end{itemize}
\item Matrix product
\end{itemize}

Sorting is tested on a sorting network where comparator gates are used. For insertion sort we would need $n(n-1)/2$ such gates. Each comparator is designed using the following algorithm.

\restylealgo{algoruled}
\linesnumbered
\begin{algorithm}[H]
 \SetVline
 \KwData{$(a_0,a_1,\ldots, a_{n-1}$), $(b_0,b_1,\ldots, b_{n-1})$ }
 \KwResult{Return Max(a,b) and Min(a,b)}
 aIsGreater=$0$\;

 \For{$i\leftarrow n-1$ \KwTo $0$}{
     aIsGreater=aIsGreater $+\neg(b_i)a_i$ \;
 }

\For{$i\leftarrow 0$ \KwTo $n-1$}{
     $Max_i$ = aIsGreater*$a_i$ + $\neg(aIsGreater)*b_i$ \;
     $Min_i$ = $\neg(aIsGreater)*a_i$ + aIsGreater*$b_i$ \;
 }

return($(Max_0,Max_1,\ldots, Max_{n-1}$), $(Min_0,Min_1,\ldots, Min_{n-1})$)
 \caption{Comparator\label{Code:algo}}
\end{algorithm}

Each comparator gate uses $n$ \texttt{AND} gate and $n$ \texttt{OR} gates and $n$ \texttt{NOT} gates to find which one of the bit sequence is bigger and then to regenerate the maximum and the minuimum it would require $4n$ \texttt{AND} gates $2n$ \texttt{NOT} and \texttt{OR} gates.

For each operation, we provide the initial algorithm and the results obtained. Observations based on the measurements are described. 
\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\

\section{Analysis of the results}

Trade-off analysis on the results obtained. Comparison with other protocols in terms of gain with security-cost trade-off. Observations and recommendations on the cost and security trade-off.\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\
\section{Conclusion}
Conclusion\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\
\bibliographystyle{abbrv}
\bibliography{}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
%\balancecolumns
\balancecolumns
% That's all folks!
\end{document}

### 2013-06-06 libScarab-1.0.0/parameters.h
add libscarab

@@ -1,0 +1,28 @@
+/*
+ *  parameters.h
+ *  integer-fhe
+ *
+ *  Created by Henning Perl on 25.11.10.
+ *  Copyright 2010 Henning Perl. All rights reserved.
+ *
+ */
+
+#pragma once
+#ifndef PARAMETERS_H
+#define PARAMETERS_H
+
+#define N 8
+
+#define MU 4
+
+
+//#define NU 2**256;
+
+#define LOG_NU 384
+
+#define S1 8
+#define S2 5
+#define T  5 // Ceiling[Log[2, S2]] + 2
+#define S  3 // Floor[Log[2, s2]] + 1
+
+#endif

### 2013-06-06 libScarab-1.0.0/test.c

@@ -1,0 +1,618 @@
+/*
+ *  test.c
+ *  integer-fhe
+ *
+ *  Created by Henning Perl on 17.12.10.
+ *
+ */
+
+#include "test.h"
+
+#define ASSERT_HALFADD(__a,__b,__sum,__carry)		\
+	fhe_halfadd(sum, carry, __a, __b, pk);			\
+	assert(fhe_decrypt(sum, sk) == __sum);			\
+	assert(fhe_decrypt(carry, sk) == __carry);
+
+#define ASSERT_FULLADD(__a,__b,__c,__sum,__carry)	\
+	fhe_fulladd(sum, carry, __a, __b, __c, pk);		\
+	assert(fhe_decrypt(sum, sk) == __sum);			\
+	assert(fhe_decrypt(carry, sk) == __carry);
+
+#define ASSERT_HOMMUL(__a, __b, __check)			\
+	fhe_mul(temp, __a, __b, pk);					\
+	assert(fhe_decrypt(temp, sk) == __check);
+
+#define ASSERT_HOMADD(__a, __b, __check)			\
+	fhe_add(temp, __a, __b, pk);					\
+	assert(fhe_decrypt(temp, sk) == __check);
+void debug_test_bit_majoritaire();
+void
+test_suite()
+{
+	//test_fully_homomorphic();
+	//test_homomorphic();
+	//test_recrypt();
+	//test_encryt_decrypt();
+	//test_halfadd();
+	//test_fulladd();
+	test_xor_bits();
+	//test_sum_bits();
+	//test_bit_majoritaire();
+	//debug_test_bit_majoritaire();
+}
+
+void debug_or(mpz_t res, mpz_t a, mpz_t b){
+	mpz_t aux1, aux2;
+	mpz_init(aux1);
+	mpz_init(aux2);
+	mpz_add(aux1, a, b);
+	mpz_mul(aux2, a, b);
+	mpz_add(res, aux1, aux2);
+	mpz_clear(aux1);
+	mpz_clear(aux2);
+}
+
+void or(mpz_t res, mpz_t a, mpz_t b, fhe_pk_t pk){
+	mpz_t aux1, aux2;
+	mpz_init(aux1);
[…]

### 2013-06-06 libScarab-1.0.0/test.h

@@ -1,0 +1,41 @@
+/*
+ *  test.h
+ *  integer-fhe
+ *
+ *  Created by Henning Perl on 17.12.10.
+ *
+ */
+
+#pragma once
+#ifndef TEST_H
+#define TEST_H
+
+#include <stdlib.h>
+#include <stdio.h>
+#include <assert.h>
+#include "integer-fhe.h"
+
+#define RUNS 60
+#define KEYRUNS 10
+
+void test_encryt_decrypt();
+
+void test_halfadd();
+
+void test_fulladd();
+
+void test_recrypt();
+
+void test_homomorphic();
+
+void test_fully_homomorphic();
+
+void test_xor_bits();
+
+void test_sum_bits();
+
+void test_bit_majoritaire();
+
+void test_suite();
+
+#endif

### 2013-06-06 Report/ReportFHE.tex
j'ai modifié xor de bits

@@
 \begin{abstract}
-Abstract \\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\
+We present a study on variants of fully homomorphic schemes and the trade-off cost/security of basic operations on bits, integers, strings... \\\\\\\\\\\\\\\\\\\\\\\\\\
 \end{abstract}
@@
 
-Motivation and significance of fully homomorphic encryption scheme such as Gentry's lattice-based scheme.  
-This work evaluates the efficiency of FHE implementations for operations varying from XOR to sort on remote machines.
-Trade-off between cost and security is analyzed.
-\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\
-
+(Motivation and significance of fully homomorphic encryption scheme such as Gentry's lattice-based scheme.  
+This work evaluates the efficiency of FHE implementations for operations varying from XOR to sort on remote machines. Trade-off between cost and security is analyzed.) \\\\\\
+A homomorphic encryption allows operations on ciphertexts which implies a known operation on plaintext, such as RSA: 
+\[\texttt{E}(\prod_{i=1}^{n}{a_i}) = \prod_{i=1}^{n}{\texttt{E}(a_i)}\] 
+\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\
 \section{Gentry's fully homomorphic scheme}
@@
 \subsection{Example}
-Description using a typical operation like modular multiplication of two $n$-bit vectors.
-Comparison with partial homomorphic encryption scheme such as RSA.
+Description using a typical operation like modular multiplication of two $n$-bit vectors. Comparison with partial homomorphic encryption scheme such as RSA.
+
+Hence it uses $(n^2-1)$ \texttt{AND} gates and $n$ \texttt{OR} gates. 
  \\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\

### 2013-06-06 libScarab-1.0.0/test.c

@@ -80,8 +80,10 @@ void not(mpz_t res, mpz_t a, fhe_pk_t pk){
 	mpz_clear(c1);
 }
 void test_xor_bits(){
-	int m, aux;
+	int  aux, i;
 	mpz_t c0, c1;
+	fmpz_poly_t poly_c;
+	fmpz_poly_init(poly_c);
 	mpz_init(c0);
 	mpz_init(c1);
 	fhe_pk_t pk;
@@ -89,25 +91,34 @@ void test_xor_bits(){
 	fhe_pk_init(pk);
 	fhe_sk_init(sk);
 	fhe_keygen(pk, sk);
-	m= 13;	
-	for(int i=13; i < 27; i++){
-		m=i;
+	//m= 13;	
+	for(int m=13; m < 27; m++){
+		aux=m;
+		i=0;
 		printf("--------->%i\n", m % 2);
-		fhe_encrypt(c0, pk, m % 2);
-		aux = m;	
+		fhe_encrypt(c0, pk, aux % 2);
+		fmpz_poly_set_coeff_mpz ( poly_c , i , c0 );
 		aux = aux >> 1;
 		do {
 			printf("--------->%i\n", aux % 2);
-			fhe_encrypt(c1, pk, aux % 2);
+			fhe_encrypt(c0, pk, aux % 2);
+			i=i+1;
+			fmpz_poly_set_coeff_mpz ( poly_c , i , c0 );
 			aux = aux >> 1;
-			fhe_add(c0, c0, c1, pk);
 		}while(aux != 0);
-////
+		fmpz_poly_get_coeff_mpz ( c0, poly_c, i);
+		i=i-1;
+		while(i>=0){
+			fmpz_poly_get_coeff_mpz ( c1, poly_c, i);
+			fhe_add(c0, c0, c1, pk);
+			i=i-1;
+		}
 		aux = fhe_decrypt(c0, sk);
 		printf("///////////////-----------!!!!!!  xor bits de %i est %i \n", m, aux);
 	}
 	mpz_clear(c0);
-	mpz_clear(c1);
+	mpz_clear(c1);	
+	fmpz_poly_clear(poly_c);
 	fhe_pk_clear(pk);
 	fhe_sk_clear(sk);
 }

### 2013-06-07 Report/ReportFHE.tex
report

@@
 This work evaluates the efficiency of FHE implementations for operations varying from XOR to sort on remote machines. Trade-off between cost and security is analyzed.) \\\\\\
-A homomorphic encryption allows operations on ciphertexts which implies a known operation on plaintext, such as RSA: 
-\[\texttt{E}(\prod_{i=1}^{n}{a_i}) = \prod_{i=1}^{n}{\texttt{E}(a_i)}\] 
+A partially homomorphic encryption allows certain operations on ciphertexts such as addition or multiplication which implies a known operation on plaintext like RSA Encryption
+\[\texttt{E}(\prod_{i=1}^{n}{a_i}) = \prod_{i=1}^{n}{\texttt{E}(a_i)}\] \\
+then Gentry proved that there is a fully homomorphic encryption which allows both addition and multiplication on encrypted bits: 
+\[\texttt{FHE}(m1) + \texttt{FHE} (m2) = \texttt{FHE}(m1+m2) ;\ \ \ m1, m2 \in \left\{ 0, 1 \right\}\] 
 \\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\

### 2013-06-07 Report/ReportFHE.tex
modif

@@
 then Gentry proved that there is a fully homomorphic encryption which allows both addition and multiplication on encrypted bits: 
-\[\texttt{FHE}(m1) + \texttt{FHE} (m2) = \texttt{FHE}(m1+m2) ;\ \ \ m1, m2 \in \left\{ 0, 1 \right\}\] 
-\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\
+\[\texttt{FHE}(m1) + \texttt{FHE} (m2) = \texttt{FHE}(m1+m2) \] 
+\[\texttt{FHE}(m1) \times \texttt{FHE} (m2) = \texttt{FHE}(m1 \times m2) ;\ \ \ m1, m2 \in \left\{ 0, 1 \right\}\] 
+\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\
 \section{Gentry's fully homomorphic scheme}
@@
 \subsection{Example}
-Description using a typical operation like modular multiplication of two $n$-bit vectors. Comparison with partial homomorphic encryption scheme such as RSA.
+(Description using a typical operation like multiplication of two $n$-bit integers. Comparison with partial homomorphic encryption scheme such as RSA.)\\
+The multipliction of two FHE-encrypted integers of n bits consists on multiplications and additions on their FHE-encrypted bits: \[(\texttt{a}_{n},\texttt{a}_{n-1}, ...
+,\texttt{a}_{1}) .
+(\texttt{b}_{n},\texttt{b}_{n-1}, ...
+,\texttt{b}_{1}) = (\texttt{r}_{2n},\texttt{r}_{2n-1}, ...
+,\texttt{r}_{1})\] \\
+We do $ n^{2}$ multiplications $ a_i.a_j$ and $ 2.(n + (n-1)(n-2)$ additions
 
-Hence it uses $(n^2-1)$ \texttt{AND} gates and $n$ \texttt{OR} gates. 
- \\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\
+\[r_1= a_1.b_1 ; c_{1,1}=0\] 
+\[(r_2,c_{1,2})=\texttt{add}(a_2.b_1 ,a_1.b_2 ,c_{1,1}  ) \] 
+\[(r_3,c_{2,3})=\texttt{add}(a_1.b_3,\texttt{add}( a_3.b_1, a_2.b_2 , c_{1,2} ))   \] 
+ \[ \vdots    \] 
+\[ (r_{n-1},c_{n-1,n-1})= ...    \] 
+\[(r_{n},c_{n,n})=\texttt{add}(a_1.b_n, ...)      \] 
+\[  (r_{n+1},c_{n+1,n+1})= ..   \] 
+\[  \vdots      \] 
+\[  (r_{2n-1},c_{2n-1,2n-1})=     \] 
+\[ (r_{2n},c_{2n,2n})=  \texttt{add}(a_n.b_n, c_{2n,2n-1})    \]
+So it has $O(n^{2})$ complexity.
+In addition to that there is the cost of key generation, encryption and decryption, and there is also the recrypt algorithm called after each addition or multiplication.
+On the other hand the RSA-Encryption is encrypted much more easier but has a similar cost on multiplication of n-bits integer.
+\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\
+\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\
 
@@
 
-Describe the FHE algorithm and its corresponding implementation choice.
+(Describe the FHE algorithm and its corresponding implementation choice.
 Installation, set-up procedure and usage of the implementation.
@@
 
-Statistical analysis of the measurements using minimum, max, mean and standard deviation.
-\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\
+Statistical analysis of the measurements using minimum, max, mean and standard deviation.) \\\\\\\\
+
+In this section we will experimentally measure time cost of Xor-bits operations using two versions of fully homomorphic encryption programs: libScarab-1.0.0 implementing Smart-Vercauteren algorithm and HElib implementing Gentry-Halevi-Smart algorithm.
+\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\
 

### 2013-06-07 Report/ReportFHE.tex
m
j
check

--- 2013-06-06 Report/ReportFHE.tex
@@
 \usepackage{algorithm2e}
+
 \begin{document}
@@
 \begin{abstract}
-We present a study on variants of fully homomorphic schemes and the trade-off cost/security of basic operations on bits, integers, strings... \\\\\\\\\\\\\\\\\\\\\\\\\\
+Abstract \\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\
 \end{abstract}
@@
 
-(Motivation and significance of fully homomorphic encryption scheme such as Gentry's lattice-based scheme.  
-This work evaluates the efficiency of FHE implementations for operations varying from XOR to sort on remote machines. Trade-off between cost and security is analyzed.) \\\\\\
-A homomorphic encryption allows operations on ciphertexts which implies a known operation on plaintext, such as RSA: 
-\[\texttt{E}(\prod_{i=1}^{n}{a_i}) = \prod_{i=1}^{n}{\texttt{E}(a_i)}\] 
-\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\
+Motivation and significance of fully homomorphic encryption scheme such as Gentry's lattice-based scheme.  
+This work evaluates the efficiency of FHE implementations for operations varying from XOR to sort on remote machines.
+Trade-off between cost and security is analyzed.
+\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\
+
 \section{Gentry's fully homomorphic scheme}
@@
 \subsection{Example}
-Description using a typical operation like modular multiplication of two $n$-bit vectors. Comparison with partial homomorphic encryption scheme such as RSA.
-
-Hence it uses $(n^2-1)$ \texttt{AND} gates and $n$ \texttt{OR} gates. 
+Description using a typical operation like modular multiplication of two $n$-bit vectors.
+Comparison with partial homomorphic encryption scheme such as RSA.
 \\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\
@@
 
-As the \textsc{hCrypt} implementation provides us with the two gates : \texttt{XOR} and \texttt{AND} which form a complete set of functional gates.
-The $\neg$\texttt{a} is \texttt{XOR(a,1)} while \texttt{OR(a,b)} is \texttt{XOR(XOR(a,b), AND(a,b))}.
+\subsection{Operations}
 
-\paragraph{ XOR of $n$-bits}
+The \textsc{Hcrypt} implementation provides two gates : \texttt{XOR} and \texttt{AND} forming a complete set of functional gates.
+We hence define $\neg$\texttt{a} as \texttt{XOR(a,1)}, while \texttt{OR(a,b)} as \texttt{XOR(XOR(a,b), AND(a,b))}, where \texttt{a,b} are bits.
 
+Using these gates we build and analyse the cost of the following operations.
+
+\paragraph{XOR of $n$-bits}
 We start with the simplest operations on bits. \texttt{XOR} of $n$-bits requires $n-1$ \texttt{XOR} gates. 
-
 \paragraph{Majority of $n$-bits} 
-
-Majority bit will be evaluated with the following circuit :
+Majority bit is evaluated with the following circuit :
 
@@
 
-Hence it uses $(n^2-1)$ \texttt{AND} gates and $n$ \texttt{OR} gates.
+where $\sum$ is the successive \texttt{OR}, and $\prod$ is the successive application of \texttt{AND}.
 
+Hence it uses $(n^2-1)$ \texttt{AND} gates, and $n$ \texttt{OR} and \texttt{NOT} gates i.e. $(n^2+n-1)$ \texttt{AND}, $3n$ \texttt{XOR} gates.
 \paragraph{Sum of integers of $n$-bits} Sum of two integers can be performed using an $n$-bit adder based on \texttt{full-adder} circuits.
-The cost of a full adder circuit is $2$ \texttt{XOR} to calculate the sum and the cost of calculating $3-bit$ majority function for the carry.
-
-\paragraph{Sum of arbtrary integers}
+The cost of a full adder circuit is $2$ \texttt{XOR} to calculate the sum and $2$ \texttt{AND}, $1$ \texttt{XOR} and $1$ \texttt{OR} for the carry.
+Hence the total complexity is $3n$ \texttt{AND}, $5n$ \texttt{XOR}.
+\paragraph{Sum of arbitrary integers}
 
@@
 
-Sorting is tested on a sorting network where comparator gates are used. For insertion sort we would need $n(n-1)/2$ such gates. Each comparator is designed using the following algorithm.
+Sorting is tested on a sorting network where comparator gates are used. Each comparator is designed using the following algorithm.
 
@@
  \For{$i\leftarrow n-1$ \KwTo $0$}{
-     aIsGreater=aIsGreater $+\neg(b_i)a_i$ \;
+     $aIsGreater=aIsGreater +\neg(b_i)a_i$ \;
  }
@@
 \For{$i\leftarrow 0$ \KwTo $n-1$}{
-     $Max_i$ = aIsGreater*$a_i$ + $\neg(aIsGreater)*b_i$ \;
-     $Min_i$ = $\neg(aIsGreater)*a_i$ + aIsGreater*$b_i$ \;
+     $Max_i = aIsGreater*a_i + \neg(aIsGreater)*b_i$ \;
+     $Min_i = \neg(aIsGreater)*a_i + aIsGreater*b_i$ \;
  }
 
-return($(Max_0,Max_1,\ldots, Max_{n-1}$), $(Min_0,Min_1,\ldots, Min_{n-1})$)
+return($Max$, $Min$)
  \caption{Comparator\label{Code:algo}}
@@
 
-Each comparator gate uses $n$ \texttt{AND} gate and $n$ \texttt{OR} gates and $n$ \texttt{NOT} gates to find which one of the bit sequence is bigger and then to regenerate the maximum and the minuimum it would require $4n$ \texttt{AND} gates $2n$ \texttt{NOT} and \texttt{OR} gates.
+Each comparator gate uses $n$ \texttt{AND} gates, $n$ \texttt{OR} gates and $n$ \texttt{NOT} gates to find the larger of the two bit sequences and then to regenerate the maximum and the minuimum $4n$ \texttt{AND} gates $2n$ \texttt{NOT} and \texttt{OR} gates i.e.
+$6n$ \texttt{AND} and \texttt{XOR} gates are required.
+
+\paragraph{Insertion sort} $n(n-1)/2$ comparator gates are use for insertion sort.
 

### 2013-06-07 libScarab-1.0.0/test.c

@@ -35,9 +35,12 @@ test_suite()
 	//test_encryt_decrypt();
 	//test_halfadd();
 	//test_fulladd();
-	test_xor_bits();
+	//test_xor_bits();
 	//test_sum_bits();
 	//test_bit_majoritaire();
+	//test_sum_integers();
+	//test_min_max();
+	test_insertion_sort();
 	//debug_test_bit_majoritaire();
 }
 
@@ -79,6 +82,510 @@ void not(mpz_t res, mpz_t a, fhe_pk_t pk){
 	mpz_clear(aux);
 	mpz_clear(c1);
 }
+
+void test_aIsGreater(mpz_t res, fmpz_poly_t polya, fmpz_poly_t polyb, fhe_pk_t pk){
+
+	long nbits = fmpz_poly_degree(polya)+1;
+	mpz_t a_k;
+	mpz_t b_k;
+	mpz_t tmp;
+
+	mpz_init(a_k);
+	mpz_init(b_k);
+	mpz_init(anot);
+	mpz_init(bnot);
+	mpz_init(tmp1);
+	mpz_init(tmp2);
+	mpz_init(count);
+	mpz_init(final);
+	
+	mpz_t aIsGreater;
+	mpz_init(aIsGreater);
+
+	fhe_encrypt(aIsGreater, pk, 0);	
+	fhe_encrypt(count, pk, 1);
+	fhe_encrypt(tmp1,pk,0);
+	fhe_encrypt(tmp2,pk,0);
+	
+	for(long k=nbits-1;k>=0;k--){
+
+		fmpz_poly_get_coeff_mpz(a_k, polya,k);	
+		fmpz_poly_get_coeff_mpz(b_k, polyb,k);
+
+		not(anot, a_k, pk);
+		not(bnot, b_k, pk);
+
+		fhe_mul(tmp1,a_k,b_k, pk);
+		fhe_mul(tmp2,anot, bnot, pk);
+		
+		fhe_add(tmp1, tmp1, tmp2, pk);
+		fhe_mul(count,count, tmp1, pk );
+		
+		fhe_mul(aIsGreater,a_k, bnot, pk);
+		fhe_mul(aIsGreater, aIsGreater,count,pk);
+		fhe_add(tmp1, tmp1, aIsGreater, pk);
+		
+	}
+	mpz_set(res,tmp1);
+	mpz_clear(a_k);
+	mpz_clear(b_k);
+	mpz_clear(tmp1);
+	mpz_clear(tmp2);
[…]

### 2013-06-07 Report/ReportFHE.tex

--- 2013-06-07 Report/ReportFHE.tex
@@
 \usepackage{algorithm2e}
+
 \begin{document}
-
 \title{Analysis of Security-Cost Trade-off of Fully Homomorphic Encryption Schemes}
@@
 \maketitle
+\tableofcontents
+
 \begin{abstract}
@@
 Overview of the algorithm and its complexity.
- \\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\
 
@@
 In addition to that there is the cost of key generation, encryption and decryption, and there is also the recrypt algorithm called after each addition or multiplication.
-On the other hand the RSA-Encryption is encrypted much more easier but has a similar cost on multiplication of n-bits integer.
+On the other hand the RSA-Encryption is much more easier and has a O(1) complexity for the multiplication of n-bits integer.
 \\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\

### 2013-06-07 Report/ReportFHE.tex
rien

--- 2013-06-07 Report/ReportFHE.tex
@@
 \subsection{The Framework}
-Overview of the algorithm and its complexity. 
+(Overview of the algorithm and its complexity. )
+In this study we use two variants of fully homomorphic encryption: 
+\begin{itemize}
+\item Smart-Vercauteren implementation
+
+\item Gentry-Halevi-Smart implementation
+
+\end{itemize}
+
  \\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\

### 2013-06-07 libScarab-1.0.0/test.c
MIN-MAX and Insertion sort

@@ -88,45 +88,48 @@ void test_aIsGreater(mpz_t res, fmpz_poly_t polya, fmpz_poly_t polyb, fhe_pk_t p
 	long nbits = fmpz_poly_degree(polya)+1;
 	mpz_t a_k;
 	mpz_t b_k;
-	mpz_t tmp;
+	mpz_t tmp1;
+	mpz_t anot;
+	mpz_t bnot;
+	mpz_t tmp2;
+	mpz_t count;
 
 	mpz_init(a_k);
 	mpz_init(b_k);
-	mpz_init(anot);
-	mpz_init(bnot);
 	mpz_init(tmp1);
 	mpz_init(tmp2);
-	mpz_init(count);
-	mpz_init(final);
-	
+	mpz_init(anot);
+	mpz_init(bnot);
+	mpz_init(count);	
+
 	mpz_t aIsGreater;
 	mpz_init(aIsGreater);
 
 	fhe_encrypt(aIsGreater, pk, 0);	
 	fhe_encrypt(count, pk, 1);
-	fhe_encrypt(tmp1,pk,0);
-	fhe_encrypt(tmp2,pk,0);
-	
+
 	for(long k=nbits-1;k>=0;k--){
 
 		fmpz_poly_get_coeff_mpz(a_k, polya,k);	
 		fmpz_poly_get_coeff_mpz(b_k, polyb,k);
-
+		
 		not(anot, a_k, pk);
-		not(bnot, b_k, pk);
+		not(bnot, b_k, pk);	
 
-		fhe_mul(tmp1,a_k,b_k, pk);
-		fhe_mul(tmp2,anot, bnot, pk);
+		fhe_mul(tmp1, a_k, b_k, pk);
+		fhe_mul(tmp2, anot, bnot,pk); 
+		or(tmp1, tmp2, tmp1, pk); //Ek
+
+		fhe_mul(tmp2, a_k, bnot, pk);
+		fhe_mul(tmp2, tmp2, count, pk);		
 		
-		fhe_add(tmp1, tmp1, tmp2, pk);
-		fhe_mul(count,count, tmp1, pk );
-		
-		fhe_mul(aIsGreater,a_k, bnot, pk);
-		fhe_mul(aIsGreater, aIsGreater,count,pk);
-		fhe_add(tmp1, tmp1, aIsGreater, pk);
-		
+		fhe_mul(count, count, tmp1,pk);		
[…]

### 2013-06-07 Report/article.tex

--- 2013-06-07 Report/ReportFHE.tex
@@
 \begin{document}
-
 \title{Analysis of Security-Cost Trade-off of Fully Homomorphic Encryption Schemes}
@@
 \maketitle
+
 \begin{abstract}
-Abstract \\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\
+We present a study on variants of fully homomorphic schemes and the trade-off cost/security of basic operations on bits, integers, strings... 
 \end{abstract}
@@
 
-\section{Introduction}
+\section{Introduction(1 page)}
 
-Motivation and significance of fully homomorphic encryption scheme such as Gentry's lattice-based scheme.  
-This work evaluates the efficiency of FHE implementations for operations varying from XOR to sort on remote machines.
-Trade-off between cost and security is analyzed.
-\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\
+Partial HME, Gentry's scheme from SWHME to FHE via bootstrapping.
+The purpose fo FHE, the protocl in general.
+Remote processing of computations on encrypted input transforms a native program into another program which has a higher circuit depth.
+The objective of this article is to analyse the security-cost tradeoff of remote computations.
+The implementations that exist and the organisation of the article.
+With citations to the referenced articles and papers.
 
-\section{Gentry's fully homomorphic scheme}
- FHE\\\\\\\
-\subsection{The Framework}
-Overview of the algorithm and its complexity. 
- \\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\
+\section{Fully homomorphic scheme(1 page)}
 
-\subsection{Example}
-Description using a typical operation like modular multiplication of two $n$-bit vectors.
-Comparison with partial homomorphic encryption scheme such as RSA.
-\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\
+A general structure of the scheme.
 
-\section{Experimental Evaluation of Cost}
+\subsection{Two Variants of Fully Homomorphic Encryption Scheme}
 
-Describe the FHE algorithm and its corresponding implementation choice.
-Installation, set-up procedure and usage of the implementation.
-We detail the measurements to be taken, like Wall time, CPU time and memory usage based on certain security or algorithmic parameters.
+A brief description of the two FHE schemes with their algorithmic complexity of the different stages in the scheme. 
+-> Smart Vercautren
+-> BGV
 
-Statistical analysis of the measurements using minimum, max, mean and standard deviation.
-\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\
+Discuss the security of these schemes.
 
-\section{Evaluation on Bench Marks}
+\subsection{Considered Implementations}
 
-We describe the system parameters and test vectors. This section also includes description of the process of evaluation for the following operations :
+The library used, version, implementaion details, versions, references, modifications required, how-to-installl, how-to-use.Platforms accepted and other depedeices.
 
-\subsection{Operations}
+\subsection{Intial set-up cost(The cost not depending on the actual program)}
 
-The \textsc{Hcrypt} implementation provides two gates : \texttt{XOR} and \texttt{AND} forming a complete set of functional gates.
-We hence define $\neg$\texttt{a} as \texttt{XOR(a,1)}, while \texttt{OR(a,b)} as \texttt{XOR(XOR(a,b), AND(a,b))}, where \texttt{a,b} are bits.
+Can be integrated with subsection 2.1
 
-Using these gates we build and analyse the cost of the following operations.
+\section{ Didactic example :  Maximum of two integer (1 page)}
 
-\paragraph{XOR of $n$-bits}
-We start with the simplest operations on bits. \texttt{XOR} of $n$-bits requires $n-1$ \texttt{XOR} gates. 
-\paragraph{Majority of $n$-bits} 
-Majority bit is evaluated with the following circuit :
+\subsection{Input Program for Fully Homomorphic Encryption Scheme}
 
-\[\prod_{i=1}^{n}{a_i}+\sum_{i=1}^{n}{(\prod_{j!=i}{a_j}) \neg a_i}\]
+Details of the circuit or the program used to calculate the maximum of two bounded integers.
 
-where $\sum$ is the successive \texttt{OR}, and $\prod$ is the successive application of \texttt{AND}.
+\subsection{Theoretical Cost with the Schemes}
 
-Hence it uses $(n^2-1)$ \texttt{AND} gates, and $n$ \texttt{OR} and \texttt{NOT} gates i.e. $(n^2+n-1)$ \texttt{AND}, $3n$ \texttt{XOR} gates.
-\paragraph{Sum of integers of $n$-bits} Sum of two integers can be performed using an $n$-bit adder based on \texttt{full-adder} circuits.
-The cost of a full adder circuit is $2$ \texttt{XOR} to calculate the sum and $2$ \texttt{AND}, $1$ \texttt{XOR} and $1$ \texttt{OR} for the carry.
-Hence the total complexity is $3n$ \texttt{AND}, $5n$ \texttt{XOR}.
-\paragraph{Sum of arbitrary integers}
+Analyse the cost of the program wrt SV, BGV.
 
+\subsection{Experimental Analysis}
+
+Once for all analysis of common operations(KeyGen, Encrypt, Decrypt of 1 bit) varying the algorithmic and security parameters.
+
+Measurements taken are CPU time, Wall Time, Memory Usage by varying the input size  and the algorithmic parameters. Noise reduction threshold.
+
+\paragraph{KeyGen}
+
+\paragraph{Encryption and Decryption}
+
+\section{Choice of Benchmarks}
+
+3 different classes of problems : 
 \begin{itemize}
-\item Sum of : 
-	\begin{itemize}
-	\item  bounded integers
-	\item unbounded integers
- 	\end{itemize}
-\item String sorting with the following methods :
-	\begin{itemize}
-	\item Insertion sort
-	\item Merge sort
-	\item Quick Sort
-	\end{itemize}
-\item Matrix product
+\item Operations on bits,
+ \item operation on integers (possibility of extension on blocks and comparision with RSA and 
+ \item branching
 \end{itemize}
 
-Sorting is tested on a sorting network where comparator gates are used. Each comparator is designed using the following algorithm.
+For each problem we propse the program, analyse their cost and eventually on security.
 
-\restylealgo{algoruled}
-\linesnumbered
-\begin{algorithm}[H]
- \SetVline
- \KwData{$(a_0,a_1,\ldots, a_{n-1}$), $(b_0,b_1,\ldots, b_{n-1})$ }
- \KwResult{Return Max(a,b) and Min(a,b)}
- aIsGreater=$0$\;
+Why certain other programs cannot be executed under homomorphic encryption.
 
- \For{$i\leftarrow n-1$ \KwTo $0$}{
-     $aIsGreater=aIsGreater +\neg(b_i)a_i$ \;
- }
+\section{Evaluation on the Benchmarks (1 page)}
 
-\For{$i\leftarrow 0$ \KwTo $n-1$}{
-     $Max_i = aIsGreater*a_i + \neg(aIsGreater)*b_i$ \;
-     $Min_i = \neg(aIsGreater)*a_i + aIsGreater*b_i$ \;
- }
-
-return($Max$, $Min$)
- \caption{Comparator\label{Code:algo}}
-\end{algorithm}
-
-Each comparator gate uses $n$ \texttt{AND} gates, $n$ \texttt{OR} gates and $n$ \texttt{NOT} gates to find the larger of the two bit sequences and then to regenerate the maximum and the minuimum $4n$ \texttt{AND} gates $2n$ \texttt{NOT} and \texttt{OR} gates i.e.
-$6n$ \texttt{AND} and \texttt{XOR} gates are required.
-
-\paragraph{Insertion sort} $n(n-1)/2$ comparator gates are use for insertion sort.
-
-For each operation, we provide the initial algorithm and the results obtained. Observations based on the measurements are described. 
-\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\
+Measurements on varying the parameters or the plaintext space. Evaluation of program dependent properties.
 
@@
 
-Trade-off analysis on the results obtained.
-Comparison with other protocols in terms of gain with security-cost trade-off.
-Observations and recommendations on the cost and security trade-off.\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\
+Anlayze the results previously obtained and its impact on security and complexity. Comparisions of security-cost tradeoff with other schemes like RSA.
 \section{Conclusion}

### 2013-06-07 Report/article.tex
intro

@@
 \section{Introduction(1 page)}
-
-Partial HME, Gentry's scheme from SWHME to FHE via bootstrapping.
-The purpose fo FHE, the protocl in general.
-Remote processing of computations on encrypted input transforms a native program into another program which has a higher circuit depth.
-The objective of this article is to analyse the security-cost tradeoff of remote computations.
-The implementations that exist and the organisation of the article.
-With citations to the referenced articles and papers.
-
+The homomorphic encryption allows few operations on encrypted data.
+Gentry was the first to establidh a fully homomorphic encryption scheme based on ideal lattices which allows operations on encrypted data
+ but with a high cost.
+Since then many researches have been made trying to improve the schemes to establish more operations on encrypted data with less cost and better secutity in order to do computations on remote machines.
+In this article we study the implementation of basic classes of operations and different aspects of 
+complexity-security, and we discuss the results of experimental measures based on several parameters.\\
+The Gentry FHE protocol consists on ``somewhat homomorphic'' scheme, ``squashing'' and ``bootstrapping''. (explain later). 
+There are variants of FHE schemes more optimized than Gentry's scheme, so we use in the experiments some open source implementations of these schemes.
 \section{Fully homomorphic scheme(1 page)}
@@
 \subsection{Two Variants of Fully Homomorphic Encryption Scheme}
-
 A brief description of the two FHE schemes with their algorithmic complexity of the different stages in the scheme. 
--> Smart Vercautren
+-> Smart Vercauteren
 -> BGV
-
 Discuss the security of these schemes.
 
+\begin{itemize}
+\item Smart-Vercauteren scheme
+
+\end{itemize}
 \subsection{Considered Implementations}

### 2013-06-08 libScarab-1.0.0/test.c
OddEvenSort implementation

@@ -40,7 +40,9 @@ test_suite()
 	//test_bit_majoritaire();
 	//test_sum_integers();
 	//test_min_max();
-	test_insertion_sort();
+	//test_insertion_sort();
+	test_oddeven_merger_sort();
+	//test_majority_bit();
 	//debug_test_bit_majoritaire();
 }
 
@@ -83,9 +85,10 @@ void not(mpz_t res, mpz_t a, fhe_pk_t pk){
 	mpz_clear(c1);
 }
 
-void test_aIsGreater(mpz_t res, fmpz_poly_t polya, fmpz_poly_t polyb, fhe_pk_t pk){
 
-	long nbits = fmpz_poly_degree(polya)+1;
+
+void test_aIsGreater(mpz_t res, fmpz_poly_t polya, fmpz_poly_t polyb, fhe_pk_t pk, int nbits){
+
 	mpz_t a_k;
 	mpz_t b_k;
 	mpz_t tmp1;
@@ -138,10 +141,8 @@ void test_aIsGreater(mpz_t res, fmpz_poly_t polya, fmpz_poly_t polyb, fhe_pk_t p
 }
 
 
-void min_max(mpz_t *min, mpz_t *max, fmpz_poly_t poly_c1, fmpz_poly_t poly_c2, fhe_pk_t pk){
+void min_max(mpz_t *min, mpz_t *max, fmpz_poly_t poly_c1, fmpz_poly_t poly_c2, fhe_pk_t pk, int nbits){
 	
-
-	int nbits = fmpz_poly_degree(poly_c1)+1; 
 	
 	mpz_t a_k;
 	mpz_t b_k;
@@ -156,7 +157,7 @@ void min_max(mpz_t *min, mpz_t *max, fmpz_poly_t poly_c1, fmpz_poly_t poly_c2, f
 		
 	int k;
 
-	test_aIsGreater(aIsGreater,poly_c1,poly_c2,pk);
+	test_aIsGreater(aIsGreater,poly_c1,poly_c2,pk, nbits);
 
 	//printf("Is a greater than b ? Ans : %i  \n", fhe_decrypt(aIsGreater,sk));
 	
@@ -343,10 +344,276 @@ void test_min_max(){
 }
 
 
+void OddEvenMerge(fmpz_poly_t * poly_nums, int n, int nbits, int lo, int r, fhe_sk_t sk , fhe_pk_t pk){
+
+		
+	mpz_t * max;
+	mpz_t * min;
[…]

### 2013-06-08 libScarab-1.0.0/test.c
Bitonic Search implementation

@@ -26,8 +26,10 @@
 	fhe_add(temp, __a, __b, pk);					\
 	assert(fhe_decrypt(temp, sk) == __check);
 void debug_test_bit_majoritaire();
-void
-test_suite()
+
+
+
+void test_suite()
 {
 	//test_fully_homomorphic();
 	//test_homomorphic();
@@ -41,7 +43,8 @@ test_suite()
 	//test_sum_integers();
 	//test_min_max();
 	//test_insertion_sort();
-	test_oddeven_merger_sort();
+	//test_oddeven_merger_sort();
+	test_bitonic_sort();
 	//test_majority_bit();
 	//debug_test_bit_majoritaire();
 }
@@ -480,23 +483,147 @@ void test_oddeven_merger_sort(){
 	}
 	
 	printf("\n");
-	
-		
-		
-				
-		
-
 
 
 }
 
-
 /*
-void test_bitonic_sort(){ // Sorts a btonic array of 2n elements
+void bitonicMerge(fmpz_poly_t * poly_nums, int nbits , int lo, int n, int dir, fhe_sk_t sk, fhe_pk_t pk ){
 
+
+	mpz_t * max;
+	mpz_t * min;
+	max = malloc(sizeof(mpz_t) * nbits);
+	min = malloc(sizeof(mpz_t) * nbits);
+	for(int i=0;i<nbits;i++){
+		mpz_init(max[i]);
+		mpz_init(min[i]);
+	}
+
+
+
+	if(n>1){
+		int m = n/2;
+		for(int i = lo; i<lo+m;i++){
+							
+			min_max(min, max, poly_nums[i], poly_nums[i+m], pk, nbits);		
+			for(int k=0;k<nbits;k++){
+				fmpz_poly_set_coeff_mpz(poly_nums[i], k, min[k]);
+				fmpz_poly_set_coeff_mpz(poly_nums[i+m],k, max[k]);
+			}
+
+			
+		
+		}
+		
+		bitonicMerge(poly_nums, nbits, lo, m, dir, sk, pk);
+		bitonicMerge(poly_nums, nbits, lo+m, m, dir, sk, pk);
+		
+	
+	}
+
+}
+
+*/
+
+
+
+
+
+void bitonicMergeUp(fmpz_poly_t *poly_nums, int  nbits, int n,  int lo , int  high, fhe_sk_t sk, fhe_pk_t pk){
+	if(high==0) return;
+	
[…]

### 2013-06-08 libScarab-1.0.0/test.h

@@ -42,6 +42,12 @@ void test_min_max();
 
 void test_insertion_sort();
 
+void test_oddeven_merger_sort();
+
+void test_bitonic_sort();
+
 void test_suite();
+
+void test_majority_bit();
 
 #endif

### 2013-06-09 Report/article.tex
em
algo sv

@@
 \begin{itemize}
-\item Smart-Vercauteren scheme
-
+\item Smart-Vercauteren scheme:\\
+The scheme has 3 parameters: ($N, \nu, \mu$ ). The somewhat homomorphic scheme uses 5 algorithms: (\texttt{KeyGen}, \texttt{Encrypt}, \texttt{Decrypt}, \texttt{Add}, \texttt{Mult}}).
+\begin{itemize}
+\item \texttt{KeyGen}:
+\begin{itemize}
+\item $F(x)= x^{n}+1$
+\item do
+\begin{itemize}
+\item $S(x)=_{R}(B_{\infty , N}(\nu/2)$
+\item $G(x)=1+2.S(x)$
+\item $p= resultant(G(x),F(x))$
+\end{itemize}
+until $p$ is prime
+\item $D(x)=gcd(G(x),F(x))$ over $\mathbb{F}_p[x]$
+\item $\alpha$: the unique root of $D(x)$
+\item apply \texttt{fmpz\_poly\_xgcd} to obtain $Z(x)$ such that $Z(x).G(x)=p$ mod $F(x)$
+\item $B=z_0$ mod $2p$
+\item $PK = (p, \alpha)$ and $Sk = (p , B)$
+\end{itemize}
+\item \texttt{Encrypt}($m \in \{0,1\} , PK$):
+\begin{itemize}
+\item $R(x)=_{R}(B_{\infty , N}(\mu/2)$
+\item $C(x)=m+2.R(x)$
+\item $c=C(\alpha) mod p$
+\item return $c$
+\end{itemize}
+\item \texttt{Decrypt}($c, SK$):
+\begin{itemize}
+\item $m= (c - round(c.B/p)) mod 2$
+\item return $m$
+\end{itemize}
+\item \texttt{Add}($c_1$, $c_2$, $PK$):
+\begin{itemize}
+\item $c_3=c_1+c_2 mod p$
+\item return $c_3$
+\end{itemize}
+\item \texttt{Mult}($c_1$, $c_2$, PK):
+\begin{itemize}
+\item $c_3=c_1.c_2 mod p$
+\item return $c_3$
+\end{itemize}
+\end{itemize}
+\item BGV:
 \end{itemize}
@@
 
-The library used, version, implementaion details, versions, references, modifications required, how-to-installl, how-to-use.Platforms accepted and other depedeices.
-
+The library used, version, implementaion details, versions, references, modifications required, how-to-installl, how-to-use.Platforms accepted and other depedeices.\\
+For the Smart-Vercauteren implementation we use the library libScarab v1.0.0 which requires the following libraries: GMP, FLINT, MPIR, MPFR.
 \subsection{Intial set-up cost(The cost not depending on the actual program)}

### 2013-06-09 Report/article.tex
Some Algos and pseudo codes added

--- 2013-06-07 Report/article.tex
@@
-% THIS IS SIGPROC-SP.TEX - VERSION 3.1
-% WORKS WITH V3.2SP OF ACM_PROC_ARTICLE-SP.CLS
-% APRIL 2009
-%
-% It is an example file showing how to use the 'acm_proc_article-sp.cls' V3.2SP
-% LaTeX2e document class file for Conference Proceedings submissions.
-% ----------------------------------------------------------------------------------------------------------------
-% This .tex file (and associated .cls V3.2SP) *DOES NOT* produce:
-%       1) The Permission Statement
-%       2) The Conference (location) Info information
-%       3) The Copyright Line with ACM data
-%       4) Page numbering
-% ---------------------------------------------------------------------------------------------------------------
-% It is an example which *does* use the .bib file (from which the .bbl file
-% is produced).
-% REMEMBER HOWEVER: After having produced the .bbl file,
-% and prior to final submission,
-% you need to 'insert'  your .bbl file into your source .tex file so as to provide
-% ONE 'self-contained' source file.
-%
-% Questions regarding SIGS should be sent to
-% Adrienne Griscti ---> griscti@acm.org
-%
-% Questions/suggestions regarding the guidelines, .tex and .cls files, etc. to
-% Gerald Murray ---> murray@hq.acm.org
-%
-% For tracking purposes - this is V3.1SP - APRIL 2009
 \documentclass{acm_proc_article-sp}
-
 \makeatletter
@@
 \let\endalgorithm\relax
+
+\usepackage{listings}
 \usepackage{algorithm2e}
-
 \begin{document}
@@
 \author{
-% You can go ahead and credit any number of authors here,
-% e.g. one 'row of three' or two rows (consisting of one row of three
-% and a second row of one, two or three).
-%
-% The command \alignauthor (no curly braces needed) should
-% precede each author name, affiliation/snail-mail address and
-% e-mail address. Additionally, tag each line of
-% affiliation/address with \affaddr, and tag the
-% e-mail address with \email.
-%
-% 1st. author
 \alignauthor
@@
 % number that will appear in the \additionalauthors section.
-
 \maketitle
-
 \begin{abstract}
@@
 \section{Fully homomorphic scheme(1 page)}
-
 A general structure of the scheme.
-
 \subsection{Two Variants of Fully Homomorphic Encryption Scheme}
@@
 
-3 different classes of problems : 
+The benchmark functions and problems on which the implementations were evaluated are categorized into three classes : functions operating on bits, functions operating directly on integers or block of bits and functions where branching is required i.e \texttt{if-then-else} condition is evaluated.
+
+Functions operating on bits provide information on the tradeoff for calculations with bits, while when operating directly on integers, the tradeoff is obtained on size of integers.
+we note that the first two categories of functions can be evaluated using straight-line-programs.
+For others we choose evaluation of \texttt{if-then-else} condition on encrypted data  wich woukd make the evlaluation circuit longer than compared to the same evaluation on unencrypted data.
+The functions evaluated are :
+
 \begin{itemize}
-\item Operations on bits,
- \item operation on integers (possibility of extension on blocks and comparision with RSA and 
- \item branching
+
+\item XOR of bits
+\item Sum of :
+
+	\begin{itemize}
+
+		\item  bounded integers
+
+		\item unbounded integers
+
+ 	\end{itemize}
+\item Majority bit
+
+\item sorting with the following methods :
+
+	\begin{itemize}
+
+		\item Insertion sort
+
+		\item Odd-Even Merge sort
+
+		\item Bitonic sort
+
 	\end{itemize}
 
-For each problem we propse the program, analyse their cost and eventually on security.
+\end{itemize}
 
-Why certain other programs cannot be executed under homomorphic encryption.
+We include the program used to evalute the above functons and their cost in terms of \texttt{XOR} and \texttt{AND} gates.
 
-\section{Evaluation on the Benchmarks (1 page)}
+\textbf{XOR of $n$-bits :} \texttt{XOR} of $n$-bits requires $n-1$ \texttt{XOR} gates.
 
+\textbf{Sum of integers of $n$-bits :} Sum of two integers is performed using an $n$ \texttt{full-adder} circuits.
+The cost of a full adder circuit is $2$ \texttt{XOR} to calculate the sum and $2$ \texttt{AND}, $1$ \texttt{XOR} and $1$ \texttt{OR} for the carry.
+Hence the total complexity is $3n$ \texttt{AND}, $5n$ \texttt{XOR}.
+
+\textbf{Sum of arbitrary integers}
+
+\textbf{Majority of $n$-bits :} Majority bit is evaluated by obtaining the sum of the bits.
+
+Sorting is tested on a sorting network where comparator gates are used. Each comparator is designed using the following algorithm.
+
+\restylealgo{algoruled}
+
+\linesnumbered
+
+\begin{algorithm}[H]
+
+ \SetVline
+
+ \KwData{a:=$(a_0,a_1,\ldots, a_{n-1}$), b:=$(b_0,b_1,\ldots, b_{n-1})$ }
+
+ \KwResult{Return Max(a,b) and Min(a,b)}
+
+ $aIsGreater \leftarrow 0$\;
+ $bitsEqual \leftarrow 1$\;
+
+ \For{$i\leftarrow n-1 $ \KwTo $0$}{
+
+     $aIsGreater \leftarrow (aIsGreater +\neg(b_i)a_i)* bitEqual$ \;
+     $bitEqual \leftarrow bitEqual*(a_ib_i + \neg(a_i)*\neg(b_i))$		       	
+ }
+
+\For{$i\leftarrow 0$ \KwTo $n-1$}{
+
+     $Max_i \leftarrow aIsGreater*a_i + \neg(aIsGreater)*b_i$ \;
+
+     $Min_i \leftarrow a \neg(aIsGreater)*a_i + aIsGreater*b_i$ \;
+
+ }
+
+return($Max$, $Min$)
+
+ \caption{Comparator\label{Code:algo}}
+
+\end{algorithm}
+
+Each comparator gate uses $n$ \texttt{AND} gates, $n$ \texttt{OR} gates and $n$ \texttt{NOT} gates to find the larger of the two bit sequences and then to regenerate the maximum and the minuimum $4n$ \texttt{AND} gates $2n$ \texttt{NOT} and \texttt{OR} gates i.e.
+$6n$ \texttt{AND} and \texttt{XOR} gates are required.
+
+\textbf{Insertion sort :} $n(n-1)/2$ comparator gates are used for insertion sort.
+
+\textbf{Odd-Even Merge sort :} The following program is used to perform Odd-Even merge sort.
+
+\lstset{                                    % line wrapping on
+  language=C,
+  frame=lines,
+  captionpos=b
+ }
+
+\renewcommand{\lstlistingname}{Code}
+
+\begin{figure}
+\begin{lstlisting}[caption=Odd-Even Merge Sort]
+
+ OddEvenMergeSort(int lo, int n)
+if (n>1)
+        {
+            int m=n/2;
+            oddEvenMergeSort(lo, m);
+            oddEvenMergeSort(lo+m, m);
+            oddEvenMerge(lo, n, 1);
+        }
+oddEvenMerge(int lo, int n, int r)
+    {
+        int m=r*2;
+        if (m<n)
+        {
+	    //even subsequence ;		
+            oddEvenMerge(lo, n, m); 
+            //odd subsequence ;
+	    oddEvenMerge(lo+r, n, m);    
+            for (int i=lo+r; i+r<lo+n; i+=m)
+                compare(i, i+r);
+        }
+        else
+            compare(lo, lo+r);
+    }
+
+\end{lstlisting}
+
+\end{figure}
+
+\textbf{Bitonic Sort}
+\begin{figure}
+\begin{lstlisting}[caption=Bitonic Sort]
+
+sortup( int m, int n) {//from m to m+n
+    if (n==1) return;
+    sortup(m,n/2);
+    sortdown(m+n/2,n/2);
+    mergeup(m,n/2);
+}
+ sortdown(int m, int n) {//from m to m+n
+    if (n==1) return;
+    sortup(m,n/2);
+    sortdown(m+n/2,n/2);
+    mergedown(m,n/2);
+}
+
+mergeup(int m, int n) {
+    if (n==0) return;
+
+    for (i=0 : n) {
+         compare(m+i,m+i+n);
+    }
+    mergeup(m,n/2);
+    mergeup(m+n,n/2);
+}
+mergedown( int m,  int n) {
+    if (n==0) return;
+    for (i=0 : n) {
+        compare(m+i,m+i+n);
+    }
+    mergedown(m,n/2);
+    mergedown(m+n,n/2);
+}
+\end{lstlisting}
+\caption{Bitonic Search}
+\end{figure}
 Measurements on varying the parameters or the plaintext space. Evaluation of program dependent properties.

### 2013-06-10 Report/article.tex
Introduction modified

@@
 \let\endalgorithm\relax
+\usepackage{hyperref}
+\usepackage[all]{hypcap}
+\usepackage[usenames,dvipsnames]{xcolor}
+\usepackage{listings}
+\usepackage{algorithm2e}
+\hypersetup{
+  bookmarks=true,         % show bookmarks bar?
+  unicode=false,          % non-Latin characters in Acrobat’s bookmarks
+  pdftoolbar=true,        % show Acrobat’s toolbar?
+  pdfmenubar=true,        % show Acrobat’s menu?
+  pdffitwindow=false,     % window fit to page when opened
+  pdfstartview={FitH},    % fits the width of the page to the window
+  pdftitle={My title},    % title
+  pdfauthor={Author},     % author
+  pdfsubject={Subject},   % subject of the document
+  pdfcreator={Creator},   % creator of the document
+  pdfproducer={Producer}, % producer of the document
+  pdfkeywords={keyword1} {key2} {key3}, % list of keywords
+  pdfnewwindow=true,      % links in new window
+  colorlinks=true,       % false: boxed links; true: colored links
+  linkcolor=cyan,          % color of internal links (change box color with linkbordercolor)
+  citecolor=green,        % color of links to bibliography
+  filecolor=magenta,      % color of file links
+  urlcolor=cyan           % color of external links
+}
 
@@
 \usepackage{algorithm2e}
+\usepackage{verbatim}
 \begin{document}
@@
 \begin{abstract}
-We present a study on variants of fully homomorphic schemes and the trade-off cost/security of basic operations on bits, integers, strings... 
+This paper presents an analysis of security-cost trade-off for homomorphic encryption schemes.
+Analysis is based on the measurements taken on the evaluation of certain functions on two  variants of fully homomorphic encryption schemes.
+These functions either operate on bits, on integers (of bounded and unbounded size)  or involve \texttt{if-then-else} branching.
 \end{abstract}
 
-\keywords{ Fully Homomorphic Encryption, Security, Cost} % NOT required for Proceedings
+\keywords{ Fully Homomorphic Encryption, Security, Cost.} % NOT required for Proceedings
 
 \section{Introduction(1 page)}
-The homomorphic encryption allows few operations on encrypted data.
-Gentry was the first to establidh a fully homomorphic encryption scheme based on ideal lattices which allows operations on encrypted data
- but with a high cost.
-Since then many researches have been made trying to improve the schemes to establish more operations on encrypted data with less cost and better secutity in order to do computations on remote machines.
+
+The notion of \textit{fully homomorphic encryption scheme}, orginally called a \textit{privacy homomorphism} was introduced by Rivest et al.
+\cite{rivest78} shortly after the invention of the RSA by Rivest, Shamir and Adleman \cite{Rivest78amethod}.
+Basic RSA is a multiplicative homomorphic encryption scheme -- i.e.
+given the public parameters $pk:=(e, N)$ and two messages $m_0, m_1$, their encryption $c_0, c_1$ verify $c_0c_1=(m_0m_1)^e \ \textrm {mod}\ N$.
+With a fully homomorphic encryption scheme : a scheme $\mathcal{E}$ with an efficient algorithm $Eval_\mathcal{E}$ that evaluates any circuit $C$ on any ciphertexts $c_i \leftarrow Encrypt(pk, m_i)$; one can arbitrarily compute any function on encrypted data without the decryption key.
+However prior to \cite{homenc}, we did not have a viable construction.
+
+As an application, such schemes can be used to query data on a remote machine.
+A user prepares his encrypted data $c_0, c_1, \ldots, c_{n-1}$  and a description of the function(or a query) i.e.
+a circuit $C$ he wants to evaluate and sends them to the remote machine.
+The machine transforms the circuit into $C^{'}$ so that it can evaluate the same function but on encrypted data, performs the operation and returns the encrypted result to the user.
+The user eventually decrypts the result.
+
+The homomorphic encryption scheme proposed by Gentry \cite{homenc} is based on ideal lattices which allows operations on encrypted data
+but with a high cost depending on the depth of the circuit representing the $Eval$ function.
+Since then, researchers have improved and proposed other schemes such as \cite{cryptoeprint:2009:571} and \cite{cryptoeprint:2011:277} which decrease the circuit complexity.
+In this article we expermentally evaluate implementation of these two schemes and analyze the cost-security trade-off for $Eval$ varying from \texttt{XOR} of the bits of an $n$ bit integer to sum of bounded and unbounded integers to sorting of $n$ integers.
+Three different sorting algorithms are tested.
+
 In this article we study the implementation of basic classes of operations and different aspects of 
@@
 \item Smart-Vercauteren scheme:\\
-The scheme has 3 parameters: ($N, \nu, \mu$ ). The somewhat homomorphic scheme uses 5 algorithms: (\texttt{KeyGen}, \texttt{Encrypt}, \texttt{Decrypt}, \texttt{Add}, \texttt{Mult}}).
+The scheme \cite{cryptoeprint:2009:571} has 3 parameters: ($N, \nu, \mu$ ).
+The somewhat homomorphic scheme uses 5 algorithms: (\texttt{KeyGen}, \texttt{Encrypt}, \texttt{Decrypt}, \texttt{Add}, \texttt{Mult}).
 \begin{itemize}
@@
 
-The benchmark functions and problems on which the implementations were evaluated are categorized into three classes : functions operating on bits, functions operating directly on integers or block of bits and functions where branching is required i.e \texttt{if-then-else} condition is evaluated.
+The benchmark problems on which the implementations were evaluated are categorized into three classes : functions operating on bits, functions operating directly on integers or block of bits and functions where branching is required i.e \texttt{if-then-else} condition is evaluated.
 
-Functions operating on bits provide information on the tradeoff for calculations with bits, while when operating directly on integers, the tradeoff is obtained on size of integers.
-we note that the first two categories of functions can be evaluated using straight-line-programs.
-For others we choose evaluation of \texttt{if-then-else} condition on encrypted data  wich woukd make the evlaluation circuit longer than compared to the same evaluation on unencrypted data.
-The functions evaluated are :
+Functions operating on bits provide information on the tradeoff for bitwise operations, while when operating directly on integers, the tradeoff is obtained as a function of the size of integers.
+The first two categories of functions can be evaluated using straight-line programs.
+For others, evaluation of \texttt{if-then-else} condition on encrypted data is choosen.
+The evaluation circuit in this case is longer than the one on non-encrypted data.
+Hence, this provides information on increase in size of the circuit(when passing from non-encrypted to enrypted data).
+The addressed problems are :
 
-\begin{itemize}
+1. \textbf{XOR of bits}\\
+2. \textbf{Sum of :}  
+\newline\noindent
+\phantom{x}\hspace{3ex} a) bounded integers 
+ b) unbounded integers\\ 
+3. \textbf{Majority bit} \\
+4. \textbf{Sorting : } \newline\noindent
+\phantom{x}\hspace{3ex} a) Insertion sort b) Oddd-Even Merge sort \\
+	\phantom{x}\hspace{3ex} 	    c) Bitonic sort
 
-\item XOR of bits
-\item Sum of :
+The implementations are evaluated on different sorting algorithms to compare the changes in the evaluation circuits.
 
-	\begin{itemize}
-
-		\item  bounded integers
-
-		\item unbounded integers
-
- 	\end{itemize}
-\item Majority bit
-
-\item sorting with the following methods :
-
-	\begin{itemize}
-
-		\item Insertion sort
-
-		\item Odd-Even Merge sort
-
-		\item Bitonic sort
-
-	\end{itemize}
-
-\end{itemize}
-
-We include the program used to evalute the above functons and their cost in terms of \texttt{XOR} and \texttt{AND} gates.
+\subsection{Theoretical Size of Evaluation Circuit}
+As the implementations provide addition and multiplicaion of ciphertexts,  size in terms of \texttt{XOR} and \texttt{AND} gates are provided for each problem.
 
@@
 
+\textbf{Sorting :}
 Sorting is tested on a sorting network where comparator gates are used. Each comparator is designed using the following algorithm.
@@
 
-Each comparator gate uses $n$ \texttt{AND} gates, $n$ \texttt{OR} gates and $n$ \texttt{NOT} gates to find the larger of the two bit sequences and then to regenerate the maximum and the minuimum $4n$ \texttt{AND} gates $2n$ \texttt{NOT} and \texttt{OR} gates i.e.
+A comparator gate uses $n$ \texttt{AND} gates, $n$ \texttt{OR} gates and $n$ \texttt{NOT} gates to find the larger of the two bit sequences and then to regenerate the maximum and the minuimum $4n$ \texttt{AND} gates and $2n$ \texttt{NOT} and \texttt{OR} gates i.e.
 $6n$ \texttt{AND} and \texttt{XOR} gates are required.
+We note that reconstruction of Max and  Min is not required when working on non-encrypted data.
+Hence, this increases the size of the transformed program operating on encrypted data.
 
-\textbf{Insertion sort :} $n(n-1)/2$ comparator gates are used for insertion sort.
+\textbf{Insertion sort :} When allowing for parallel comparators, bubble sort and insertion sort are identical. Hence $n(n-1)/2$ comparator gates are used for insertion sort.
 
-\textbf{Odd-Even Merge sort :} The following program is used to perform Odd-Even merge sort.
+\textbf{Odd-Even Merge sort :} \autoref{oesort} and \autoref{oemerge} are used to perform Odd-Even merge sort and hence  $n/2(log(n)-1) + 1 $ comparator gates are required.
+
+\textbf{Bitonic Sort :} \autoref{bitsort} and \autoref{bitmerge} are used to perform Bitonic Sort and hence $log(n) · (log(n)+1) / 2 $ gates are required.
 
@@
 
-\begin{figure}
-\begin{lstlisting}[caption=Odd-Even Merge Sort]
+\section{Analysis of the results}
+
+Anlayze the results previously obtained and its impact on security and complexity. Comparisions of security-cost tradeoff with other schemes like RSA.
+\section{Conclusion}
+
+\bibliographystyle{alpha}
+\bibliography{article}
+
+%\begin{comment}
+\section{Appendix}
+
+ The programs used for Odd-Even Merge sort and Bitonic sort are provided below :
+
+\begin{figure}[h]
+\begin{lstlisting}[label = oesort ]
 
  OddEvenMergeSort(int lo, int n)
-if (n>1)
+if (n > 1)
         {
-            int m=n/2;
+            int m = n/2;
             oddEvenMergeSort(lo, m);
-            oddEvenMergeSort(lo+m, m);
+            oddEvenMergeSort(lo + m, m);
             oddEvenMerge(lo, n, 1);
         }
+
+\end{lstlisting}
+\caption{Odd-Even Merge Sort : sort from index lo to n }
+\end{figure}
+
+\begin{figure}
+\begin{lstlisting}[label = oemerge ]
+
 oddEvenMerge(int lo, int n, int r)
     {
-        int m=r*2;
-        if (m<n)
+        int m = r*2;
+        if (m < n)
         {
@@
 	    oddEvenMerge(lo+r, n, m); 
-            for (int i=lo+r; i+r<lo+n; i+=m)
-                compare(i, i+r);
+	    int i = lo+r;   
+            for (;i + r < lo + n;){
+		compare(i, i + r);
+		i += m;
+	    }
         }
         else
-            compare(lo, lo+r);
+            compare(lo, lo + r);
     }
@@
 \end{lstlisting} 
-
+\caption{Odd-Even Merge Sort : merging function}
 \end{figure}
 
-\textbf{Bitonic Sort}
 \begin{figure}
-\begin{lstlisting}[caption=Bitonic Sort]
+\begin{lstlisting}[label=bitsort]
 
 sortup( int m, int n) {//from m to m+n
-    if (n==1) return;
-    sortup(m,n/2);
-    sortdown(m+n/2,n/2);
-    mergeup(m,n/2);
+    if (n == 1) return;
+    sortup(m, n/2);
+    sortdown(m + n/2, n/2);
+    mergeup(m, n/2);
 }
  sortdown(int m, int n) {//from m to m+n
-    if (n==1) return;
-    sortup(m,n/2);
-    sortdown(m+n/2,n/2);
-    mergedown(m,n/2);
+    if (n == 1) return;
+    sortup(m, n/2);
+    sortdown(m + n/2, n/2);
+    mergedown(m, n/2);
+}
+\end{lstlisting}
+\caption{Bitonic Sort : sort form m to n}
+\end{figure}
+
+\begin{figure}[t]
+\begin{lstlisting}[label=bitmerge]
+mergeup(int m, int n) {  
+    if (n == 0) return;
+
+    for (i = 0 : n)
+        // Increasing Comparator
+	 compare(m + i,m + i + n);
+    mergeup(m, n/2);
+    mergeup(m + n,n/2);
 }
 
-mergeup(int m, int n) {
-    if (n==0) return;
-
-    for (i=0 : n) {
-         compare(m+i,m+i+n);
-    }
-    mergeup(m,n/2);
-    mergeup(m+n,n/2);
-}
 mergedown( int m,  int n) { 
-    if (n==0) return;
-    for (i=0 : n) {
-        compare(m+i,m+i+n);
-    }
-    mergedown(m,n/2);
-    mergedown(m+n,n/2);
+    if (n == 0) return;
+    for (i = 0 : n) 
+        // Decreasing Comparator
+	compare(m + i, m + i + n); 
+    mergedown(m, n/2);
+    mergedown(m + n, n/2);
 }
 \end{lstlisting}
-\caption{Bitonic Search}
+\caption{Bitonic Merge} 
 \end{figure} 
-Measurements on varying the parameters or the plaintext space. Evaluation of program dependent properties.
+%\begin{comment}
 
-\section{Analysis of the results}
-
-Anlayze the results previously obtained and its impact on security and complexity. Comparisions of security-cost tradeoff with other schemes like RSA.
-\section{Conclusion}
-Conclusion\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\
-\bibliographystyle{abbrv}
-\bibliography{}  % sigproc.bib is the name of the Bibliography in this case
+% sigproc.bib is the name of the Bibliography in this case
 % You must have a proper ".bib" file

### 2013-06-10 Report/article.tex
mesure

--- 2013-06-09 Report/article.tex
@@
+% THIS IS SIGPROC-SP.TEX - VERSION 3.1
+% WORKS WITH V3.2SP OF ACM_PROC_ARTICLE-SP.CLS
+% APRIL 2009
+%
+% It is an example file showing how to use the 'acm_proc_article-sp.cls' V3.2SP
+% LaTeX2e document class file for Conference Proceedings submissions.
+% ----------------------------------------------------------------------------------------------------------------
+% This .tex file (and associated .cls V3.2SP) *DOES NOT* produce:
+%       1) The Permission Statement
+%       2) The Conference (location) Info information
+%       3) The Copyright Line with ACM data
+%       4) Page numbering
+% ---------------------------------------------------------------------------------------------------------------
+% It is an example which *does* use the .bib file (from which the .bbl file
+% is produced).
+% REMEMBER HOWEVER: After having produced the .bbl file,
+% and prior to final submission,
+% you need to 'insert'  your .bbl file into your source .tex file so as to provide
+% ONE 'self-contained' source file.
+%
+% Questions regarding SIGS should be sent to
+% Adrienne Griscti ---> griscti@acm.org
+%
+% Questions/suggestions regarding the guidelines, .tex and .cls files, etc. to
+% Gerald Murray ---> murray@hq.acm.org
+%
+% For tracking purposes - this is V3.1SP - APRIL 2009
 \documentclass{acm_proc_article-sp}
+
 \makeatletter
@@
 \let\endalgorithm\relax
+\usepackage{algorithm2e}
 
-\usepackage{listings}
-\usepackage{algorithm2e}
 \begin{document}
@@
 \author{
+% You can go ahead and credit any number of authors here,
+% e.g. one 'row of three' or two rows (consisting of one row of three
+% and a second row of one, two or three).
+%
+% The command \alignauthor (no curly braces needed) should
+% precede each author name, affiliation/snail-mail address and
+% e-mail address. Additionally, tag each line of
+% affiliation/address with \affaddr, and tag the
+% e-mail address with \email.
+%
+% 1st. author
 \alignauthor
@@
 % number that will appear in the \additionalauthors section.
+
 \maketitle
+
 \begin{abstract}
@@
 \section{Fully homomorphic scheme(1 page)}
+
 A general structure of the scheme.
+
 \subsection{Two Variants of Fully Homomorphic Encryption Scheme}
@@
 
-\section{ Didactic example :  Maximum of two integer (1 page)}
-
+\section{ Didactic example :  Min-Max of two integers (1 page)}
+Min-Max of two bounded integers of n-btis.
 \subsection{Input Program for Fully Homomorphic Encryption Scheme}
-
-Details of the circuit or the program used to calculate the maximum of two bounded integers.
+\texttt{aIsGreater}($a=(a_{n-1},...,a_0}), b=(b_{n-1},...,b_0}$)):
+\begin{itemize}
+\item G= encrypt($0, PK$); Count= encrypt($1, PK$) \\
+for $i \in $nbits-1 .. $0$
+\begin{itemize}
+\item tmp1= or($a_i.b_i , \neg(a_i).\neg(b_i)$)
+\item tmp2= $a_i.\neg(b_i).$Count
+\item Count= Count . tmp1
+\item G= or(G, tmp2)
+\end{itemize}
+\end{itemize}
+\texttt{min\_max}: 
+\begin{itemize}
+\item G= aIsGreater(a, b) 
+\item max_i = or($a_i.G, b_i. \neg{G}$)
+\item min_i = or($a_i.\neg{G}, b_i.G$)
+\end{itemize}
 
@@
 Analyse the cost of the program wrt SV, BGV.
+
+The cost of this algorithm \texttt{aIsGreater} is:\\
+ $2*encrypt+n*(3*encrypt+7*add+7*mul)$ .\\
+The cost of this algorithm \texttt{min\_max} is:\\
+$ encrypt+aIsGreater+2*n*(encrypt+3add+3mull)$\\
+Thus this algorithm has $O(n^2)$ complexity.
 
@@
 Measurements taken are CPU time, Wall Time, Memory Usage by varying the input size  and the algorithmic parameters. Noise reduction threshold.
+\begin{itemize}
+\item KeyGen\\
+The measured time execution for KeyGen($N, \mu$)  for fixed values of parameters: $N=8$ and $\mu = 4$ shows a variation from 0.31 s to 13.41 s with mean = 2.726 s.\\
+\item {Encryption and Decryption}\\
 
-\paragraph{KeyGen}
-
-\paragraph{Encryption and Decryption}
-
+\item {Cost time of Min-Max program}\\
+\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
+  \hline
+  nbits  & 3 & 4 & 5 & 6 & 7 & 8 &  9  & 10 \\
+  \hline
+  time(s) & 4.17 & 5.84 & 7.18 & 4.29 & 4.65 & 5.9 & 6.71 & 6.73\\
+  \hline
+\end{tabular}
+\end{itemize}
 \section{Choice of Benchmarks}
 
-The benchmark functions and problems on which the implementations were evaluated are categorized into three classes : functions operating on bits, functions operating directly on integers or block of bits and functions where branching is required i.e \texttt{if-then-else} condition is evaluated.
-
-Functions operating on bits provide information on the tradeoff for calculations with bits, while when operating directly on integers, the tradeoff is obtained on size of integers.
-we note that the first two categories of functions can be evaluated using straight-line-programs.
-For others we choose evaluation of \texttt{if-then-else} condition on encrypted data  wich woukd make the evlaluation circuit longer than compared to the same evaluation on unencrypted data.
-The functions evaluated are :
-
+3 different classes of problems : 
 \begin{itemize}
-
-\item XOR of bits
-\item Sum of :
-
-	\begin{itemize}
-
-		\item  bounded integers
-
-		\item unbounded integers
-
- 	\end{itemize}
-\item Majority bit
-
-\item sorting with the following methods :
-
-	\begin{itemize}
-
-		\item Insertion sort
-
-		\item Odd-Even Merge sort
-
-		\item Bitonic sort
-
+\item Operations on bits,
+ \item operation on integers (possibility of extension on blocks and comparision with RSA and 
+ \item branching
 \end{itemize}
 
-\end{itemize}
+For each problem we propse the program, analyse their cost and eventually on security.
 
-We include the program used to evalute the above functons and their cost in terms of \texttt{XOR} and \texttt{AND} gates.
+Why certain other programs cannot be executed under homomorphic encryption.
 
-\textbf{XOR of $n$-bits :} \texttt{XOR} of $n$-bits requires $n-1$ \texttt{XOR} gates.
+\section{Evaluation on the Benchmarks (1 page)}
 
-\textbf{Sum of integers of $n$-bits :} Sum of two integers is performed using an $n$ \texttt{full-adder} circuits.
-The cost of a full adder circuit is $2$ \texttt{XOR} to calculate the sum and $2$ \texttt{AND}, $1$ \texttt{XOR} and $1$ \texttt{OR} for the carry.
-Hence the total complexity is $3n$ \texttt{AND}, $5n$ \texttt{XOR}.
-
-\textbf{Sum of arbitrary integers}
-
-\textbf{Majority of $n$-bits :} Majority bit is evaluated by obtaining the sum of the bits.
-
-Sorting is tested on a sorting network where comparator gates are used. Each comparator is designed using the following algorithm.
-
-\restylealgo{algoruled}
-
-\linesnumbered
-
-\begin{algorithm}[H]
-
- \SetVline
-
- \KwData{a:=$(a_0,a_1,\ldots, a_{n-1}$), b:=$(b_0,b_1,\ldots, b_{n-1})$ }
-
- \KwResult{Return Max(a,b) and Min(a,b)}
-
- $aIsGreater \leftarrow 0$\;
- $bitsEqual \leftarrow 1$\;
-
- \For{$i\leftarrow n-1 $ \KwTo $0$}{
-
-     $aIsGreater \leftarrow (aIsGreater +\neg(b_i)a_i)* bitEqual$ \;
-     $bitEqual \leftarrow bitEqual*(a_ib_i + \neg(a_i)*\neg(b_i))$		       	
- }
-
-\For{$i\leftarrow 0$ \KwTo $n-1$}{
-
-     $Max_i \leftarrow aIsGreater*a_i + \neg(aIsGreater)*b_i$ \;
-
-     $Min_i \leftarrow a \neg(aIsGreater)*a_i + aIsGreater*b_i$ \;
-
- }
-
-return($Max$, $Min$)
-
- \caption{Comparator\label{Code:algo}}
-
-\end{algorithm}
-
-Each comparator gate uses $n$ \texttt{AND} gates, $n$ \texttt{OR} gates and $n$ \texttt{NOT} gates to find the larger of the two bit sequences and then to regenerate the maximum and the minuimum $4n$ \texttt{AND} gates $2n$ \texttt{NOT} and \texttt{OR} gates i.e.
-$6n$ \texttt{AND} and \texttt{XOR} gates are required.
-
-\textbf{Insertion sort :} $n(n-1)/2$ comparator gates are used for insertion sort.
-
-\textbf{Odd-Even Merge sort :} The following program is used to perform Odd-Even merge sort.
-
-\lstset{                                    % line wrapping on
-  language=C,
-  frame=lines,
-  captionpos=b
- }
-
-\renewcommand{\lstlistingname}{Code}
-
-\begin{figure}
-\begin{lstlisting}[caption=Odd-Even Merge Sort]
-
- OddEvenMergeSort(int lo, int n)
-if (n>1)
-        {
-            int m=n/2;
-            oddEvenMergeSort(lo, m);
-            oddEvenMergeSort(lo+m, m);
-            oddEvenMerge(lo, n, 1);
-        }
-oddEvenMerge(int lo, int n, int r)
-    {
-        int m=r*2;
-        if (m<n)
-        {
-	    //even subsequence ;		
-            oddEvenMerge(lo, n, m); 
-            //odd subsequence ;
-	    oddEvenMerge(lo+r, n, m);    
-            for (int i=lo+r; i+r<lo+n; i+=m)
-                compare(i, i+r);
-        }
-        else
-            compare(lo, lo+r);
-    }
-
-\end{lstlisting}
-
-\end{figure}
-
-\textbf{Bitonic Sort}
-\begin{figure}
-\begin{lstlisting}[caption=Bitonic Sort]
-
-sortup( int m, int n) {//from m to m+n
-    if (n==1) return;
-    sortup(m,n/2);
-    sortdown(m+n/2,n/2);
-    mergeup(m,n/2);
-}
- sortdown(int m, int n) {//from m to m+n
-    if (n==1) return;
-    sortup(m,n/2);
-    sortdown(m+n/2,n/2);
-    mergedown(m,n/2);
-}
-
-mergeup(int m, int n) {
-    if (n==0) return;
-
-    for (i=0 : n) {
-         compare(m+i,m+i+n);
-    }
-    mergeup(m,n/2);
-    mergeup(m+n,n/2);
-}
-mergedown( int m,  int n) {
-    if (n==0) return;
-    for (i=0 : n) {
-        compare(m+i,m+i+n);
-    }
-    mergedown(m,n/2);
-    mergedown(m+n,n/2);
-}
-\end{lstlisting}
-\caption{Bitonic Search}
-\end{figure}
 Measurements on varying the parameters or the plaintext space. Evaluation of program dependent properties.

### 2013-06-10 libScarab-1.0.0/test.c

@@ -41,23 +41,22 @@ void test_suite()
 	//test_sum_bits();
 	//test_bit_majoritaire();
 	//test_sum_integers();
-	//test_min_max();
+	test_min_max();
 	//test_insertion_sort();
 	//test_oddeven_merger_sort();
-	test_bitonic_sort();
+	//test_bitonic_sort();
 	//test_majority_bit();
 	//debug_test_bit_majoritaire();
+	//test_keygen();
 }
-
-void debug_or(mpz_t res, mpz_t a, mpz_t b){
-	mpz_t aux1, aux2;
-	mpz_init(aux1);
-	mpz_init(aux2);
-	mpz_add(aux1, a, b);
-	mpz_mul(aux2, a, b);
-	mpz_add(res, aux1, aux2);
-	mpz_clear(aux1);
-	mpz_clear(aux2);
+void test_keygen(){
+	fhe_pk_t pk;
+	fhe_sk_t sk;
+	fhe_pk_init(pk);
+	fhe_sk_init(sk);
+	fhe_keygen(pk, sk);
+	fhe_pk_clear(pk);
+	fhe_sk_clear(sk);
 }
 
 void or(mpz_t res, mpz_t a, mpz_t b, fhe_pk_t pk){
@@ -71,13 +70,6 @@ void or(mpz_t res, mpz_t a, mpz_t b, fhe_pk_t pk){
 	mpz_clear(aux2);
 }
 
-void debug_not(mpz_t res, mpz_t a){
-	mpz_t c1;
-	mpz_init(c1);
-	mpz_set_ui(c1, 1);
-	mpz_sub(res, c1, a);
-	mpz_clear(c1);
-}
 void not(mpz_t res, mpz_t a, fhe_pk_t pk){
 	mpz_t aux, c1;
 	mpz_init(aux);
@@ -87,8 +79,6 @@ void not(mpz_t res, mpz_t a, fhe_pk_t pk){
 	mpz_clear(aux);
 	mpz_clear(c1);
 }
-
-
 
 void test_aIsGreater(mpz_t res, fmpz_poly_t polya, fmpz_poly_t polyb, fhe_pk_t pk, int nbits){
 
@@ -179,7 +169,6 @@ void min_max(mpz_t *min, mpz_t *max, fmpz_poly_t poly_c1, fmpz_poly_t poly_c2, f
 		fmpz_poly_get_coeff_mpz(a_k, poly_c1,k);	
 		fmpz_poly_get_coeff_mpz(b_k, poly_c2,k);
 			
-
[…]

### 2013-06-10 Report/article.tex

--- 2013-06-10 Report/article.tex
@@
 Measurements taken are CPU time, Wall Time, Memory Usage by varying the input size  and the algorithmic parameters. Noise reduction threshold.
+\begin{itemize}
+\item KeyGen\\
+The measured time execution for KeyGen($N, \mu$)  for fixed values of parameters: $N=8$ and $\mu = 4$ shows a variation from 0.31 s to 13.41 s with mean = 2.726 s.\\
+\item {Encryption and Decryption}\\
 
-\paragraph{KeyGen}
-
-\paragraph{Encryption and Decryption}
-
+\item {Cost time of Min-Max program}\\
+\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
+  \hline
+  nbits  & 3 & 4 & 5 & 6 & 7 & 8 &  9  & 10 \\
+  \hline
+  time(s) & 4.17 & 5.84 & 7.18 & 4.29 & 4.65 & 5.9 & 6.71 & 6.73\\
+  \hline
+\end{tabular}
+\end{itemize}
 \section{Choice of Benchmarks}

### 2013-06-10 libScarab-1.0.0/test.c
version avec Majorité(y a encore du travail)

@@ -41,11 +41,11 @@ void test_suite()
 	//test_sum_bits();
 	//test_bit_majoritaire();
 	//test_sum_integers();
-	test_min_max();
+	//test_min_max();
 	//test_insertion_sort();
 	//test_oddeven_merger_sort();
 	//test_bitonic_sort();
-	//test_majority_bit();
+	test_majority_bit();
 	//debug_test_bit_majoritaire();
 	//test_keygen();
 }
@@ -200,7 +200,7 @@ void test_min_max(){
 	printf("a = %d et b = %d\n", a, b);
 	aux1 = a ; aux2=b;
 	int i = 0;
-	int nbits = 7;   // Number of bits in the binary representation of the integers
+	int nbits = 7 ;   // Number of bits in the binary representation of the integers
 	mpz_t c0, c1;
 	
 	fhe_pk_t pk;
@@ -489,46 +489,6 @@ void test_oddeven_merger_sort(){
 
 
 }
-
-/*
-void bitonicMerge(fmpz_poly_t * poly_nums, int nbits , int lo, int n, int dir, fhe_sk_t sk, fhe_pk_t pk ){
-
-
-	mpz_t * max;
-	mpz_t * min;
-	max = malloc(sizeof(mpz_t) * nbits);
-	min = malloc(sizeof(mpz_t) * nbits);
-	for(int i=0;i<nbits;i++){
-		mpz_init(max[i]);
-		mpz_init(min[i]);
-	}
-
-
-
-	if(n>1){
-		int m = n/2;
-		for(int i = lo; i<lo+m;i++){
-							
-			min_max(min, max, poly_nums[i], poly_nums[i+m], pk, nbits);		
-			for(int k=0;k<nbits;k++){
-				fmpz_poly_set_coeff_mpz(poly_nums[i], k, min[k]);
-				fmpz_poly_set_coeff_mpz(poly_nums[i+m],k, max[k]);
-			}
-
-			
-		
-		}
-		
-		bitonicMerge(poly_nums, nbits, lo, m, dir, sk, pk);
-		bitonicMerge(poly_nums, nbits, lo+m, m, dir, sk, pk);
-		
-	
-	}
-
-}
-
-*/
-
 
 
 
[…]

### 2013-06-10 Report/article.tex
l
Article changed
min max

--- 2013-06-10 Report/article.tex
@@
 
-\section{ Didactic example :  Maximum of two integer (1 page)}
-
+\section{ Didactic example :  Min-Max (1 page)}
+Min-Max of sequence of n-btis with arithmetic operations and without branching.
 \subsection{Input Program for Fully Homomorphic Encryption Scheme}
 
-Details of the circuit or the program used to calculate the maximum of two bounded integers.
+\restylealgo{algoruled}
+
+\linesnumbered
+
+\begin{algorithm}[H]
+
+\SetVline
+
+ \KwData{a:=$(a_0,a_1,\ldots, a_{n-1}$), b:=$(b_0,b_1,\ldots, b_{n-1})$ }
+
+ \KwResult{Return Max(a,b) and Min(a,b)}
+
+ $aIsGreater \leftarrow 0$\;
+ $bitsEqual \leftarrow 1$\;
+
+ \For{$i\leftarrow n-1 $ \KwTo $0$}{
+
+     $aIsGreater \leftarrow (aIsGreater +\neg(b_i)a_i)* bitEqual$ \;
+     $bitEqual \leftarrow bitEqual*(a_ib_i + \neg(a_i)*\neg(b_i))$		       	
+ }
+
+\For{$i\leftarrow 0$ \KwTo $n-1$}{
+
+     $Max_i \leftarrow aIsGreater*a_i + \neg(aIsGreater)*b_i$ \;
+
+     $Min_i \leftarrow a \neg(aIsGreater)*a_i + aIsGreater*b_i$ \;
+
+ }
+
+return($Max$, $Min$)
+
+ \caption{Min-Max\label{Code:algo}}
+
+\end{algorithm}
 
@@
 
-Analyse the cost of the program wrt SV, BGV.
+The cost \texttt{aIsGreater} is:\\
+ $2*encrypt+n*(3*encrypt+7*add+7*mul)$ .\\
+The cost of this algorithm \texttt{min\_max} is:\\
+$ encrypt+aIsGreater+2*n*(encrypt+3add+3mull)$\\
+Thus this algorithm has $\theta(n)$ complexity.
 
@@
 
-Once for all analysis of common operations(KeyGen, Encrypt, Decrypt of 1 bit) varying the algorithmic and security parameters.
+Measurements taken are CPU time, Wall Time, Memory Usage by varying the input size  and the algorithmic parameters. Noise reduction threshold.\\
+Here we estimate the performance of this program in terms of run time for KeyGen, Encrypt, Decrypt and the Min-Max algorithm.
+\begin{itemize}
 
-Measurements taken are CPU time, Wall Time, Memory Usage by varying the input size  and the algorithmic parameters. Noise reduction threshold.
+\item KeyGen\\
+The measured time execution for KeyGen($N, \mu$)  for fixed values of parameters: $N=8$ and $\mu = 4$ shows a variation from 0.31 s to 13.41 s with mean = 2.726 s.\\
+\item {Encryption and Decryption}\\
 
-\paragraph{KeyGen}
-
-\paragraph{Encryption and Decryption}
-
+\item {Cost time of Min-Max program}\\
+\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
+  \hline
+  nbits  & 3 & 4 & 5 & 6 & 7 & 8 &  9  & 10 \\
+  \hline
+  time(s) & 4.17 & 5.84 & 7.18 & 4.29 & 4.65 & 5.9 & 6.71 & 6.73\\
+  \hline
+\end{tabular}
+\end{itemize}
 \section{Choice of Benchmarks}
@@
 
+\section{Evaluation on the benchmarks}
+Measurements by varying the parameters or the plaintext size.
 \section{Analysis of the results}

### 2013-06-10 libScarab-1.0.0/test.c

@@ -25,9 +25,9 @@
 #define ASSERT_HOMADD(__a, __b, __check)			\
 	fhe_add(temp, __a, __b, pk);					\
 	assert(fhe_decrypt(temp, sk) == __check);
-void debug_test_bit_majoritaire();
 
 
+void test_keygen();
 
 void test_suite()
 {
@@ -46,9 +46,9 @@ void test_suite()
 	//test_oddeven_merger_sort();
 	//test_bitonic_sort();
 	//test_majority_bit();
-	//debug_test_bit_majoritaire();
 	//test_keygen();
 }
+
 void test_keygen(){
 	fhe_pk_t pk;
 	fhe_sk_t sk;
@@ -58,6 +58,7 @@ void test_keygen(){
 	fhe_pk_clear(pk);
 	fhe_sk_clear(sk);
 }
+
 
 void or(mpz_t res, mpz_t a, mpz_t b, fhe_pk_t pk){
 	mpz_t aux1, aux2;
@@ -136,7 +137,6 @@ void test_aIsGreater(mpz_t res, fmpz_poly_t polya, fmpz_poly_t polyb, fhe_pk_t p
 
 void min_max(mpz_t *min, mpz_t *max, fmpz_poly_t poly_c1, fmpz_poly_t poly_c2, fhe_pk_t pk, int nbits){
 	
-	
 	mpz_t a_k;
 	mpz_t b_k;
 	mpz_t tmp;
@@ -196,11 +196,11 @@ void min_max(mpz_t *min, mpz_t *max, fmpz_poly_t poly_c1, fmpz_poly_t poly_c2, f
 void test_min_max(){
 	
 	unsigned a ,b, aux1, aux2;
-	a=3; b=2;   // Integers to be compared suppposed to be of the same size
+	a=1450; b=1030;  
 	printf("a = %d et b = %d\n", a, b);
 	aux1 = a ; aux2=b;
 	int i = 0;
-	int nbits = 7;   // Number of bits in the binary representation of the integers
+	int nbits;   // Number of bits in the binary representation of the integers
 	mpz_t c0, c1;
 	
 	fhe_pk_t pk;
@@ -239,19 +239,23 @@ void test_min_max(){
[…]

### 2013-06-10 libScarab-1.0.0/test.c
Avec Mesures de temps

@@ -7,6 +7,11 @@
  */
 
 #include "test.h"
+#include <sys/time.h>
+#include <time.h>
+#include <unistd.h>
+#include <stdio.h>
+#include <stdint.h>
 
 #define ASSERT_HALFADD(__a,__b,__sum,__carry)		\
 	fhe_halfadd(sum, carry, __a, __b, pk);			\
@@ -29,6 +34,7 @@ void debug_test_bit_majoritaire();
 
 
 
+
 void test_suite()
 {
 	//test_fully_homomorphic();
@@ -41,11 +47,11 @@ void test_suite()
 	//test_sum_bits();
 	//test_bit_majoritaire();
 	//test_sum_integers();
-	//test_min_max();
+	test_min_max();
 	//test_insertion_sort();
 	//test_oddeven_merger_sort();
 	//test_bitonic_sort();
-	test_majority_bit();
+	//test_majority_bit();
 	//debug_test_bit_majoritaire();
 	//test_keygen();
 }
@@ -195,20 +201,25 @@ void min_max(mpz_t *min, mpz_t *max, fmpz_poly_t poly_c1, fmpz_poly_t poly_c2, f
 
 void test_min_max(){
 	
+	clock_t START_init = clock();
+
+	struct timeval start, end;
+	
+    	long mtime, seconds, useconds;    
+
+   	 gettimeofday(&start, NULL);
+    	
+   
+ 	
+	////////////////  Initialization ////////////////
+
 	unsigned a ,b, aux1, aux2;
-	a=3; b=2;   // Integers to be compared suppposed to be of the same size
+	a=4; b=2;   // Integers to be compared suppposed to be of the same size
 	printf("a = %d et b = %d\n", a, b);
 	aux1 = a ; aux2=b;
 	int i = 0;
 	int nbits = 7 ;   // Number of bits in the binary representation of the integers
 	mpz_t c0, c1;
-	
-	fhe_pk_t pk;
-	fhe_sk_t sk;
-	fhe_pk_init(pk);
-	fhe_sk_init(sk);
-	fhe_keygen(pk, sk);
-	
 	fmpz_poly_t poly_c1;
 	fmpz_poly_t poly_c2;	
 	
[…]

### 2013-06-11 libScarab-1.0.0/test.c
Matrix product implem

@@ -47,16 +47,13 @@ void test_suite()
 	//test_sum_bits();
 	//test_bit_majoritaire();
 	//test_sum_integers();
-	test_min_max();
+	//test_min_max();
 	//test_insertion_sort();
 	//test_oddeven_merger_sort();
 	//test_bitonic_sort();
 	//test_majority_bit();
-<<<<<<< HEAD
+	test_matrix_prod();
 	//debug_test_bit_majoritaire();
-=======
-
->>>>>>> 68d73d62936a4314a91ff9fea660a71445447f41
 	//test_keygen();
 }
 
@@ -219,11 +216,11 @@ void test_min_max(){
 	////////////////  Initialization ////////////////
 
 	unsigned a ,b, aux1, aux2;
-<<<<<<< HEAD
+
 	a=4; b=2;   // Integers to be compared suppposed to be of the same size
-=======
+
 	a=1450; b=1030;  
->>>>>>> 68d73d62936a4314a91ff9fea660a71445447f41
+
 	printf("a = %d et b = %d\n", a, b);
 	aux1 = a ; aux2=b;
 	int i = 0;
@@ -305,7 +302,7 @@ void test_min_max(){
 		aux2 = aux2 >> 1;
 
 	}while(aux1 != 0 || aux2 !=0);
-<<<<<<< HEAD
+
 	
 	double T_Elapsed3 = (double) (clock () - START_enc);
 	printf(" Encryption took %f clocks/sec \n ", T_Elapsed3);	
@@ -331,24 +328,23 @@ void test_min_max(){
 		mpz_init(max[i]);
 		mpz_init(min[i]);
 	}
-=======
 
 
 	/////////// Evaluation ////////////////////
-	nbits= i +1;
-	fmpz_poly_t max;
-	fmpz_poly_t min;
+	//nbits= i +1;
+	//fmpz_poly_t max;
+	//fmpz_poly_t min;
 	//mpz_t * max;
 	//mpz_t * min;
-	fmpz_poly_init(max);
-	fmpz_poly_init(min);
+	//fmpz_poly_init(max);
+	//fmpz_poly_init(min);
 	//max = malloc(sizeof(mpz_t) * nbits);
 	//min = malloc(sizeof(mpz_t) * nbits);
 	//for(i=0;i<nbits;i++){
 	//	mpz_init(max[i]);
 	//	mpz_init(min[i]);
[…]

### 2013-06-11 libScarab-1.0.0/test.c
r

@@ -52,11 +52,7 @@ void test_suite()
 	//test_oddeven_merger_sort();
 	//test_bitonic_sort();
 	//test_majority_bit();
-<<<<<<< HEAD
-	//debug_test_bit_majoritaire();
-=======
 
->>>>>>> 68d73d62936a4314a91ff9fea660a71445447f41
 	//test_keygen();
 }
 
@@ -69,7 +65,6 @@ void test_keygen(){
 	fhe_pk_clear(pk);
 	fhe_sk_clear(sk);
 }
-
 
 void or(mpz_t res, mpz_t a, mpz_t b, fhe_pk_t pk){
 	mpz_t aux1, aux2;
@@ -145,7 +140,6 @@ void test_aIsGreater(mpz_t res, fmpz_poly_t polya, fmpz_poly_t polyb, fhe_pk_t p
 	mpz_clear(aIsGreater);
 }
 
-
 void min_max(mpz_t *min, mpz_t *max, fmpz_poly_t poly_c1, fmpz_poly_t poly_c2, fhe_pk_t pk, int nbits){
 	
 	mpz_t a_k;
@@ -163,7 +157,7 @@ void min_max(mpz_t *min, mpz_t *max, fmpz_poly_t poly_c1, fmpz_poly_t poly_c2, f
 
 	test_aIsGreater(aIsGreater,poly_c1,poly_c2,pk, nbits);
 
-	//printf("Is a greater than b ? Ans : %i  \n", fhe_decrypt(aIsGreater,sk));
+	//printf("Is a greater than b ? Ans : %i\n",fhe_decrypt(aIsGreater,sk));
 	
 	for(k=0;k<nbits;k++){
 		
@@ -185,8 +179,7 @@ void min_max(mpz_t *min, mpz_t *max, fmpz_poly_t poly_c1, fmpz_poly_t poly_c2, f
 		fhe_mul(a_k, a_k, tmp,pk);
 		or(tmp, a_k,b_k, pk);
 
-		mpz_set(min[k],tmp);		
-			
+		mpz_set(min[k],tmp);					
 	}
 
 	
@@ -212,23 +205,17 @@ void test_min_max(){
 	
     	long mtime, seconds, useconds;    
 
-   	 gettimeofday(&start, NULL);
-    	
-   
- 	
+	gettimeofday(&start, NULL);
+    		
 	////////////////  Initialization ////////////////
 
 	unsigned a ,b, aux1, aux2;
-<<<<<<< HEAD
[…]

### 2013-06-11 libScarab-1.0.0/test.c
bien

@@ -34,6 +34,7 @@
 
 void test_keygen();
 
+void bitonicSortUp(fmpz_poly_t *poly_nums, int  nbits, int n,  int lo , int  high, fhe_sk_t sk, fhe_pk_t pk);
 
 void test_suite()
 {
@@ -47,13 +48,12 @@ void test_suite()
 	//test_sum_bits();
 	//test_bit_majoritaire();
 	//test_sum_integers();
-	//test_min_max();
+	test_min_max();
 	//test_insertion_sort();
 	//test_oddeven_merger_sort();
 	//test_bitonic_sort();
 	//test_majority_bit();
-	test_matrix_prod();
-	//debug_test_bit_majoritaire();
+	//test_matrix_prod();
 	//test_keygen();
 }
 
@@ -203,13 +203,13 @@ void min_max(mpz_t *min, mpz_t *max, fmpz_poly_t poly_c1, fmpz_poly_t poly_c2, f
 
 void test_min_max(){
 	
-	clock_t START_init = clock();
+	//clock_t START_init = clock();
 
 	struct timeval start, end;
 	
     	long mtime, seconds, useconds;    
 
-   	 gettimeofday(&start, NULL);
+	//gettimeofday(&start, NULL);
     	
    
  	
@@ -217,9 +217,8 @@ void test_min_max(){
 
 	unsigned a ,b, aux1, aux2;
 
-	a=4; b=2;   // Integers to be compared suppposed to be of the same size
 
-	a=1450; b=1030;  
+	a=30010; b=454;  
 
 	printf("a = %d et b = %d\n", a, b);
 	aux1 = a ; aux2=b;
@@ -242,7 +241,7 @@ void test_min_max(){
 	fhe_sk_t sk;
 	fhe_pk_init(pk);
 	fhe_sk_init(sk);
-	
+	/*
 	double T_Elapsed1 = (double) ( clock () - START_init ); 
 	printf(" Initialization of the variables etc took %f clocks / sec \n ", T_Elapsed1);
 
@@ -252,18 +251,18 @@ void test_min_max(){
    	mtime = ((seconds) * 1000 + useconds/1000.0) + 0.5;
 
    	 printf("Elapsed time in Init : %ld milliseconds\n", mtime);
-  	
+	*/
 	////////////////////// Initialization Ends ////////////////////
 	
 
[…]

### 2013-06-11 libScarab-1.0.0/test.c
mesure

@@ -189,7 +189,7 @@ void min_max(mpz_t *min, mpz_t *max, fmpz_poly_t poly_c1, fmpz_poly_t poly_c2, f
 	
 	//////////////// Decryption ///////////////////////////
 
-	printf("Inside min-max method \n");
+	//printf("Inside min-max method \n");
 	
 	mpz_clear(a_k);
 	mpz_clear(b_k); 
@@ -214,15 +214,11 @@ void test_min_max(){
    
  	
 	////////////////  Initialization ////////////////
+	unsigned a =300501045183, b= 50419815648;
+	unsigned aux1, aux2;
 
-	unsigned a ,b, aux1, aux2;
 
 
-	a=30010; b=454;  
-
-	printf("a = %d et b = %d\n", a, b);
-	aux1 = a ; aux2=b;
-	int i = 0;
 
 	int nbits;   // Number of bits in the binary representation of the integers
 
@@ -280,18 +276,29 @@ void test_min_max(){
 	clock_t  START_enc = clock();
 	gettimeofday(&start, NULL);
 */
+
+	int i;
+	clock_t  START_eval;
+
+	mpz_t a_k;
+	mpz_t b_k;
+	mpz_t tmp;
+	mpz_t aIsGreater;
+	double T_Elapsed4;
+	unsigned d; int k;
+	//a=7; b=6;
+
+
+	//printf("a = %d et b = %d\n", a, b);
+	aux1 = a ; aux2=b;
+	i=0;
 	fhe_encrypt(c0, pk, a % 2);
 	fhe_encrypt(c1, pk, b % 2);
-
 	fmpz_poly_set_coeff_mpz( poly_c1 , i , c0 );
 	fmpz_poly_set_coeff_mpz( poly_c2, i, c1 );
-
-	aux1 = aux1 >> 1;
-	
+	aux1 = aux1 >> 1;	
 	aux2 = aux2 >> 1;
-	
 	do {
-		//printf("--------->%i\n", aux % 2);
 		fhe_encrypt(c0, pk, aux1 % 2);
 		fhe_encrypt(c1, pk, aux2 %2);
 		i++;
@@ -299,116 +306,84 @@ void test_min_max(){
 		fmpz_poly_set_coeff_mpz (poly_c2, i, c1);
 		aux1 = aux1 >> 1;
 		aux2 = aux2 >> 1;
-
 	}while(aux1 != 0 || aux2 !=0);
-
 	nbits=i + 1;
 /*
[…]

### 2013-06-12 libScarab-1.0.0/test.c
test.c in Evlauation phase

@@ -12,6 +12,7 @@
 #include <unistd.h>
 #include <stdio.h>
 #include <stdint.h>
+#include <math.h>
 
 #define ASSERT_HALFADD(__a,__b,__sum,__carry)		\
 	fhe_halfadd(sum, carry, __a, __b, pk);			\
@@ -50,9 +51,9 @@ void test_suite()
 	//test_min_max();
 	//test_insertion_sort();
 	//test_oddeven_merger_sort();
-	//test_bitonic_sort();
+	test_bitonic_sort();
 	//test_majority_bit();
-	test_matrix_prod();
+	//test_matrix_prod();
 	//debug_test_bit_majoritaire();
 	//test_keygen();
 }
@@ -189,7 +190,7 @@ void min_max(mpz_t *min, mpz_t *max, fmpz_poly_t poly_c1, fmpz_poly_t poly_c2, f
 	
 	//////////////// Decryption ///////////////////////////
 
-	printf("Inside min-max method \n");
+	//printf("Inside min-max method \n");
 	
 	mpz_clear(a_k);
 	mpz_clear(b_k); 
@@ -197,8 +198,6 @@ void min_max(mpz_t *min, mpz_t *max, fmpz_poly_t poly_c1, fmpz_poly_t poly_c2, f
 	mpz_clear(aIsGreater);
 
 }
-
-
 
 
 void test_min_max(){
@@ -217,9 +216,7 @@ void test_min_max(){
 
 	unsigned a ,b, aux1, aux2;
 
-	a=4; b=2;   // Integers to be compared suppposed to be of the same size
-
-	a=1450; b=1030;  
+	a=2; b=5;  
 
 	printf("a = %d et b = %d\n", a, b);
 	aux1 = a ; aux2=b;
@@ -303,6 +300,9 @@ void test_min_max(){
 
 	}while(aux1 != 0 || aux2 !=0);
 
+	nbits=i+1;
+
+	printf("Maximum number of bits is %d", nbits);
 	
 	double T_Elapsed3 = (double) (clock () - START_enc);
 	printf(" Encryption took %f clocks/sec \n ", T_Elapsed3);	
@@ -689,10 +689,10 @@ void bitonicSortUp(fmpz_poly_t *poly_nums, int  nbits, int n,  int lo , int  hig
 
 
[…]

### 2013-06-12 Report/article.tex
test.c in Evlauation phase
modif

@@
 
- \KwData{a:=$(a_0,a_1,\ldots, a_{n-1}$), b:=$(b_0,b_1,\ldots, b_{n-1})$ }
+ \KwData{a':=$(a_0',a_1',\ldots, a_{n-1}'$), b':=$(b_0',b_1',\ldots, b_{n-1}')$ }
 
- \KwResult{Return Max(a,b) and Min(a,b)}
+ \KwResult{Return Max(a',b') and Min(a',b')}
 
@@
 
-     $aIsGreater \leftarrow (aIsGreater +\neg(b_i)a_i)* bitEqual$ \;
-     $bitEqual \leftarrow bitEqual*(a_ib_i + \neg(a_i)*\neg(b_i))$		       	
+     $aIsGreater \leftarrow (aIsGreater +\neg(b_i')a_i')* bitEqual$ \;
+     $bitEqual \leftarrow bitEqual*(a_i'b_i' + \neg(a_i)'*\neg(b_i'))$		       	
  }
@@
 
-     $Max_i \leftarrow aIsGreater*a_i + \neg(aIsGreater)*b_i$ \;
+     $Max_i \leftarrow aIsGreater*a_i' + \neg(aIsGreater)*b_i'$ \;
 
-     $Min_i \leftarrow a \neg(aIsGreater)*a_i + aIsGreater*b_i$ \;
+     $Min_i \leftarrow  \neg(aIsGreater)*a_i' + aIsGreater*b_i'$ \;
 
@@
 
- \caption{Min-Max\label{Code:algo}}
+ \caption{Min-Max on ciphertext \label{Code:algo}}
 
@@
 \item KeyGen\\
-The measured time execution for KeyGen($N, \mu$)  for fixed values of parameters: $N=8$ and $\mu = 4$ shows a variation from 0.31 s to 13.41 s with mean = 2.726 s.\\
+The measured time execution for KeyGen($N, \mu$)  for fixed values of parameters: $N=8$ and $\mu = 4$ show a variation from 0.2 s to 14.41 s with big density at the interval [0.2s, 1s].\\
+\begin{figure}[!h] %on ouvre l'environnement figure
+\centering
+\includegraphics[width=5cm]{f3.eps} 
+\caption{Run time of KeyGen(ms)} 
+\label{image_f2} %l'étiquette pour faire référence à cette image
+\end{figure}
 \item {Encryption and Decryption}\\
@@
 \item {Cost time of Min-Max program}\\
-\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
-  \hline
-  nbits  & 3 & 4 & 5 & 6 & 7 & 8 &  9  & 10 \\
-  \hline
-  time(s) & 4.17 & 5.84 & 7.18 & 4.29 & 4.65 & 5.9 & 6.71 & 6.73\\
-  \hline
-\end{tabular}
+We measure the run time from $n=1$ to $32$ bits,we find a linear cost which confirms the $\theta(n)$ complexity. During these measures the result of Min-Max is correct. 
+\begin{figure}[!h] %on ouvre l'environnement figure
+\centering
+\includegraphics[width=5cm]{f2.eps} 
+\caption{Run time(ms)} 
+\label{image_f2} %l'étiquette pour faire référence à cette image
+\end{figure}
+
+\item The cost of this algorithm on ciphertext is linear with bit number, like  the algorithm on plaintext, the extra cost in this case is encryption-decryption cost and especially the code generation which is very inpreductible and take often a long time in the SV-Scheme.
 \end{itemize}

### 2013-06-12 libScarab-1.0.0/test.c

@@ -34,6 +34,10 @@
 
 void test_keygen();
 
+void measure_test_keygen(){
+	for(int i=0; i< 40; i++) test_keygen();
+}
+
 void bitonicSortUp(fmpz_poly_t *poly_nums, int  nbits, int n,  int lo , int  high, fhe_sk_t sk, fhe_pk_t pk);
 
 void test_suite()
@@ -48,16 +52,22 @@ void test_suite()
 	//test_sum_bits();
 	//test_bit_majoritaire();
 	//test_sum_integers();
-	test_min_max();
+	//test_min_max();
 	//test_insertion_sort();
 	//test_oddeven_merger_sort();
 	//test_bitonic_sort();
 	//test_majority_bit();
 	//test_matrix_prod();
-	//test_keygen();
+	measure_test_keygen();
 }
 
 void test_keygen(){
+	struct timeval start, end;	
+    	long mtime, seconds, useconds;    
+	clock_t  START_eval;
+	double T_Elapsed4;
+	START_eval = clock();
+	gettimeofday(&start, NULL);    
 	fhe_pk_t pk;
 	fhe_sk_t sk;
 	fhe_pk_init(pk);
@@ -65,6 +75,13 @@ void test_keygen(){
 	fhe_keygen(pk, sk);
 	fhe_pk_clear(pk);
 	fhe_sk_clear(sk);
+	T_Elapsed4 = (double) (clock () - START_eval);
+	//printf(" Evaluation took %f clock/sec \n ", T_Elapsed4);     	
+	gettimeofday(&end, NULL);
+	seconds  = end.tv_sec  - start.tv_sec;
+	useconds = end.tv_usec - start.tv_usec;
+	mtime = ((seconds) * 1000 + useconds/1000.0) + 0.5;
+	printf("Elapsed time in KeyGen : %ld ms \n", mtime );
 }
 
 
@@ -214,7 +231,7 @@ void test_min_max(){
    
  	
 	////////////////  Initialization ////////////////
-	unsigned a =300501045183, b= 50419815648;
+	unsigned a =30050183, b= 504195648;
 	unsigned aux1, aux2;
 
 

### 2013-06-12 Report/article.tex
Avec changement d'algo

--- 2013-06-10 Report/article.tex
@@
 
-\begin{itemize}
-\item Smart-Vercauteren scheme:\\
+Smart-Vercauteren scheme:\\
 The scheme \cite{cryptoeprint:2009:571} has 3 parameters: ($N, \nu, \mu$ ).
 The somewhat homomorphic scheme uses 5 algorithms: (\texttt{KeyGen}, \texttt{Encrypt}, \texttt{Decrypt}, \texttt{Add}, \texttt{Mult}).
-\begin{itemize}
-\item \texttt{KeyGen}:
-\begin{itemize}
-\item $F(x)= x^{n}+1$
-\item do
-\begin{itemize}
-\item $S(x)=_{R}(B_{\infty , N}(\nu/2)$
-\item $G(x)=1+2.S(x)$
-\item $p= resultant(G(x),F(x))$
-\end{itemize}
-until $p$ is prime
-\item $D(x)=gcd(G(x),F(x))$ over $\mathbb{F}_p[x]$
-\item $\alpha$: the unique root of $D(x)$
-\item apply \texttt{fmpz\_poly\_xgcd} to obtain $Z(x)$ such that $Z(x).G(x)=p$ mod $F(x)$
-\item $B=z_0$ mod $2p$
-\item $PK = (p, \alpha)$ and $Sk = (p , B)$
-\end{itemize}
-\item \texttt{Encrypt}($m \in \{0,1\} , PK$):
-\begin{itemize}
-\item $R(x)=_{R}(B_{\infty , N}(\mu/2)$
-\item $C(x)=m+2.R(x)$
-\item $c=C(\alpha) mod p$
-\item return $c$
-\end{itemize}
-\item \texttt{Decrypt}($c, SK$):
-\begin{itemize}
-\item $m= (c - round(c.B/p)) mod 2$
-\item return $m$
-\end{itemize}
-\item \texttt{Add}($c_1$, $c_2$, $PK$):
-\begin{itemize}
-\item $c_3=c_1+c_2 mod p$
-\item return $c_3$
-\end{itemize}
-\item \texttt{Mult}($c_1$, $c_2$, PK):
-\begin{itemize}
-\item $c_3=c_1.c_2 mod p$
-\item return $c_3$
-\end{itemize}
-\end{itemize}
-\item BGV:
-\end{itemize}
+
+\restylealgo{algoruled}
+
+\linesnumbered
+
+\begin{algorithm}[H]
+
+ \SetVline
+
+ \KwData{$N, \nu, \mu$ }
+
+ \KwResult{$pk, sk$}
+
+  $F(x)= x^{n}+1$
+
+ \While{$p$ is not prime}{
+
+	$S(x)=_{R}(B_{\infty , N}(\nu/2)$\;
+
+	$G(x)=1+2.S(x)$\;
+
+	$p= resultant(G(x),F(x))$\;
+
+}
+
+ 	$D(x)=gcd(G(x),F(x))$ over $\mathbb{F}_p[x]$\;
+
+	$\alpha$: the unique root of $D(x)$\;
+
+ 	apply \texttt{fmpz\_poly\_xgcd} to obtain $Z(x)$ such that $Z(x).G(x)=p$ mod $F(x)$\;
+
+	$B=z_0$ mod $2p$\;
+
+	$pk = (p, \alpha)$ and $sk = (p , B)$\;
+
+return($pk$, $sk$)
+
+ \caption{Comparator\label{Code:algo}}
+
+\end{algorithm}
+\texttt{Encrypt}($m \in \{0,1\} , PK$): 
+\newline \phantom{x}\hspace{3ex}  $R(x)=_{R}(B_{\infty , N}(\mu/2)$
+ \; $C(x)=m+2.R(x)$ 
+\newline \phantom{x}\hspace{3ex} return  $c=C(\alpha) mod p$
+\newline \texttt{Decrypt}($c, SK$):
+\newline \phantom{x}\hspace{3ex} $m = (c - round(c.B/p)) mod 2$;
+\phantom{x}\hspace{1ex} return $m$
+
+\texttt{Add}($c_1$, $c_2$, $PK$):
+\newline \phantom{x}\hspace{3ex} $c_3=c_1+c_2 mod p$
+  \phantom{x}\hspace{1ex}  return $c_3$
+\newline \texttt{Mult}($c_1$, $c_2$, PK):
+ \newline \phantom{x}\hspace{3ex}  $c_3=c_1.c_2 mod p$
+ ; \phantom{x}\hspace{1ex}  return $c_3$
 \subsection{Considered Implementations}
@@
 Measurements by varying the parameters or the plaintext size.
+
+\begin{figure*}
+
+\incudegraphics{"/home/honey/Documents/Mosig\_1/ProjSpec/Measurements\Insertion\_sort\_CPU.jpg"}
+
+\end{figure*}
+
 \section{Analysis of the results}

### 2013-06-12 libScarab-1.0.0/test.c

@@ -35,7 +35,6 @@
 
 void test_keygen();
 
-void bitonicSortUp(fmpz_poly_t *poly_nums, int  nbits, int n,  int lo , int  high, fhe_sk_t sk, fhe_pk_t pk);
 
 void test_suite()
 {
@@ -55,7 +54,8 @@ void test_suite()
 	test_bitonic_sort();
 	//test_majority_bit();
 	//test_matrix_prod();
-	  //test_keygen();
+	//debug_test_bit_majoritaire();
+	//test_keygen();
 }
 
 void test_keygen(){
@@ -202,19 +202,25 @@ void min_max(mpz_t *min, mpz_t *max, fmpz_poly_t poly_c1, fmpz_poly_t poly_c2, f
 
 void test_min_max(){
 	
-	//clock_t START_init = clock();
+	clock_t START_init = clock();
 
 	struct timeval start, end;
 	
     	long mtime, seconds, useconds;    
 
-	//gettimeofday(&start, NULL);
+   	 gettimeofday(&start, NULL);
     	
    
  	
 	////////////////  Initialization ////////////////
-	unsigned a =300501045183, b= 50419815648;
-	unsigned aux1, aux2;
+
+	unsigned a ,b, aux1, aux2;
+
+	a=2; b=5;  
+
+	printf("a = %d et b = %d\n", a, b);
+	aux1 = a ; aux2=b;
+	int i = 0;
 
 	int nbits;   // Number of bits in the binary representation of the integers
 
@@ -233,7 +239,7 @@ void test_min_max(){
 	fhe_sk_t sk;
 	fhe_pk_init(pk);
 	fhe_sk_init(sk);
-	/*
+	
 	double T_Elapsed1 = (double) ( clock () - START_init ); 
 	printf(" Initialization of the variables etc took %f clocks / sec \n ", T_Elapsed1);
 
@@ -243,18 +249,18 @@ void test_min_max(){
    	mtime = ((seconds) * 1000 + useconds/1000.0) + 0.5;
 
    	 printf("Elapsed time in Init : %ld milliseconds\n", mtime);
-	*/
+  	
 	////////////////////// Initialization Ends ////////////////////
 	
 
 	//////////////////////// Key Generation /////////
-	/*
+	
[…]

### 2013-06-12 Report/article.tex

@@
 
-\begin{figure*}
+\begin{figure}[!h] %on ouvre l'environnement figure
+\centering
+\includegraphics[width=5cm]{./Insertion_sort_CPU.jpg} 
+\caption{Run time of } 
+\label{image_f2} %l'étiquette pour faire référence à cette image
+\end{figure}
+\
 
-\incudegraphics{"/home/honey/Documents/Mosig\_1/ProjSpec/Measurements\Insertion\_sort\_CPU.jpg"}
+%\begin{figure*}
 
-\end{figure*}
+%\incudegraphics{"/home/honey/Documents/Mosig\_1/ProjSpec/Measurements\Insertion\_sort\_CPU.jpg"}
+
+%\end{figure*}
 

### 2013-06-13 libScarab-1.0.0/test.c
test xor de bits

@@ -1458,7 +1458,7 @@ void test_matrix_prod(){
 
 
 void test_xor_bits(){
-	int m, aux;
+	unsigned m, aux;
 	mpz_t c0, c1;
 	fmpz_poly_t poly_c;
 	mpz_init(c0);
@@ -1469,31 +1469,47 @@ void test_xor_bits(){
 	fhe_pk_init(pk);
 	fhe_sk_init(sk);
 	fhe_keygen(pk, sk);
-	int j;	
-	for(int i=13; i < 27; i++){
-		m=i;
+	int j, nbits;	
+
+	struct timeval start, end;	
+	long mtime, seconds, useconds;    
+	//clock_t  START_eval;
+	//double T_Elapsed4;
+
+	m= 2147483648	;
+	for(int i=0; i< 250; i++){
+		m= m + 2;
 		j=0;
-		printf("--------->%i\n", m % 2);
+		//printf("--------->%i\n", m % 2);
 		fhe_encrypt(c0, pk, m % 2);
 		fmpz_poly_set_coeff_mpz ( poly_c , 0 , c0 );
 		aux = m;	
 		aux = aux >> 1;
 		do {
-			printf("--------->%i\n", aux % 2);
+			//	printf("--------->%i\n", aux % 2);
 			fhe_encrypt(c0, pk, aux % 2);
 			aux = aux >> 1;
 			j++;
 			fmpz_poly_set_coeff_mpz ( poly_c , j , c0 );
 			//fhe_add(c0, c0, c1, pk);
 		}while(aux != 0);
+		nbits= j+1;
+		//START_eval = clock();
+		gettimeofday(&start, NULL);    
 		mpz_set(c1, c0);
 		while(j>0){
 			j--;
 			fmpz_poly_get_coeff_mpz ( c0 , poly_c , j );
 			fhe_add(c1, c0, c1, pk);
 		}
+		gettimeofday(&end, NULL);
+		seconds  = end.tv_sec  - start.tv_sec;
+		useconds = end.tv_usec - start.tv_usec;
+		mtime = ((seconds) * 1000 + useconds/1000.0) + 0.5;
+		//printf("Elapsed time in KeyGen : %ld ms \n", mtime );
+
 		aux = fhe_decrypt(c1, sk);
-		printf("///////////////-----------!!!!!!  xor bits de %i est %i \n", m, aux);
[…]

### 2013-06-13 Report/article.tex
Report modified

@@
 \usepackage{algorithm2e}
+%\usepackage{amsfont}
+%\usepackage{amsmath}
+%\usepackage{amssymb}
 \hypersetup{
@@
 \begin{abstract}
-This paper presents an analysis of security-cost trade-off for homomorphic encryption schemes.
-Analysis is based on the measurements taken on the evaluation of certain functions on two  variants of fully homomorphic encryption schemes.
-These functions either operate on bits, on integers (of bounded and unbounded size)  or involve \texttt{if-then-else} branching.
+This paper investigates the feasibility of transformation of a (possibly) non-straight-line program (on unencrypted data) to a straight-line program on encrypted data.
+We present an analysis of security-cost trade-off for homomorphic encryption schemes on such programs.
+Analysis is based on the measurements (CPU time and  Wall time) taken for programs : performing \texttt{XOR} of an $n$-bit sequence, determining the majority bit of an $n$-bit sequence, evaluating the sum of $n$-bit integers, \textcolor{orange}{sum of integers with any number of bits} and sorting $n$ bit sequences of length $nbits$ (requires verifying the validity of a boolean predicate).
+The evaluation is performed on an available implementation ``Scarab library'' of a fully homomorphic encryption scheme.
+
 \end{abstract}
@@
 given the public parameters $pk:=(e, N)$ and two messages $m_0, m_1$, their encryption $c_0, c_1$ verify $c_0c_1=(m_0m_1)^e \ \textrm {mod}\ N$.
-With a fully homomorphic encryption scheme : a scheme $\mathcal{E}$ with an efficient algorithm $Eval_\mathcal{E}$ that evaluates any circuit $C$ on any ciphertexts $c_i \leftarrow Encrypt(pk, m_i)$; one can arbitrarily compute any function on encrypted data without the decryption key.
+Hence, without knowing the associated secret key, an external agent can compute the encryption of the product of the messages.
+
+Fully homomorphic encryption scheme extends the above property to addition.
+A Fully homomorphic scheme is a tuple of an ecryption $\mathcal{E}$, decryption $\mathcal{D}$ algorithm together with an efficient algorithm $Eval_\mathcal{E}$ that evaluates any circuit $C$ on any ciphertexts $c_i \leftarrow \mathcal{E}(pk, m_i)$.
+The property that it can evaluate the encryption of addition and multiplication of two plaintexts (without access to the secret key) allows it to arbitrarily compute any function on encrypted data without the decryption key.
 However prior to \cite{homenc}, we did not have a viable construction.
 
-As an application, such schemes can be used to query data on a remote machine.
-A user prepares his encrypted data $c_0, c_1, \ldots, c_{n-1}$  and a description of the function(or a query) i.e.
+As an application, such schemes can be used to query encrypted data stored on a remote machine.
+A user prepares his encrypted input data $c_0, c_1, \ldots, c_{n-1}$  and a description of the query i.e.
 a circuit $C$ he wants to evaluate and sends them to the remote machine.
-The machine transforms the circuit into $C^{'}$ so that it can evaluate the same function but on encrypted data, performs the operation and returns the encrypted result to the user.
+The machine transforms the circuit into $C^{'}$ so that it can evaluate the same query but on encrypted data, performs the operation and returns the encrypted result to the user.
 The user eventually decrypts the result.
 
-The homomorphic encryption scheme proposed by Gentry \cite{homenc} is based on ideal lattices which allows operations on encrypted data
-but with a high cost depending on the depth of the circuit representing the $Eval$ function.
-Since then, researchers have improved and proposed other schemes such as \cite{cryptoeprint:2009:571} and \cite{cryptoeprint:2011:277} which decrease the circuit complexity.
-In this article we expermentally evaluate implementation of these two schemes and analyze the cost-security trade-off for $Eval$ varying from \texttt{XOR} of the bits of an $n$ bit integer to sum of bounded and unbounded integers to sorting of $n$ integers.
+The immediate question that is raised, is how do we perform the transformation and how does the circuit size change to adapt to computations on encrypted data.
+We provide answer to this question by analyzing circuit complexity for finding the minimum-maximum of two $n$-bit sequences in \autoref{sec:ex} and for some other opertation in \autoref{sec:bm}.
+Moreover, the cost of evaluation depends on the depth of the circuit representing the $Eval_{\mathcal{E}}$ function.
+Some researchers have improved and proposed other schemes such as \cite{cryptoeprint:2009:571} and \cite{cryptoeprint:2011:277} which decrease the circuit complexity.
+In \autoref{Sec:Eval} and \autoref{Sec:Analysis} we expermentally evaluate implementation of these two schemes and analyze the cost-security trade-off for $Eval_{\mathcal{E}}$ varying from \texttt{XOR} of the bits of an $n$ bit integer to sum of bounded and unbounded integers to sorting of $n$ integers.
 Three different sorting algorithms are tested.
+Through these experiments, we also provide information on the additional cost to be paid (for these computations) to increase the security of the cyptosystem.
 
-In this article we study the implementation of basic classes of operations and different aspects of 
-complexity-security, and we discuss the results of experimental measures based on several parameters.\\
-The Gentry FHE protocol consists on ``somewhat homomorphic'' scheme, ``squashing'' and ``bootstrapping''. (explain later). 
-There are variants of FHE schemes more optimized than Gentry's scheme, so we use in the experiments some open source implementations of these schemes.
-\section{Fully homomorphic scheme(1 page)}
-A general structure of the scheme.
-\subsection{Two Variants of Fully Homomorphic Encryption Scheme}
-A brief description of the two FHE schemes with their algorithmic complexity of the different stages in the scheme. 
--> Smart Vercauteren
--> BGV
-Discuss the security of these schemes.
+\section{Fully homomorphic scheme (FHE) \\(1 page)}
 
-Smart-Vercauteren scheme:\\
-The scheme \cite{cryptoeprint:2009:571} has 3 parameters: ($N, \nu, \mu$ ).
+The homomorphic encryption scheme proposed by Gentry \cite{homenc} is based on ideal lattices.
+The Gentry's non-determi-nistic scheme builds on a \textit{somewhat homomorphic} scheme which can perform additions and multiplications on encrypted data till a bounded depth.
+The non-determinism introduced in the form of a noise renders the scheme secure.
+But, the noise increases with the depth  of the evaluation circuit.
+To counter this problem, Gentry introduces \textit{bootstrapping} technique which ensures unbounded depth operatability of the scheme.
+Smart Vercauteren \cite{cryptoeprint:2009:571} have proposed an integer based approach and we use one of its implementation detailed in \cite{perl:poster} for our experiments.
+
+\subsection{Smart-Vercauteren  scheme}
+
+The scheme proposed in \cite{cryptoeprint:2009:571} has 3 parameters:($N, \nu, \mu$ ).
 The somewhat homomorphic scheme uses 5 algorithms: (\texttt{KeyGen}, \texttt{Encrypt}, \texttt{Decrypt}, \texttt{Add}, \texttt{Mult}).
@@
 \restylealgo{algoruled}
-
 \linesnumbered
-
 \begin{algorithm}[H]
-
  \SetVline
-
  \KwData{$N, \nu, \mu$ }
-
- \KwResult{$pk, sk$}
-
-  $F(x)= x^{n}+1$
-
+\KwResult{($pk, sk$)}
+ $F(x)$ monic irreducible over $\mathbb{Z}[x]$ of degree $n$\;
 \While{$p$ is not prime}{
-
-	$S(x)=_{R}(B_{\infty , N}(\nu/2)$\;
-
+  $S(x) \leftarrow_{R}(B_{\infty , N}(\nu/2)$\; \tcc{Random choice}
   $G(x)=1+2.S(x)$\;
-
   $p= resultant(G(x),F(x))$\;						
-
 }
@@
 $D(x)=gcd(G(x),F(x))$ over $\mathbb{F}_p[x]$\;
+$\alpha$ $\leftarrow$ unique root of $D(x)$\;
+apply \texttt{xgcd} algorithm to obtain $Z(x) = \sum_{i=0}^{n-1}{z_ix^i} $  such that $Z(x).G(x)=p$ mod $F(x)$\;
+$B=z_0$ mod $2p$\;
+$pk = (p, \alpha)$ and $sk = (p , B)$\;
+return ($pk$, $sk$)\;
+\caption{KeyGen\label{Code:SV}}
+\end{algorithm}
 
-	$\alpha$: the unique root of $D(x)$\;
+where $ B_{\infty , n}(r) = \{\sum_{i=0}^{n-1}{a_i}x^i : -r \leq a_i \leq r \} $
 
- 	apply \texttt{fmpz\_poly\_xgcd} to obtain $Z(x)$ such that $Z(x).G(x)=p$ mod $F(x)$\;
+\texttt{Encrypt}($m \in \{0,1\} , pk$): 
+\newline \phantom{x}\hspace{3ex}  $R(x)=_{R}(B_{\infty , N}(\mu/2)$
+ \; $C(x)=m+2\cdot R(x)$ 
+\newline \phantom{x}\hspace{3ex} return  $c=C(\alpha)$ mod $p$
+\newline \texttt{Decrypt}($c, sk$):
+\newline \phantom{x}\hspace{3ex} $m = (c - \lfloor c \cdot B/p \rceil )$ mod $2$;
+\phantom{x}\hspace{1ex} return $m$
+\newline \texttt{Add}($c_1$, $c_2$, $pk$):
+\newline \phantom{x}\hspace{3ex} $c_3=c_1+c_2$ mod $p$
+;  \phantom{x}\hspace{1ex}  return $c_3$
+;
+\newline \texttt{Mult}($c_1$, $c_2$, $pk$):
+ \newline \phantom{x}\hspace{3ex}  $c_3=c_1.c_2$ mod $p$
+ ; \phantom{x}\hspace{1ex}  return $c_3$
+;
+\subsection{Considered Implementations}
+We used the open source implementation Scarab library \cite{hcrypt}  version $1.0.0$ of the Smart-Vercauteren scheme and is a part of \textsc{hcryptProject}.
+The implementation is in beta version.
+The software requires GMP \cite{gmp}, The GNU Multiple Precision Arithmetic Library; FLINT \cite{flint} , Fast Library for Number Theory; MPIR \cite{mpir}, Multiple Precision Integers and Rationals and MPFR \cite{mpfr}, multiple-precision floating-point computations with correct rounding.
+Linux is supposed to be the only supported platform.
+The libraries are in implemented in  C and the installation guide is provided with the package.
+\autoref{funs} presents the list of functions provided by the implementation with their description.
+The library provides a file \texttt{test.c} where a user can write his own function to test different operations.
+\begin{table*}
+\caption{Function available in Scarab}
+\begin{tabular}{|l|c||}
+  \hline
+  function prototype & semantics 2 \\
+  \hline
+ \texttt{fhe\_keygen(fhe\_pk\_t pk, fhe\_sk\_t sk);}  & 	Generate a keypair \\
+\texttt{fhe\_encrypt(mpz\_t c, fhe\_pk\_t pk, int m);} &	Encrypt a message (0 or 1) \\
+\texttt{fhe\_decrypt(mpz\_t c, fhe\_sk\_t sk);} &	Decrypt a cyphertext\\
+\texttt{fhe\_recrypt(mpz\_t c, fhe\_pk\_t pk, fhe\_sk\_t sk); }	&Recrypt a cyphertext ( ``refreshing'' it) \\
+\texttt{fhe\_add(mpz\_t res, mpz\_t a, mpz\_t b, fhe\_pk\_t pk);} &	Add cyphertexts (= XOR) \\
+\texttt{fhe\_mul(mpz\_t res, mpz\_t a, mpz\_t b, fhe\_pk\_t pk);} &	Multiply cyphertexts (= AND) \\
+\texttt{fhe\_fulladd(mpz\_t sum, mpz\_t c\_out, mpz\_t a, mpz\_t b,} &	Add with carry in and carry out \\
+\phantom{x}\hspace{12ex} \texttt{ mpz\_t c\_in, fhe\_pk\_t pk);} & \\
+\texttt{fhe\_halfadd(mpz\_t sum, mpz\_t c\_out, mpz\_t a,} &	Add with carry out \\
+\phantom{x}\hspace{12ex} \texttt{ mpz\_t b, fhe\_pk\_t pk);} & \\  
+\hline
+\end{tabular}
+\label{funs}
+\end{table*}
 
-	$B=z_0$ mod $2p$\;
+To simplify out computational circuit added, we added two basic functions \texttt{or(mpz\_t res, mpz\_t a, mpz\_t b, fhe\_pk\_t pk);} and \texttt{not(mpz\_t res, mpz\_t a, fhe\_pk\_t pk);} which compute the logical or of encrypted bits and the negation of an encrypted bit respectively.
 
-	$pk = (p, \alpha)$ and $sk = (p , B)$\;
+We time the various algorithms on two desktop machines.
+Both these machines were x86-64 platform running linux kernel $3.2.0$-$45$-generic  and used GCC $4.6.3$ C compiler.
+The first machine housed Intel Core i3 M330 (2.13GHz x 4) processor and will be referred in this article as machine M1 while the other used  housed Intel Core i5 2430 M(2.40 x4) processor and will be referred as machine M2.
 
-return($pk$, $sk$)
-
- \caption{Comparator\label{Code:algo}}
-
-\end{algorithm}
-\texttt{Encrypt}($m \in \{0,1\} , PK$): 
-\newline \phantom{x}\hspace{3ex}  $R(x)=_{R}(B_{\infty , N}(\mu/2)$
- \; $C(x)=m+2.R(x)$ 
-\newline \phantom{x}\hspace{3ex} return  $c=C(\alpha) mod p$
-\newline \texttt{Decrypt}($c, SK$):
-\newline \phantom{x}\hspace{3ex} $m = (c - round(c.B/p)) mod 2$;
-\phantom{x}\hspace{1ex} return $m$
-
-\texttt{Add}($c_1$, $c_2$, $PK$):
-\newline \phantom{x}\hspace{3ex} $c_3=c_1+c_2 mod p$
-  \phantom{x}\hspace{1ex}  return $c_3$
-\newline \texttt{Mult}($c_1$, $c_2$, PK):
- \newline \phantom{x}\hspace{3ex}  $c_3=c_1.c_2 mod p$
- ; \phantom{x}\hspace{1ex}  return $c_3$
-\subsection{Considered Implementations}
-
-The library used, version, implementaion details, versions, references, modifications required, how-to-installl, how-to-use.Platforms accepted and other depedeices.\\
-For the Smart-Vercauteren implementation we use the library libScarab v1.0.0 which requires the following libraries: GMP, FLINT, MPIR, MPFR.
 \subsection{Intial set-up cost(The cost not depending on the actual program)}
@@
 \section{ Didactic example :  Min-Max (1 page)}
+\label{sec:ex}
 Min-Max of sequence of n-btis with arithmetic operations and without branching.
@@
  $aIsGreater \leftarrow 0$\;
- $bitsEqual \leftarrow 1$\;
+ $bitEqual \leftarrow 1$\;
 
@@
 The measured time execution for KeyGen($N, \mu$)  for fixed values of parameters: $N=8$ and $\mu = 4$ show a variation from 0.2 s to 14.41 s with big density at the interval [0.2s, 1s].\\
+\begin{comment}
 \begin{figure}[!h] %on ouvre l'environnement figure
@@
 \end{figure}
+\end{comment}
 \item {Encryption and Decryption}\\
@@
 We measure the run time from $n=1$ to $32$ bits,we find a linear cost which confirms the $\theta(n)$ complexity. During these measures the result of Min-Max is correct.
+\begin{comment} 
 \begin{figure}[!h] %on ouvre l'environnement figure
@@
 \end{figure}
-
+\end{comment}
 \item The cost of this algorithm on ciphertext is linear with bit number, like  the algorithm on plaintext, the extra cost in this case is encryption-decryption cost and especially the code generation which is very inpreductible and take often a long time in the SV-Scheme.
@@
 \section{Choice of Benchmarks}
+\label{sec:bm}
 
@@
 
-\restylealgo{algoruled}
-
-\linesnumbered
-
-\begin{algorithm}[H]
-
- \SetVline
-
- \KwData{a:=$(a_0,a_1,\ldots, a_{n-1}$), b:=$(b_0,b_1,\ldots, b_{n-1})$ }
-
- \KwResult{Return Max(a,b) and Min(a,b)}
-
- $aIsGreater \leftarrow 0$\;
- $bitsEqual \leftarrow 1$\;
-
- \For{$i\leftarrow n-1 $ \KwTo $0$}{
-
-     $aIsGreater \leftarrow (aIsGreater +\neg(b_i)a_i)* bitEqual$ \;
-     $bitEqual \leftarrow bitEqual*(a_ib_i + \neg(a_i)*\neg(b_i))$		       	
- }
-
-\For{$i\leftarrow 0$ \KwTo $n-1$}{
-
-     $Max_i \leftarrow aIsGreater*a_i + \neg(aIsGreater)*b_i$ \;
-
-     $Min_i \leftarrow a \neg(aIsGreater)*a_i + aIsGreater*b_i$ \;
-
- }
-
-return($Max$, $Min$)
-
- \caption{Comparator\label{Code:algo}}
-
-\end{algorithm}
-
 A comparator gate uses $n$ \texttt{AND} gates, $n$ \texttt{OR} gates and $n$ \texttt{NOT} gates to find the larger of the two bit sequences and then to regenerate the maximum and the minuimum $4n$ \texttt{AND} gates and $2n$ \texttt{NOT} and \texttt{OR} gates i.e.
@@
 \section{Evaluation on the benchmarks}
+\label{Sec:Eval}
 Measurements by varying the parameters or the plaintext size.
@@
 \centering
-\includegraphics[width=5cm]{./Insertion_sort_CPU.jpg} 
+\includegraphics[width=8cm]{./Insertion_sort_CPU.jpg} 
 \caption{Run time of } 
@@
 \section{Analysis of the results}
-
+\label{Sec:Analysis}
 Anlayze the results previously obtained and its impact on security and complexity. Comparisions of security-cost tradeoff with other schemes like RSA.
@@
 %\begin{comment}
+\newpage
 \section{Appendix}

### 2013-06-13 libScarab-1.0.0/test.c

@@ -52,13 +52,13 @@ void test_suite()
 	//test_encryt_decrypt();
 	//test_halfadd();
 	//test_fulladd();
-	test_xor_bits();
+//	test_xor_bits();
 	//test_sum_bits();
 	//test_bit_majoritaire();
 	//test_sum_integers();
 	//test_min_max();
 	//test_insertion_sort();
-	//test_oddeven_merger_sort();
+	test_oddeven_merger_sort();
 	//test_bitonic_sort();
 	//test_majority_bit();
 	//test_matrix_prod();
@@ -482,7 +482,7 @@ void test_min_max(){
 }
 
 
-void OddEvenMerge(fmpz_poly_t * poly_nums, int n, int nbits, int lo, int r, fhe_sk_t sk , fhe_pk_t pk){
+void OddEvenMerge(fmpz_poly_t * poly_nums, int n, int nbits, int lo, int r, fhe_pk_t pk){
 
 		
 	mpz_t * max;
@@ -498,8 +498,8 @@ void OddEvenMerge(fmpz_poly_t * poly_nums, int n, int nbits, int lo, int r, fhe_
 	
 	if(m<n){
 		
-		OddEvenMerge(poly_nums, n, nbits, lo, m, sk, pk); // even subsequence
-		OddEvenMerge(poly_nums, n, nbits, lo+r, m, sk, pk); //odd subsequence	
+		OddEvenMerge(poly_nums, n, nbits, lo, m, pk); // even subsequence
+		OddEvenMerge(poly_nums, n, nbits, lo+r, m, pk); //odd subsequence	
 		for(int i=lo+r; i+r <lo+n; i+=m){
 			min_max(min, max, poly_nums[i], poly_nums[i+r], pk, nbits);		
 			for(int k=0;k<nbits;k++){
@@ -524,29 +524,36 @@ void OddEvenMerge(fmpz_poly_t * poly_nums, int n, int nbits, int lo, int r, fhe_
 	}
 
 
-
+	for(int k=0;k<n;k++){
+		mpz_clear(max[k]);
+		mpz_clear(min[k]);
+	}
+	free(max);
+	free(min);
+	
+	
 }
 
 
 
-void OddEvenMergeSort(fmpz_poly_t * poly_nums, int n, int nbits, int lo, fhe_sk_t sk, fhe_pk_t pk)
[…]

### 2013-06-14 libScarab-1.0.0/test.c
sum

@@ -35,7 +35,7 @@
 
 void test_keygen();
 
-
+void mesure_sum_integers();
 
 void measure_test_keygen(){
 	for(int i=0; i< 40; i++) test_keygen();
@@ -52,29 +52,27 @@ void test_suite()
 	//test_encryt_decrypt();
 	//test_halfadd();
 	//test_fulladd();
-	test_xor_bits();
+	//test_xor_bits();
 	//test_sum_bits();
 	//test_bit_majoritaire();
-	//test_sum_integers();
+	mesure_sum_integers();
 	//test_min_max();
 	//test_insertion_sort();
 	//test_oddeven_merger_sort();
 	//test_bitonic_sort();
 	//test_majority_bit();
 	//test_matrix_prod();
-
-	//debug_test_bit_majoritaire();
+	//test_sum_unbounded();
 	//measure_test_keygen();
-
 	//test_keygen();
 }
 
 void test_keygen(){
 	struct timeval start, end;	
     	long mtime, seconds, useconds;    
-	clock_t  START_eval;
+	//clock_t  START_eval;
 	//double T_Elapsed4;
-	START_eval = clock();
+	//START_eval = clock();
 	gettimeofday(&start, NULL);    
 	fhe_pk_t pk;
 	fhe_sk_t sk;
@@ -1083,7 +1081,7 @@ void test_sum_mpz_t(fmpz_poly_t sum_result, fmpz_poly_t poly_c1, fmpz_poly_t pol
 	mpz_init(c_in);	
 	mpz_init(c_out);
 	fhe_encrypt(c_in, pk, 0);
-	fhe_encrypt(c_out, pk, 0);
+	//fhe_encrypt(c_out, pk, 0);
 
 	int k;
 	for(k=0;k<nbits;k++){
@@ -1128,74 +1126,75 @@ void test_sum_mpz_t(fmpz_poly_t sum_result, fmpz_poly_t poly_c1, fmpz_poly_t pol
 
 void test_majority_bit(){
 	
-	unsigned a ,aux1, aux2;
-	a=35;
-	aux1= a; 
-	int i = 0;
-	int nbits=6;
-	aux2=nbits;
+	unsigned aux1, aux2;
[…]

### 2013-06-14 libScarab-1.0.0/test.c
modif sum

@@ -36,7 +36,8 @@
 void test_keygen();
 
 void mesure_sum_integers();
-
+void mesure_encrypt_decrypt();
+//void mesure_decrypt();
 void measure_test_keygen(){
 	for(int i=0; i< 40; i++) test_keygen();
 }
@@ -55,19 +56,35 @@ void test_suite()
 	//test_xor_bits();
 
 	//test_sum_bits();
-	//test_bit_majoritaire();
 	mesure_sum_integers();
 	//test_min_max();
 	//test_insertion_sort();
-	test_oddeven_merger_sort();
+	//test_oddeven_merger_sort();
 	//test_bitonic_sort();
 	//test_majority_bit();
 	//test_matrix_prod();
 	//test_sum_unbounded();
 	//measure_test_keygen();
 	//test_keygen();
+	//mesure_encrypt_decrypt();
+	//essai();
 }
 
+void essai(){
+	fhe_pk_t pk;
+	fhe_sk_t sk;
+	fhe_pk_init(pk);
+	fhe_sk_init(sk);
+	fhe_keygen(pk, sk);
+	mpz_t c;
+	mpz_init(c);
+	mpz_set_ui(c, 1);
+	int m= fhe_decrypt(c, sk);
+	printf("m= %d\n",m);
+	mpz_clear(c);
+	fhe_pk_clear(pk);
+	fhe_sk_clear(sk);
+}
 void test_keygen(){
 	struct timeval start, end;	
     	long mtime, seconds, useconds;    
@@ -91,6 +108,70 @@ void test_keygen(){
 	printf("Elapsed time in KeyGen : %ld ms \n", mtime );
 }
 
+void mesure_encrypt_decrypt(){
+	fhe_pk_t pk;
+	fhe_sk_t sk;	
+	mpz_t c, aux1, aux2;
+	int m, k =0;
+	mpz_init(c);
+	mpz_init(aux1);
+	mpz_init(aux2);
+	mpz_set_ui(aux2, 0);
+	fhe_pk_init(pk);
+	fhe_sk_init(sk);
+	struct timeval start, end;	
+    	long mtime, seconds, useconds;  
+	gettimeofday(&start, NULL);
+	fhe_keygen(pk, sk);
+	gettimeofday(&end, NULL);
+		seconds  = end.tv_sec  - start.tv_sec;
[…]

### 2013-06-14 libScarab-1.0.0/test.c
Previous version

@@ -57,8 +57,8 @@ void test_suite()
 	//test_bit_majoritaire();
 	//test_sum_integers();
 	//test_min_max();
-	//test_insertion_sort();
-	test_oddeven_merger_sort();
+	test_insertion_sort();
+	//test_oddeven_merger_sort();
 	//test_bitonic_sort();
 	//test_majority_bit();
 	//test_matrix_prod();
@@ -482,9 +482,9 @@ void test_min_max(){
 }
 
 
-void OddEvenMerge(fmpz_poly_t * poly_nums, int n, int nbits, int lo, int r, fhe_pk_t pk){
+void OddEvenMerge(fmpz_poly_t * poly_nums, int n, int nbits, int lo, int high, int r, fhe_pk_t pk){
 
-		
+	//printf("Inside OddEven Merge");		
 	mpz_t * max;
 	mpz_t * min;
 	max = malloc(sizeof(mpz_t) * nbits);
@@ -494,25 +494,25 @@ void OddEvenMerge(fmpz_poly_t * poly_nums, int n, int nbits, int lo, int r, fhe_
 		mpz_init(min[i]);
 	}
 
+	
 	int m = 2*r;
 	
-	if(m<n){
-		
-		OddEvenMerge(poly_nums, n, nbits, lo, m, pk); // even subsequence
-		OddEvenMerge(poly_nums, n, nbits, lo+r, m, pk); //odd subsequence	
-		for(int i=lo+r; i+r <lo+n; i+=m){
-			min_max(min, max, poly_nums[i], poly_nums[i+r], pk, nbits);		
+	if(m<high){
+		OddEvenMerge(poly_nums, n, nbits, lo, high, m, pk); // even subsequence
+		OddEvenMerge(poly_nums, n, nbits, lo+r, high, m, pk); //odd subsequence	
+	for(int i=lo+r; i+r<lo+high; i+=m){
+			min_max(min, max, poly_nums[i], poly_nums[i+r], pk, nbits);
 			for(int k=0;k<nbits;k++){
 				fmpz_poly_set_coeff_mpz(poly_nums[i], k, min[k]);
 				fmpz_poly_set_coeff_mpz(poly_nums[i+r],k, max[k]);
 			}
+		
 
-			
+
 		}
 
 	}	
 	else {
-	
 		min_max(min, max, poly_nums[lo], poly_nums[lo+r], pk, nbits);		
 		for(int k=0;k<nbits;k++){
[…]

### 2013-06-15 libScarab-1.0.0/test.c
With Prof's example

@@ -56,9 +56,9 @@ void test_suite()
 	//test_xor_bits();
 
 	//test_sum_bits();
-	mesure_sum_integers();
+	//mesure_sum_integers();
 	//test_min_max();
-	//test_insertion_sort();
+	test_insertion_sort();
 	//test_oddeven_merger_sort();
 	//test_bitonic_sort();
 	//test_majority_bit();
@@ -663,9 +663,9 @@ void test_oddeven_merger_sort(){
 		int mod = (int)pow(2, nbits);
 		for(int t=0;t<n;t++){
 			list[t]= rand()%mod;
-			//printf("%d ",list[t]);	
+			printf("%d ",list[t]);	
 		}
-	//printf("\n");
+	printf("\n");
 	nbits=0;
 	for(int k = 0; k < n ; k++){
 		i=0;
@@ -706,7 +706,7 @@ void test_oddeven_merger_sort(){
 
 	
 	////////////// Decryption /////////////////////
-	/*intf("After OddEven sort \n");
+	printf("After OddEven sort \n");
 	for (i=0;i<n;i++){
 		aux = 0;
 		d=0;
@@ -720,7 +720,7 @@ void test_oddeven_merger_sort(){
 	}
 	printf("\n");
 
-*/
+
 }
 
 	for(int k=0;k<n;k++)
@@ -969,8 +969,8 @@ void test_bitonic_sort(){ // Sorts a bitonic array of 2^n elements
 }
 
 void test_insertion_sort(){   // Generate n random numbers of nbits each and sort them
-	int n = 15; // Nombre d'entiers à trier
-	int nbits = 8; // Size in number of bits
+	int n = 14;// Nombre d'entiers à trier
+	int nbits = 4; // Size in number of bits
 	int *list = malloc(sizeof(int)*n); // List d'entiers à trier
 	//printf("\n");
 

### 2013-06-15 libScarab-1.0.0/test.c
des mesures

@@ -34,10 +34,9 @@
 
 
 void test_keygen();
-
+void mesure_matrix_prod();
 void mesure_sum_integers();
 void mesure_encrypt_decrypt();
-//void mesure_decrypt();
 void measure_test_keygen(){
 	for(int i=0; i< 40; i++) test_keygen();
 }
@@ -56,13 +55,13 @@ void test_suite()
 	//test_xor_bits();
 
 	//test_sum_bits();
-	mesure_sum_integers();
-	//test_min_max();
+	//mesure_sum_integers();
+	test_min_max();
 	//test_insertion_sort();
 	//test_oddeven_merger_sort();
 	//test_bitonic_sort();
 	//test_majority_bit();
-	//test_matrix_prod();
+	//mesure_matrix_prod();
 	//test_sum_unbounded();
 	//measure_test_keygen();
 	//test_keygen();
@@ -97,6 +96,15 @@ void test_keygen(){
 	fhe_pk_init(pk);
 	fhe_sk_init(sk);
 	fhe_keygen(pk, sk);
+	printf("N: %d\n", N);
+	printf("taille binaire de p: %d\n", mpz_sizeinbase( pk->p, 2));
+	gmp_printf("p: %Zd \n", pk->p);
+	gmp_printf("alpha: %Zd \n", pk->alpha);
+	gmp_printf("B: %Zd \n", sk->B);
+	for(int i=0; i < S1; i++){
+		gmp_printf("c[%d]: %Zd \n", i, pk->c[i]);
+		gmp_printf("B[%d]: %Zd \n", i, pk->B[i]);
+	}
 	fhe_pk_clear(pk);
 	fhe_sk_clear(sk);
 	//T_Elapsed4 = (double) (clock () - START_eval);
@@ -105,7 +113,7 @@ void test_keygen(){
 	seconds  = end.tv_sec  - start.tv_sec;
 	useconds = end.tv_usec - start.tv_usec;
 	mtime = ((seconds) * 1000 + useconds/1000.0) + 0.5;
-	printf("Elapsed time in KeyGen : %ld ms \n", mtime );
+	//printf("Elapsed time in KeyGen : %ld ms \n", mtime );
 }
 
 void mesure_encrypt_decrypt(){
@@ -1503,93 +1511,101 @@ void test_sum_integers(unsigned a , unsigned b, fhe_pk_t pk, fhe_sk_t sk){
 	//
 	fmpz_poly_clear(s);
 	mpz_clear(c);
-
 }
 
[…]

### 2013-06-15 Report/article.tex
final version

@@
 
-\section{Introduction(1 page)}
+\section{Introduction}
 
@@
 Some researchers have improved and proposed other schemes such as \cite{cryptoeprint:2009:571} and \cite{cryptoeprint:2011:277} which decrease the circuit complexity.
-In \autoref{Sec:Eval} and \autoref{Sec:Analysis} we expermentally evaluate implementation of these two schemes and analyze the cost-security trade-off for $Eval_{\mathcal{E}}$ varying from \texttt{XOR} of the bits of an $n$ bit integer to sum of bounded and unbounded integers to sorting of $n$ integers.
+In \autoref{Sec:Eval} we expermentally evaluate an implementation of  \cite{cryptoeprint:2009:571} and analyze the cost-security trade-off for $Eval_{\mathcal{E}}$ varying from \texttt{XOR} of the bits of an $n$ bit integer to sum of bounded and unbounded integers to sorting of $n$ integers.
 Three different sorting algorithms are tested.
@@
 
-\section{Fully homomorphic scheme (FHE) \\(1 page)}
+\section{Fully homomorphic Encryption scheme (FHE) }
 
@@
 The somewhat homomorphic scheme uses 5 algorithms: (\texttt{KeyGen}, \texttt{Encrypt}, \texttt{Decrypt}, \texttt{Add}, \texttt{Mult}).
+Algorithm \autoref{Code:SV} presents the \texttt{KeyGen} algorithm.
 
@@
 ;
+
+\textbf{Security of the scheme} The scheme is semantically secure under the assumption that the \textit{Polyomial Coset Problem} is hard.
+One wayness of the encryption is believed to be true under the assumption that the \textit{Bounded distance decoding problem} BDDP is hard while key recovery is assumed to be difficult under the assumption that the \textit{Small Principal Ideal Problem} is hard.
+Solutions to all of these problems have either a sub-exponential algorithm or in general take exponential time.
+
+If we choose $F(x)$ \footnote{a choice that authors of SV scheme propose and is always a safe choice for monic and irreducible polynomial over $\mathbb{Z}[x] $} to be $x^N+1$, and take $2 ^ \lambda = \frac{\nu}{2\cdot \mu \sqrt{N}} $, then the SV scheme provides $N /\lambda$ bits of security.
+
+\textbf{SWHE to FHE :} We recall that the authors have proved that the multiplicative depth $d$ of SWHE  verifies \[d \cdot log(2) \leq log( log(\frac{\nu}{2\cdot \sqrt{N}}) ) - log(log( N\mu))\]
+when $F(x)= x^N+1$.
+Turning the SWHE to FHE is achieved by recasting Gentr's method for the parameters of this scheme.
+To achive this the authors propose to generate $s_1$ uniformly random integers $B_i$ in $[-p, \ldots, p]$ such that there exists a subset $S$ of $s_2$ elements with $\sum_{j \in S}{B_j}= B$ over integers.
+By defining $sk_i =1$ iff $i\in S$ and taking $c_i=Encrypt(sk_i,pk)$ we generate a new public key which contains hint of the secret key $sk$.
+The public key now comprises of \[(p, \alpha, s_1, s_2, \{c_i, B_i\}_{i=1}^{s1})\].
+
+To ensure that the hint doesn't provide considerable advantage to an attacker, the underlying \textit{sparse subset-sum problem} SSSP must remain remain hard.
+If we take $s_1$ to be slightly greater than $p$, then we need to select $s_2$ such that $\sqrt {{s_1}  \choose {s_2} } \leq 2 ^{N/\lambda}$ so as to ensure that SSSP difficulty is at least as difficult as the difficulty of the BDDP underlying the SWHE scheme.
 \subsection{Considered Implementations}
@@
 \caption{Function available in Scarab}
-\begin{tabular}{|l|c||}
+\begin{tabular}{|l|l||}
   \hline
-  function prototype & semantics 2 \\
+  \textbf{function prototype} & \textbf{semantics}  \\
   \hline
@@
 
-\subsection{Intial set-up cost(The cost not depending on the actual program)}
+\subsection{Intial set-up cost}
+Measurements taken are CPU time, Wall Time, Memory Usage by varying the input size  and the algorithmic parameters. Noise reduction threshold.\\
+Here we estimate the performance of this program in terms of run time for KeyGen, Encrypt, Decrypt and the Min-Max algorithm.
 
-Can be integrated with subsection 2.1
+\textbf{KeyGen}\\
+The measured time execution for KeyGen($N, \mu$)  for fixed values of parameters: $N=8$ and $\mu = 4$ show a variation from 0.2 s to 14.41 s with big density at the interval [0.2s, 1s].
+\begin{comment}
+\begin{figure}[!h] %on ouvre l'environnement figure
+\centering
+\includegraphics[width=5cm]{f3.eps} 
+\caption{Run time of KeyGen(ms)} 
+\label{image_f2} %l'étiquette pour faire référence à cette image
+\end{figure}
+\end{comment}
 
-\section{ Didactic example :  Min-Max (1 page)}
+\textbf{Encryption and Decryption}\\
+
+\section{Circuit Transformation}
+As previously discussed, a user sends his program which works on unencrypted data and his encrypted input to the cloud.
+The cloud then performs the demanded computation and returns the result.
+However, the program in the same form cannot always be used for computations on encrypted data.
+
+Consider a program involves the following test on two inputs : \texttt{if(a > b) instruction\_1; else instruction\_2;}.
+As the cloud does not know the result of the test\texttt{ a' > b'} where \texttt{a'} and \texttt{b'} are the encryptions of \texttt{a} and \texttt{b}, he does not know which of the instructions he has perform.
+In fact he performs both the instrunctions by transforming the actual program into : \texttt{test(a'> b')*} \texttt{instruction\_1 +}$\neg$\texttt{test(a'> b')*instruction\_2}, where \texttt{test()}  is a function on encrypted inputs \texttt{a'}, \texttt{b'} and returns an encryption of $1$ iff \texttt{a > b}.
+Hence, if the program used has braching i.e.
+it involves \texttt{if(cond\_0)} \texttt{\{inst\_0\} else if(cond\_1)\{inst\_1\}}\linebreak \texttt{ ...else if(cond\_n-2) \{inst\_n-2\}} \texttt{else\{inst\_n-1 \}}; the cloud has to perform all the $n$ instructions i.e.
+the size of the circuit changes from a constant size to a size linear in the number of tests.
+
+This increase in size is due to the fact that the cloud transforms a non-straight line program into a straight-line program.
+
+\textbf{Another transformation}: We consider the following program that a cloud receives : \\
+ \phantom{x} \texttt{i=0, res=0;}
+\newline \phantom{x} \texttt{do\{ }
+\newline \phantom{x} \hspace{9ex} \texttt{i++;} 
+\newline   \phantom{x} \} \texttt{while(i < n \&\& cond\_i);} 
+\newline  \phantom{x} \texttt{res = f(i)};\\
+In this case, the cloud needs to transform a loop with condititonal stopping into a loop with unconditional branching. We propose the following possible transformation : \\
+ \phantom{x} \texttt{endLoop=0', res=0', i=0;}
+\newline \phantom{x} \texttt{do\{ }
+\newline \phantom{x} \hspace{6ex} \texttt{endLoop = $\neg$cond\_i;}
+\newline \phantom{x} \hspace{6ex} \texttt{res = $\neg$endLoop*f(i)+($\neg$cond\_i)*res;}
+\newline \phantom{x} \hspace{6ex} \texttt{i++;} 
+\newline   \phantom{x} \} \texttt{while(i < n);}
+
+\textbf{Correctness of the code :} If \texttt{cond\_i} is always \texttt{true}, \texttt{endLoop} is always false hence the \texttt{res=f(n)}.
+If at the $t^{th}$iteration, \texttt{cond\_i} is \texttt{false}, \texttt{endLoop} becomes \texttt{false} and hence \texttt{res} contains its previous value $f(t-1)$.
+
+We note that the cost of the above program is $n$ times the computational complexity of the function, however in the initial program the function is evaluated only once.
+
+\subsection{ Didactic example :  Min-Max}
 \label{sec:ex}
-Min-Max of sequence of n-btis with arithmetic operations and without branching.
-\subsection{Input Program for Fully Homomorphic Encryption Scheme}
+
+We suppose that a user wants to find the maximum and the minimum of two $n$-bit sequences $a = (a_0,a_1,\ldots, a_{n-1})$, $b=(b_0,b_1,\ldots, b_{n-1})$.
+He provides the following algorithm to the cloud :
+\newline \phantom{x} \texttt{aIsGreater=0, i=0;}
+\newline \phantom{x} \texttt{do\{ }
+\newline \phantom{x} \hspace{6ex} \texttt{ if(a[i]==1 \&\& b[i]==0) 
+\newline \phantom{x} \hspace{14ex}aIsGreater = 1;}
+\newline \phantom{x} \hspace{7ex} \texttt{i++;} 
+\newline   \phantom{x} \} \texttt{while(i < n);}
+
+We note that, we do not know how an optimized version :  using \texttt{break} to exit the loop once \texttt{aIsGreater} is set to \texttt{true}, could be transformed into a program for the cloud.
+We believe that the possibility to quit the loop would mean that the cloud knows the result of the \texttt{if(condition)}.
+
+We propose the transformed algorithm \autoref{Code:algo} of the above program.
+It inspects the relative magnitude of pairs of bits, starting from the most significant bit and gradually proceeding towards lower significant bits until an inequality is found.
 
@@
 
- \KwData{a':=$(a_0',a_1',\ldots, a_{n-1}'$), b':=$(b_0',b_1',\ldots, b_{n-1}')$ }
+ \KwData{$a'$:=$(a_0',a_1',\ldots, a_{n-1}'$), $b'$:=$(b_0',b_1',\ldots, b_{n-1}')$ }
 
- \KwResult{Return Max(a',b') and Min(a',b')}
+ \KwResult{$Max(a',b')$ and $Min(a',b')$}
 
@@
 
- \For{$i\leftarrow n-1 $ \KwTo $0$}{
+ \For{$i\leftarrow 0 $ \KwTo $n-1$}{
 
-     $aIsGreater \leftarrow (aIsGreater +\neg(b_i')a_i')* bitEqual$ \;
-     $bitEqual \leftarrow bitEqual*(a_i'b_i' + \neg(a_i)'*\neg(b_i'))$		       	
+     $aIsGreater \leftarrow (aIsGreater +\neg(b_i')a_i') bitEqual$ \;
+     $bitEqual \leftarrow bitEqual(a_i'b_i' + \neg(a_i)'\neg(b_i'))$		       	
  }
@@
 
-     $Max_i \leftarrow aIsGreater*a_i' + \neg(aIsGreater)*b_i'$ \;
+     $Max_i \leftarrow aIsGreater\cdot a_i' + \neg(aIsGreater)b_i'$ \;
 
-     $Min_i \leftarrow  \neg(aIsGreater)*a_i' + aIsGreater*b_i'$ \;
+     $Min_i \leftarrow  \neg(aIsGreater)a_i' + aIsGreater \cdot b_i'$ \;
 
@@
 
-\subsection{Theoretical Cost with the Schemes}
+\newtheorem{theorem}{Lemma}
+\begin{theorem}
+Algorithm \autoref{Code:algo} returns the maximum and the minimum of the input bit sequences. 
+\end{theorem}
 
-The cost \texttt{aIsGreater} is:\\
- $2*encrypt+n*(3*encrypt+7*add+7*mul)$ .\\
-The cost of this algorithm \texttt{min\_max} is:\\
-$ encrypt+aIsGreater+2*n*(encrypt+3add+3mull)$\\
-Thus this algorithm has $\theta(n)$ complexity.
+\begin{proof}
 
-\subsection{Experimental Analysis}
+Consider $x_i = a_ib_i+\neg(a_i)\neg(b_i) $.
+$x_i$ is $1$ iff $a_i$ and $b_i$ are equal.
+We note that, $bitEqual$ is the product of $x_i$ and is $1$ at the $t^{th}$ iteration iff $a_i=b_i$ for $i < t$.
+The term $\neg(b_i)a_i$ is $1$ iff $a_i=1$ and $b_i =0$.
+Hence at the $t^{th}$ iteration, the algorithm using $bitEqual$ tests if the previous bits were equal.
+Hence, $aIsGreater$ is $1$ iff at any stage  $a_t\neg(b_t)=1$ and the previous bits were equal.
 
-Measurements taken are CPU time, Wall Time, Memory Usage by varying the input size  and the algorithmic parameters. Noise reduction threshold.\\
-Here we estimate the performance of this program in terms of run time for KeyGen, Encrypt, Decrypt and the Min-Max algorithm.
-\begin{itemize}
+Max and Min regenerate $a_i$ and $b_i$ and hence contain the correct result.  
+\end{proof}
+\textbf{Theoretical Cost:} Algorithm \autoref{Code:algo} uses $n$ \texttt{AND} gates, $n$ \texttt{OR} gates and $n$ \texttt{NOT} gates to find the larger of the two bit sequences and then to regenerate the maximum and the minuimum $4n$ \texttt{AND} gates and $2n$ \texttt{NOT} and \texttt{OR} gates.
+We note that reconstruction of Max and  Min is not required when working on non-encrypted data.
+Hence, this is an additional cost to pay to use the transformed program operating on encrypted data.
 
-\item KeyGen\\
-The measured time execution for KeyGen($N, \mu$)  for fixed values of parameters: $N=8$ and $\mu = 4$ show a variation from 0.2 s to 14.41 s with big density at the interval [0.2s, 1s].\\
-\begin{comment}
-\begin{figure}[!h] %on ouvre l'environnement figure
-\centering
-\includegraphics[width=5cm]{f3.eps} 
-\caption{Run time of KeyGen(ms)} 
-\label{image_f2} %l'étiquette pour faire référence à cette image
-\end{figure}
-\end{comment}
-\item {Encryption and Decryption}\\
-
-\item {Cost time of Min-Max program}\\
-We measure the run time from $n=1$ to $32$ bits,we find a linear cost which confirms the $\theta(n)$ complexity. During these measures the result of Min-Max is correct.
+\textbf{Experimental Analysis :} We measure the run time from $n=1$ to $32$ bits, we find a linear cost which confirms the $\theta(n)$ complexity.
+During these measures the result of Min-Max is correct.
 \begin{comment} 
@@
 \end{comment}
-\item The cost of this algorithm on ciphertext is linear with bit number, like  the algorithm on plaintext, the extra cost in this case is encryption-decryption cost and especially the code generation which is very inpreductible and take often a long time in the SV-Scheme.
-\end{itemize}
+The cost of this algorithm on ciphertext is linear with bit number, like  the algorithm on plaintext, the extra cost in this case is encryption-decryption cost and especially the code generation which is very inpreductible and take often a long time in the SV-Scheme.
+
 \section{Choice of Benchmarks}
@@
 
-The benchmark problems on which the implementations were evaluated are categorized into three classes : functions operating on bits, functions operating directly on integers or block of bits and functions where branching is required i.e \texttt{if-then-else} condition is evaluated.
+We propose a set of benchmark functions to evaluate the implementations.
+These functions can be categorized into three classes : functions operating on bits, \textcolor{orange}{functions operating directly on integers or block of bits} and functions where branching is usually required i.e \texttt{if-then-else} condition is evaluated.
 
-Functions operating on bits provide information on the tradeoff for bitwise operations, while when operating directly on integers, the tradeoff is obtained as a function of the size of integers.
-The first two categories of functions can be evaluated using straight-line programs.
+Functions operating on bits provide information on the security-cost tradeoff for bitwise operations, \textcolor{orange}{while when operating directly on integers}, the tradeoff is obtained as a function of the size of integers.
+The first two categories of functions with straight-line programs on non-encrypted data can directly be translated to operate on encrypted bits.
 For others, evaluation of \texttt{if-then-else} condition on encrypted data is choosen.
-The evaluation circuit in this case is longer than the one on non-encrypted data.
-Hence, this provides information on increase in size of the circuit(when passing from non-encrypted to enrypted data).
-The addressed problems are :
+In this case, a circuit(program) transformation is required and which often makes the size longer than the one on non-encrypted data.
+Hence, this provides information on increase in size of the circuit(when passing from non-encrypted to enrypted data) and the associated trade-off.
+We study the security-cost tradeoff for the following problems :
 
-1. \textbf{XOR of bits}\\
+1. \textbf{XOR of an $n$-bit sequence}\\
 2. \textbf{Sum of :}  
 \newline\noindent
-\phantom{x}\hspace{3ex} a) bounded integers 
- b) unbounded integers\\ 
-3. \textbf{Majority bit} \\
-4. \textbf{Sorting : } \newline\noindent
-\phantom{x}\hspace{3ex} a) Insertion sort b) Oddd-Even Merge sort \\
-	\phantom{x}\hspace{3ex} 	    c) Bitonic sort
+\phantom{x}\hspace{3ex} a) integers having $n$ bits 
+ \textcolor{orange}{b) integers having arbitrary
+\newline \phantom{x}\hspace{6ex}  number of bits}\\ 
+3. \textbf{Majority bit of an $n$-bit sequence} \\
+4. \textbf{Product of two $n\times n$ matrices} \\
+5. \textbf{Sorting of $n$ sequences of $nbits$: } \newline\noindent
+\phantom{x}\hspace{3ex} a) Insertion sort c) Bitonic sort \\
+	\phantom{x}\hspace{3ex} 	     b) Odd-Even Merge sort
 
-The implementations are evaluated on different sorting algorithms to compare the changes in the evaluation circuits.
+The interest of choosing the above sorting algorithms is that all of them can be parallelized and hence are ideal for distributed environments such as cloud.
 
-\subsection{Theoretical Size of Evaluation Circuit}
+\subsection{Size of Evaluation Circuit}
 As the implementations provide addition and multiplicaion of ciphertexts,  size in terms of \texttt{XOR} and \texttt{AND} gates are provided for each problem.
 
-\textbf{XOR of $n$-bits :} \texttt{XOR} of $n$-bits requires $n-1$ \texttt{XOR} gates.
-
+\textbf{XOR of $n$-bits :} \texttt{XOR} of $n$-bits requires $n-1$ \texttt{XOR} gates. \newline
 \textbf{Sum of integers of $n$-bits :} Sum of two integers is performed using an $n$ \texttt{full-adder} circuits.
@@
 Hence the total complexity is $3n$ \texttt{AND}, $5n$ \texttt{XOR}.
-
-\textbf{Sum of arbitrary integers}
-
-\textbf{Majority of $n$-bits :} Majority bit is evaluated by obtaining the sum of the bits.
-
-\textbf{Sorting :}
-Sorting is tested on a sorting network where comparator gates are used. Each comparator is designed using the following algorithm.
-
-A comparator gate uses $n$ \texttt{AND} gates, $n$ \texttt{OR} gates and $n$ \texttt{NOT} gates to find the larger of the two bit sequences and then to regenerate the maximum and the minuimum $4n$ \texttt{AND} gates and $2n$ \texttt{NOT} and \texttt{OR} gates i.e.
-$6n$ \texttt{AND} and \texttt{XOR} gates are required.
-We note that reconstruction of Max and  Min is not required when working on non-encrypted data.
-Hence, this increases the size of the transformed program operating on encrypted data.
-
-\textbf{Insertion sort :} When allowing for parallel comparators, bubble sort and insertion sort are identical. Hence $n(n-1)/2$ comparator gates are used for insertion sort.
-
-\textbf{Odd-Even Merge sort :} \autoref{oesort} and \autoref{oemerge} are used to perform Odd-Even merge sort and hence  $n/2(log(n)-1) + 1 $ comparator gates are required.
-
-\textbf{Bitonic Sort :} \autoref{bitsort} and \autoref{bitmerge} are used to perform Bitonic Sort and hence $log(n) · (log(n)+1) / 2 $ gates are required.
+\newline
+\textcolor{orange}{\textbf{Sum of arbitrary integers}} \newline
+\textbf{Majority of $n$-bits :} Majority bit is evaluated by obtaining the sum of the bits and then returning the result of the comparision of the sum and $n/2$. \newline \newline
+\textbf{Product of two $n\times n$ matrices}: This resquires $n^3$ \texttt{AND} gates and \texttt{$n^2(n-1)$} \texttt{XOR} gates. \newline \newline
+\textbf{Sorting} Several straight-line programs for sorting have have been proposed in litterature \cite{dk}, \cite{Batcher:1968:SNA:1468075.1468121}.
+These programs use a comparator gate : a logical gate with two inputs and two ouputs, that computes the minimum and maximum of two $n$ bit sequences.
+Algorithm \autoref{Code:algo} implements a comparator gate.
+Hence we do not need to perform any transformation for these algorithms.
+\newline \newline
+\textbf{Insertion sort :} When allowing for parallel comparators, bubble sort and insertion sort are identical. Hence $n(n-1)/2$ comparator gates are used for insertion sort.\newline \newline
+\textbf{Bitonic Sort :} \autoref{bitsort} and \autoref{bitmerge} are used to perform Bitonic Sort. The algorithm use $log(n) · (log(n)+1) / 2 $ gates are required. \newline \newline
+\textbf{Odd-Even Merge sort :} \autoref{oesort} and \autoref{oemerge} are used to perform Odd-Even merge sort and hence  $n/2(log(n)-1) + 1 $ comparator gates are required.\newline
+We note that the sorting programs used do not increase the size of the circuit operating on encrypted input bit sequences.
 
@@
 
-\section{Evaluation on the benchmarks}
+\section{Experimental evaluation \\ and analysis}
 \label{Sec:Eval}
@@
 
-\section{Analysis of the results}
-\label{Sec:Analysis}
-Anlayze the results previously obtained and its impact on security and complexity. Comparisions of security-cost tradeoff with other schemes like RSA.
 \section{Conclusion}

### 2013-06-15 Report/article.tex
rap

@@
 \subsection{Intial set-up cost}
-Measurements taken are CPU time, Wall Time, Memory Usage by varying the input size  and the algorithmic parameters. Noise reduction threshold.\\
-Here we estimate the performance of this program in terms of run time for KeyGen, Encrypt, Decrypt and the Min-Max algorithm.
+(Measurements taken are CPU time, Wall Time, Memory Usage by varying the input size  and the algorithmic parameters. Noise reduction threshold).\\
+Here we estimate the performance in terms of run time for KeyGen, Encrypt, Decrypt, Add, Mult, Recrypt.
 

### 2013-06-15 libScarab-1.0.0/test.c
mesure

@@ -56,8 +56,7 @@ void test_suite()
 
 	//test_sum_bits();
 	//mesure_sum_integers();
-
-	test_min_max();
+	//test_min_max();
 	//test_insertion_sort();
 	//test_oddeven_merger_sort();
 	//test_bitonic_sort();
@@ -66,7 +65,7 @@ void test_suite()
 	//test_sum_unbounded();
 	//measure_test_keygen();
 	//test_keygen();
-	//mesure_encrypt_decrypt();
+	mesure_encrypt_decrypt();
 	//essai();
 }
 
@@ -133,46 +132,62 @@ void mesure_encrypt_decrypt(){
 	gettimeofday(&start, NULL);
 	fhe_keygen(pk, sk);
 	gettimeofday(&end, NULL);
-		seconds  = end.tv_sec  - start.tv_sec;
-		useconds = end.tv_usec - start.tv_usec;
-		mtime = ((seconds) * 1000 + useconds/1000.0) + 0.5;
-		printf("time keygen: %ld ms", mtime );
-   
-	for(int i=0; i < 10; i++){
+	seconds  = end.tv_sec  - start.tv_sec;
+	useconds = end.tv_usec - start.tv_usec;
+	mtime = ((seconds) * 1000 + useconds/1000.0) + 0.5;
+	printf("keygen: %ld ", mtime );
+  
+	gettimeofday(&start, NULL);  
+	for(int i=0; i < 100; i++){
 		k= 1 - k;
-		gettimeofday(&start, NULL);    
 		fhe_encrypt(c, pk, k);
-		gettimeofday(&end, NULL);
-		seconds  = end.tv_sec  - start.tv_sec;
-		useconds = end.tv_usec - start.tv_usec;
-		mtime = ((seconds) * 1000 + useconds/1000.0) + 0.5;
-		printf("time encrypt : %ld ms", mtime );
-
-		gettimeofday(&start, NULL);    
-		fhe_fulladd(c, aux1,c,c,aux2, pk);
-		gettimeofday(&end, NULL);
-		seconds  = end.tv_sec  - start.tv_sec;
-		useconds = end.tv_usec - start.tv_usec;
-		mtime = ((seconds) * 1000 + useconds/1000.0) + 0.5;
-		printf("time add : %ld ms", mtime );
-
-		gettimeofday(&start, NULL);    
-		fhe_mul(c,c, c, pk);
[…]

### 2013-06-15 Report/article.tex
rapport

@@
 \subsection{Intial set-up cost}
-(Measurements taken are CPU time, Wall Time, Memory Usage by varying the input size  and the algorithmic parameters. Noise reduction threshold).\\
-Here we estimate the performance in terms of run time for KeyGen, Encrypt, Decrypt, Add, Mult, Recrypt.
+Here we mesure the performance in terms of run time for KeyGen, Encrypt, Add, Mult, Recrypt, Decrypt.\\
+\begin{tabular}{|c|c|c|c|c|c|c|c|}
+  \hline
+  \multicolumn{8}{|c|}{$\mu = 4$} \\
+  \hline
+  N & $log_{2}(p)$ & KeyGen & Encrypt & Add & Mult & Recrypt & Decrypt \\
+  \hline
+  $2^{1}$ & 1.2 & & 1.3 & & & & \\
+  $2^{2}$ & 2.2 & & 2.3 & & & & \\
+  $2^{3}$ & 2.2 & & 2.3 & & & & \\
+  $2^{4}$ & 2.2 & & 2.3 & & & & \\
+  $2^{5}$ & 2.2 & & 2.3 & & & & \\
+  \hline
+\end{tabular}
 
 \textbf{KeyGen}\\
-The measured time execution for KeyGen($N, \mu$)  for fixed values of parameters: $N=8$ and $\mu = 4$ show a variation from 0.2 s to 14.41 s with big density at the interval [0.2s, 1s].
-\begin{comment}
+The measured time execution for KeyGen($N, \mu$)  for fixed values of parameters: $N=8$ and $\mu = 4$ show a variation from 0.2 s to 14.41 s with big density at the interval [0.2s, 2s]\autoref{image_f2}.
+
 \begin{figure}[!h] %on ouvre l'environnement figure
 \centering
-\includegraphics[width=5cm]{f3.eps} 
+\includegraphics[width=5cm]{f3.pdf} 
 \caption{Run time of KeyGen(ms)} 
@@
 \end{figure}
-\end{comment}
 

### 2013-06-15 libScarab-1.0.0/parameters.h
n=8

@@ -12,7 +12,7 @@
 #define PARAMETERS_H
 
 //#define N 8
-#define N 2
+#define N 8
 
 #define MU 4
 

### 2013-06-16 libScarab-1.0.0/integer-fhe.c
varying mu and testing OddEvenSort

@@ -43,7 +43,7 @@ fhe_keygen(fhe_pk_t pk, fhe_sk_t sk)
 		fmpz_to_mpz(temp, fmpz_p);
 		fmpz_clear(fmpz_p);
 	} while (!mpz_probab_prime_p(temp, 10));
-
+//	gmp_printf("Choosing Prime p = %Zd\n", temp);
 #ifdef DEBUG
 	gmp_printf("Choosing Prime p = %Zd\n", temp);
 	printf("Choosing F(x) = ");

### 2013-06-16 libScarab-1.0.0/parameters.h

@@ -14,7 +14,7 @@
 //#define N 8
 #define N 8
 
-#define MU 4
+#define MU 8
 
 
 //#define NU 2**256;

### 2013-06-16 libScarab-1.0.0/test.c

@@ -58,8 +58,8 @@ void test_suite()
 	//test_sum_bits();
 	//mesure_sum_integers();
 	//test_min_max();
-	test_insertion_sort();
-	//test_oddeven_merger_sort();
+	//test_insertion_sort();
+	test_oddeven_merger_sort();
 	//test_bitonic_sort();
 	//test_majority_bit();
 	//test_matrix_prod();
@@ -630,9 +630,9 @@ void OddEvenMergeSort(fmpz_poly_t * poly_nums, int n, int nbits, int lo, int hig
 
 void test_oddeven_merger_sort(){
 	int n = 32;// Nombre d'entiers à trier
-	int nbits = 4;// Size in number of bits
+	int nbits = 6;// Size in number of bits
 	int *list = malloc(sizeof(int)*n); // List d'entiers à trier
-	//int list[]= {3, 6, 10, 6, 5, 6, 2, 2};
+	//int list[]= {8,7,13,2};
 	fmpz_poly_t * poly_nums;
 	poly_nums = malloc(sizeof(fmpz_poly_t) * n);
 	
@@ -832,8 +832,8 @@ void bitonicSortUp(fmpz_poly_t *poly_nums, int  nbits, int n,  int lo , int  hig
 
 
 void test_bitonic_sort(){ // Sorts a bitonic array of 2^n elements
-	int n = 4;// Nombre d'entiers à trier
-	int nbits = 4 ;// Size in number of bits
+	int n = 32;// Nombre d'entiers à trier
+	int nbits = 8 ;// Size in number of bits
 	int *list = malloc(sizeof(int)*n); // List d'entiers à trier
 	
 	fmpz_poly_t * poly_nums;
@@ -859,7 +859,7 @@ void test_bitonic_sort(){ // Sorts a bitonic array of 2^n elements
 	mpz_init(c0);
 	struct timeval start, end;
 	long mtime, seconds, useconds;    
-	for(int obs=0;obs<5;obs++){
+	for(int obs=0;obs<3;obs++){
 	////////////// Encryption of the bit sequennces //////////
 		srand(time(NULL));
 		int mod = (int)pow(2, nbits);
@@ -969,7 +969,7 @@ void test_bitonic_sort(){ // Sorts a bitonic array of 2^n elements
 }
 
 void test_insertion_sort(){   // Generate n random numbers of nbits each and sort them
-	int n = 14;// Nombre d'entiers à trier
[…]

### 2013-06-16 Report/article.tex

@@
 Here we mesure the performance in terms of run time for KeyGen, Encrypt, Add, Mult, Recrypt, Decrypt.\\
+\begin{table}[htb]
+  \centering
+  \caption{Run time (ms)}
+\resizebox{9 cm}{!}{
 \begin{tabular}{|c|c|c|c|c|c|c|c|}
   \hline
-  \multicolumn{8}{|c|}{$\mu = 4$} \\
+  \multicolumn{8}{|c|}{$\mu = 4$ , $\eta = 2^{384}$} \\
   \hline
-  N & $log_{2}(p)$ & KeyGen & Encrypt & Add & Mult & Recrypt & Decrypt \\
+  $N=2^{n}$ & $log_{2}(p)$ & KeyGen & Encrypt & Add & Mult & Recrypt & Decrypt \\
   \hline
-  $2^{1}$ & 1.2 & & 1.3 & & & & \\
-  $2^{2}$ & 2.2 & & 2.3 & & & & \\
-  $2^{3}$ & 2.2 & & 2.3 & & & & \\
-  $2^{4}$ & 2.2 & & 2.3 & & & & \\
-  $2^{5}$ & 2.2 & & 2.3 & & & & \\
+  $2^{1}$ & 764 & 99 & 0.057 & 0.0 & 2.372 & 2.371 & 0.0 \\
+  $2^{2}$ & 1535 & 221 & 0.072 & 0.0 & 	3.012 & 3.023 & 0.001\\
+  $2^{3}$ & 3077 & 1131 & 0.079 & 0.001 & 3.396 & 3.380 & 0.004 \\
+  $2^{4}$ & 6155 & 8560 & 0.135 & 0.002 & 5.881 & 5.889 & 0.012\\
+  $2^{5}$ & 12329 & 852849 & 0.477 & 0.005 & 20.230 & 20.057 & 0.028\\
   \hline
 \end{tabular}
+\normalsize
+\label{common cost}
+}
+\end{table}
 
 \textbf{KeyGen}\\
-The measured time execution for KeyGen($N, \mu$)  for fixed values of parameters: $N=8$ and $\mu = 4$ show a variation from 0.2 s to 14.41 s with big density at the interval [0.2s, 2s]\autoref{image_f2}.
+The measured time execution for KeyGen($N, \mu$)  for fixed values of parameters: $N=8$ and $\mu = 4$ show a variation from 0.2 s to 14.41 s with big density at the interval [0.2s, 2s]\autoref{fig:image_f2}.
 
@@
 \caption{Run time of KeyGen(ms)} 
-\label{image_f2} %l'étiquette pour faire référence à cette image
+\label{fig:image_f2} %l'étiquette pour faire référence à cette image
 \end{figure}
@@
 
-\section{Experimental evaluation \\ and analysis}
+\section{Experimental evaluation and analysis}
 \label{Sec:Eval}

### 2013-06-16 Report/article.tex
alpha version article.tex

@@
 \begin{document}
-\title{Analysis of Security-Cost Trade-off of Fully Homomorphic Encryption Schemes}
-
-%
-% You need the command \numberofauthors to handle the 'placement
-% and alignment' of the authors beneath the title.
-%
-% For aesthetic reasons, we recommend 'three authors at a time'
-% i.e. three 'name/affiliation blocks' be placed beneath the title.
-%
-% NOTE: You are NOT restricted in how many 'rows' of
-% "name/affiliations" may appear. We just ask that you restrict
-% the number of 'columns' to three.
-% Because of the available 'opening page real-estate'
-% we ask you to refrain from putting more than six authors
-% (two rows with three columns) beneath the article title.
-% More than six makes the first-page appear very cluttered indeed.
-%
-% Use the \alignauthor commands to handle the names
-% and affiliations for an 'aesthetic maximum' of six authors.
-% Add names, affiliations, addresses for
-% the seventh etc. author(s) as the argument for the
-% \additionalauthors command.
-% These 'additional authors' will be output/set for you
-% without further effort on your part as the last section in
-% the body of your article BEFORE References or any Appendices.
+\title{Analyzing Security-Cost Trade-off for a \\ Fully Homomorphic Encryption Scheme}
 
@@
 \begin{abstract}
-This paper investigates the feasibility of transformation of a (possibly) non-straight-line program (on unencrypted data) to a straight-line program on encrypted data.
-We present an analysis of security-cost trade-off for homomorphic encryption schemes on such programs.
-Analysis is based on the measurements (CPU time and  Wall time) taken for programs : performing \texttt{XOR} of an $n$-bit sequence, determining the majority bit of an $n$-bit sequence, evaluating the sum of $n$-bit integers, \textcolor{orange}{sum of integers with any number of bits} and sorting $n$ bit sequences of length $nbits$ (requires verifying the validity of a boolean predicate).
+This paper investigates the feasibility of transformation of a (possibly) non-straight-line program (on unencrypted data) into a straight-line program on encrypted data.
+We present an analysis of security-cost trade-off for a homomorphic encryption scheme on such programs.
+Analysis is based on the measurements (CPU time and  Wall time) taken for programs : performing \texttt{XOR} of an $n$-bit sequence,  evaluating the sum of two $n$-bit sequences, determining the majority bit of an $n$-bit sequence, finding the product of two $n \times n$ matrices, and sorting $n$ bit sequences of length $nbits$ (usually requiring validity of a boolean predicate).
 The evaluation is performed on an available implementation ``Scarab library'' of a fully homomorphic encryption scheme.
@@
 
-The notion of \textit{fully homomorphic encryption scheme}, orginally called a \textit{privacy homomorphism} was introduced by Rivest et al.
+The notion of \textit{fully homomorphic encryption scheme}, originally called a \textit{privacy homomorphism} was introduced by Rivest et al.
 \cite{rivest78} shortly after the invention of the RSA by Rivest, Shamir and Adleman \cite{Rivest78amethod}.
@@
 Fully homomorphic encryption scheme extends the above property to addition.
-A Fully homomorphic scheme is a tuple of an ecryption $\mathcal{E}$, decryption $\mathcal{D}$ algorithm together with an efficient algorithm $Eval_\mathcal{E}$ that evaluates any circuit $C$ on any ciphertexts $c_i \leftarrow \mathcal{E}(pk, m_i)$.
-The property that it can evaluate the encryption of addition and multiplication of two plaintexts (without access to the secret key) allows it to arbitrarily compute any function on encrypted data without the decryption key.
+A Fully homomorphic scheme is a tuple of an encryption $\mathcal{E}$, decryption $\mathcal{D}$ algorithm together with an efficient algorithm $Eval_\mathcal{E}$ that evaluates any circuit $C$ on any cipher-texts $c_i \leftarrow \mathcal{E}(pk, m_i)$.
+The property that it can evaluate the encryption of addition and multiplication of two plain-texts (without access to the secret key) allows it to arbitrarily compute any function on encrypted data without the decryption key.
 However prior to \cite{homenc}, we did not have a viable construction.
@@
 The immediate question that is raised, is how do we perform the transformation and how does the circuit size change to adapt to computations on encrypted data.
-We provide answer to this question by analyzing circuit complexity for finding the minimum-maximum of two $n$-bit sequences in \autoref{sec:ex} and for some other opertation in \autoref{sec:bm}.
-Moreover, the cost of evaluation depends on the depth of the circuit representing the $Eval_{\mathcal{E}}$ function.
+We provide answer to this question by analyzing circuit complexity for finding the minimum-maximum of two $n$-bit sequences in \autoref{sec:ex} and for some other operations in \autoref{sec:bm}.
+Moreover, the cost of evaluation increases with the depth of the circuit representing the $Eval_{\mathcal{E}}$ function.
 Some researchers have improved and proposed other schemes such as \cite{cryptoeprint:2009:571} and \cite{cryptoeprint:2011:277} which decrease the circuit complexity.
-In \autoref{Sec:Eval} we expermentally evaluate an implementation of  \cite{cryptoeprint:2009:571} and analyze the cost-security trade-off for $Eval_{\mathcal{E}}$ varying from \texttt{XOR} of the bits of an $n$ bit integer to sum of bounded and unbounded integers to sorting of $n$ integers.
+In \autoref{Sec:Eval} we experimentally evaluate an implementation of  \cite{cryptoeprint:2009:571} and analyze the cost-security trade-off for $Eval_{\mathcal{E}}$ varying from \texttt{XOR} of the bits of an $n$ bit integer to sum of two $n$ bit sequences to sorting of $n$ sequences of $nbits$ each.
 Three different sorting algorithms are tested.
-Through these experiments, we also provide information on the additional cost to be paid (for these computations) to increase the security of the cyptosystem.
+Through these experiments, we also provide information on the additional cost to be paid (for these computations) when security of the cryptosystem is increased.
 
@@
 The homomorphic encryption scheme proposed by Gentry \cite{homenc} is based on ideal lattices.
-The Gentry's non-determi-nistic scheme builds on a \textit{somewhat homomorphic} scheme which can perform additions and multiplications on encrypted data till a bounded depth.
+The Gentry's non-deterministic scheme builds on a \textit{somewhat homomorphic encryption}(SWHE) scheme which can perform additions and multiplications on encrypted data till a bounded depth.
 The non-determinism introduced in the form of a noise renders the scheme secure.
-But, the noise increases with the depth  of the evaluation circuit.
+But, the noise increases with the depth  of the evaluation circuit and hence the decryption algorithm fails to produce the correct plain-text after a certain depth.
 To counter this problem, Gentry introduces \textit{bootstrapping} technique which ensures unbounded depth operatability of the scheme.
-Smart Vercauteren \cite{cryptoeprint:2009:571} have proposed an integer based approach and we use one of its implementation detailed in \cite{perl:poster} for our experiments.
+Smart Vercauteren \cite{cryptoeprint:2009:571} have proposed an integer based approach and we use one of its implementations detailed in \cite{perl:poster} for our experiments.
 
@@
 
-The scheme proposed in \cite{cryptoeprint:2009:571} has 3 parameters:($N, \nu, \mu$ ).
+The scheme proposed in \cite{cryptoeprint:2009:571} has 3 parameters :($N, \nu, \mu$ ).
 The somewhat homomorphic scheme uses 5 algorithms: (\texttt{KeyGen}, \texttt{Encrypt}, \texttt{Decrypt}, \texttt{Add}, \texttt{Mult}).
 Algorithm \autoref{Code:SV} presents the \texttt{KeyGen} algorithm.
+This scheme will be referred to as SV scheme in this paper.
 
@@
  \; $C(x)=m+2\cdot R(x)$ 
-\newline \phantom{x}\hspace{3ex} return  $c=C(\alpha)$ mod $p$
+\newline \phantom{x}\hspace{3ex} return  $c=C(\alpha)$ mod $p$;
 \newline \texttt{Decrypt}($c, sk$):
 \newline \phantom{x}\hspace{3ex} $m = (c - \lfloor c \cdot B/p \rceil )$ mod $2$;
-\phantom{x}\hspace{1ex} return $m$
+\phantom{x}\hspace{1ex} return $m$;
 \newline \texttt{Add}($c_1$, $c_2$, $pk$):
-\newline \phantom{x}\hspace{3ex} $c_3=c_1+c_2$ mod $p$
-;  \phantom{x}\hspace{1ex}  return $c_3$
-;
+\newline \phantom{x}\hspace{3ex} $c_3=c_1+c_2$ mod $p$; 
+\phantom{x}\hspace{1ex}  return $c_3$;
 \newline \texttt{Mult}($c_1$, $c_2$, $pk$):
- \newline \phantom{x}\hspace{3ex}  $c_3=c_1.c_2$ mod $p$
- ; \phantom{x}\hspace{1ex}  return $c_3$
-;
+ \newline \phantom{x}\hspace{3ex}  $c_3=c_1.c_2$ mod $p$; 
+\phantom{x}\hspace{1ex}  return $c_3$;
 
-\textbf{Security of the scheme} The scheme is semantically secure under the assumption that the \textit{Polyomial Coset Problem} is hard.
-One wayness of the encryption is believed to be true under the assumption that the \textit{Bounded distance decoding problem} BDDP is hard while key recovery is assumed to be difficult under the assumption that the \textit{Small Principal Ideal Problem} is hard.
+\textbf{Security of the scheme :} The scheme is semantically secure under the assumption that the \textit{Polynomial Coset Problem}(PCP) is hard.
+One wayness of the encryption is believed to be true under the assumption that the \textit{Bounded distance decoding problem} BDDP is hard while key recovery is assumed to be difficult under the assumption that the \textit{Small Principal Ideal Problem}(SPIP) is hard.
 Solutions to all of these problems have either a sub-exponential algorithm or in general take exponential time.
@@
 
-\textbf{SWHE to FHE :} We recall that the authors have proved that the multiplicative depth $d$ of SWHE  verifies \[d \cdot log(2) \leq log( log(\frac{\nu}{2\cdot \sqrt{N}}) ) - log(log( N\mu))\]
+\textbf{SWHE to FHE :} We recall that the authors of the scheme have proved that the multiplicative depth $d$ of SWHE scheme verifies: \[d \cdot \mathrm{log}(2) \leq  \mathrm{log}\left( \mathrm{log}\left(\frac{\nu}{2\cdot \sqrt{N}}\right) \right) - \mathrm{log}\left(\mathrm{log}\left( N\mu\right)\right)\]
 when $F(x)= x^N+1$.
-Turning the SWHE to FHE is achieved by recasting Gentr's method for the parameters of this scheme.
-To achive this the authors propose to generate $s_1$ uniformly random integers $B_i$ in $[-p, \ldots, p]$ such that there exists a subset $S$ of $s_2$ elements with $\sum_{j \in S}{B_j}= B$ over integers.
-By defining $sk_i =1$ iff $i\in S$ and taking $c_i=Encrypt(sk_i,pk)$ we generate a new public key which contains hint of the secret key $sk$.
-The public key now comprises of \[(p, \alpha, s_1, s_2, \{c_i, B_i\}_{i=1}^{s1})\].
+Turning the SWHE to FHE is achieved by recasting Gentry's method for the parameters of this scheme.
+To achieve this, the authors propose to generate $s_1$ uniformly random integers $B_i$ in $[-p, \ldots, p]$ such that there exists a subset $S$ of $s_2$ elements with $\sum_{j \in S}{B_j}= B$ over integers.
+By defining $sk_i =1$ iff $i\in S$ and taking $c_i=\texttt{Encrypt}(sk_i,pk)$ we generate a new public key which contains hint of the secret key $sk$.
+The public key now comprises of \[(p, \alpha, s_1, s_2, \{c_i, B_i\}_{i=1}^{s1})\]
+To ensure that the hint does not provide any considerable advantage to an attacker, the underlying \textit{sparse subset-sum problem} SSSP must remain remain hard.
+If we take $s_1$ to be slightly greater than $p$, then we need to select $s_2$ such that $\sqrt {{s_1}  \choose {s_2} } \leq 2 ^{N/\lambda}$ so as to ensure that SSSP difficulty is at least as difficult as the difficulty of the BDDP underlying the SWHE scheme.
 
-To ensure that the hint doesn't provide considerable advantage to an attacker, the underlying \textit{sparse subset-sum problem} SSSP must remain remain hard.
-If we take $s_1$ to be slightly greater than $p$, then we need to select $s_2$ such that $\sqrt {{s_1}  \choose {s_2} } \leq 2 ^{N/\lambda}$ so as to ensure that SSSP difficulty is at least as difficult as the difficulty of the BDDP underlying the SWHE scheme.
 \subsection{Considered Implementations}
-We used the open source implementation Scarab library \cite{hcrypt}  version $1.0.0$ of the Smart-Vercauteren scheme and is a part of \textsc{hcryptProject}.
+We used the open source implementation Scarab library \cite{hcrypt}  version $1.0.0$ of the Smart-Vercauteren scheme which is a part of \textsc{hcryptProject}.
 The implementation is in beta version.
-The software requires GMP \cite{gmp}, The GNU Multiple Precision Arithmetic Library; FLINT \cite{flint} , Fast Library for Number Theory; MPIR \cite{mpir}, Multiple Precision Integers and Rationals and MPFR \cite{mpfr}, multiple-precision floating-point computations with correct rounding.
+The software requires GMP(we tested with version $5.1.2$) \cite{gmp} : GNU Multiple Precision Arithmetic Library; FLINT version $1.6$ \cite{flint}: Fast Library for Number Theory; MPIR (we tested with $2.6.0$) \cite{mpir} : Multiple Precision Integers and Rationals and MPFR (tested with version $3.1.2$) \cite{mpfr} :  Multiple-Precision Floating-point computations with correct Rounding.
 Linux is supposed to be the only supported platform.
-The libraries are in implemented in  C and the installation guide is provided with the package.
+The libraries are implemented in  C and an installation guide is provided with the package.
+
 \autoref{funs} presents the list of functions provided by the implementation with their description.
-The library provides a file \texttt{test.c} where a user can write his own function to test different operations.
+The library provides a file \texttt{test.c} where a user can write his own functions to test different operations.
+It also provides a header file \texttt{parameters.h} to set the parameters $N, \nu, \mu, s_1$ and $ s_2$ of the cryptosystem.
+To simplify our computational circuit, we added two basic functions \texttt{or(mpz\_t res, mpz\_t a, mpz\_t b, fhe\_pk\_t pk);} and \texttt{not(mpz\_t res, mpz\_t a, fhe\_pk\_t pk);} which compute the logical \texttt{or}(+) of encrypted bits and the negation ($\neg$) of an encrypted bit respectively.
+
 \begin{table*}
-\caption{Function available in Scarab}
+\centering
+\caption{Functions available in Scarab}
 \begin{tabular}{|l|l||}
@@
 \texttt{fhe\_recrypt(mpz\_t c, fhe\_pk\_t pk, fhe\_sk\_t sk); }	&Recrypt a cyphertext ( ``refreshing'' it) \\
-\texttt{fhe\_add(mpz\_t res, mpz\_t a, mpz\_t b, fhe\_pk\_t pk);} &	Add cyphertexts (= XOR) \\
-\texttt{fhe\_mul(mpz\_t res, mpz\_t a, mpz\_t b, fhe\_pk\_t pk);} &	Multiply cyphertexts (= AND) \\
+\texttt{fhe\_add(mpz\_t res, mpz\_t a, mpz\_t b, fhe\_pk\_t pk);} &	Add cypher-texts (= XOR) \\
+\texttt{fhe\_mul(mpz\_t res, mpz\_t a, mpz\_t b, fhe\_pk\_t pk);} &	Multiply cypher-texts (= AND) \\
 \texttt{fhe\_fulladd(mpz\_t sum, mpz\_t c\_out, mpz\_t a, mpz\_t b,} &	Add with carry in and carry out \\
@@
 
-To simplify out computational circuit added, we added two basic functions \texttt{or(mpz\_t res, mpz\_t a, mpz\_t b, fhe\_pk\_t pk);} and \texttt{not(mpz\_t res, mpz\_t a, fhe\_pk\_t pk);} which compute the logical or of encrypted bits and the negation of an encrypted bit respectively.
+We time the various algorithms on two desktop machines.
+Both these machines were x86-64 platform running Linux kernel $3.2.0$-$45$-generic  and used GCC $4.6.3$ C compiler.
+The first machine housed Intel Core i3 M330 (2.13GHz x 4) processor and will be referred in this article as machine M1 while the other used  housed Intel Core i5 M2430 (2.40GHz x 4) processor and will be referred as machine M2.
+During the experiments these machines were not connected to any network and were running ony the most needed applications.
 
-We time the various algorithms on two desktop machines.
-Both these machines were x86-64 platform running linux kernel $3.2.0$-$45$-generic  and used GCC $4.6.3$ C compiler.
-The first machine housed Intel Core i3 M330 (2.13GHz x 4) processor and will be referred in this article as machine M1 while the other used  housed Intel Core i5 2430 M(2.40 x4) processor and will be referred as machine M2.
-
-\subsection{Intial set-up cost}
+\subsection{Initial set-up cost}
 Here we mesure the performance in terms of run time for KeyGen, Encrypt, Add, Mult, Recrypt, Decrypt.\\
@@
 \textbf{Encryption and Decryption}\\
-
 \section{Circuit Transformation}
-As previously discussed, a user sends his program which works on unencrypted data and his encrypted input to the cloud.
-The cloud then performs the demanded computation and returns the result.
+As previously discussed, a user sends his program which runs on unencrypted data and his encrypted input to the cloud.
+The cloud then performs the demanded computation and returns the encrypted result.
 However, the program in the same form cannot always be used for computations on encrypted data.
 
-Consider a program involves the following test on two inputs : \texttt{if(a > b) instruction\_1; else instruction\_2;}.
-As the cloud does not know the result of the test\texttt{ a' > b'} where \texttt{a'} and \texttt{b'} are the encryptions of \texttt{a} and \texttt{b}, he does not know which of the instructions he has perform.
-In fact he performs both the instrunctions by transforming the actual program into : \texttt{test(a'> b')*} \texttt{instruction\_1 +}$\neg$\texttt{test(a'> b')*instruction\_2}, where \texttt{test()}  is a function on encrypted inputs \texttt{a'}, \texttt{b'} and returns an encryption of $1$ iff \texttt{a > b}.
-Hence, if the program used has braching i.e.
-it involves \texttt{if(cond\_0)} \texttt{\{inst\_0\} else if(cond\_1)\{inst\_1\}}\linebreak \texttt{ ...else if(cond\_n-2) \{inst\_n-2\}} \texttt{else\{inst\_n-1 \}}; the cloud has to perform all the $n$ instructions i.e.
+Consider a program which involves the following test on two inputs : \texttt{if(a > b) instruction\_1; else instruction\_2;}.
+As the cloud does not know the result of the test\texttt{ a' > b'} where \texttt{a'} and \texttt{b'} are the encryption of \texttt{a} and \texttt{b}, he does not know which of the instructions he has perform.
+In fact, he performs both the instructions by transforming the actual program into : \texttt{test(a'> b')*} \texttt{instruction\_1 +}$\neg$\texttt{test(a'> b')*instruction\_2}, where \texttt{test()}  is a function on encrypted inputs \texttt{a'}, \texttt{b'} and returns an encryption of $1$ iff \texttt{a > b}.
+Hence, if the program used has branching i.e.
+it involves \texttt{if(cond\_0)} \texttt{\{inst\_0\} else if(cond\_1)\{inst\_1\}} \texttt{ ...else if(cond\_n-2) \{inst\_n-2\}} \texttt{else\{inst\_n-1 \}}; the cloud has to perform all the $n$ instructions i.e.
 the size of the circuit changes from a constant size to a size linear in the number of tests.
@@
 \newline  \phantom{x} \texttt{res = f(i)};\\
-In this case, the cloud needs to transform a loop with condititonal stopping into a loop with unconditional branching. We propose the following possible transformation : \\
+In this case, the cloud needs to transform a loop with conditional stopping into a loop with unconditional branching. We propose the following transformation : \\
  \phantom{x} \texttt{endLoop=0', res=0', i=0;}
@@
 
-\textbf{Correctness of the code :} If \texttt{cond\_i} is always \texttt{true}, \texttt{endLoop} is always false hence the \texttt{res=f(n)}.
-If at the $t^{th}$iteration, \texttt{cond\_i} is \texttt{false}, \texttt{endLoop} becomes \texttt{false} and hence \texttt{res} contains its previous value $f(t-1)$.
+\textbf{Correctness of the code :} If \texttt{cond\_i} is always \texttt{true}, \texttt{endLoop} is always \texttt{false} and \texttt{res=f(n)}.
+If at the $t^{th}$ iteration, \texttt{cond\_i} is \texttt{false}, \texttt{endLoop} becomes \texttt{true} and hence \texttt{res} contains its previous value $f(t-1)$.
 
@@
 \label{sec:ex}
-
-We suppose that a user wants to find the maximum and the minimum of two $n$-bit sequences $a = (a_0,a_1,\ldots, a_{n-1})$, $b=(b_0,b_1,\ldots, b_{n-1})$.
+Suppose that a user wants to find the maximum and the minimum of two $n$-bit sequences $a = (a_0,a_1,\ldots, a_{n-1})$, $b=(b_0,b_1,\ldots, b_{n-1})$ where $a_0$ is the highest significant bit.
 He provides the following algorithm to the cloud :
@@
 
- \caption{Min-Max on ciphertext \label{Code:algo}}
+ \caption{Min-Max on cipher-text \label{Code:algo}}
 
@@
 
-Consider $x_i = a_ib_i+\neg(a_i)\neg(b_i) $.
-$x_i$ is $1$ iff $a_i$ and $b_i$ are equal.
-We note that, $bitEqual$ is the product of $x_i$ and is $1$ at the $t^{th}$ iteration iff $a_i=b_i$ for $i < t$.
-The term $\neg(b_i)a_i$ is $1$ iff $a_i=1$ and $b_i =0$.
+  Consider $x_i = a_i'b_i'+\neg(a_i')\neg(b_i') $.
+$x_i$ is $1$ iff $a_i'$ and $b_i'$ are equal.
+We note that, $bitEqual$ is the product of $x_i$ and is $1$ at the $t^{th}$ iteration iff $a_i'=b_i'$ for all $i < t$.
+The term $\neg(b_i')a_i'$ is $1$ iff $a_i'=1$ and $b_i'=0$.
 Hence at the $t^{th}$ iteration, the algorithm using $bitEqual$ tests if the previous bits were equal.
-Hence, $aIsGreater$ is $1$ iff at any stage  $a_t\neg(b_t)=1$ and the previous bits were equal.
+Hence, $aIsGreater$ is $1$ iff at any stage  $\neg(b_t')a_t'=1$ and the previous bits were equal.
 
@@
 \end{proof}
-\textbf{Theoretical Cost:} Algorithm \autoref{Code:algo} uses $n$ \texttt{AND} gates, $n$ \texttt{OR} gates and $n$ \texttt{NOT} gates to find the larger of the two bit sequences and then to regenerate the maximum and the minuimum $4n$ \texttt{AND} gates and $2n$ \texttt{NOT} and \texttt{OR} gates.
+\textbf{Theoretical Cost :} Algorithm \autoref{Code:algo} uses $5n$ \texttt{AND} gates, $2n$ \texttt{OR} gates and $2n$ \texttt{NOT} gates to find the larger of the two bit sequences and then to regenerate the maximum and the minimum $4n$ \texttt{AND} gates and $2n$ \texttt{NOT} and \texttt{OR} gates.
 We note that reconstruction of Max and  Min is not required when working on non-encrypted data.
@@
 \end{comment}
-The cost of this algorithm on ciphertext is linear with bit number, like  the algorithm on plaintext, the extra cost in this case is encryption-decryption cost and especially the code generation which is very inpreductible and take often a long time in the SV-Scheme.
+The cost of this algorithm on cipher-text is linear with bit number, like  the algorithm on plain-text, the extra cost in this case is encryption-decryption cost and especially the code generation which is very unpredictable and take often a long time in the SV scheme.
 
@@
 We propose a set of benchmark functions to evaluate the implementations.
-These functions can be categorized into three classes : functions operating on bits, \textcolor{orange}{functions operating directly on integers or block of bits} and functions where branching is usually required i.e \texttt{if-then-else} condition is evaluated.
+These functions can be categorized into three classes : functions operating on bits, functions operating on block of bits and functions where branching is usually required i.e \texttt{if-then-else} condition is evaluated.
 
-Functions operating on bits provide information on the security-cost tradeoff for bitwise operations, \textcolor{orange}{while when operating directly on integers}, the tradeoff is obtained as a function of the size of integers.
-The first two categories of functions with straight-line programs on non-encrypted data can directly be translated to operate on encrypted bits.
-For others, evaluation of \texttt{if-then-else} condition on encrypted data is choosen.
+Functions operating on bits provide information on the security-cost trade-off for bit-wise operations.
+The first two categories of functions have straight-line programs on non-encrypted data and hence can directly be translated to operate on encrypted bits.
+For others, evaluation of \texttt{if-then-else} condition on encrypted data is chosen.
 In this case, a circuit(program) transformation is required and which often makes the size longer than the one on non-encrypted data.
-Hence, this provides information on increase in size of the circuit(when passing from non-encrypted to enrypted data) and the associated trade-off.
-We study the security-cost tradeoff for the following problems :
+Hence, this provides information on increase in size of the circuit(when passing from non-encrypted to encrypted data) and the associated trade-off.
+We study the security-cost trade-off for the following problems :
 
 1. \textbf{XOR of an $n$-bit sequence}\\
-2. \textbf{Sum of :}  
-\newline\noindent
-\phantom{x}\hspace{3ex} a) integers having $n$ bits 
- \textcolor{orange}{b) integers having arbitrary
-\newline \phantom{x}\hspace{6ex}  number of bits}\\ 
+2. \textbf{Sum of :}  two $n$ bit sequences  \newline 
 3. \textbf{Majority bit of an $n$-bit sequence} \\
-4. \textbf{Product of two $n\times n$ matrices} \\
-5. \textbf{Sorting of $n$ sequences of $nbits$: } \newline\noindent
-\phantom{x}\hspace{3ex} a) Insertion sort c) Bitonic sort \\
-	\phantom{x}\hspace{3ex} 	     b) Odd-Even Merge sort
+4. \textbf{Product of two $n\times n$ boolean matrices} \\
+5. \textbf{Sorting of $n$ sequences of $nbits$ using :} \newline\noindent
+\phantom{x}\hspace{3ex} a) Insertion sort \phantom{x}\hspace{2ex} b) Bitonic sort \\
+	\phantom{x}\hspace{3ex} 	     c) Odd-Even Merge sort
 
@@
 \subsection{Size of Evaluation Circuit}
-As the implementations provide addition and multiplicaion of ciphertexts,  size in terms of \texttt{XOR} and \texttt{AND} gates are provided for each problem.
+As the implementations provide addition and multiplication of cipher-texts,  size in terms of \texttt{XOR} and \texttt{AND} gates are provided for each problem.
 
-\textbf{XOR of $n$-bits :} \texttt{XOR} of $n$-bits requires $n-1$ \texttt{XOR} gates. \newline
-\textbf{Sum of integers of $n$-bits :} Sum of two integers is performed using an $n$ \texttt{full-adder} circuits.
+\textbf{XOR of $n$-bits :} \texttt{XOR} of $n$-bits requires $n-1$ \texttt{XOR} gates. \newline \newline
+\textbf{Sum of two $n$-bit sequences :} Sum of two $n$-bits sequences is performed using $n$ \texttt{full-adder} circuits (provided as \texttt{fhe\_fulladd(...)} function in the Scarab library).
 The cost of a full adder circuit is $2$ \texttt{XOR} to calculate the sum and $2$ \texttt{AND}, $1$ \texttt{XOR} and $1$ \texttt{OR} for the carry.
 Hence the total complexity is $3n$ \texttt{AND}, $5n$ \texttt{XOR}.
-\newline
-\textcolor{orange}{\textbf{Sum of arbitrary integers}} \newline
-\textbf{Majority of $n$-bits :} Majority bit is evaluated by obtaining the sum of the bits and then returning the result of the comparision of the sum and $n/2$. \newline \newline
-\textbf{Product of two $n\times n$ matrices}: This resquires $n^3$ \texttt{AND} gates and \texttt{$n^2(n-1)$} \texttt{XOR} gates. \newline \newline
-\textbf{Sorting} Several straight-line programs for sorting have have been proposed in litterature \cite{dk}, \cite{Batcher:1968:SNA:1468075.1468121}.
-These programs use a comparator gate : a logical gate with two inputs and two ouputs, that computes the minimum and maximum of two $n$ bit sequences.
-Algorithm \autoref{Code:algo} implements a comparator gate.
-Hence we do not need to perform any transformation for these algorithms.
+\newline \newline
+\textbf{Majority of $n$-bits :} Majority bit is evaluated by obtaining the sum of the bits and then returning the result of the comparison of the sum and $n/2$.
+This comparison is done using algorithm \autoref{Code:algo}.
+The operation is interesting in the sense that if the same program is evaluated on the user's side, he has to store the sum of the bits, hence  needs $\mathrm{\lfloor\log_{2}n \rfloor +1}$ bits of memory.
+However, if he performs the operation remotely on a cloud, he only requires a constant number of bits to retrieve the result.
+\newline \newline
+\textbf{Product of two $n\times n$ matrices :} This requires $n^3$ \texttt{AND} gates and \texttt{$n^2(n-1)$} \texttt{XOR} gates. \newline \newline
+\textbf{Sorting :} Several straight-line programs for sorting have have been proposed in literature \cite{dk}, \cite{Batcher:1968:SNA:1468075.1468121}.
+These programs use a comparator gate : a logical gate with two inputs and two outputs, that computes the minimum and maximum of two $n$ bit sequences.
+Algorithm \autoref{Code:algo} implements such a comparator gate.
+We do not need to perform any transformation for these algorithms.
+The algorithms used for Bitonic and Odd-Even merge sort are provided in the appendix.
+They accept $n$ which are powers of $2$.
 \newline \newline
 \textbf{Insertion sort :} When allowing for parallel comparators, bubble sort and insertion sort are identical. Hence $n(n-1)/2$ comparator gates are used for insertion sort.\newline \newline
-\textbf{Bitonic Sort :} \autoref{bitsort} and \autoref{bitmerge} are used to perform Bitonic Sort. The algorithm use $log(n) · (log(n)+1) / 2 $ gates are required. \newline \newline
-\textbf{Odd-Even Merge sort :} \autoref{oesort} and \autoref{oemerge} are used to perform Odd-Even merge sort and hence  $n/2(log(n)-1) + 1 $ comparator gates are required.\newline
+\textbf{Bitonic Sort :} \autoref{bitsort} and \autoref{bitmerge} are used to perform Bitonic Sort. The algorithm uses $\mathrm{log}(n)·(\mathrm{log}(n)+1)/2$ comparator gates. \newline \newline
+\textbf{Odd-Even Merge sort :} \autoref{oesort} and \autoref{oemerge} are used to perform Odd-Even merge sort and hence  $n(\mathrm{log}^{2}(n)-1)/2 + 1 $ comparator gates are required.\newline
 We note that the sorting programs used do not increase the size of the circuit operating on encrypted input bit sequences.
 
-\lstset{                                    % line wrapping on
-  language=C,
-  frame=lines,
-  captionpos=b
+\section{Experimental evaluation \\ and results}
+\label{Sec:Eval}
+
+\begin{figure}[t] %on ouvre l'environnement figure
+\centering
+\includegraphics[width=7cm]{fsort1.pdf} 
+\caption{Run time of KeyGen(ms)} 
+\label{fig:image_f2} %l'étiquette pour faire référence à cette image
+
+\centering
+\includegraphics[width=7cm]{fsort2.pdf} 
+\caption{Run time of KeyGen(ms)} 
+\label{fig:image_f2} %l'étiquette pour faire référence à cette image
+\centering
+\includegraphics[width=7cm]{fsort3.pdf} 
+\caption{Run time of KeyGen(ms)} 
+\label{fig:image_f2} %l'étiquette pour faire référence à cette image
+\end{figure}
+
+\begin{figure}[t] %on ouvre l'environnement figure
+\centering
+\includegraphics[width=7cm]{fsort4.pdf} 
+\caption{Run time of KeyGen(ms)} 
+\label{fig:image_f2} %l'étiquette pour faire référence à cette image
+\end{figure}
+
+\begin{figure}[t] %on ouvre l'environnement figure
+\centering
+\includegraphics[width=7cm]{fsort5.pdf} 
+\caption{Run time of KeyGen(ms)} 
+\label{fig:image_f2} %l'étiquette pour faire référence à cette image
+\end{figure}
+
+\begin{figure}[t] %on ouvre l'environnement figure
+\centering
+\includegraphics[width=7cm]{fsort6.pdf} 
+\caption{Run time of KeyGen(ms)} 
+\label{fig:image_f2} %l'étiquette pour faire référence à cette image
+\end{figure}
+
+\begin{figure}[t] %on ouvre l'environnement figure
+\centering
+\includegraphics[width=7cm]{fsort7.pdf} 
+\caption{Run time of KeyGen(ms)} 
+\label{fig:image_f2} %l'étiquette pour faire référence à cette image
+\end{figure}
+
+\begin{figure}[t] %on ouvre l'environnement figure
+\centering
+\includegraphics[width=7cm]{fsort8.pdf} 
+\caption{Run time of KeyGen(ms)} 
+\label{fig:image_f2} %l'étiquette pour faire référence à cette image
+\end{figure}
+
+ \textbf{Sorting :} 
+The experiments on the sorting algorithms were performed on the machine M1.
+For each test, $5-10$ random samples were taken.
+These were generated using the Unix \texttt{rand()} function by setting the seed using \texttt{srand(time(NULL))}.
+
+Intially, the cryptographic parameters were set to $(N = 8, \nu = 2^{384}, \mu = 4, s_1 = 8, s_2 = 5)$ which is the default setting in the software.
+The \textcolor{orange}{above figures} show the variation of CPU time and Wall time with the increase in the number of sequences to sort and the number of bits.
+These experiments were done for Insertion Sort algorithm.
+We also present a  curve fitting plot that verifies the quadratic complexity of this algorithm.
+
+\begin{table}
+\caption{Wall time for Bitonic Sort}
+\resizebox{8cm}{!}{
+
+\begin{tabular}{|l|l|l||}
+  \hline
+  (Number of sequences,  & Maximum time (in ms) & Minimum time (in ms) \\
+  Number of bits) &  &    \\
+  \hline
+  (4,4)  &  34584 & 32759\\
+  (8,4)  &  189685 & 130157\\
+  (16,4) &  635705 &  438146\\
+  (32,4) &  1315663 & 1313082\\
+  (4,6)  &  49668 & 49038 \\
+  (8,6)  & 197853 & 196183 \\
+  (16,6) & 667521 & 656369 \\
+  (32,6) & 1976534 & 1946724 \\ 
+ \hline
+\end{tabular}
+\label{bitonicsort}
 }
+\end{table}
 
-\renewcommand{\lstlistingname}{Code}
+\begin{table}
+\caption{Wall time for Odd-Even Merge Sort}
+\resizebox{8cm}{!}{
 
-\section{Experimental evaluation and analysis}
-\label{Sec:Eval}
-Measurements by varying the parameters or the plaintext size.
+\begin{tabular}{|l|l|l||}
+  \hline
+  (Number of sequences,  & Maximum time (in ms) & Minimum time (in ms) \\
+  Number of bits) &  &    \\
+  \hline
+  (4, 4) & 28363 & 27321  \\
+  (8, 4)  & 158674 & 120868 \\
+  (16,4) & 459895  & 340981  \\
+  (32,4) & 1043093 &  1041674 \\
+  (4,6) & 41350 & 41204 \\
+  (8,6) & 158272  &156721 \\
+  (16,6) & 543735 & 520719 \\
+  (32,6) & 1638711 & 1594432 \\
+\hline
+\end{tabular}
+\label{OddEvensort1}
+}
+\end{table}
 
-\begin{figure}[!h] %on ouvre l'environnement figure
-\centering
-\includegraphics[width=8cm]{./Insertion_sort_CPU.jpg} 
-\caption{Run time of } 
-\label{image_f2} %l'étiquette pour faire référence à cette image
-\end{figure}
-\
+\autoref{bitonicsort}, \autoref{OddEvensort1} justify the fact that Odd-Even Merge algorithm performs better than the Bitonic sort(even though they have the same worst case complexity) as it uses less number of comparator gates.
+We further remark that for small values, Insertion sort performs better than Bitonic, but we estimate that for $32$ sequences of $4$ bits each, Bitonic search would be faster.
+This estimate comes from the fact that the insertion sort would cost $16$ times the cost of sorting only $8$ such sequences i.e.
+around $3000000$ ms.
+This is experimentally confirmed by the obtained value : 3639429 which is thrice the time = 1315663 taken by Bitonic sort.
 
-%\begin{figure*}
+\begin{table}
+\caption{Wall time for Odd-Even Merge Sort}
+\resizebox{8cm}{!}{
 
-%\incudegraphics{"/home/honey/Documents/Mosig\_1/ProjSpec/Measurements\Insertion\_sort\_CPU.jpg"}
+\begin{tabular}{|l|l|l||}
+  \hline
+  (Number of sequences,  & Maximum time (in ms) & Minimum time (in ms) \\
+  Number of bits) &  &    \\
+  \hline
+  (4, 4) &  27958 & 27455\\
+  (8, 4)  &    108197  & 103683\\
+  (16,4) &   354188 &  341522\\
+  (32,4) &  1587427 &  1044640\\
+  (32,6) &   1629722 & 610464\\
+\hline
+\end{tabular}
+\label{OddEvensort2}
+}
+\end{table}
 
-%\end{figure*}
+When we increase the security of the system by setting the parameters to  $(N = 256, \nu = 16, \mu = 2, s_1 = 5000, s_2 = 5)$(as suggested in \cite{cryptoeprint:2009:571}) which ensures $25$ bits of security, the Odd-Even sorting algorithm on  $4$ sequences, each of $4$ bits takes hours.
+By lowering the security level to only $8$ bits using the parameters :$(N = 16, \nu = 32, \mu = 2, s_1 = 85, s_2 = 5)$, the result did not decrypt to the desired output; which we believe is an implementation bug in the bootstrapping mechanism.
+However, by increasing $\mu$ also increases security, and setting the parameters to :  $(N = 8, \nu = 2^{384}, \mu = 8, s_1 = 8, s_2 = 5)$ we obtained the results as in \autoref{OddEvensort2} :
+\section{Conclusion}
 
-\section{Conclusion}
+With the examples and the programs discussed, we conclude that the tranformation of a non-straight line programs(with branching) in general increases the circuit complexity.
+The experiments on the implementation and the operations ........
+\pagebreak
 
@@
 
-%\begin{comment}
-\newpage
 \section{Appendix}
-
 The programs used for Odd-Even Merge sort and Bitonic sort are provided below : 
-
 \begin{figure}[h]
@@
         }
+\end{lstlisting}
 
-\end{lstlisting}
 \caption{Odd-Even Merge Sort : sort from index lo to n }

### 2013-06-16 libScarab-1.0.0/integer-fhe.c
With sorting datas

@@ -43,7 +43,7 @@ fhe_keygen(fhe_pk_t pk, fhe_sk_t sk)
 		fmpz_to_mpz(temp, fmpz_p);
 		fmpz_clear(fmpz_p);
 	} while (!mpz_probab_prime_p(temp, 10));
-//	gmp_printf("Choosing Prime p = %Zd\n", temp);
+	gmp_printf("Choosing Prime p = %Zd\n", temp);
 #ifdef DEBUG
 	gmp_printf("Choosing Prime p = %Zd\n", temp);
 	printf("Choosing F(x) = ");

### 2013-06-16 libScarab-1.0.0/parameters.h

@@ -14,16 +14,16 @@
 //#define N 8
 #define N 8
 
-#define MU 8
+#define MU 4
 
 
 //#define NU 2**256;
 
 //#define LOG_NU 384
 //#define LOG_NU 310
-#define LOG_NU 384
+#define LOG_NU 8
 
-#define S1 8
+#define S1 65
 #define S2 5
 #define T  5 // Ceiling[Log[2, S2]] + 2
 #define S  3 // Floor[Log[2, s2]] + 1

### 2013-06-16 libScarab-1.0.0/test.c

@@ -34,9 +34,10 @@
 
 
 void test_keygen();
-void mesure_matrix_prod();
+
 void mesure_sum_integers();
 void mesure_encrypt_decrypt();
+//void mesure_decrypt();
 void measure_test_keygen(){
 	for(int i=0; i< 40; i++) test_keygen();
 }
@@ -58,10 +59,10 @@ void test_suite()
 	//mesure_sum_integers();
 	//test_min_max();
 	//test_insertion_sort();
-        test_oddeven_merger_sort();
+	test_oddeven_merger_sort();
 	//test_bitonic_sort();
 	//test_majority_bit();
-	//mesure_matrix_prod();
+	//test_matrix_prod();
 	//test_sum_unbounded();
 	//measure_test_keygen();
 	//test_keygen();
@@ -96,15 +97,6 @@ void test_keygen(){
 	fhe_pk_init(pk);
 	fhe_sk_init(sk);
 	fhe_keygen(pk, sk);
-	printf("N: %d\n", N);
-	printf("taille binaire de p: %d\n", mpz_sizeinbase( pk->p, 2));
-	gmp_printf("p: %Zd \n", pk->p);
-	gmp_printf("alpha: %Zd \n", pk->alpha);
-	gmp_printf("B: %Zd \n", sk->B);
-	for(int i=0; i < S1; i++){
-		gmp_printf("c[%d]: %Zd \n", i, pk->c[i]);
-		gmp_printf("B[%d]: %Zd \n", i, pk->B[i]);
-	}
 	fhe_pk_clear(pk);
 	fhe_sk_clear(sk);
 	//T_Elapsed4 = (double) (clock () - START_eval);
@@ -113,7 +105,7 @@ void test_keygen(){
 	seconds  = end.tv_sec  - start.tv_sec;
 	useconds = end.tv_usec - start.tv_usec;
 	mtime = ((seconds) * 1000 + useconds/1000.0) + 0.5;
-	//printf("Elapsed time in KeyGen : %ld ms \n", mtime );
+	printf("Elapsed time in KeyGen : %ld ms \n", mtime );
 }
 
 void mesure_encrypt_decrypt(){
@@ -132,62 +124,46 @@ void mesure_encrypt_decrypt(){
 	gettimeofday(&start, NULL);
 	fhe_keygen(pk, sk);
 	gettimeofday(&end, NULL);
-	seconds  = end.tv_sec  - start.tv_sec;
[…]

### 2013-06-16 libScarab-1.0.0/test.c
z

@@ -61,11 +61,11 @@ void test_suite()
 	//test_oddeven_merger_sort();
 	//test_bitonic_sort();
 	//test_majority_bit();
-	//mesure_matrix_prod();
+	mesure_matrix_prod();
 	//test_sum_unbounded();
 	//measure_test_keygen();
 	//test_keygen();
-	mesure_encrypt_decrypt();
+	//mesure_encrypt_decrypt();
 	//essai();
 }
 
@@ -90,7 +90,7 @@ void test_keygen(){
 	//clock_t  START_eval;
 	//double T_Elapsed4;
 	//START_eval = clock();
-	gettimeofday(&start, NULL);    
+ 	gettimeofday(&start, NULL);    
 	fhe_pk_t pk;
 	fhe_sk_t sk;
 	fhe_pk_init(pk);
@@ -135,8 +135,7 @@ void mesure_encrypt_decrypt(){
 	seconds  = end.tv_sec  - start.tv_sec;
 	useconds = end.tv_usec - start.tv_usec;
 	mtime = ((seconds) * 1000 + useconds/1000.0) + 0.5;
-	printf("keygen: %ld ", mtime );
-  
+	printf("N:%d , log(p): %d , keygen: %ld ",N,mpz_sizeinbase( pk->p, 2), mtime );
 	gettimeofday(&start, NULL);  
 	for(int i=0; i < 100; i++){
 		k= 1 - k;
@@ -1267,93 +1266,101 @@ void test_majority_bit(){
 	mpz_init(c1);
 	fmpz_poly_init(poly_c1);
 	fmpz_poly_init(poly_c2);
-	unsigned a = 173;
-	printf("a: %d\n", a);
-	aux1= a; 
-	i=0;
-	////// Encryption of the bit sequences ////////////////
-	printf("aux1[i] -----> %i\n", aux1 % 2);
-	fhe_encrypt(c0, pk, a % 2);
-	fmpz_poly_set_coeff_mpz( poly_c1 , i , c0 );
-	i++;		
-	aux1 = aux1 >> 1;
-	do {		
-		printf("aux1[i] -----> %i\n", aux1 % 2);
-		fhe_encrypt(c0, pk, aux1 % 2);
-		fmpz_poly_set_coeff_mpz (poly_c1 , i , c0 );
-		i++;
-		aux1 = aux1 >> 1;	
[…]

### 2013-06-16 Report/article.tex

@@
 \usepackage{algorithm2e}
-%\usepackage{amsfont}
+\usepackage{subfigure}
 %\usepackage{amsmath}
@@
 }
-
 \usepackage{listings}
@@
 4. \textbf{Product of two $n\times n$ boolean matrices} \\
-5. \textbf{Sorting of $n$ sequences of $nbits$ using :} \newline\noindent
+5. \textbf{Sorting of $n$ sequences of $nbit$ using :} \newline\noindent
 \phantom{x}\hspace{3ex} a) Insertion sort \phantom{x}\hspace{2ex} b) Bitonic sort \\
@@
 \textbf{Insertion sort :} When allowing for parallel comparators, bubble sort and insertion sort are identical. Hence $n(n-1)/2$ comparator gates are used for insertion sort.\newline \newline
-\textbf{Bitonic Sort :} \autoref{bitsort} and \autoref{bitmerge} are used to perform Bitonic Sort. The algorithm uses $\mathrm{log}(n)·(\mathrm{log}(n)+1)/2$ comparator gates. \newline \newline
+\textbf{Bitonic Sort :} \autoref{bitsort} and \autoref{bitmerge} are used to perform Bitonic Sort. The algorithm uses $n\mathrm{log}(n)·(\mathrm{log}(n)+1)/4$ comparator gates. \newline \newline
 \textbf{Odd-Even Merge sort :} \autoref{oesort} and \autoref{oemerge} are used to perform Odd-Even merge sort and hence  $n(\mathrm{log}^{2}(n)-1)/2 + 1 $ comparator gates are required.\newline
@@
 
-\begin{figure}[t] %on ouvre l'environnement figure
+\begin{figure}[!H]
+\centering
+\includegraphics[width=7cm]{fsort3.pdf} 
+\caption{Runtime for Insertion sort, nbit=4} 
+\label{fig:image_sf3} %l'étiquette pour faire référence à cette image
+\end{figure}
+
+\begin{figure}[!H] %on ouvre l'environnement figure
+\centering
+\includegraphics[width=7cm]{fsort4.pdf} 
+\caption{Runtime for Insertion sort, nbit=6} 
+\label{fig:image_sf4} %l'étiquette pour faire référence à cette image
+\end{figure}
+
+\begin{figure}[!H] %on ouvre l'environnement figure
+\centering
+\includegraphics[width=7cm]{fsort5.pdf} 
+\caption{Run time for Insertion sort, nbit=8} 
+\label{fig:image_sf5} %l'étiquette pour faire référence à cette image
+\end{figure}
+
+\begin{figure}[!H] %on ouvre l'environnement figure
+\centering
+\includegraphics[width=7cm]{fsort6.pdf} 
+\caption{CPU time for Insertion sort, nbit=4} 
+\label{fig:image_sf6} %l'étiquette pour faire référence à cette image
+\end{figure}
+
+\begin{figure}[!H] %on ouvre l'environnement figure
+\centering
+\includegraphics[width=7cm]{fsort8.pdf} 
+\caption{CPU time for Insertion sort, nbit=6} 
+\label{fig:image_sf8} %l'étiquette pour faire référence à cette image
+\end{figure}
+
+\begin{figure}[!H]%on ouvre l'environnement figure
+\centering
+\includegraphics[width=7cm]{fsort7.pdf} 
+\caption{CPU time for Insertion sort, nbit=8} 
+\label{fig:image_sf7} %l'étiquette pour faire référence à cette image
+\end{figure}
+
+\begin{figure}[!H]
+\centering
+\includegraphics[width=7cm]{fsort2.pdf} 
+\caption{Runtime Comparison for insertion sort} 
+\label{fig:image_sf2} %l'étiquette pour faire référence à cette image
+\end{figure}
+
+\begin{figure}[!H]%nouvre l'environnement figure
 \centering
 \includegraphics[width=7cm]{fsort1.pdf} 
-\caption{Run time of KeyGen(ms)} 
-\label{fig:image_f2} %l'étiquette pour faire référence à cette image
-
-\centering
-\includegraphics[width=7cm]{fsort2.pdf} 
-\caption{Run time of KeyGen(ms)} 
-\label{fig:image_f2} %l'étiquette pour faire référence à cette image
-\centering
-\includegraphics[width=7cm]{fsort3.pdf} 
-\caption{Run time of KeyGen(ms)} 
-\label{fig:image_f2} %l'étiquette pour faire référence à cette image
-\end{figure}
-
-\begin{figure}[t] %on ouvre l'environnement figure
-\centering
-\includegraphics[width=7cm]{fsort4.pdf} 
-\caption{Run time of KeyGen(ms)} 
-\label{fig:image_f2} %l'étiquette pour faire référence à cette image
-\end{figure}
-
-\begin{figure}[t] %on ouvre l'environnement figure
-\centering
-\includegraphics[width=7cm]{fsort5.pdf} 
-\caption{Run time of KeyGen(ms)} 
-\label{fig:image_f2} %l'étiquette pour faire référence à cette image
-\end{figure}
-
-\begin{figure}[t] %on ouvre l'environnement figure
-\centering
-\includegraphics[width=7cm]{fsort6.pdf} 
-\caption{Run time of KeyGen(ms)} 
-\label{fig:image_f2} %l'étiquette pour faire référence à cette image
-\end{figure}
-
-\begin{figure}[t] %on ouvre l'environnement figure
-\centering
-\includegraphics[width=7cm]{fsort7.pdf} 
-\caption{Run time of KeyGen(ms)} 
-\label{fig:image_f2} %l'étiquette pour faire référence à cette image
-\end{figure}
-
-\begin{figure}[t] %on ouvre l'environnement figure
-\centering
-\includegraphics[width=7cm]{fsort8.pdf} 
-\caption{Run time of KeyGen(ms)} 
-\label{fig:image_f2} %l'étiquette pour faire référence à cette image
+\caption{Curve fitting for insertion sort}
+\label{fig:image_sf1} %l'étiquette pour faire référence à cette image
 \end{figure}
@@
 Intially, the cryptographic parameters were set to $(N = 8, \nu = 2^{384}, \mu = 4, s_1 = 8, s_2 = 5)$ which is the default setting in the software.
-The \textcolor{orange}{above figures} show the variation of CPU time and Wall time with the increase in the number of sequences to sort and the number of bits.
+\autoref{fig:image_sf3},\autoref{fig:image_sf4}, \autoref{fig:image_sf5}, \autoref{fig:image_sf6}, \\ \autoref{fig:image_sf8}, \autoref{fig:image_sf7} and \autoref{fig:image_sf2} show the variation of CPU time and Wall time with the increase in the number of sequences to sort and the number of bits.
 These experiments were done for Insertion Sort algorithm.
-We also present a  curve fitting plot that verifies the quadratic complexity of this algorithm.
+\autoref{fig:image_sf1} presents a  curve fitting plot that verifies the quadratic complexity of this algorithm.
 
@@
 \begin{table}
-\caption{Wall time for Odd-Even Merge Sort}
+\caption{Wall time for Odd-Even Merge Sort with increased security}
 \resizebox{8cm}{!}{
@@
   (32,4) &  1587427 &  1044640\\
-  (32,6) &   1629722 & 610464\\
+  (32,6) &   1629722 & 1610464\\
 \hline
@@
 By lowering the security level to only $8$ bits using the parameters :$(N = 16, \nu = 32, \mu = 2, s_1 = 85, s_2 = 5)$, the result did not decrypt to the desired output; which we believe is an implementation bug in the bootstrapping mechanism.
-However, by increasing $\mu$ also increases security, and setting the parameters to :  $(N = 8, \nu = 2^{384}, \mu = 8, s_1 = 8, s_2 = 5)$ we obtained the results as in \autoref{OddEvensort2} :
+Lowering the security even further to only $5$ bits using the parameters: $(N = 8, \nu = 2^8, \mu = 4, s_1 = 65, s_2 = 5)$, and testing odd-even sorting for $32$ sequences of $6$ bits each took more than an hour.
+However, increasing $\mu$ also increases security, and setting the parameters to :  $(N = 8, \nu = 2^{384}, \mu = 8, s_1 = 8, s_2 = 5)$ we obtained the results as in \autoref{OddEvensort2}.
+The results show that this set of parameters provide a better security and at almost no extra cost.
+For this result to be conclusive, we need to perfom tests for large $n$.
 \section{Conclusion}

### 2013-06-16 libScarab-1.0.0/test.c
g

@@ -66,8 +66,8 @@ void test_suite()
 	//mesure_test_matrix_prod();
 	//test_sum_unbounded();
 	//measure_test_keygen();
-	test_keygen();
-	//mesure_encrypt_decrypt();
+	//test_keygen();
+	mesure_encrypt_decrypt();
 	//essai();
 }
 
@@ -113,7 +113,7 @@ void mesure_encrypt_decrypt(){
 	fhe_pk_t pk;
 	fhe_sk_t sk;	
 	mpz_t c, aux1, aux2;
-	int m, k =0;
+	int m;
 	mpz_init(c);
 	mpz_init(aux1);
 	mpz_init(aux2);
@@ -128,44 +128,74 @@ void mesure_encrypt_decrypt(){
 	seconds  = end.tv_sec  - start.tv_sec;
 	useconds = end.tv_usec - start.tv_usec;
 	mtime = ((seconds) * 1000 + useconds/1000.0) + 0.5;
+	//gmp_printf("p: %Zd \n", pk->p);
+	//gmp_printf("alpha: %Zd \n", pk->alpha);
+	//gmp_printf("B: %Zd \n", sk->B);
+
 	printf("N:%d , log(p): %d , keygen: %ld ",N,mpz_sizeinbase( pk->p, 2), mtime );
+	
+	
 	gettimeofday(&start, NULL);  
 	for(int i=0; i < 100; i++){
-
-		k= 1 - k;
-		gettimeofday(&start, NULL);    
-		fhe_encrypt(c, pk, k);
-		gettimeofday(&end, NULL);
-		seconds  = end.tv_sec  - start.tv_sec;
-		useconds = end.tv_usec - start.tv_usec;
-		mtime = ((seconds) * 1000 + useconds/1000.0) + 0.5;
-		printf("time encrypt : %ld ms", mtime );
-
-		gettimeofday(&start, NULL);    
-		fhe_fulladd(c, aux1,c,c,aux2, pk);
-		gettimeofday(&end, NULL);
-		seconds  = end.tv_sec  - start.tv_sec;
-		useconds = end.tv_usec - start.tv_usec;
-		mtime = ((seconds) * 1000 + useconds/1000.0) + 0.5;
-		printf("time add : %ld ms", mtime );
-
-		gettimeofday(&start, NULL);    
-		fhe_mul(c,c, c, pk);
-		gettimeofday(&end, NULL);
-		seconds  = end.tv_sec  - start.tv_sec;
[…]

### 2013-06-16 Report/article.tex
Report with depth & security results

@@
 
-The scheme proposed in \cite{cryptoeprint:2009:571} has 3 parameters :($N, \nu, \mu$ ).
+The scheme proposed in \cite{cryptoeprint:2009:571} has 3 parameters : \\$(N=2^n, \eta, \mu)$, where $n\in \mathbb{N}$.
 The somewhat homomorphic scheme uses 5 algorithms: (\texttt{KeyGen}, \texttt{Encrypt}, \texttt{Decrypt}, \texttt{Add}, \texttt{Mult}).
@@
  \SetVline
- \KwData{$N, \nu, \mu$ }
+ \KwData{$N, \eta, \mu$ }
 \KwResult{($pk, sk$)}
@@
 \While{$p$ is not prime}{
-  $S(x) \leftarrow_{R}(B_{\infty , N}(\nu/2)$\; \tcc{Random choice}
+  $S(x) \leftarrow_{R}(B_{\infty , N}(\eta/2)$\; \tcc{Random polynomial in the ball}
   $G(x)=1+2.S(x)$\;
@@
 \texttt{Encrypt}($m \in \{0,1\} , pk$): 
-\newline \phantom{x}\hspace{3ex}  $R(x)=_{R}(B_{\infty , N}(\mu/2)$
+\newline \phantom{x}\hspace{3ex}  $R(x) \leftarrow_{R}(B_{\infty , N}(\mu/2)$
  \; $C(x)=m+2\cdot R(x)$ 
@@
 
-\textbf{Security of the scheme :} The scheme is semantically secure under the assumption that the \textit{Polynomial Coset Problem}(PCP) is hard.
+\textbf{Security of SWHE scheme :} The scheme is semantically secure under the assumption that the \textit{Polynomial Coset Problem}(PCP) is hard.
 One wayness of the encryption is believed to be true under the assumption that the \textit{Bounded distance decoding problem} BDDP is hard while key recovery is assumed to be difficult under the assumption that the \textit{Small Principal Ideal Problem}(SPIP) is hard.
@@
 
-If we choose $F(x)$ \footnote{a choice that authors of SV scheme propose and is always a safe choice for monic and irreducible polynomial over $\mathbb{Z}[x] $} to be $x^N+1$, and take $2 ^ \lambda = \frac{\nu}{2\cdot \mu \sqrt{N}} $, then the SV scheme provides $N /\lambda$ bits of security.
+If we choose $F(x)$ \footnote{a choice that authors of SV scheme propose and is always a safe choice for monic and irreducible polynomial over $\mathbb{Z}[x] $} to be $x^N+1$, and take \begin{equation}2 ^ \epsilon = \frac{\eta}{2\cdot \mu \sqrt{N}} \end{equation} then the SV scheme provides $N /\epsilon$ bits of security.
 
-\textbf{SWHE to FHE :} We recall that the authors of the scheme have proved that the multiplicative depth $d$ of SWHE scheme verifies: \[d \cdot \mathrm{log}(2) \leq  \mathrm{log}\left( \mathrm{log}\left(\frac{\nu}{2\cdot \sqrt{N}}\right) \right) - \mathrm{log}\left(\mathrm{log}\left( N\mu\right)\right)\]
+\textbf{SWHE to FHE :} We recall that the authors of the scheme have proved that the multiplicative depth $d$ of SWHE scheme verifies: \begin{equation}d \cdot \mathrm{log}(2) \leq  \mathrm{log}\left( \mathrm{log}\left(\frac{\eta}{2\cdot \sqrt{N}}\right) \right) - \mathrm{log}\left(\mathrm{log}\left( N\mu\right)\right)\end{equation}
 when $F(x)= x^N+1$.
 Turning the SWHE to FHE is achieved by recasting Gentry's method for the parameters of this scheme.
-To achieve this, the authors propose to generate $s_1$ uniformly random integers $B_i$ in $[-p, \ldots, p]$ such that there exists a subset $S$ of $s_2$ elements with $\sum_{j \in S}{B_j}= B$ over integers.
+To achieve this, authors define another algorithm \texttt{Recrypt} which takes a ciphertext $c$ and re-encrypts it to $c_{new}$, whilst at the same time removing some of the noise in $c$.
+This requires augmenting the encryption key with some additional information by extending the \texttt{KeyGen} algorithm.
+The FHE scheme now generates $s_1$ uniformly random integers $B_i$ in $[-p, \ldots, p]$ such that there exists a subset $S$ of $s_2$ elements with $\sum_{j \in S}{B_j}= B$ over integers.
 By defining $sk_i =1$ iff $i\in S$ and taking $c_i=\texttt{Encrypt}(sk_i,pk)$ we generate a new public key which contains hint of the secret key $sk$.
@@
 To ensure that the hint does not provide any considerable advantage to an attacker, the underlying \textit{sparse subset-sum problem} SSSP must remain remain hard.
-If we take $s_1$ to be slightly greater than $p$, then we need to select $s_2$ such that $\sqrt {{s_1}  \choose {s_2} } \leq 2 ^{N/\lambda}$ so as to ensure that SSSP difficulty is at least as difficult as the difficulty of the BDDP underlying the SWHE scheme.
+If we take $s_1$ to be slightly greater than $\mathrm{log}_{2}(p)$, then we need to select $s_2$ such that $\sqrt {{s_1}  \choose {s_2} } \leq 2 ^{N/\epsilon}$ so as to ensure that SSSP difficulty is at least as difficult as the difficulty of the BDDP underlying the SWHE scheme.
 
@@
 The library provides a file \texttt{test.c} where a user can write his own functions to test different operations.
-It also provides a header file \texttt{parameters.h} to set the parameters $N, \nu, \mu, s_1$ and $ s_2$ of the cryptosystem.
+It also provides a header file \texttt{parameters.h} to set the parameters $N, \eta, \mu, s_1$ and $ s_2$ of the cryptosystem.
 To simplify our computational circuit, we added two basic functions \texttt{or(mpz\_t res, mpz\_t a, mpz\_t b, fhe\_pk\_t pk);} and \texttt{not(mpz\_t res, mpz\_t a, fhe\_pk\_t pk);} which compute the logical \texttt{or}(+) of encrypted bits and the negation ($\neg$) of an encrypted bit respectively.
@@
 
-\subsection{Initial set-up cost}
-Here we mesure the performance in terms of run time for KeyGen, Encrypt, Add, Mult, Recrypt, Decrypt.\\
+\subsection{Cost of Cryptosytem}
+ In the SV scheme, performing any operation on encrypted bits requires  \texttt{KeyGen}, \texttt{Encrypt}, \texttt{Add},\texttt{ Mult}, \texttt{Recrypt}, \texttt{Decrypt} and hence we measure their performance in terms of run time.
+These measuremens are done by varying the parameter $N$ that determines the degree of all intermediate polynomials in the cryptostystem and keeping all other parameters fixed.
+The measurements in this section were taken on the machine M2.
+
 \begin{table}[htb]
@@
 
-\textbf{KeyGen}\\
-The measured time execution for KeyGen($N, \mu$)  for fixed values of parameters: $N=8$ and $\mu = 4$ show a variation from 0.2 s to 14.41 s with big density at the interval [0.2s, 2s]\autoref{fig:image_f2}.
+\autoref{fig:image_f2} measures execution time for \texttt{KeyGen} for fixed values of parameters: $N=8$ and $\eta = 2^{384}$.
+It shows a variation from 0.2 s to 14.41 s with high density in the interval [0.2s, 2s].
 
@@
 \centering
-\includegraphics[width=5cm]{f3.pdf} 
+\includegraphics[width=5cm, height=4cm]{f3.pdf} 
 \caption{Run time of KeyGen(ms)} 
@@
 
-\textbf{Encryption and Decryption}\\
+As the time taken by \texttt{KeyGen} depends on how fast the prime $p$ is found, its cost is related with the density of primes which is $\frac{1}{\mathrm{log(n)}}$.
+\autoref{fig:image_f2} is in accordance with the density of primes over $\mathbb{N}$.
+
+\subsection{Security }
+
+Using (1), and (2), we calculate the theoretical security level and the depth provided by the crytosystem, and we find that security level increases with increasing $N$ and for $\mu =4$ and $\eta=2^{384}$ fixed.
+But \autoref{common cost} show that the cost of the cryptosystem increases(ex.
+15 mins for \texttt{KeyGen}).
+We note that for $N \geq 2^6$, \texttt{KeyGen} takes hours.
+Hence, we choose $N=8$ for our experiments which provides $1.01472$ level of security and we vary $\mu$ and $\eta$.
+Due to some erroneous results provided by the decryption function for $d<5.3$, we choose $\mu$ and $\eta$ to ensure that the depth is greater than the threshold value $5.9$.
+
+\begin{table}[htb]
+  \centering
+  \caption{Run time (ms)}
+\begin{tabular}{|c|c|c||}
+  \hline
+  \multicolumn{3}{|c||}{$\mu = 4$ , $\eta = 2^{384}$} \\
+  \hline
+  $N=2^{n}$ &  $2^{\frac{N}{\epsilon}}$ & d \\
+  \hline
+  $2^{1}$ &  1.00365 & 6.99 \\
+  $2^{2}$ &  1.00732 & 6.57\\
+  $2^{3}$ &  1.01472 & 6.25\\
+  $2^{4}$ &  1.02969 & 5.98\\
+  $2^{5}$ & 1.06035 & 5.76\\
+  \hline
+\end{tabular}
+\normalsize
+\label{tab:securitytab}
+\end{table}
+
 \section{Circuit Transformation}
@@
 \textbf{Experimental Analysis :} We measure the run time from $n=1$ to $32$ bits, we find a linear cost which confirms the $\theta(n)$ complexity.
-During these measures the result of Min-Max is correct.
-\begin{comment} 
+
 \begin{figure}[!h] %on ouvre l'environnement figure
 \centering
-\includegraphics[width=5cm]{f2.eps} 
+\includegraphics[width=5cm,height=5cm]{f2.pdf} 
 \caption{Run time(ms)} 
@@
 \end{figure}
-\end{comment}
-The cost of this algorithm on cipher-text is linear with bit number, like  the algorithm on plain-text, the extra cost in this case is encryption-decryption cost and especially the code generation which is very unpredictable and take often a long time in the SV scheme.
 
@@
 
-\begin{figure}[!H]
+\begin{figure}[!h]
 \centering
-\includegraphics[width=7cm]{fsort3.pdf} 
+\includegraphics[width=5cm]{fsort3.pdf} 
 \caption{Runtime for Insertion sort, nbit=4} 
@@
 
-\begin{figure}[!H] %on ouvre l'environnement figure
+\begin{figure}[!h] %on ouvre l'environnement figure
 \centering
-\includegraphics[width=7cm]{fsort4.pdf} 
+\includegraphics[width=5cm]{fsort4.pdf} 
 \caption{Runtime for Insertion sort, nbit=6} 
@@
 
-\begin{figure}[!H] %on ouvre l'environnement figure
+\begin{figure}[!h] %on ouvre l'environnement figure
 \centering
@@
 
-\begin{figure}[!H] %on ouvre l'environnement figure
+\begin{figure}[!h]%on ouvre l'environnement figure
 \centering
@@
 
-When we increase the security of the system by setting the parameters to  $(N = 256, \nu = 16, \mu = 2, s_1 = 5000, s_2 = 5)$(as suggested in \cite{cryptoeprint:2009:571}) which ensures $25$ bits of security, the Odd-Even sorting algorithm on  $4$ sequences, each of $4$ bits takes hours.
-By lowering the security level to only $8$ bits using the parameters :$(N = 16, \nu = 32, \mu = 2, s_1 = 85, s_2 = 5)$, the result did not decrypt to the desired output; which we believe is an implementation bug in the bootstrapping mechanism.
-Lowering the security even further to only $5$ bits using the parameters: $(N = 8, \nu = 2^8, \mu = 4, s_1 = 65, s_2 = 5)$, and testing odd-even sorting for $32$ sequences of $6$ bits each took more than an hour.
-However, increasing $\mu$ also increases security, and setting the parameters to :  $(N = 8, \nu = 2^{384}, \mu = 8, s_1 = 8, s_2 = 5)$ we obtained the results as in \autoref{OddEvensort2}.
+When we increase the security of the system by setting the parameters to  $(N = 256,\eta  = 16, \mu = 2, s_1 = 5000, s_2 = 5)$(as suggested in \cite{cryptoeprint:2009:571}) which ensures $25$ bits of security, the Odd-Even sorting algorithm on  $4$ sequences, each of $4$ bits takes hours.
+By lowering the security level to only $8$ bits using the parameters :$(N = 16, \eta = 32, \mu = 2, s_1 = 85, s_2 = 5)$, the result did not decrypt to the desired output; which we believe is an implementation bug in the bootstrapping mechanism.
+Lowering the security even further to only $5$ bits using the parameters: $(N = 8, \eta = 2^8, \mu = 4, s_1 = 65, s_2 = 5)$, and testing odd-even sorting for $32$ sequences of $6$ bits each took more than an hour.
+However, increasing $\mu$ also increases security, and setting the parameters to :  $(N = 8, \eta = 2^{384}, \mu = 8, s_1 = 8, s_2 = 5)$ we obtained the results as in \autoref{OddEvensort2}.
 The results show that this set of parameters provide a better security and at almost no extra cost.
@@
 \bibliography{article}
-
-\section{Appendix}
-The programs used for Odd-Even Merge sort and Bitonic sort are provided below : 
-\begin{figure}[h]
-\begin{lstlisting}[label = oesort ]
-
- OddEvenMergeSort(int lo, int n)
-if (n > 1)
-        {
-            int m = n/2;
-            oddEvenMergeSort(lo, m);
-            oddEvenMergeSort(lo + m, m);
-            oddEvenMerge(lo, n, 1);
-        }
-\end{lstlisting}
-
-\caption{Odd-Even Merge Sort : sort from index lo to n }
-\end{figure}
-
-\begin{figure}
-\begin{lstlisting}[label = oemerge ]
-
-oddEvenMerge(int lo, int n, int r)
-    {
-        int m = r*2;
-        if (m < n)
-        {
-	    //even subsequence ;		
-            oddEvenMerge(lo, n, m); 
-            //odd subsequence ;
-	    oddEvenMerge(lo+r, n, m); 
-	    int i = lo+r;   
-            for (;i + r < lo + n;){
-		compare(i, i + r);
-		i += m;
-	    }
-        }
-        else
-            compare(lo, lo + r);
-    }
-
-\end{lstlisting} 
-\caption{Odd-Even Merge Sort : merging function}
-\end{figure}
-
-\begin{figure}
-\begin{lstlisting}[label=bitsort]
-
-sortup( int m, int n) {//from m to m+n
-    if (n == 1) return;
-    sortup(m, n/2);
-    sortdown(m + n/2, n/2);
-    mergeup(m, n/2);
-}
- sortdown(int m, int n) {//from m to m+n
-    if (n == 1) return;
-    sortup(m, n/2);
-    sortdown(m + n/2, n/2);
-    mergedown(m, n/2);
-}
-\end{lstlisting}
-\caption{Bitonic Sort : sort form m to n}
-\end{figure}
-
-\begin{figure}[t]
-\begin{lstlisting}[label=bitmerge]
-mergeup(int m, int n) {  
-    if (n == 0) return;
-
-    for (i = 0 : n)
-        // Increasing Comparator
-	 compare(m + i,m + i + n);
-    mergeup(m, n/2);
-    mergeup(m + n,n/2);
-}
-
-mergedown( int m,  int n) { 
-    if (n == 0) return;
-    for (i = 0 : n) 
-        // Decreasing Comparator
-	compare(m + i, m + i + n); 
-    mergedown(m, n/2);
-    mergedown(m + n, n/2);
-}
-\end{lstlisting}
-\caption{Bitonic Merge} 
-\end{figure} 
-%\begin{comment}
 

### 2013-06-16 libScarab-1.0.0/parameters.h

@@ -21,9 +21,9 @@
 
 //#define LOG_NU 384
 //#define LOG_NU 310
-#define LOG_NU 8
+#define LOG_NU 300
 
-#define S1 65
+#define S1 8
 #define S2 5
 #define T  5 // Ceiling[Log[2, S2]] + 2
 #define S  3 // Floor[Log[2, s2]] + 1

### 2013-06-16 libScarab-1.0.0/parameters.h
res

@@ -14,16 +14,16 @@
 //#define N 8
 #define N 8
 
-#define MU 4
+#define MU 2
 
 
 //#define NU 2**256;
 
 //#define LOG_NU 384
 //#define LOG_NU 310
-#define LOG_NU 8
+#define LOG_NU 250
 
-#define S1 65
+#define S1 8
 #define S2 5
 #define T  5 // Ceiling[Log[2, S2]] + 2
 #define S  3 // Floor[Log[2, s2]] + 1

### 2013-06-16 libScarab-1.0.0/test.c
nu et mu

@@ -132,7 +132,7 @@ void mesure_encrypt_decrypt(){
 	//gmp_printf("alpha: %Zd \n", pk->alpha);
 	//gmp_printf("B: %Zd \n", sk->B);
 
-	printf("N:%d , log(p): %d , keygen: %ld ",N,mpz_sizeinbase( pk->p, 2), mtime );
+	printf("N: %d , log(p): %d , Mu: %d , Nu: %d , keygen: %ld ",N,mpz_sizeinbase( pk->p, 2), MU, LOG_NU, mtime );
 	
 	
 	gettimeofday(&start, NULL);  
@@ -186,7 +186,7 @@ void mesure_encrypt_decrypt(){
 	seconds  = end.tv_sec  - start.tv_sec;
 	useconds = end.tv_usec - start.tv_usec;
 	mtime = ((seconds) * 1000 + useconds/1000.0) + 0.5;
-	printf("decrypt : %ld ms\n", mtime );
+	printf("decrypt : %ld ms ", mtime );
 	
 	
 	gettimeofday(&start, NULL);
@@ -195,7 +195,7 @@ void mesure_encrypt_decrypt(){
 	seconds  = end.tv_sec  - start.tv_sec;
 	useconds = end.tv_usec - start.tv_usec;
 	mtime = ((seconds) * 1000 + useconds/1000.0) + 0.5;
-	printf("time sum: %ld ms \n", mtime );
+	printf("sum: %ld ms \n", mtime );
 	mpz_clear(c); mpz_clear(aux1); mpz_clear(aux2);
 	fhe_pk_clear(pk);
 	fhe_sk_clear(sk);

### 2013-06-16 libScarab-1.0.0/parameters.h
Check

@@ -14,14 +14,14 @@
 //#define N 8
 #define N 8
 
-#define MU 4
+#define MU 2
 
 
 //#define NU 2**256;
 
 //#define LOG_NU 384
 //#define LOG_NU 310
-#define LOG_NU 300
+#define LOG_NU 200
 
 #define S1 8
 #define S2 5

### 2013-06-16 libScarab-1.0.0/parameters.h
h

@@ -14,7 +14,7 @@
 //#define N 8
 #define N 8
 
-#define MU 2
+#define MU 4
 
 
 //#define NU 2**256;
@@ -22,7 +22,7 @@
 //#define LOG_NU 384
 //#define LOG_NU 310
 
-#define LOG_NU 250
+#define LOG_NU 200
 
 
 #define S1 8

### 2013-06-16 libScarab-1.0.0/parameters.h
more figures

@@ -14,14 +14,14 @@
 //#define N 8
 #define N 8
 
-#define MU 2
+#define MU 8
 
 
 //#define NU 2**256;
 
 //#define LOG_NU 384
 //#define LOG_NU 310
-#define LOG_NU 200
+#define LOG_NU 400 
 
 //#define LOG_NU 250
 

### 2013-06-16 Report/article.tex
Check
figures added

@@
 \resizebox{9 cm}{!}{
-\begin{tabular}{|c|c|c|c|c|c|c|c|}
+\begin{tabular}{|c|c|c|c|c|c|c|c||}
   \hline
-  \multicolumn{8}{|c|}{$\mu = 4$ , $\eta = 2^{384}$} \\
+  \multicolumn{8}{|c||}{$\mu = 4$ , $\eta = 2^{384}$} \\
   \hline
@@
 \centering
-\includegraphics[width=5cm, height=4cm]{f3.pdf} 
+\includegraphics[width=5cm, height=4.5cm]{f3.pdf} 
 \caption{Run time of KeyGen(ms)} 
@@
 \textbf{Insertion sort :} When allowing for parallel comparators, bubble sort and insertion sort are identical. Hence $n(n-1)/2$ comparator gates are used for insertion sort.\newline \newline
-\textbf{Bitonic Sort :} \autoref{bitsort} and \autoref{bitmerge} are used to perform Bitonic Sort. The algorithm uses $n\mathrm{log}(n)·(\mathrm{log}(n)+1)/4$ comparator gates. \newline \newline
-\textbf{Odd-Even Merge sort :} \autoref{oesort} and \autoref{oemerge} are used to perform Odd-Even merge sort and hence  $n(\mathrm{log}^{2}(n)-1)/2 + 1 $ comparator gates are required.\newline
+\textbf{Bitonic Sort :} The standard algorithm uses $n\mathrm{log}(n)·(\mathrm{log}(n)+1)/4$ comparator gates. \newline \newline
+\textbf{Odd-Even Merge sort :} Odd-Even merge sort requires  $n(\mathrm{log}^{2}(n)-1)/2 + 1 $ comparator gates.\newline
 We note that the sorting programs used do not increase the size of the circuit operating on encrypted input bit sequences.
@@
 \centering
-\includegraphics[width=5cm]{fsort3.pdf} 
+\includegraphics[width=7cm, height=6cm]{fsort3.pdf} 
 \caption{Runtime for Insertion sort, nbit=4} 
@@
 \centering
-\includegraphics[width=5cm]{fsort4.pdf} 
+\includegraphics[width=7cm, height=6cm]{fsort4.pdf} 
 \caption{Runtime for Insertion sort, nbit=6} 
@@
 \centering
-\includegraphics[width=7cm]{fsort5.pdf} 
+\includegraphics[width=7cm, height=6cm]{fsort5.pdf} 
 \caption{Run time for Insertion sort, nbit=8} 
@@
 \centering
-\includegraphics[width=7cm]{fsort6.pdf} 
+\includegraphics[width=7cm, height=6cm]{fsort6.pdf} 
 \caption{CPU time for Insertion sort, nbit=4} 
@@
 \centering
-\includegraphics[width=7cm]{fsort2.pdf} 
+\includegraphics[width=7cm, height=6cm]{fsort2.pdf} 
 \caption{Runtime Comparison for insertion sort} 
@@
 \centering
-\includegraphics[width=7cm]{fsort1.pdf} 
+\includegraphics[width=7cm, height=6cm]{fsort1.pdf} 
 \caption{Curve fitting for insertion sort}
 \label{fig:image_sf1} %l'étiquette pour faire référence à cette image
+\end{figure}
+
+\textbf{XOR of $n$ bits}
+\begin{figure}[!H]%on ouvre l'environnement figure
+\centering
+\includegraphics[width=7cm, height=6cm]{f4.pdf} 
+\caption{Wall time for XOR} 
+\label{fig:image_sf7} %l'étiquette pour faire référence à cette image
+\end{figure}
+
+\textbf{Sum of two $n$ bit sequences}
+\begin{figure}[!H]%on ouvre l'environnement figure
+\centering
+\includegraphics[width=6cm]{f8.pdf} 
+\caption{Wall time for sum} 
+\label{fig:image_sf7} %l'étiquette pour faire référence à cette image
+\end{figure}
+
+\textbf{Majority of $n$ bits}
+
+\textbf{Product of two $n\times n$ matrices}
+
+\begin{figure}[!H]%on ouvre l'environnement figure
+\centering
+\includegraphics[width=9cm, height=6cm]{f9.pdf} 
+\caption{Wall time for matrix product} 
+\label{fig:image_sf7} %l'étiquette pour faire référence à cette image
 \end{figure}
@@
 For this result to be conclusive, we need to perfom tests for large $n$.
+
 \section{Conclusion}
-
 With the examples and the programs discussed, we conclude that the tranformation of a non-straight line programs(with branching) in general increases the circuit complexity.
-The experiments on the implementation and the operations ........
+The experiments with the implementation
 \pagebreak
@@
 \bibliography{article}  
-
-% sigproc.bib is the name of the Bibliography in this case
-% You must have a proper ".bib" file
-%  and remember to run:
-% latex bibtex latex latex
-% to resolve all references
-%
-% ACM needs 'a single self-contained file'!
-%
-%APPENDICES are optional
-%\balancecolumns
 \balancecolumns

### 2013-06-16 Report/article.tex
m

--- 2013-06-16 Report/article.tex
@@
 The measurements in this section were taken on the machine M2.
+We can infer that the cost of these functions increase with the increase of the the degree  polynomials.
 
@@
 
+We can see that the size of the public key is increasing lineary with $n$ such that $N=2^n$ 
 \autoref{fig:image_f2} measures execution time for \texttt{KeyGen} for fixed values of parameters: $N=8$ and $\eta = 2^{384}$.

### 2013-06-16 Report/article.tex
figures

--- 2013-06-16 Report/article.tex
@@
 
+\textbf{XOR of $n$ bits}
+\begin{figure}[!H]%on ouvre l'environnement figure
+\centering
+\includegraphics[width=7cm, height=6cm]{f4.pdf} 
+\caption{Wall time for XOR} 
+\label{fig:image_sf7} %l'étiquette pour faire référence à cette image
+\end{figure}
+
+\textbf{Sum of two $n$ bit sequences}
+\begin{figure}[!H]%on ouvre l'environnement figure
+\centering
+\includegraphics[width=6cm]{f8.pdf} 
+\caption{Wall time for sum} 
+\label{fig:image_sf7} %l'étiquette pour faire référence à cette image
+\end{figure}
+
+\textbf{Majority of $n$ bits}
+
+\textbf{Product of two $n\times n$ matrices}
+
+\begin{figure}[!H]%on ouvre l'environnement figure
+\centering
+\includegraphics[width=9cm, height=6cm]{f9.pdf} 
+\caption{Wall time for matrix product} 
+\label{fig:image_sf7} %l'étiquette pour faire référence à cette image
+\end{figure}
+
 \begin{figure}[!h]
@@
 \label{fig:image_sf1} %l'étiquette pour faire référence à cette image
-\end{figure}
-
-\textbf{XOR of $n$ bits}
-\begin{figure}[!H]%on ouvre l'environnement figure
-\centering
-\includegraphics[width=7cm, height=6cm]{f4.pdf} 
-\caption{Wall time for XOR} 
-\label{fig:image_sf7} %l'étiquette pour faire référence à cette image
-\end{figure}
-
-\textbf{Sum of two $n$ bit sequences}
-\begin{figure}[!H]%on ouvre l'environnement figure
-\centering
-\includegraphics[width=6cm]{f8.pdf} 
-\caption{Wall time for sum} 
-\label{fig:image_sf7} %l'étiquette pour faire référence à cette image
-\end{figure}
-
-\textbf{Majority of $n$ bits}
-
-\textbf{Product of two $n\times n$ matrices}
-
-\begin{figure}[!H]%on ouvre l'environnement figure
-\centering
-\includegraphics[width=9cm, height=6cm]{f9.pdf} 
-\caption{Wall time for matrix product} 
-\label{fig:image_sf7} %l'étiquette pour faire référence à cette image
 \end{figure}
@@
 \section{Conclusion}
+
 With the examples and the programs discussed, we conclude that the tranformation of a non-straight line programs(with branching) in general increases the circuit complexity.
-The experiments with the implementation
+The experiments on the implementation and the operations ........
 \pagebreak

### 2013-06-16 Report/article.tex
j

@@
 1. \textbf{XOR of an $n$-bit sequence}\\
-2. \textbf{Sum of :}  two $n$ bit sequences  \newline 
 3. \textbf{Majority bit of an $n$-bit sequence} \\
+2. \textbf{Sum of :}  two unsigned integers of $32$ bits  \newline 
+2. \textbf{Sum of :}  two unsigned integers  \newline 
 4. \textbf{Product of two $n\times n$ boolean matrices} \\
@@
 \textbf{XOR of $n$-bits :} \texttt{XOR} of $n$-bits requires $n-1$ \texttt{XOR} gates. \newline \newline
-\textbf{Sum of two $n$-bit sequences :} Sum of two $n$-bits sequences is performed using $n$ \texttt{full-adder} circuits (provided as \texttt{fhe\_fulladd(...)} function in the Scarab library).
-The cost of a full adder circuit is $2$ \texttt{XOR} to calculate the sum and $2$ \texttt{AND}, $1$ \texttt{XOR} and $1$ \texttt{OR} for the carry.
-Hence the total complexity is $3n$ \texttt{AND}, $5n$ \texttt{XOR}.
-\newline \newline
+
 \textbf{Majority of $n$-bits :} Majority bit is evaluated by obtaining the sum of the bits and then returning the result of the comparison of the sum and $n/2$.
@@
 \newline \newline
+
+\textbf{Sum of two unsigned integers of $32$ bits :} Sum of two $n$-bits sequences is performed using $n$ \texttt{full-adder} circuits (provided as \texttt{fhe\_fulladd(...)} function in the Scarab library).
+The cost of a full adder circuit is $2$ \texttt{XOR} to calculate the sum and $2$ \texttt{AND}, $1$ \texttt{XOR} and $1$ \texttt{OR} for the carry.
+Hence the total complexity is $3n$ \texttt{AND}, $5n$ \texttt{XOR}.
+\newline \newline
+
+\textbf{Sum of two unsigned integers :} Sum of two $n$-bits sequences is performed using $n$ \texttt{full-adder} circuits (provided as \texttt{fhe\_fulladd(...)} function in the Scarab library).
+The cost of a full adder circuit is $2$ \texttt{XOR} to calculate the sum and $2$ \texttt{AND}, $1$ \texttt{XOR} and $1$ \texttt{OR} for the carry.
+Hence the total complexity is $3n$ \texttt{AND}, $5n$ \texttt{XOR}.
+\newline \newline
+
 \textbf{Product of two $n\times n$ matrices :} This requires $n^3$ \texttt{AND} gates and \texttt{$n^2(n-1)$} \texttt{XOR} gates. \newline \newline
@@
 \label{Sec:Eval}
-
-\textbf{XOR of $n$ bits}
+In this we execute the implementations of the programs above, and we measure their wall time and compare this cost with the theoretical complexity depending on the sizes of the input data.
+The figure \autoref{fig:image_sf7} represents minumum and maximum wall time of \texttt{XOR} done on random inputs.
+We can see that the wall time increase lineary with number of bits which confirm the theoretical cost.
 \begin{figure}[!H]%on ouvre l'environnement figure
@@
 \caption{Wall time for XOR} 
-\label{fig:image_sf7} %l'étiquette pour faire référence à cette image
+\label{fig:image_sf0} %l'étiquette pour faire référence à cette image
 \end{figure}
 
-\textbf{Sum of two $n$ bit sequences}
+We notice the same complexity for both \texttt{Bit Majority} and \texttt{sum of integers}\autoref{fig:image_sf1}.
 \begin{figure}[!H]%on ouvre l'environnement figure
 \centering
-\includegraphics[width=6cm]{f8.pdf} 
+\includegraphics[width=6cm, height=5cm]{f8.pdf} 
 \caption{Wall time for sum} 
-\label{fig:image_sf7} %l'étiquette pour faire référence à cette image
+\label{fig:image_sf1} %l'étiquette pour faire référence à cette image
 \end{figure}
 
-\textbf{Majority of $n$ bits}
-
-\textbf{Product of two $n\times n$ matrices}
-
+And we confirm as well the $O(n^{3})$ complexity for the \texttt{matrix product}\autoref{fig:image_sf2}.
 \begin{figure}[!H]%on ouvre l'environnement figure
@@
 \caption{Wall time for matrix product} 
-\label{fig:image_sf7} %l'étiquette pour faire référence à cette image
+\label{fig:image_sf2} %l'étiquette pour faire référence à cette image
 \end{figure}

### 2013-06-16 Report/article.tex
g

@@
 
-\textbf{Sum of two unsigned integers of $32$ bits :} Sum of two $n$-bits sequences is performed using $n$ \texttt{full-adder} circuits (provided as \texttt{fhe\_fulladd(...)} function in the Scarab library).
+\textbf{Sum of two unsigned integers of $32$ bits :} It is a sum of two $n$-bits sequences such as $n<32$ and it is performed using $n$ \texttt{full-adder} circuits (provided as \texttt{fhe\_fulladd(...)} function in the Scarab library).
 The cost of a full adder circuit is $2$ \texttt{XOR} to calculate the sum and $2$ \texttt{AND}, $1$ \texttt{XOR} and $1$ \texttt{OR} for the carry.
@@
 
-\textbf{Sum of two unsigned integers :} Sum of two $n$-bits sequences is performed using $n$ \texttt{full-adder} circuits (provided as \texttt{fhe\_fulladd(...)} function in the Scarab library).
-The cost of a full adder circuit is $2$ \texttt{XOR} to calculate the sum and $2$ \texttt{AND}, $1$ \texttt{XOR} and $1$ \texttt{OR} for the carry.
-Hence the total complexity is $3n$ \texttt{AND}, $5n$ \texttt{XOR}.
-\newline \newline
+\textbf{Sum of two unsigned integers :} This program select the first $32$-bits sequences of the $2$ integers and does the sum of themexactly like the previous algorithm and then perform the sum with next $32$-bits sequences with the carry from the previous addition untill there is no sequence left.n in the Scarab library).
+So this program has approximately the same linear cost with the previous one \newline \newline
 

### 2013-06-16 Report/article.tex
Check again

--- 2013-06-16 Report/article.tex
@@
 \centering
-\includegraphics[width=7cm, height=6cm]{fsort3.pdf} 
+\includegraphics[width=7cm]{fsort3.pdf} 
 \caption{Runtime for Insertion sort, nbit=4} 
@@
 \centering
-\includegraphics[width=7cm, height=6cm]{fsort4.pdf} 
+\includegraphics[width=7cm]{fsort4.pdf} 
 \caption{Runtime for Insertion sort, nbit=6} 
@@
 \centering
-\includegraphics[width=7cm, height=6cm]{fsort5.pdf} 
+\includegraphics[width=7cm]{fsort5.pdf} 
 \caption{Run time for Insertion sort, nbit=8} 
@@
 \centering
-\includegraphics[width=7cm, height=6cm]{fsort6.pdf} 
+\includegraphics[width=7cm]{fsort6.pdf} 
 \caption{CPU time for Insertion sort, nbit=4} 
@@
 \centering
-\includegraphics[width=7cm, height=6cm]{fsort2.pdf} 
+\includegraphics[width=7cm]{fsort2.pdf} 
 \caption{Runtime Comparison for insertion sort} 
@@
 \centering
-\includegraphics[width=7cm, height=6cm]{fsort1.pdf} 
+\includegraphics[width=7cm]{fsort1.pdf} 
 \caption{Curve fitting for insertion sort}
@@
 For this result to be conclusive, we need to perfom tests for large $n$.
+For our last test, we set the parameters to  $(N = 8, \eta = 2^{200}, \mu = 8, s_1 = 8, s_2 = 5)$ which gave us incorrect decryption.
+We note that decryption fails in case the depth is too small for recrypt to function.
 
 \section{Conclusion}
-
-With the examples and the programs discussed, we conclude that the tranformation of a non-straight line programs(with branching) in general increases the circuit complexity.
-The experiments on the implementation and the operations ........
-\pagebreak
+With the examples and the programs discussed, we conclude that the tranformation of a non-straight line program on unencrypted data(with branching) into a straight line program on encrypted data increases the circuit complexity.
+We experimentally measured the cost of different operations on encrypted data.
+The existing implementation of Smart-Vercauteren scheme remains practical only for $1$ bit of security, when a user wants to apply a sorting algorithm on his encrypted bit sequences.
 

### 2013-06-16 libScarab-1.0.0/parameters.h

@@ -23,7 +23,7 @@
 //#define LOG_NU 384
 //#define LOG_NU 310
 
-#define LOG_NU 384
+#define LOG_NU 400
 
 
 

### 2013-06-16 Report/article.tex
figuref10

--- 2013-06-16 Report/article.tex
@@
 
-We notice the same complexity for both \texttt{Bit Majority} and \texttt{sum of integers}\autoref{fig:image_sf1}.
+We notice the same complexity for both \texttt{Bit Majority}\autoref{fig:image_sf0bis} and \texttt{sum of integers}\autoref{fig:image_sf1}.
+
+\begin{figure}[!H]%on ouvre l'environnement figure
+\centering
+\includegraphics[width=6cm, height=5cm]{f8.pdf} 
+\caption{Wall time for bit majority} 
+\label{fig:image_sf0bis} %l'étiquette pour faire référence à cette image
+\end{figure}
+
 \begin{figure}[!H]%on ouvre l'environnement figure

### 2013-06-16 libScarab-1.0.0/test.c

@@ -61,13 +61,13 @@ void test_suite()
 	//test_insertion_sort();
 	//test_oddeven_merger_sort();
 	//test_bitonic_sort();
-	//test_majority_bit();
+	test_majority_bit();
 
 	//mesure_test_matrix_prod();
 	//test_sum_unbounded();
 	//measure_test_keygen();
 	//test_keygen();
-	mesure_encrypt_decrypt();
+	//mesure_encrypt_decrypt();
 	//essai();
 }
 
@@ -1277,99 +1277,99 @@ void test_majority_bit(){
 	fmpz_poly_init(poly_c2);
 	struct timeval start, end;	
     	long mtime, seconds, useconds;    
-	for(unsigned a = 45; a < 55; a++){
-		printf("a: %d , ", a);
-		gettimeofday(&start, NULL);   
-		aux1= a * 50; 
-		i=0;
-		////// Encryption of the bit sequences ////////////////
+	unsigned a = 1300000000;
+	printf("a: %d , ", a);
+	gettimeofday(&start, NULL);   
+	aux1= a ; 
+	i=0;
+	////// Encryption of the bit sequences ////////////////
+	//printf("aux1[i] -----> %i\n", aux1 % 2);
+	fhe_encrypt(c0, pk, a % 2);
+	fmpz_poly_set_coeff_mpz( poly_c1 , i , c0 );
+	i++;		
+	aux1 = aux1 >> 1;
+	do {		
 		//printf("aux1[i] -----> %i\n", aux1 % 2);
-		fhe_encrypt(c0, pk, a % 2);
-		fmpz_poly_set_coeff_mpz( poly_c1 , i , c0 );
-		i++;		
-		aux1 = aux1 >> 1;
-		do {		
-			//printf("aux1[i] -----> %i\n", aux1 % 2);
-			fhe_encrypt(c0, pk, aux1 % 2);
-			fmpz_poly_set_coeff_mpz (poly_c1 , i , c0 );
-			i++;
-			aux1 = aux1 >> 1;	
-		}while(aux1 != 0 );
-		////////////////////////////////////////
+		fhe_encrypt(c0, pk, aux1 % 2);
+		fmpz_poly_set_coeff_mpz (poly_c1 , i , c0 );
+		i++;
+		aux1 = aux1 >> 1;	
[…]

### 2013-06-16 Report/article.tex
Version Final****

--- 2013-06-16 Report/article.tex
@@
 
+\autoref{tab:tradeofftab1} presents the security-cost tradeoff for 10000 multiplications as a function of $\eta$.
+We remark that : decreasing $\eta$ with other parameters fixed increases the security of the system at the cost of decreasing the depth.
+We further note that increasing the value of $\eta$ increases the computational cost.
+On the contrary, \autoref{tab:tradeofftab2} presents the security-cost tradeoff for 10000 multiplications as a function of $\mu$.
+Here, increasing $\mu$ with other parameters fixed increases the security of the system at the cost of decreasing the depth.
+However, in this case the cost does not vary much.
+Hence it is profitable to increase $\mu$ to increase the security of the system.
+
+\begin{table}[htb]
+  \centering
+  \caption{Trade-off for 10000 multiplications}
+\begin{tabular}{|c|c|c|c||}
+  \hline
+  \multicolumn{4}{|c||}{$\mu = 4$ , $N=8$} \\
+  \hline
+  $\eta$ &  time(in s)  & depth & $2^{\frac{N}{\epsilon}}$ \\
+  \hline
+  $2^{600}$ & 619  & 6.90 & 1.009 \\
+  $2^{400}$ &  580 & 6.31 & 1.014 \\
+  $2^{200}$ &  509 & 5.03 & 1.028 \\
+  $2^{100}$ &  490 & 4.28 & 1.059 \\
+   \hline
+\end{tabular}
+\normalsize
+\label{tab:tradeofftab1}
+\end{table}
+
+\begin{table}[htb]
+  \centering
+  \caption{Trade-off for 10000 multiplications}
+\begin{tabular}{|c|c|c|c||}
+  \hline
+  \multicolumn{4}{|c||}{$\eta = 2^{300}$ , $N=8$} \\
+  \hline
+  $\mu$ &  time(in s)  & depth & $2^{\frac{N}{\epsilon}}$ \\
+  \hline
+  $2$ & 527  & 6.90 & 1.01887 \\
+  $4$ & 526 & 5.89 & 1.01894 \\
+  $8$ & 528  & 5.63 & 1.01900 \\
+  $16$ & 529  & 5.40 & 1.01907 \\
+   \hline
+\end{tabular}
+\normalsize
+\label{tab:tradeofftab2}
+\end{table}
+
 \section{Circuit Transformation}
@@
 \centering
-\includegraphics[width=5cm,height=5cm]{f2.pdf} 
+\includegraphics[width=5cm,height=4cm]{f2.pdf} 
 \caption{Run time(ms)} 
@@
 \textbf{XOR of $n$-bits :} \texttt{XOR} of $n$-bits requires $n-1$ \texttt{XOR} gates. \newline \newline
-
 \textbf{Majority of $n$-bits :} Majority bit is evaluated by obtaining the sum of the bits and then returning the result of the comparison of the sum and $n/2$.
@@
 \newline \newline
-
 \textbf{Sum of two unsigned integers of $32$ bits :} It is a sum of two $n$-bits sequences such as $n<32$ and it is performed using $n$ \texttt{full-adder} circuits (provided as \texttt{fhe\_fulladd(...)} function in the Scarab library).
@@
 \newline \newline
-
 \textbf{Sum of two unsigned integers :} This program select the first $32$-bits sequences of the $2$ integers and does the sum of themexactly like the previous algorithm and then perform the sum with next $32$-bits sequences with the carry from the previous addition untill there is no sequence left.n in the Scarab library).
 So this program has approximately the same linear cost with the previous one \newline \newline
-
 \textbf{Product of two $n\times n$ matrices :} This requires $n^3$ \texttt{AND} gates and \texttt{$n^2(n-1)$} \texttt{XOR} gates. \newline \newline
@@
 \centering
-\includegraphics[width=7cm, height=6cm]{f4.pdf} 
+\includegraphics[width=5cm, height=4cm]{f4.pdf} 
 \caption{Wall time for XOR} 
@@
 \centering
-\includegraphics[width=6cm, height=5cm]{f8.pdf} 
+\includegraphics[width=5cm, height=4cm]{f8.pdf} 
 \caption{Wall time for sum} 
@@
 \centering
-\includegraphics[width=9cm, height=6cm]{f9.pdf} 
+\includegraphics[width=5cm, height=4cm]{f9.pdf} 
 \caption{Wall time for matrix product} 

### 2013-06-16 libScarab-1.0.0/parameters.h

@@ -15,7 +15,7 @@
 #define N 8
 
 
-#define MU 4
+#define MU 16
 
 
 //#define NU 2**256;
@@ -23,7 +23,7 @@
 //#define LOG_NU 384
 //#define LOG_NU 310
 
-#define LOG_NU 400
+#define LOG_NU 300
 
 
 

### 2013-06-17 Report/article.tex

@@
 This paper investigates the feasibility of transformation of a (possibly) non-straight-line program (on unencrypted data) into a straight-line program on encrypted data.
-We present an analysis of security-cost trade-off for a homomorphic encryption scheme on such programs.
+We present an analysis of security-cost trade-off for a homomorphic encryption scheme executing such programs.
 Analysis is based on the measurements (CPU time and  Wall time) taken for programs : performing \texttt{XOR} of an $n$-bit sequence,  evaluating the sum of two $n$-bit sequences, determining the majority bit of an $n$-bit sequence, finding the product of two $n \times n$ matrices, and sorting $n$ bit sequences of length $nbits$ (usually requiring validity of a boolean predicate).
@@
 The notion of \textit{fully homomorphic encryption scheme}, originally called a \textit{privacy homomorphism} was introduced by Rivest et al.
-\cite{rivest78} shortly after the invention of the RSA by Rivest, Shamir and Adleman \cite{Rivest78amethod}.
+\cite{rivest78} shortly after the invention of RSA by Rivest, Shamir and Adleman \cite{Rivest78amethod}.
 Basic RSA is a multiplicative homomorphic encryption scheme -- i.e.
@@
 Fully homomorphic encryption scheme extends the above property to addition.
-A Fully homomorphic scheme is a tuple of an encryption $\mathcal{E}$, decryption $\mathcal{D}$ algorithm together with an efficient algorithm $Eval_\mathcal{E}$ that evaluates any circuit $C$ on any cipher-texts $c_i \leftarrow \mathcal{E}(pk, m_i)$.
+A fully homomorphic encryption scheme is a tuple of an encryption $\mathcal{E}$, decryption $\mathcal{D}$ algorithm together with an efficient algorithm $Eval_\mathcal{E}$ that evaluates any circuit $C$ on any cipher-texts $c_i \leftarrow \mathcal{E}(pk, m_i)$.
 The property that it can evaluate the encryption of addition and multiplication of two plain-texts (without access to the secret key) allows it to arbitrarily compute any function on encrypted data without the decryption key.
@@
 The immediate question that is raised, is how do we perform the transformation and how does the circuit size change to adapt to computations on encrypted data.
-We provide answer to this question by analyzing circuit complexity for finding the minimum-maximum of two $n$-bit sequences in \autoref{sec:ex} and for some other operations in \autoref{sec:bm}.
-Moreover, the cost of evaluation increases with the depth of the circuit representing the $Eval_{\mathcal{E}}$ function.
-Some researchers have improved and proposed other schemes such as \cite{cryptoeprint:2009:571} and \cite{cryptoeprint:2011:277} which decrease the circuit complexity.
-In \autoref{Sec:Eval} we experimentally evaluate an implementation of  \cite{cryptoeprint:2009:571} and analyze the cost-security trade-off for $Eval_{\mathcal{E}}$ varying from \texttt{XOR} of the bits of an $n$ bit integer to sum of two $n$ bit sequences to sorting of $n$ sequences of $nbits$ each.
+We provide an answer by analyzing circuit complexity for finding the minimum-maximum of two $n$-bit sequences in \autoref{sec:ex} and for some other operations in \autoref{sec:bm}.
+Moreover, the cost of using a fully homomorphic encryption scheme increases with the depth of the circuit representing the $Eval_{\mathcal{E}}$ function.
+
+Some researchers have improved Gentry's scheme and proposed other schemes such as \cite{cryptoeprint:2009:571} and \cite{cryptoeprint:2011:277} which improve the complexity of the scheme.
+In \autoref{Sec:Eval} we experimentally evaluate an implementation of  \cite{cryptoeprint:2009:571} and analyze the security-cost trade-off for $Eval_{\mathcal{E}}$ varying from \texttt{XOR} of an $n$-bit sequence to sum of two $n$-bit sequences to sorting of $n$ sequences of $nbits$ each.
 Three different sorting algorithms are tested.
-Through these experiments, we also provide information on the additional cost to be paid (for these computations) when security of the cryptosystem is increased.
+Through these experiments, we also provide information on the additional cost to be paid (for these computations) when a higher security is desired.
 
@@
 The homomorphic encryption scheme proposed by Gentry \cite{homenc} is based on ideal lattices.
-The Gentry's non-deterministic scheme builds on a \textit{somewhat homomorphic encryption}(SWHE) scheme which can perform additions and multiplications on encrypted data till a bounded depth.
-The non-determinism introduced in the form of a noise renders the scheme secure.
-But, the noise increases with the depth  of the evaluation circuit and hence the decryption algorithm fails to produce the correct plain-text after a certain depth.
+Gentry's non-deterministic scheme builds on a \textit{somewhat homomorphic encryption}(SWHE) scheme which can perform additions and multiplications on encrypted data till a bounded depth.
+The non-determinism introduced in the form of noise renders the scheme secure.
+However, the noise increases with the depth  of the evaluation circuit and hence the decryption algorithm fails to produce the correct plain-text after a certain depth.
 To counter this problem, Gentry introduces \textit{bootstrapping} technique which ensures unbounded depth operatability of the scheme.
-Smart Vercauteren \cite{cryptoeprint:2009:571} have proposed an integer based approach and we use one of its implementations detailed in \cite{perl:poster} for our experiments.
+Smart and Vercauteren \cite{cryptoeprint:2009:571} have proposed an integer based approach and we use one of its implementations detailed in \cite{perl:poster} for our experiments.
 
@@
 
-The scheme proposed in \cite{cryptoeprint:2009:571} has 3 parameters : \\$(N=2^n, \eta, \mu)$, where $n\in \mathbb{N}$.
-The somewhat homomorphic scheme uses 5 algorithms: (\texttt{KeyGen}, \texttt{Encrypt}, \texttt{Decrypt}, \texttt{Add}, \texttt{Mult}).
+The scheme proposed in \cite{cryptoeprint:2009:571} has 3 parameters : $(N=2^n, \eta, \mu)$, where $n\in \mathbb{N}$.
+The somewhat homomorphic encryption scheme uses 5 algorithms : (\texttt{KeyGen}, \texttt{Encrypt}, \texttt{Decrypt}, \texttt{Add}, \texttt{Mult}).
 Algorithm \autoref{Code:SV} presents the \texttt{KeyGen} algorithm.
@@
 \KwResult{($pk, sk$)}
- $F(x)$ monic irreducible over $\mathbb{Z}[x]$ of degree $n$\;
+ $F(x)$ monic irreducible over $\mathbb{Z}[x]$ of degree $N$\;
 \While{$p$ is not prime}{
-  $S(x) \leftarrow_{R}(B_{\infty , N}(\eta/2)$\; \tcc{Random polynomial in the ball}
+  $S(x) \leftarrow_{R}B_{\infty , N}(\eta/2)$\; \tcc{Random polynomial in the ball}
   $G(x)=1+2.S(x)$\;
-  $p= resultant(G(x),F(x))$\;						
+  $p= \mathrm{\textbf{resultant}}(G(x),F(x))$\;						
 }
 
-$D(x)=gcd(G(x),F(x))$ over $\mathbb{F}_p[x]$\;
-$\alpha$ $\leftarrow$ unique root of $D(x)$\;
-apply \texttt{xgcd} algorithm to obtain $Z(x) = \sum_{i=0}^{n-1}{z_ix^i} $  such that $Z(x).G(x)=p$ mod $F(x)$\;
+$D(x)=\mathrm{\textbf{gcd}}(G(x),F(x))$ over $\mathbb{F}_p[x]$\;
+$\alpha$ $\leftarrow$ unique root of $D(x) \in \mathbb{F}_p $ \;
+apply \texttt{xgcd} algorithm over $\mathbb{Q}[x]$ to obtain $Z(x) = \sum_{i=0}^{n-1}{z_ix^i} \in \mathbb{Z}[x] $  such that $Z(x).G(x)=p$ mod $F(x)$\;
 $B=z_0$ mod $2p$\;
@@
 
-where $ B_{\infty , n}(r) = \{\sum_{i=0}^{n-1}{a_i}x^i : -r \leq a_i \leq r \} $
-
+where $ B_{\infty , k}(r) = \{\sum_{i=0}^{k-1}{a_i}x^i : -r \leq a_i \leq r \} $ \newline \newline
 \texttt{Encrypt}($m \in \{0,1\} , pk$): 
-\newline \phantom{x}\hspace{3ex}  $R(x) \leftarrow_{R}(B_{\infty , N}(\mu/2)$
+\newline \phantom{x}\hspace{3ex}  $R(x) \leftarrow_{R}B_{\infty , N}(\mu/2)$
  \; $C(x)=m+2\cdot R(x)$ 
@@
 \textbf{Security of SWHE scheme :} The scheme is semantically secure under the assumption that the \textit{Polynomial Coset Problem}(PCP) is hard.
-One wayness of the encryption is believed to be true under the assumption that the \textit{Bounded distance decoding problem} BDDP is hard while key recovery is assumed to be difficult under the assumption that the \textit{Small Principal Ideal Problem}(SPIP) is hard.
+One-wayness of the encryption is believed to be true under the assumption that the \textit{Bounded distance decoding problem} BDDP is hard while key recovery is assumed to be difficult under the assumption that the \textit{Small Principal Ideal Problem}(SPIP) is hard.
 Solutions to all of these problems have either a sub-exponential algorithm or in general take exponential time.
@@
 when $F(x)= x^N+1$.
-Turning the SWHE to FHE is achieved by recasting Gentry's method for the parameters of this scheme.
-To achieve this, authors define another algorithm \texttt{Recrypt} which takes a ciphertext $c$ and re-encrypts it to $c_{new}$, whilst at the same time removing some of the noise in $c$.
+Turning the SWHE scheme to FHE scheme is achieved by recasting Gentry's method for the parameters of this scheme.
+To achieve this, authors define another algorithm \texttt{Recrypt} which takes a cipher-text $c$ and re-encrypts it to $c_{new}$, whilst at the same time removing some of the noise in $c$.
 This requires augmenting the encryption key with some additional information by extending the \texttt{KeyGen} algorithm.
 The FHE scheme now generates $s_1$ uniformly random integers $B_i$ in $[-p, \ldots, p]$ such that there exists a subset $S$ of $s_2$ elements with $\sum_{j \in S}{B_j}= B$ over integers.
-By defining $sk_i =1$ iff $i\in S$ and taking $c_i=\texttt{Encrypt}(sk_i,pk)$ we generate a new public key which contains hint of the secret key $sk$.
+By defining $sk_i =1$ iff $i\in S$(else $sk_i=0$) and taking $c_i=\texttt{Encrypt}(sk_i,pk)$ we generate a new public key which contains hint of the secret key $sk$.
 The public key now comprises of \[(p, \alpha, s_1, s_2, \{c_i, B_i\}_{i=1}^{s1})\]
-To ensure that the hint does not provide any considerable advantage to an attacker, the underlying \textit{sparse subset-sum problem} SSSP must remain remain hard.
-If we take $s_1$ to be slightly greater than $\mathrm{log}_{2}(p)$, then we need to select $s_2$ such that $\sqrt {{s_1}  \choose {s_2} } \leq 2 ^{N/\epsilon}$ so as to ensure that SSSP difficulty is at least as difficult as the difficulty of the BDDP underlying the SWHE scheme.
+To ensure that the hint does not provide any considerable advantage to an attacker, the underlying \textit{sparse subset-sum problem} SSSP must remain hard.
+If we take $s_1$ to be slightly greater than $\mathrm{log}_{2}(p)$, then we need to select $s_2$ such that $\sqrt {{s_1}  \choose {s_2} } > 2 ^{N/\epsilon}$ so as to ensure that SSSP difficulty is at least as difficult as the difficulty of the BDDP underlying the SWHE scheme.
 
 \subsection{Considered Implementations}
-We used the open source implementation Scarab library \cite{hcrypt}  version $1.0.0$ of the Smart-Vercauteren scheme which is a part of \textsc{hcryptProject}.
+We used the open source implementation Scarab library \cite{hcrypt}  version $1.0.0$ of the SV scheme which is a part of \textsc{hcryptProject}.
 The implementation is in beta version.
-The software requires GMP(we tested with version $5.1.2$) \cite{gmp} : GNU Multiple Precision Arithmetic Library; FLINT version $1.6$ \cite{flint}: Fast Library for Number Theory; MPIR (we tested with $2.6.0$) \cite{mpir} : Multiple Precision Integers and Rationals and MPFR (tested with version $3.1.2$) \cite{mpfr} :  Multiple-Precision Floating-point computations with correct Rounding.
+The software requires GMP(we tested with version $5.1.2$) \cite{gmp} : GNU Multiple Precision Arithmetic Library; FLINT version $1.6$ \cite{flint}: Fast Library for Number Theory; MPIR (we tested with $2.6.0$) \cite{mpir} : Multiple-Precision Integers and Rationals and MPFR (tested with version $3.1.2$) \cite{mpfr} :  Multiple-Precision Floating-point computations with correct Rounding.
 Linux is supposed to be the only supported platform.
@@
 
-\autoref{funs} presents the list of functions provided by the implementation with their description.
+\autoref{funs} presents the list of functions provided by Scarab with their description.
 The library provides a file \texttt{test.c} where a user can write his own functions to test different operations.
@@
 Both these machines were x86-64 platform running Linux kernel $3.2.0$-$45$-generic  and used GCC $4.6.3$ C compiler.
-The first machine housed Intel Core i3 M330 (2.13GHz x 4) processor and will be referred in this article as machine M1 while the other used  housed Intel Core i5 M2430 (2.40GHz x 4) processor and will be referred as machine M2.
-During the experiments these machines were not connected to any network and were running ony the most needed applications.
+The first machine housed Intel Core i3 M330 (2.13GHz x 4) processor and will be referred in this article as machine M1 while the other housed Intel Core i5 M2430 (2.40GHz x 4) processor and will be referred as M2.
+During the experiments these machines were not connected to any network and were running only the most needed applications.
 
-\subsection{Cost of Cryptosytem}
- In the SV scheme, performing any operation on encrypted bits requires  \texttt{KeyGen}, \texttt{Encrypt}, \texttt{Add},\texttt{ Mult}, \texttt{Recrypt}, \texttt{Decrypt} and hence we measure their performance in terms of run time.
-These measuremens are done by varying the parameter $N$ that determines the degree of all intermediate polynomials in the cryptostystem and keeping all other parameters fixed.
-The measurements in this section were taken on the machine M2.
-We can infer that the cost of these functions increase with the increase of the the degree  polynomials.
+\subsection{Cost of the Cryptosystem}
+ In the SV scheme, performing any operation on encrypted bits requires  \texttt{KeyGen}, \texttt{Encrypt}, \texttt{Add},\texttt{ Mult}, \texttt{Recrypt}, \texttt{Decrypt}, and hence we measure their performance in terms of run time.
+These measurements are done by varying the parameter $N$(keeping all other parameters fixed) that determines the degree of all intermediate polynomials of the cryptosystem.
+The measurements in this section were taken on M2.
+From \autoref{common cost}, we can infer that the cost of these functions increase with the increase of the degree of the polynomial $F(x)$.
+Futhermore, we observe that the size of the public key is increasing linearly with $n$  where $N=2^n$.
 
@@
 
-We can see that the size of the public key is increasing lineary with $n$ such that $N=2^n$ 
 \autoref{fig:image_f2} measures execution time for \texttt{KeyGen} for fixed values of parameters: $N=8$ and $\eta = 2^{384}$.
-It shows a variation from 0.2 s to 14.41 s with high density in the interval [0.2s, 2s].
+It shows a variation from 0.2 s to 14.41 s with a very high density in the interval [0.2s, 2s].
 
@@
 
-As the time taken by \texttt{KeyGen} depends on how fast the prime $p$ is found, its cost is related with the density of primes which is $\frac{1}{\mathrm{log(n)}}$.
+As the time taken by \texttt{KeyGen} depends on how fast the prime $p$ is found, its cost is related with the density of primes i.e.
+$\frac{1}{\mathrm{log(n)}}$.
 \autoref{fig:image_f2} is in accordance with the density of primes over $\mathbb{N}$.
@@
 
-Using (1), and (2), we calculate the theoretical security level and the depth provided by the crytosystem, and we find that security level increases with increasing $N$ and for $\mu =4$ and $\eta=2^{384}$ fixed.
-But \autoref{common cost} show that the cost of the cryptosystem increases(ex.
-15 mins for \texttt{KeyGen}).
+Using (1), and (2), we calculate the theoretical security level and the depth provided by the cryptosystem, and we find that the security level increases with increase in $N$ and for $\mu =4$ and $\eta=2^{384}$ fixed.
+\autoref{common cost} asserts that  \texttt{KeyGen} takes 15mins for $N=2^5$.
 We note that for $N \geq 2^6$, \texttt{KeyGen} takes hours.
@@
   \centering
-  \caption{Run time (ms)}
+  \caption{Security, Depth}
 \begin{tabular}{|c|c|c||}
@@
 
-\autoref{tab:tradeofftab1} presents the security-cost tradeoff for 10000 multiplications as a function of $\eta$.
+\autoref{tab:tradeofftab1} presents the security-cost trade-off for 10000 multiplications as a function of $\eta$.
 We remark that : decreasing $\eta$ with other parameters fixed increases the security of the system at the cost of decreasing the depth.
@@
 Consider a program which involves the following test on two inputs : \texttt{if(a > b) instruction\_1; else instruction\_2;}.
-As the cloud does not know the result of the test\texttt{ a' > b'} where \texttt{a'} and \texttt{b'} are the encryption of \texttt{a} and \texttt{b}, he does not know which of the instructions he has perform.
+As the cloud does not know the result of the test\texttt{ a' > b'} where \texttt{a'} and \texttt{b'} are the encryption of \texttt{a} and \texttt{b}, he does not know which of the instructions he has to perform.
 In fact, he performs both the instructions by transforming the actual program into : \texttt{test(a'> b')*} \texttt{instruction\_1 +}$\neg$\texttt{test(a'> b')*instruction\_2}, where \texttt{test()}  is a function on encrypted inputs \texttt{a'}, \texttt{b'} and returns an encryption of $1$ iff \texttt{a > b}.
@@
 
+\newtheorem{theorem}{Lemma}
+\begin{theorem}
+Algorithm \autoref{Code:algo} returns the maximum and the minimum of the input bit sequences. 
+\end{theorem}
+
+\begin{proof}
+
+  Consider $x_i = a_i'b_i'+\neg(a_i')\neg(b_i') $.
+$x_i$ is $1$ iff $a_i'$ and $b_i'$ are equal.
+We note that, $bitEqual$ is the product of $x_i$ and is $1$ at the $t^{th}$ iteration iff $a_i'=b_i'$ for all $i < t$.
+The term $\neg(b_i')a_i'$ is $1$ iff $a_i'=1$ and $b_i'=0$.
+Hence at the $t^{th}$ iteration, the algorithm using $bitEqual$ tests if the previous bits were equal.
+Hence, $aIsGreater$ is $1$ iff at any stage  $\neg(b_t')a_t'=1$ and the previous bits were equal.
+
+Max and Min regenerate $a_i$ and $b_i$ and hence contain the correct result.  
+\end{proof}
+
 \restylealgo{algoruled}
@@
 
-\newtheorem{theorem}{Lemma}
-\begin{theorem}
-Algorithm \autoref{Code:algo} returns the maximum and the minimum of the input bit sequences. 
-\end{theorem}
-
-\begin{proof}
-
-  Consider $x_i = a_i'b_i'+\neg(a_i')\neg(b_i') $.
-$x_i$ is $1$ iff $a_i'$ and $b_i'$ are equal.
-We note that, $bitEqual$ is the product of $x_i$ and is $1$ at the $t^{th}$ iteration iff $a_i'=b_i'$ for all $i < t$.
-The term $\neg(b_i')a_i'$ is $1$ iff $a_i'=1$ and $b_i'=0$.
-Hence at the $t^{th}$ iteration, the algorithm using $bitEqual$ tests if the previous bits were equal.
-Hence, $aIsGreater$ is $1$ iff at any stage  $\neg(b_t')a_t'=1$ and the previous bits were equal.
-
-Max and Min regenerate $a_i$ and $b_i$ and hence contain the correct result.  
-\end{proof}
 \textbf{Theoretical Cost :} Algorithm \autoref{Code:algo} uses $5n$ \texttt{AND} gates, $2n$ \texttt{OR} gates and $2n$ \texttt{NOT} gates to find the larger of the two bit sequences and then to regenerate the maximum and the minimum $4n$ \texttt{AND} gates and $2n$ \texttt{NOT} and \texttt{OR} gates.
@@
 
-\textbf{Experimental Analysis :} We measure the run time from $n=1$ to $32$ bits, we find a linear cost which confirms the $\theta(n)$ complexity.
+\textbf{Experimental Analysis :} We measure the run time to perform min-max by varying $n=1$ to $32$ bits, \autoref{image_f2}. We find a linear cost which confirms the $\theta(n)$ complexity.
 
@@
 In this case, a circuit(program) transformation is required and which often makes the size longer than the one on non-encrypted data.
-Hence, this provides information on increase in size of the circuit(when passing from non-encrypted to encrypted data) and the associated trade-off.
-We study the security-cost trade-off for the following problems :
-
+Hence, this provides information on the increase in size of the circuit(when passing from non-encrypted to encrypted data) and the associated trade-off.
+We study the security-cost trade-off for the following problems : \newline
 1. \textbf{XOR of an $n$-bit sequence}\\
@@
 \subsection{Size of Evaluation Circuit}
-As the implementations provide addition and multiplication of cipher-texts,  size in terms of \texttt{XOR} and \texttt{AND} gates are provided for each problem.
-
+As the implementation(\autoref{funs}) provides addition and multiplication of cipher-texts,  size in terms of \texttt{XOR} and \texttt{AND} gates are provided for each problem. \newline \newline
 \textbf{XOR of $n$-bits :} \texttt{XOR} of $n$-bits requires $n-1$ \texttt{XOR} gates. \newline \newline
 \textbf{Majority of $n$-bits :} Majority bit is evaluated by obtaining the sum of the bits and then returning the result of the comparison of the sum and $n/2$.
-This comparison is done using algorithm \autoref{Code:algo}.
-The operation is interesting in the sense that if the same program is evaluated on the user's side, he has to store the sum of the bits, hence  needs $\mathrm{\lfloor\log_{2}n \rfloor +1}$ bits of memory.
+The comparison is done using algorithm \autoref{Code:algo}.
+This operation is interesting in the sense that if the same program is evaluated on the user's side, he has to store the sum of the bits, hence  needs $\mathrm{\lfloor\log_{2}n \rfloor +1}$ bits of memory.
 However, if he performs the operation remotely on a cloud, he only requires a constant number of bits to retrieve the result.
@@
 \newline \newline
-\textbf{Sum of two unsigned integers :} This program select the first $32$-bits sequences of the $2$ integers and does the sum of themexactly like the previous algorithm and then perform the sum with next $32$-bits sequences with the carry from the previous addition untill there is no sequence left.n in the Scarab library).
-So this program has approximately the same linear cost with the previous one \newline \newline
+\textbf{Sum of two unsigned integers :} This program selects the first $32$-bits sequences of the $2$ integers and does the sum of them exactly like the previous algorithm and then perform the sum with next $32$-bits sequences with the carry from the previous addition until there is no sequence left.
+So this program has approximately the same linear cost as the previous one.
+\newline \newline
 \textbf{Product of two $n\times n$ matrices :} This requires $n^3$ \texttt{AND} gates and \texttt{$n^2(n-1)$} \texttt{XOR} gates. \newline \newline
@@
 \label{Sec:Eval}
-In this we execute the implementations of the programs above, and we measure their wall time and compare this cost with the theoretical complexity depending on the sizes of the input data.
-The figure \autoref{fig:image_sf7} represents minumum and maximum wall time of \texttt{XOR} done on random inputs.
-We can see that the wall time increase lineary with number of bits which confirm the theoretical cost.
+We execute the implementations of the above programs, and we measure their wall time and compare the cost with the theoretical complexity depending on the sizes of the input data.
+For each test, $5-10$ random samples were taken.
+These were generated using the Unix \texttt{rand()} function by setting the seed using \texttt{srand(time(NULL))}.
+
+ \autoref{fig:image_sf7} represents minimum and maximum wall time of \texttt{XOR}.
+We can see that the wall time increases linearly with number of bits which confirm the theoretical cost.
+We notice the same complexity for both \texttt{Bit Majority} \autoref{fig:image_sf0bis} and \texttt{sum of integers} \autoref{fig:image_sf1}.
+We further confirm the $O(n^{3})$ complexity for the \texttt{matrix product} \autoref{fig:image_sf2}.
+These experiments were performed on M2.
+
 \begin{figure}[!H]%on ouvre l'environnement figure
@@
 
-We notice the same complexity for both \texttt{Bit Majority} and \texttt{sum of integers}\autoref{fig:image_sf1}.
-\begin{figure}[!H]%on ouvre l'environnement figure
+\begin{figure}%on ouvre l'environnement figure
+\centering
+\includegraphics[width=5cm, height=4cm]{f8.pdf} 
+\caption{Wall time for bit majority} 
+\label{fig:image_sf0bis} %l'étiquette pour faire référence à cette image
+\end{figure}
+\begin{figure}%on ouvre l'environnement figure
 \centering
@@
 
-And we confirm as well the $O(n^{3})$ complexity for the \texttt{matrix product}\autoref{fig:image_sf2}.
-\begin{figure}[!H]%on ouvre l'environnement figure
+\begin{figure}%on ouvre l'environnement figure
 \centering
@@
 
-\begin{figure}[!h]
+\begin{figure}
 \centering
-\includegraphics[width=7cm]{fsort3.pdf} 
-\caption{Runtime for Insertion sort, nbit=4} 
+\includegraphics[width=6cm, height=6cm]{fsort3.pdf} 
+\caption{Run time for Insertion sort, nbit=4} 
 \label{fig:image_sf3} %l'étiquette pour faire référence à cette image
@@
 
-\begin{figure}[!h] %on ouvre l'environnement figure
+\begin{figure} %on ouvre l'environnement figure
 \centering
-\includegraphics[width=7cm]{fsort4.pdf} 
-\caption{Runtime for Insertion sort, nbit=6} 
+\includegraphics[width=6cm, height=6cm]{fsort4.pdf} 
+\caption{Run time for Insertion sort, nbit=6} 
 \label{fig:image_sf4} %l'étiquette pour faire référence à cette image
@@
 
-\begin{figure}[!h] %on ouvre l'environnement figure
+\begin{figure} %on ouvre l'environnement figure
 \centering
-\includegraphics[width=7cm]{fsort5.pdf} 
+\includegraphics[width=6cm, height=6cm]{fsort5.pdf} 
 \caption{Run time for Insertion sort, nbit=8} 
@@
 
-\begin{figure}[!h]%on ouvre l'environnement figure
+\begin{figure}%on ouvre l'environnement figure
 \centering
-\includegraphics[width=7cm]{fsort6.pdf} 
+\includegraphics[width=6cm, height=6cm]{fsort6.pdf} 
 \caption{CPU time for Insertion sort, nbit=4} 
@@
 
-\begin{figure}[!H] %on ouvre l'environnement figure
+\begin{figure} %on ouvre l'environnement figure
 \centering
-\includegraphics[width=7cm]{fsort8.pdf} 
+\includegraphics[width=6cm, height=6cm]{fsort8.pdf} 
 \caption{CPU time for Insertion sort, nbit=6} 
@@
 
-\begin{figure}[!H]%on ouvre l'environnement figure
+\begin{figure}%on ouvre l'environnement figure
 \centering
-\includegraphics[width=7cm]{fsort7.pdf} 
+\includegraphics[width=6cm,height=6cm]{fsort7.pdf} 
 \caption{CPU time for Insertion sort, nbit=8} 
@@
 
-\begin{figure}[!H]
+\begin{figure}
 \centering
-\includegraphics[width=7cm]{fsort2.pdf} 
-\caption{Runtime Comparison for insertion sort} 
+\includegraphics[width=6cm, height=6cm]{fsort2.pdf} 
+\caption{Run time Comparison for insertion sort} 
 \label{fig:image_sf2} %l'étiquette pour faire référence à cette image
@@
 
-\begin{figure}[!H]%nouvre l'environnement figure
+\begin{figure}%nouvre l'environnement figure
 \centering
-\includegraphics[width=7cm]{fsort1.pdf} 
+\includegraphics[width=6cm, height=6cm]{fsort1.pdf} 
 \caption{Curve fitting for insertion sort}
@@
 The experiments on the sorting algorithms were performed on the machine M1. 
-For each test, $5-10$ random samples were taken.
-These were generated using the Unix \texttt{rand()} function by setting the seed using \texttt{srand(time(NULL))}.
-
-Intially, the cryptographic parameters were set to $(N = 8, \nu = 2^{384}, \mu = 4, s_1 = 8, s_2 = 5)$ which is the default setting in the software.
+Initially, the cryptographic parameters were set to $(N = 8, \nu = 2^{384}, \mu = 4, s_1 = 8, s_2 = 5)$ which is the default setting in the software.
 \autoref{fig:image_sf3},\autoref{fig:image_sf4}, \autoref{fig:image_sf5}, \autoref{fig:image_sf6}, \\ \autoref{fig:image_sf8}, \autoref{fig:image_sf7} and \autoref{fig:image_sf2} show the variation of CPU time and Wall time with the increase in the number of sequences to sort and the number of bits.
@@
 When we increase the security of the system by setting the parameters to  $(N = 256,\eta  = 16, \mu = 2, s_1 = 5000, s_2 = 5)$(as suggested in \cite{cryptoeprint:2009:571}) which ensures $25$ bits of security, the Odd-Even sorting algorithm on  $4$ sequences, each of $4$ bits takes hours.
-By lowering the security level to only $8$ bits using the parameters :$(N = 16, \eta = 32, \mu = 2, s_1 = 85, s_2 = 5)$, the result did not decrypt to the desired output; which we believe is an implementation bug in the bootstrapping mechanism.
-Lowering the security even further to only $5$ bits using the parameters: $(N = 8, \eta = 2^8, \mu = 4, s_1 = 65, s_2 = 5)$, and testing odd-even sorting for $32$ sequences of $6$ bits each took more than an hour.
+By lowering the security level to only $16$ bits using the parameters :$(N = 16, \eta = 32, \mu = 2, s_1 = 85, s_2 = 5)$, the result did not decrypt to the desired output; which confirms to the theory that $\epsilon$ must be greater than 1 for correct decryption.
+Lowering the security even further to only $2$ bits using the parameters: $(N = 8, \eta = 2^8, \mu = 4, s_1 = 65, s_2 = 5)$, and testing odd-even sorting for $32$ sequences of $6$ bits each took more than an hour.
 However, increasing $\mu$ also increases security, and setting the parameters to :  $(N = 8, \eta = 2^{384}, \mu = 8, s_1 = 8, s_2 = 5)$ we obtained the results as in \autoref{OddEvensort2}.
-The results show that this set of parameters provide a better security and at almost no extra cost.
-For this result to be conclusive, we need to perfom tests for large $n$.
+The results show that this set of parameters provide a better security(than the default parameters) and at almost no extra cost.
+For this result to be conclusive, we need to perform tests for large $n$.
 For our last test, we set the parameters to  $(N = 8, \eta = 2^{200}, \mu = 8, s_1 = 8, s_2 = 5)$ which gave us incorrect decryption.
-We note that decryption fails in case the depth is too small for recrypt to function.
+We note that decryption fails in case the depth is too small for re-crypt to function.
 
 \section{Conclusion}
-With the examples and the programs discussed, we conclude that the tranformation of a non-straight line program on unencrypted data(with branching) into a straight line program on encrypted data increases the circuit complexity.
-We experimentally measured the cost of different operations on encrypted data.
-The existing implementation of Smart-Vercauteren scheme remains practical only for $1$ bit of security, when a user wants to apply a sorting algorithm on his encrypted bit sequences.
+With the examples and the programs discussed, we conclude that the transformation of a non-straight-line program on unencrypted data(with branching) into a straight line program on encrypted data increases the circuit complexity.
+We experimentally measured the cost of different operations on encrypted data and the security-cost trade-off for certain operations.
+The existing implementation of Smart-Vercauteren scheme remains practical only for very low level of security, when a user wants to apply a sorting algorithm on his encrypted bit sequences.
 

### 2013-06-17 Report/article.tex

@@
 
+\subsection{Non-secret branching}
+
+We consider a scenario where a user wants to compute the \texttt{xor} of an $n$ bit sequence $a_0,a_1,\ldots, a_{n-1}$. A program on the unencrypted bits would be :
+
+ \phantom{x} \texttt{res=0, i=0;}
+\newline \phantom{x} \texttt{do\{ }
+\newline \phantom{x} \hspace{9ex} \texttt{res=res$\oplus$a\_i;}
+\newline \phantom{x} \hspace{9ex} \texttt{i++;} 
+\newline   \phantom{x} \} \texttt{while(i < n);} 
+\newline  \phantom{x} \texttt{return res;}\\
+
+This program can be directly be used by the cloud, as it only has to check \texttt{if(i<n)} where $i$ and $n$ are unencrypted integers.
+
+\subsection{Secret Branching}
+
 Consider a program which involves the following test on two inputs : \texttt{if(a > b) instruction\_1; else instruction\_2;}.
@@
 
-\textbf{Another transformation}: We consider the following program that a cloud receives : \\
+\subsection{Secret Conditional branching}
+We consider the following program that a cloud receives : \\
  \phantom{x} \texttt{i=0, res=0;}

### 2013-06-17 Report/article.tex
test modified

--- 2013-06-17 Report/article.tex
@@
 We present an analysis of security-cost trade-off for a homomorphic encryption scheme executing such programs.
-Analysis is based on the measurements (CPU time and  Wall time) taken for programs : performing \texttt{XOR} of an $n$-bit sequence,  evaluating the sum of two $n$-bit sequences, determining the majority bit of an $n$-bit sequence, finding the product of two $n \times n$ matrices, and sorting $n$ bit sequences of length $nbits$ (usually requiring validity of a boolean predicate).
+Analysis is based on the measurements (CPU time and  Wall time) taken for programs : performing \texttt{XOR} of an $n$-bit sequence,  evaluating the sum of two $n$-bit integers, determining the majority bit of an $n$-bit sequence, finding the product of two $n \times n$ matrices, and sorting $n$ bit sequences of length $nbits$ (usually requiring validity of a boolean predicate).
 The evaluation is performed on an available implementation ``Scarab library'' of a fully homomorphic encryption scheme.
@@
 A fully homomorphic encryption scheme is a tuple of an encryption $\mathcal{E}$, decryption $\mathcal{D}$ algorithm together with an efficient algorithm $Eval_\mathcal{E}$ that evaluates any circuit $C$ on any cipher-texts $c_i \leftarrow \mathcal{E}(pk, m_i)$.
-The property that it can evaluate the encryption of addition and multiplication of two plain-texts (without access to the secret key) allows it to arbitrarily compute any function on encrypted data without the decryption key.
-However prior to \cite{homenc}, we did not have a viable construction.
+The property that it can evaluate the encryption of addition and multiplication of two plain-texts (without access to the secret key) allows it to arbitrarily compute any boolean function on encrypted data without the decryption key.
+However, we assume that no branching is involved.
+Prior to \cite{homenc}, we did not have a viable construction.
 
@@
 
-The immediate question that is raised, is how do we perform the transformation and how does the circuit size change to adapt to computations on encrypted data.
+The immediate question that is raised, is how do we perform the transformation and how does the circuit size change to adapt to computations on encrypted data, especially when the function involves \texttt{if-then-else} condition.
 We provide an answer by analyzing circuit complexity for finding the minimum-maximum of two $n$-bit sequences in \autoref{sec:ex} and for some other operations in \autoref{sec:bm}.
@@
 
-\section{Fully homomorphic Encryption scheme (FHE) }
+\section{Overview of Fully homomorphic Encryption scheme (FHE) }
 
@@
 It also provides a header file \texttt{parameters.h} to set the parameters $N, \eta, \mu, s_1$ and $ s_2$ of the cryptosystem.
-To simplify our computational circuit, we added two basic functions \texttt{or(mpz\_t res, mpz\_t a, mpz\_t b, fhe\_pk\_t pk);} and \texttt{not(mpz\_t res, mpz\_t a, fhe\_pk\_t pk);} which compute the logical \texttt{or}(+) of encrypted bits and the negation ($\neg$) of an encrypted bit respectively.
+To simplify our computational circuit, we added two basic functions \texttt{or(mpz\_t res, mpz\_t a, mpz\_t b, fhe\_pk\_t pk);} and \texttt{not(mpz\_t res, mpz\_t a, fhe\_pk\_t pk);} which compute the logical \texttt{or}(denoted by $\vee$) of encrypted bits and the negation (denoted by $\neg$) of an encrypted bit respectively.
+In this article we denote logical \texttt{AND} using $\wedge$ and \texttt{XOR} using $\oplus$.
 
@@
 
-Consider a program which involves the following test on two inputs : \texttt{if(a > b) instruction\_1; else instruction\_2;}.
-As the cloud does not know the result of the test\texttt{ a' > b'} where \texttt{a'} and \texttt{b'} are the encryption of \texttt{a} and \texttt{b}, he does not know which of the instructions he has to perform.
-In fact, he performs both the instructions by transforming the actual program into : \texttt{test(a'> b')*} \texttt{instruction\_1 +}$\neg$\texttt{test(a'> b')*instruction\_2}, where \texttt{test()}  is a function on encrypted inputs \texttt{a'}, \texttt{b'} and returns an encryption of $1$ iff \texttt{a > b}.
+\textbf{Non-secret branching}: We consider a scenario where a user wants to compute the \texttt{xor} of an $n$ bit sequence $a_0,a_1,\ldots,$ \\ $a_{n-1}$. A program on the unencrypted bits would be :
+
+ \phantom{x} \texttt{res=0, i=0;}
+\newline \phantom{x} \texttt{do\{ }
+\newline \phantom{x} \hspace{9ex} \texttt{res=res$\oplus$a\_i;}
+\newline \phantom{x} \hspace{9ex} \texttt{i++;} 
+\newline   \phantom{x} \} \texttt{while(i < n);} 
+\newline  \phantom{x} \texttt{return res;}\\
+
+This program can directly be used by the cloud, as it only has to check \texttt{if(i<n)} where $i$ and $n$ are unencrypted integers.
+
+\subsection{Secret Branching}
+
+Consider a program which involves the following test on two inputs : \texttt{if(a > b) instruction\_1; else instruction\_2;} If the cloud could know how to perform \texttt{if(a' > b') instruction\_1; else instruction\_2;} (where \texttt{a'} and \texttt{b'} are the encryptions of \texttt{a} and \texttt{b}) without executing both the instructions, he would know the decryption of the comparison \texttt{a'>b'}, which means that he would have information on \texttt{a} and \texttt{b}.
+The cloud transforms the actual program into : \texttt{test(a'> b')$\wedge$} \texttt{instruction\_1 +}$\neg$\texttt{test(a'> b')$\wedge$ } \\ \texttt{instruction\_2}, where \texttt{test()}  is a function on encrypted inputs \texttt{a'}, \texttt{b'} and returns an encryption of $1$ iff \texttt{a > b}.
 Hence, if the program used has branching i.e.
@@
 
-\textbf{Another transformation}: We consider the following program that a cloud receives : \\
+\subsection{Secret Conditional Stopping}
+We consider the following program that a cloud receives where \texttt{f} is a boolean function. : \\
  \phantom{x} \texttt{i=0, res=0;}
@@
 In this case, the cloud needs to transform a loop with conditional stopping into a loop with unconditional branching. We propose the following transformation : \\
- \phantom{x} \texttt{endLoop=0', res=0', i=0;}
+ \phantom{x} \texttt{cont=1', res=0', i=0;}
 \newline \phantom{x} \texttt{do\{ }
-\newline \phantom{x} \hspace{6ex} \texttt{endLoop = $\neg$cond\_i;}
-\newline \phantom{x} \hspace{6ex} \texttt{res = $\neg$endLoop*f(i)+($\neg$cond\_i)*res;}
+\newline \phantom{x} \hspace{6ex} \texttt{res = res$\vee$(cont$\wedge$f(i)$\wedge\neg$cond\_i);}
+\newline \phantom{x} \hspace{6ex} \texttt{cont = cont$\wedge$cond\_i;}
 \newline \phantom{x} \hspace{6ex} \texttt{i++;} 
 \newline   \phantom{x} \} \texttt{while(i < n);} 
+\newline \phantom{x} \texttt{res=($\neg$(cond\_i)$\wedge$res)$\vee$(f(n)$\wedge$cond\_i);}
+\newline 
+\textbf{Correctness of the code :} We consider the following three cases :
 
-\textbf{Correctness of the code :} If \texttt{cond\_i} is always \texttt{true}, \texttt{endLoop} is always \texttt{false} and \texttt{res=f(n)}.
-If at the $t^{th}$ iteration, \texttt{cond\_i} is \texttt{false}, \texttt{endLoop} becomes \texttt{true} and hence \texttt{res} contains its previous value $f(t-1)$.
+1. \texttt{cond\_i} \textbf{is always} \texttt{true}: res equals $f(n)$ after the end of the loop.\newline
+\phantom{x} 2.
+\texttt{cond\_i} is \texttt{true} for $i<t$ and \texttt{false} afterwards: \texttt{res} is \texttt{false} and \texttt{cont}=\texttt{true} for $i<t$.
+At $i=t$, \texttt{cond\_i}=\texttt{false}, so \texttt{res = f(t)}.
+For $i>t$ \texttt{cont}=\texttt{false} and so hence \texttt{res} retains its value till the end of the loop.
+\newline
+\phantom{x} 3.
+\texttt{cond\_i} is \texttt{false} for the first time at $i=t_1$ and becomes \texttt{true} at $i=t_2$ with $t_1<t_2$ : With the previous argument, \texttt{res=f(t\_1)}$\; \forall i<t_2$.
+At $i=t_2$, \texttt{$\neg$(cond\_i)}=\texttt{false} hence \texttt{res} retains the value \texttt{f(t\_1)} till the end of the loop.
 
@@
 \newline \phantom{x} \texttt{do\{ }
-\newline \phantom{x} \hspace{6ex} \texttt{ if(a[i]==1 \&\& b[i]==0) 
-\newline \phantom{x} \hspace{14ex}aIsGreater = 1;}
+\newline \phantom{x} \hspace{6ex} \texttt{aIsGreater = a\_i$ \wedge \neg$(b\_i);} 
 \newline \phantom{x} \hspace{7ex} \texttt{i++;} 
-\newline   \phantom{x} \} \texttt{while(i < n);}
+\newline   \phantom{x} \} \texttt{while(i<n \&\& (a\_i$\wedge$b\_i) $\vee$ ($\neg$(a\_i)$\wedge \neg$(b\_i));}
+\newline \newline
+where \texttt{ (a\_i$\wedge$b\_i) $\vee$ ($\neg$(a\_i)$\wedge \neg$(b\_i)} tests the equality of the bits.
 
-We note that, we do not know how an optimized version :  using \texttt{break} to exit the loop once \texttt{aIsGreater} is set to \texttt{true}, could be transformed into a program for the cloud.
-We believe that the possibility to quit the loop would mean that the cloud knows the result of the \texttt{if(condition)}.
-
-We propose the transformed algorithm \autoref{Code:algo} of the above program.
-It inspects the relative magnitude of pairs of bits, starting from the most significant bit and gradually proceeding towards lower significant bits until an inequality is found.
+We propose the transformed algorithm \autoref{Code:algo} of the abov
+e program.
+It recasts the same ideas used for the previous example.
+The algorithm inspects the relative magnitude of pairs of bits, starting from the most significant bit and gradually proceeding towards lower significant bits until an inequality is found.
 
@@
 
-  Consider $x_i = a_i'b_i'+\neg(a_i')\neg(b_i') $.
+  Consider $x_{-1}=1$ and $x_i = (a_i'\wedge b_i)'\vee (\neg(a_i')\wedge\neg(b_i')) $ in line 5.
 $x_i$ is $1$ iff $a_i'$ and $b_i'$ are equal.
-We note that, $bitEqual$ is the product of $x_i$ and is $1$ at the $t^{th}$ iteration iff $a_i'=b_i'$ for all $i < t$.
-The term $\neg(b_i')a_i'$ is $1$ iff $a_i'=1$ and $b_i'=0$.
-Hence at the $t^{th}$ iteration, the algorithm using $bitEqual$ tests if the previous bits were equal.
-Hence, $aIsGreater$ is $1$ iff at any stage  $\neg(b_t')a_t'=1$ and the previous bits were equal.
+We denote by $bitEqual_{t}$ the value of $bitEqual$ at $i=t$ before assignment at line 5.
+In fact, $bitEqual_{t} = \bigwedge_{i<t}{x_i} $ at this stage and it is $1$ iff $a_i'=b_i'$ for all $i < t$.
+
+The term $\neg(b_i')\wedge a_i'$ at line 4 is $1$ iff $a_i'=1$ and $b_i'=0$.
+Hence at the iteration $i=t$, the algorithm using $bitEqual$ tests if $a'_i = b'_i \;\forall i<t$, while using $\neg(b_t')\wedge a_t'$, the algorithm tests if $a_t>b_t$.
+Hence $aIsGreater$ at $i=t$ is set to $1$ if all the bits till $i<t$ are equal and $a_t>b_t$.
+Once $aIsGreater$ is set to 1, it retains its value till the end of the loop.
 
@@
 
-     $aIsGreater \leftarrow (aIsGreater +\neg(b_i')a_i') bitEqual$ \;
-     $bitEqual \leftarrow bitEqual(a_i'b_i' + \neg(a_i)'\neg(b_i'))$		       	
+     $aIsGreater \leftarrow aIsGreater \vee (\neg(b_i')\wedge a_i'\wedge bitEqual$) \;
+     $bitEqual \leftarrow bitEqual\wedge((a_i'\wedge b_i')\vee(\neg(a_i)'\wedge\neg(b_i')))$		       	
  }
@@
 
-     $Max_i \leftarrow aIsGreater\cdot a_i' + \neg(aIsGreater)b_i'$ \;
+     $Max_i \leftarrow (aIsGreater \wedge a_i') \vee (b_i'\wedge \neg(aIsGreater))$ \;
 
-     $Min_i \leftarrow  \neg(aIsGreater)a_i' + aIsGreater \cdot b_i'$ \;
+     $Min_i \leftarrow  (a_i' \wedge \neg(aIsGreater) ) \vee (aIsGreater \wedge b_i')$ \;
 
@@
 1. \textbf{XOR of an $n$-bit sequence}\\
-3. \textbf{Majority bit of an $n$-bit sequence} \\
-2. \textbf{Sum of :}  two unsigned integers of $32$ bits  \newline 
-2. \textbf{Sum of :}  two unsigned integers  \newline 
+2. \textbf{Majority bit of an $n$-bit sequence} \\
+3. \textbf{Sum of :}  a) two unsigned integers of $32$ bits  \newline 
+\phantom{x}\hspace{12ex} b) two unsigned integers of arbitrary  \newline \phantom{x}\hspace{15ex} number of bits  \newline
 4. \textbf{Product of two $n\times n$ boolean matrices} \\
@@
 \newline \newline
-\textbf{Product of two $n\times n$ matrices :} This requires $n^3$ \texttt{AND} gates and \texttt{$n^2(n-1)$} \texttt{XOR} gates. \newline \newline
+\textbf{Product of two $n\times n$ matrices :} Thes standard two loops algorithm requires $n^3$ \texttt{AND} gates and \texttt{$n^2(n-1)$} \texttt{XOR} gates. \newline \newline
 \textbf{Sorting :} Several straight-line programs for sorting have have been proposed in literature \cite{dk}, \cite{Batcher:1968:SNA:1468075.1468121}.
@@
 They accept $n$ which are powers of $2$.
-\newline \newline
-\textbf{Insertion sort :} When allowing for parallel comparators, bubble sort and insertion sort are identical. Hence $n(n-1)/2$ comparator gates are used for insertion sort.\newline \newline
-\textbf{Bitonic Sort :} The standard algorithm uses $n\mathrm{log}(n)·(\mathrm{log}(n)+1)/4$ comparator gates. \newline \newline
-\textbf{Odd-Even Merge sort :} Odd-Even merge sort requires  $n(\mathrm{log}^{2}(n)-1)/2 + 1 $ comparator gates.\newline
+
+\textbf{Insertion sort :} When allowing for parallel comparators, bubble sort and insertion sort are identical. Hence $n(n-1)/2$ comparator gates are used for insertion sort.
+
+\textbf{Bitonic Sort :} The standard algorithm uses $n\mathrm{log}(n)·(\mathrm{log}(n)+1)/4$ comparator gates.
+
+\textbf{Odd-Even Merge sort :} Odd-Even merge sort requires  $n(\mathrm{log}^{2}(n)-1)/2 + 1 $ comparator gates.
 We note that the sorting programs used do not increase the size of the circuit operating on encrypted input bit sequences.
@@
 
-\begin{figure}
-\centering
-\includegraphics[width=6cm, height=6cm]{fsort3.pdf} 
-\caption{Run time for Insertion sort, nbit=4} 
-\label{fig:image_sf3} %l'étiquette pour faire référence à cette image
-\end{figure}
-
-\begin{figure} %on ouvre l'environnement figure
-\centering
-\includegraphics[width=6cm, height=6cm]{fsort4.pdf} 
-\caption{Run time for Insertion sort, nbit=6} 
-\label{fig:image_sf4} %l'étiquette pour faire référence à cette image
-\end{figure}
-
-\begin{figure} %on ouvre l'environnement figure
-\centering
-\includegraphics[width=6cm, height=6cm]{fsort5.pdf} 
-\caption{Run time for Insertion sort, nbit=8} 
-\label{fig:image_sf5} %l'étiquette pour faire référence à cette image
-\end{figure}
-
-\begin{figure}%on ouvre l'environnement figure
-\centering
-\includegraphics[width=6cm, height=6cm]{fsort6.pdf} 
-\caption{CPU time for Insertion sort, nbit=4} 
-\label{fig:image_sf6} %l'étiquette pour faire référence à cette image
-\end{figure}
+ \textbf{Sorting :} 
+The experiments on the sorting algorithms were performed on machine M1. 
+Initially, the cryptographic parameters were set to $(N = 8, \nu = 2^{384}, \mu = 4, s_1 = 8, s_2 = 5)$ which is the default setting in the software.
+We measured CPU time and Wall time by varying the sequence length(nbit) and the number of sequences(n).
+We plot maximum and minimum time in minutes for nbit=6, \autoref{fsort8.pdf}.
 
@@
 
-\begin{figure}%on ouvre l'environnement figure
-\centering
-\includegraphics[width=6cm,height=6cm]{fsort7.pdf} 
-\caption{CPU time for Insertion sort, nbit=8} 
-\label{fig:image_sf7} %l'étiquette pour faire référence à cette image
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics[width=6cm, height=6cm]{fsort2.pdf} 
-\caption{Run time Comparison for insertion sort} 
-\label{fig:image_sf2} %l'étiquette pour faire référence à cette image
-\end{figure}
-
-\begin{figure}%nouvre l'environnement figure
-\centering
-\includegraphics[width=6cm, height=6cm]{fsort1.pdf} 
-\caption{Curve fitting for insertion sort}
-\label{fig:image_sf1} %l'étiquette pour faire référence à cette image
-\end{figure}
-
- \textbf{Sorting :} 
-The experiments on the sorting algorithms were performed on the machine M1. 
-Initially, the cryptographic parameters were set to $(N = 8, \nu = 2^{384}, \mu = 4, s_1 = 8, s_2 = 5)$ which is the default setting in the software.
  \autoref{fig:image_sf3},\autoref{fig:image_sf4}, \autoref{fig:image_sf5}, \autoref{fig:image_sf6}, \\ \autoref{fig:image_sf8}, \autoref{fig:image_sf7} and \autoref{fig:image_sf2} show the variation of CPU time and Wall time with the increase in the number of sequences to sort and the number of bits.
@@
 We experimentally measured the cost of different operations on encrypted data and the security-cost trade-off for certain operations.
-The existing implementation of Smart-Vercauteren scheme remains practical only for very low level of security, when a user wants to apply a sorting algorithm on his encrypted bit sequences.
+The existing implementation of Smart-Vercauteren scheme remains practical only for very low level of security, when a user wants to apply a sorting algorithm on encrypted bit sequences of short length.
+
+As the sorting algorithms used can be parallelized to obtain better results, it would be interesting to perform computations on GPU.
 

### 2013-06-17 libScarab-1.0.0/test.c

@@ -61,13 +61,13 @@ void test_suite()
 	//test_insertion_sort();
 	//test_oddeven_merger_sort();
 	//test_bitonic_sort();
-	test_majority_bit();
+	//test_majority_bit();
 
 	//mesure_test_matrix_prod();
 	//test_sum_unbounded();
 	//measure_test_keygen();
 	//test_keygen();
-	//mesure_encrypt_decrypt();
+	mesure_encrypt_decrypt();
 	//essai();
 }
 
@@ -147,9 +147,9 @@ void mesure_encrypt_decrypt(){
 	
 
 	gettimeofday(&start, NULL); 
-	for(int i=0; i < 100; i++){   
+/*	for(int i=0; i < 100; i++){   
 		fhe_fulladd(c, aux1,c,c,aux2, pk);
-	}
+	}*/
 	gettimeofday(&end, NULL);
 	seconds  = end.tv_sec  - start.tv_sec;
 	useconds = end.tv_usec - start.tv_usec;
@@ -160,6 +160,7 @@ void mesure_encrypt_decrypt(){
 	gettimeofday(&start, NULL);  
 	for(int i=0; i < 10000; i++){  
 		fhe_mul(c,c, c, pk);
+		printf("\nCheck decryption depth %d \n",fhe_decrypt(c,sk));
 	}
 	gettimeofday(&end, NULL);
 	seconds  = end.tv_sec  - start.tv_sec;

### 2013-06-17 Report/article.tex
jo

@@
 From \autoref{common cost}, we can infer that the cost of these functions increase with the increase of the degree of the polynomial $F(x)$.
-Futhermore, we observe that the size of the public key is increasing linearly with $n$  where $N=2^n$.
+Futhermore, we observe that the size of the public key is increasing with the increase of $N$ which can be explained by the fact that the resultant of 2 polynomials increases with the increase of the degree which makes the prime number $p$ harder to be found and so it increases the duration of key generation.
 
@@
   $16$ & 529  & 5.40 & 1.01907 \\
+  $32$ & 801  & 5.40 & 1.01907 \\
+  $64$ & 824  & 5.40 & 1.01907 \\
+
    \hline

### 2013-06-17 libScarab-1.0.0/parameters.h

@@ -15,7 +15,7 @@
 #define N 8
 
 
-#define MU 16
+#define MU 4
 
 
 //#define NU 2**256;
@@ -23,7 +23,7 @@
 //#define LOG_NU 384
 //#define LOG_NU 310
 
-#define LOG_NU 300
+#define LOG_NU 400
 
 
 

### 2013-06-17 libScarab-1.0.0/test.c

@@ -132,7 +132,7 @@ void mesure_encrypt_decrypt(){
 	//gmp_printf("alpha: %Zd \n", pk->alpha);
 	//gmp_printf("B: %Zd \n", sk->B);
 
-	printf("N: %d , log(p): %d , Mu: %d , Nu: %d , keygen: %ld ",N,mpz_sizeinbase( pk->p, 2), MU, LOG_NU, mtime );
+	//printf("N: %d , log(p): %d , Mu: %d , Nu: %d , keygen: %ld ",N,mpz_sizeinbase( pk->p, 2), MU, LOG_NU, mtime );
 	
 	
 	gettimeofday(&start, NULL);  
@@ -158,7 +158,7 @@ void mesure_encrypt_decrypt(){
 
 
 	gettimeofday(&start, NULL);  
-	for(int i=0; i < 10000; i++){  
+	for(int i=0; i < 100; i++){  
 		fhe_mul(c,c, c, pk);
 		printf("\nCheck decryption depth %d \n",fhe_decrypt(c,sk));
 	}
@@ -197,6 +197,8 @@ void mesure_encrypt_decrypt(){
 	useconds = end.tv_usec - start.tv_usec;
 	mtime = ((seconds) * 1000 + useconds/1000.0) + 0.5;
 	printf("sum: %ld ms \n", mtime );
+	printf("N: %d , log(p): %d , Mu: %d , Nu: %d , keygen: %ld ",N,mpz_sizeinbase( pk->p, 2), MU, LOG_NU, mtime );
+	
 	mpz_clear(c); mpz_clear(aux1); mpz_clear(aux2);
 	fhe_pk_clear(pk);
 	fhe_sk_clear(sk);

### 2013-06-17 libScarab-1.0.0/parameters.h
Conflict

@@ -15,7 +15,7 @@
 #define N 8
 
 
-#define MU 16
+#define MU 32
 
 
 //#define NU 2**256;
@@ -23,7 +23,7 @@
 //#define LOG_NU 384
 //#define LOG_NU 310
 
-#define LOG_NU 300
+#define LOG_NU 400
 
 
 

### 2013-06-18 Report/Appendix.tex
Appendix added

\documentclass[12pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{textcomp}
\usepackage[english,french]{babel}
\usepackage{etex}
\usepackage[left=0.5in, right=0.5in, top=1.0in, bottom=1.0in]{geometry}
\usepackage{layout}
\usepackage{lmodern}
\usepackage{stmaryrd}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{textcomp}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[all]{hypcap}
\usepackage{tabularx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{listings}
\usepackage{algorithm2e}
\usepackage{verbatim}
\hypersetup{
  bookmarks=true,         % show bookmarks bar?
  unicode=false,          % non-Latin characters in Acrobat’s bookmarks
  pdftoolbar=true,        % show Acrobat’s toolbar?
  pdfmenubar=true,        % show Acrobat’s menu?
  pdffitwindow=false,     % window fit to page when opened
  pdfstartview={FitH},    % fits the width of the page to the window
  pdftitle={My title},    % title
  pdfauthor={Author},     % author
  pdfsubject={Subject},   % subject of the document
  pdfcreator={Creator},   % creator of the document
  pdfproducer={Producer}, % producer of the document
  pdfkeywords={keyword1} {key2} {key3}, % list of keywords
  pdfnewwindow=true,      % links in new window
  colorlinks=true,       % false: boxed links; true: colored links
  linkcolor=cyan,          % color of internal links (change box color with linkbordercolor)
  citecolor=green,        % color of links to bibliography
  filecolor=magenta,      % color of file links
  urlcolor=cyan           % color of external links
}
\usepackage{parcolumns}
\begin{document}

\lstset{                                    % line wrapping on
  language=C,
  frame=lines,
  captionpos=b
 }

\renewcommand{\lstlistingname}{Code}
\section*{APPENDIX}

 The programs used for Odd-Even Merge sort and Bitonic sort are provided below : \\

\noindent\begin{minipage}{.45\textwidth}
\begin{lstlisting}[label=bitsort, caption=Bitonic Sort : sort from m to n,frame=tlrb]{Name}
sortup( int m, int n) {
//from m to m+n
    if (n == 1) return;
    sortup(m, n/2);
    sortdown(m + n/2, n/2);
    mergeup(m, n/2);
}
 sortdown(int m, int n) {
//from m to m+n
    if (n == 1) return;
    sortup(m, n/2);
    sortdown(m + n/2, n/2);
    mergedown(m, n/2);
}

\end{lstlisting}
\end{minipage}\hfill
\begin{minipage}{.50\textwidth}
\begin{lstlisting}[label=bitmerge, caption = Bitonic Merge,frame=tlrb]{Name}
mergeup(int m, int n) {  
    if (n == 0) return;

    for (i = 0 : n)
        // Increasing Comparator
	 compare(m + i,m + i + n);
    mergeup(m, n/2);
    mergeup(m + n,n/2);
}

mergedown( int m,  int n) { 
    if (n == 0) return;
    for (i = 0 : n) 
        // Decreasing Comparator
	compare(m + i, m + i + n); 
    mergedown(m, n/2);
    mergedown(m + n, n/2);
}
\end{lstlisting}
\end{minipage}
\noindent\begin{minipage}{.45\textwidth}
\begin{lstlisting}[label=oemerge, caption=Odd-Even Merge,frame=tlrb]{Name}
oddEvenMerge(int lo, int n, int r){
  int m = r*2;
  if (m < n){
    //even subsequence ;		
    oddEvenMerge(lo, n, m); 
    //odd subsequence ;
    oddEvenMerge(lo+r, n, m); 
    int i = lo+r;   
    for (;i + r < lo + n;){
      compare(i, i + r);
      i += m;
    }
  }
  else
  compare(lo, lo + r);
}
\end{lstlisting}
\end{minipage}\hfill
\begin{minipage}{.50\textwidth}
\begin{lstlisting}[label=oesort, caption = Odd-Even sort from lo to n,frame=tlrb]{Name}

 OddEvenMergeSort(int lo, int n)
if (n > 1){
  int m = n/2;
  oddEvenMergeSort(lo, m);
  oddEvenMergeSort(lo + m, m);
  oddEvenMerge(lo, n, 1);
}
\end{lstlisting}
\end{minipage}

\begin{figure}
\centering
\includegraphics[width=12cm]{fsort3.pdf} 
\caption{Run time for Insertion sort, nbit=4} 
\label{fig:image_sf3} %l'étiquette pour faire référence à cette image
\end{figure}

\begin{figure} %on ouvre l'environnement figure
\centering
\includegraphics[width=12cm]{fsort5.pdf} 
\caption{Run time for Insertion sort, nbit=8} 
\label{fig:image_sf5} %l'étiquette pour faire référence à cette image
\end{figure}

\begin{figure}%on ouvre l'environnement figure
\centering
\includegraphics[width=12cm]{fsort6.pdf} 
\caption{CPU time for Insertion sort, nbit=4} 
\label{fig:image_sf6} %l'étiquette pour faire référence à cette image
\end{figure}

\begin{figure}%on ouvre l'environnement figure
\centering
\includegraphics[width=12cm]{fsort8.pdf} 
\caption{CPU time for Insertion sort, nbit=6} 
\label{fig:image_sf8} %l'étiquette pour faire référence à cette image
\end{figure}

\begin{figure}%on ouvre l'environnement figure
\centering
\includegraphics[width=12cm]{fsort7.pdf} 
\caption{CPU time for Insertion sort, nbit=8} 
\label{fig:image_sf7} %l'étiquette pour faire référence à cette image
\end{figure}

\end{document}

### 2013-06-18 Report/article.tex
Appendix added

@@
 We remark that : decreasing $\eta$ with other parameters fixed increases the security of the system at the cost of decreasing the depth.
-We further note that increasing the value of $\eta$ increases the computational cost.
+This confirms equation (1) and (2).
+We further note that increasing the value of $\eta$ increases the computational cost as $p$ increases which makes the the ciphertexts longer.
 On the contrary, \autoref{tab:tradeofftab2} presents the security-cost tradeoff for 10000 multiplications as a function of $\mu$.
-Here, increasing $\mu$ with other parameters fixed increases the security of the system at the cost of decreasing the depth.
-However, in this case the cost does not vary much.
-Hence it is profitable to increase $\mu$ to increase the security of the system.
+In this case, increasing $\mu$ with other parameters fixed increases the security of the system(confirms (1)) at the cost of decreasing the depth.
+With small values of $\mu$, the cost remains stable.
+However, for larger values, the cost increases considerably and this is due to the fact that, the coefficients of the random polynomial in \texttt{Encrypt} increase  which is reflected in the size of the ciphertexts.
+Hence it is profitable to increase $\mu$ to increase the security of the system when $\mu$ is not too large
 
+.
 \begin{table}[htb]
@@
   $16$ & 529  & 5.40 & 1.01907 \\
-  $32$ & 801  & 5.40 & 1.01907 \\
-  $64$ & 824  & 5.40 & 1.01907 \\
+  $32$ & 801  & 5.40 & 1.01913 \\
+  $64$ & 824  & 5.40 & 1.01920 \\
 
@@
 \label{Sec:Eval}
-We execute the implementations of the above programs, and we measure their wall time and compare the cost with the theoretical complexity depending on the sizes of the input data.
+We execute the implementations of the above programs, and we measure their wall time and CPU time, and compare the experimental cost with the theoretical complexity.
 For each test, $5-10$ random samples were taken.
@@
 \centering
-\includegraphics[width=5cm, height=4cm]{f4.pdf} 
+\includegraphics[width=8cm, height=6cm]{f4.pdf} 
 \caption{Wall time for XOR} 
@@
 \centering
-\includegraphics[width=5cm, height=4cm]{f8.pdf} 
+\includegraphics[width=8cm, height=6cm]{f8.pdf} 
 \caption{Wall time for bit majority} 
@@
 \centering
-\includegraphics[width=5cm, height=4cm]{f8.pdf} 
+\includegraphics[width=8cm, height=6cm]{f8.pdf} 
 \caption{Wall time for sum} 
@@
 \centering
-\includegraphics[width=5cm, height=4cm]{f9.pdf} 
+\includegraphics[width=8cm, height=6cm]{f9.pdf} 
 \caption{Wall time for matrix product} 
@@
 Initially, the cryptographic parameters were set to $(N = 8, \nu = 2^{384}, \mu = 4, s_1 = 8, s_2 = 5)$ which is the default setting in the software.
-We measured CPU time and Wall time by varying the sequence length(nbit) and the number of sequences(n).
-We plot maximum and minimum time in minutes for nbit=6, \autoref{fsort8.pdf}.
+We measured CPU time and Wall time by varying the sequence length($nbit$) and the number of sequences(n).
+We plot maximum and minimum time in minutes for $nbit=6$ for insertion sort, \autoref{fig:image_sf4} .
+\autoref{fig:image_sf2} compares the results with changing values of $nbit$.
+\autoref{fig:image_sf1} presents a curve fitting plot that verifies the quadratic complexity of this algorithm.
 
@@
 \centering
-\includegraphics[width=6cm, height=6cm]{fsort8.pdf} 
-\caption{CPU time for Insertion sort, nbit=6} 
-\label{fig:image_sf8} %l'étiquette pour faire référence à cette image
+\includegraphics[width=10cm, height=10cm]{fsort4.pdf} 
+\caption{Wall time for Insertion sort, nbit=6} 
+\label{fig:image_sf4} %l'étiquette pour faire référence à cette image
 \end{figure}
 
- \autoref{fig:image_sf3},\autoref{fig:image_sf4}, \autoref{fig:image_sf5}, \autoref{fig:image_sf6}, \\ \autoref{fig:image_sf8}, \autoref{fig:image_sf7} and \autoref{fig:image_sf2} show the variation of CPU time and Wall time with the increase in the number of sequences to sort and the number of bits.
-These experiments were done for Insertion Sort algorithm.
-\autoref{fig:image_sf1} presents a  curve fitting plot that verifies the quadratic complexity of this algorithm.
+\begin{figure} %on ouvre l'environnement figure
+\centering
+\includegraphics[width=10cm, height=10cm]{fsort2.pdf} 
+\caption{Wall time in minutes for Insertion sort} 
+\label{fig:image_sf2} %l'étiquette pour faire référence à cette image
+\end{figure}
+
+Graphs for other values of $nbit$ and with wall time and CPU time are presented in Appendix.
+
+\begin{figure} %on ouvre l'environnement figure
+\centering
+\includegraphics[width=10cm, height=10cm]{fsort1.pdf} 
+\caption{Curve fitting for Insertion sort, nbit=6} 
+\label{fig:image_sf1} %l'étiquette pour faire référence à cette image
+\end{figure}
 

### 2013-06-18 Report/article.tex
Preserving

--- 2013-06-17 Report/article.tex
@@
 \usepackage{algorithm2e}
-\usepackage{subfigure}
+%\usepackage{amsfont}
 %\usepackage{amsmath}
@@
 }
+
 \usepackage{listings}
@@
 \begin{document}
-\title{Analyzing Security-Cost Trade-off for a \\ Fully Homomorphic Encryption Scheme}
+\title{Analysis of Security-Cost Trade-off of Fully Homomorphic Encryption Schemes}
+
+%
+% You need the command \numberofauthors to handle the 'placement
+% and alignment' of the authors beneath the title.
+%
+% For aesthetic reasons, we recommend 'three authors at a time'
+% i.e. three 'name/affiliation blocks' be placed beneath the title.
+%
+% NOTE: You are NOT restricted in how many 'rows' of
+% "name/affiliations" may appear. We just ask that you restrict
+% the number of 'columns' to three.
+% Because of the available 'opening page real-estate'
+% we ask you to refrain from putting more than six authors
+% (two rows with three columns) beneath the article title.
+% More than six makes the first-page appear very cluttered indeed.
+%
+% Use the \alignauthor commands to handle the names
+% and affiliations for an 'aesthetic maximum' of six authors.
+% Add names, affiliations, addresses for
+% the seventh etc. author(s) as the argument for the
+% \additionalauthors command.
+% These 'additional authors' will be output/set for you
+% without further effort on your part as the last section in
+% the body of your article BEFORE References or any Appendices.
 
@@
 \begin{abstract}
-This paper investigates the feasibility of transformation of a (possibly) non-straight-line program (on unencrypted data) into a straight-line program on encrypted data.
-We present an analysis of security-cost trade-off for a homomorphic encryption scheme executing such programs.
-Analysis is based on the measurements (CPU time and  Wall time) taken for programs : performing \texttt{XOR} of an $n$-bit sequence,  evaluating the sum of two $n$-bit integers, determining the majority bit of an $n$-bit sequence, finding the product of two $n \times n$ matrices, and sorting $n$ bit sequences of length $nbits$ (usually requiring validity of a boolean predicate).
+This paper investigates the feasibility of transformation of a (possibly) non-straight-line program (on unencrypted data) to a straight-line program on encrypted data.
+We present an analysis of security-cost trade-off for homomorphic encryption schemes on such programs.
+Analysis is based on the measurements (CPU time and  Wall time) taken for programs : performing \texttt{XOR} of an $n$-bit sequence, determining the majority bit of an $n$-bit sequence, evaluating the sum of $n$-bit integers, \textcolor{orange}{sum of integers with any number of bits} and sorting $n$ bit sequences of length $nbits$ (requires verifying the validity of a boolean predicate).
 The evaluation is performed on an available implementation ``Scarab library'' of a fully homomorphic encryption scheme.
@@
 
-The notion of \textit{fully homomorphic encryption scheme}, originally called a \textit{privacy homomorphism} was introduced by Rivest et al.
-\cite{rivest78} shortly after the invention of RSA by Rivest, Shamir and Adleman \cite{Rivest78amethod}.
+The notion of \textit{fully homomorphic encryption scheme}, orginally called a \textit{privacy homomorphism} was introduced by Rivest et al.
+\cite{rivest78} shortly after the invention of the RSA by Rivest, Shamir and Adleman \cite{Rivest78amethod}.
 Basic RSA is a multiplicative homomorphic encryption scheme -- i.e.
@@
 Fully homomorphic encryption scheme extends the above property to addition.
-A fully homomorphic encryption scheme is a tuple of an encryption $\mathcal{E}$, decryption $\mathcal{D}$ algorithm together with an efficient algorithm $Eval_\mathcal{E}$ that evaluates any circuit $C$ on any cipher-texts $c_i \leftarrow \mathcal{E}(pk, m_i)$.
-The property that it can evaluate the encryption of addition and multiplication of two plain-texts (without access to the secret key) allows it to arbitrarily compute any boolean function on encrypted data without the decryption key.
-However, we assume that no branching is involved.
-Prior to \cite{homenc}, we did not have a viable construction.
+A Fully homomorphic scheme is a tuple of an ecryption $\mathcal{E}$, decryption $\mathcal{D}$ algorithm together with an efficient algorithm $Eval_\mathcal{E}$ that evaluates any circuit $C$ on any ciphertexts $c_i \leftarrow \mathcal{E}(pk, m_i)$.
+The property that it can evaluate the encryption of addition and multiplication of two plaintexts (without access to the secret key) allows it to arbitrarily compute any function on encrypted data without the decryption key.
+However prior to \cite{homenc}, we did not have a viable construction.
 
@@
 
-The immediate question that is raised, is how do we perform the transformation and how does the circuit size change to adapt to computations on encrypted data, especially when the function involves \texttt{if-then-else} condition.
-We provide an answer by analyzing circuit complexity for finding the minimum-maximum of two $n$-bit sequences in \autoref{sec:ex} and for some other operations in \autoref{sec:bm}.
-Moreover, the cost of using a fully homomorphic encryption scheme increases with the depth of the circuit representing the $Eval_{\mathcal{E}}$ function.
+The immediate question that is raised, is how do we perform the transformation and how does the circuit size change to adapt to computations on encrypted data.
+We provide answer to this question by analyzing circuit complexity for finding the minimum-maximum of two $n$-bit sequences in \autoref{sec:ex} and for some other opertation in \autoref{sec:bm}.
+Moreover, the cost of evaluation depends on the depth of the circuit representing the $Eval_{\mathcal{E}}$ function.
+Some researchers have improved and proposed other schemes such as \cite{cryptoeprint:2009:571} and \cite{cryptoeprint:2011:277} which decrease the circuit complexity.
+In \autoref{Sec:Eval} we expermentally evaluate an implementation of  \cite{cryptoeprint:2009:571} and analyze the cost-security trade-off for $Eval_{\mathcal{E}}$ varying from \texttt{XOR} of the bits of an $n$ bit integer to sum of bounded and unbounded integers to sorting of $n$ integers.
+Three different sorting algorithms are tested.
+Through these experiments, we also provide information on the additional cost to be paid (for these computations) to increase the security of the cyptosystem.
 
-Some researchers have improved Gentry's scheme and proposed other schemes such as \cite{cryptoeprint:2009:571} and \cite{cryptoeprint:2011:277} which improve the complexity of the scheme.
-In \autoref{Sec:Eval} we experimentally evaluate an implementation of  \cite{cryptoeprint:2009:571} and analyze the security-cost trade-off for $Eval_{\mathcal{E}}$ varying from \texttt{XOR} of an $n$-bit sequence to sum of two $n$-bit sequences to sorting of $n$ sequences of $nbits$ each.
-Three different sorting algorithms are tested.
-Through these experiments, we also provide information on the additional cost to be paid (for these computations) when a higher security is desired.
-
-\section{Overview of Fully homomorphic Encryption scheme (FHE) }
+\section{Fully homomorphic Encryption scheme (FHE) }
 
 The homomorphic encryption scheme proposed by Gentry \cite{homenc} is based on ideal lattices.
-Gentry's non-deterministic scheme builds on a \textit{somewhat homomorphic encryption}(SWHE) scheme which can perform additions and multiplications on encrypted data till a bounded depth.
-The non-determinism introduced in the form of noise renders the scheme secure.
-However, the noise increases with the depth  of the evaluation circuit and hence the decryption algorithm fails to produce the correct plain-text after a certain depth.
+The Gentry's non-determi-nistic scheme builds on a \textit{somewhat homomorphic encryption}(SWHE) scheme which can perform additions and multiplications on encrypted data till a bounded depth.
+The non-determinism introduced in the form of a noise renders the scheme secure.
+But, the noise increases with the depth  of the evaluation circuit.
 To counter this problem, Gentry introduces \textit{bootstrapping} technique which ensures unbounded depth operatability of the scheme.
-Smart and Vercauteren \cite{cryptoeprint:2009:571} have proposed an integer based approach and we use one of its implementations detailed in \cite{perl:poster} for our experiments.
+Smart Vercauteren \cite{cryptoeprint:2009:571} have proposed an integer based approach and we use one of its implementation detailed in \cite{perl:poster} for our experiments.
 
@@
 
-The scheme proposed in \cite{cryptoeprint:2009:571} has 3 parameters : $(N=2^n, \eta, \mu)$, where $n\in \mathbb{N}$.
-The somewhat homomorphic encryption scheme uses 5 algorithms : (\texttt{KeyGen}, \texttt{Encrypt}, \texttt{Decrypt}, \texttt{Add}, \texttt{Mult}).
+The scheme proposed in \cite{cryptoeprint:2009:571} has 3 parameters:($N, \nu, \mu$ ).
+The somewhat homomorphic scheme uses 5 algorithms: (\texttt{KeyGen}, \texttt{Encrypt}, \texttt{Decrypt}, \texttt{Add}, \texttt{Mult}).
 Algorithm \autoref{Code:SV} presents the \texttt{KeyGen} algorithm.
-This scheme will be referred to as SV scheme in this paper.
+This sheme will be referred to as SV scheme in this paper.
 
@@
  \SetVline
- \KwData{$N, \eta, \mu$ }
+ \KwData{$N, \nu, \mu$ }
 \KwResult{($pk, sk$)}
- $F(x)$ monic irreducible over $\mathbb{Z}[x]$ of degree $N$\;
+ $F(x)$ monic irreducible over $\mathbb{Z}[x]$ of degree $n$\;
 \While{$p$ is not prime}{
-  $S(x) \leftarrow_{R}B_{\infty , N}(\eta/2)$\; \tcc{Random polynomial in the ball}
+  $S(x) \leftarrow_{R}(B_{\infty , N}(\nu/2)$\; \tcc{Random choice}
   $G(x)=1+2.S(x)$\;
-  $p= \mathrm{\textbf{resultant}}(G(x),F(x))$\;						
+  $p= resultant(G(x),F(x))$\;						
 }
 
-$D(x)=\mathrm{\textbf{gcd}}(G(x),F(x))$ over $\mathbb{F}_p[x]$\;
-$\alpha$ $\leftarrow$ unique root of $D(x) \in \mathbb{F}_p $ \;
-apply \texttt{xgcd} algorithm over $\mathbb{Q}[x]$ to obtain $Z(x) = \sum_{i=0}^{n-1}{z_ix^i} \in \mathbb{Z}[x] $  such that $Z(x).G(x)=p$ mod $F(x)$\;
+$D(x)=gcd(G(x),F(x))$ over $\mathbb{F}_p[x]$\;
+$\alpha$ $\leftarrow$ unique root of $D(x)$\;
+apply \texttt{xgcd} algorithm to obtain $Z(x) = \sum_{i=0}^{n-1}{z_ix^i} $  such that $Z(x).G(x)=p$ mod $F(x)$\;
 $B=z_0$ mod $2p$\;
@@
 
-where $ B_{\infty , k}(r) = \{\sum_{i=0}^{k-1}{a_i}x^i : -r \leq a_i \leq r \} $ \newline \newline
+where $ B_{\infty , n}(r) = \{\sum_{i=0}^{n-1}{a_i}x^i : -r \leq a_i \leq r \} $
+
 \texttt{Encrypt}($m \in \{0,1\} , pk$): 
-\newline \phantom{x}\hspace{3ex}  $R(x) \leftarrow_{R}B_{\infty , N}(\mu/2)$
+\newline \phantom{x}\hspace{3ex}  $R(x)=_{R}(B_{\infty , N}(\mu/2)$
  \; $C(x)=m+2\cdot R(x)$ 
@@
 \newline \texttt{Add}($c_1$, $c_2$, $pk$):
-\newline \phantom{x}\hspace{3ex} $c_3=c_1+c_2$ mod $p$; 
-\phantom{x}\hspace{1ex}  return $c_3$;
+\newline \phantom{x}\hspace{3ex} $c_3=c_1+c_2$ mod $p$
+;  \phantom{x}\hspace{1ex}  return $c_3$
+;
 \newline \texttt{Mult}($c_1$, $c_2$, $pk$):
- \newline \phantom{x}\hspace{3ex}  $c_3=c_1.c_2$ mod $p$; 
-\phantom{x}\hspace{1ex}  return $c_3$;
+ \newline \phantom{x}\hspace{3ex}  $c_3=c_1.c_2$ mod $p$
+ ; \phantom{x}\hspace{1ex}  return $c_3$
+;
 
-\textbf{Security of SWHE scheme :} The scheme is semantically secure under the assumption that the \textit{Polynomial Coset Problem}(PCP) is hard.
-One-wayness of the encryption is believed to be true under the assumption that the \textit{Bounded distance decoding problem} BDDP is hard while key recovery is assumed to be difficult under the assumption that the \textit{Small Principal Ideal Problem}(SPIP) is hard.
+\textbf{Security of the scheme} The scheme is semantically secure under the assumption that the \textit{Polyomial Coset Problem} is hard.
+One wayness of the encryption is believed to be true under the assumption that the \textit{Bounded distance decoding problem} BDDP is hard while key recovery is assumed to be difficult under the assumption that the \textit{Small Principal Ideal Problem} is hard.
 Solutions to all of these problems have either a sub-exponential algorithm or in general take exponential time.
 
-If we choose $F(x)$ \footnote{a choice that authors of SV scheme propose and is always a safe choice for monic and irreducible polynomial over $\mathbb{Z}[x] $} to be $x^N+1$, and take \begin{equation}2 ^ \epsilon = \frac{\eta}{2\cdot \mu \sqrt{N}} \end{equation} then the SV scheme provides $N /\epsilon$ bits of security.
+If we choose $F(x)$ \footnote{a choice that authors of SV scheme propose and is always a safe choice for monic and irreducible polynomial over $\mathbb{Z}[x] $} to be $x^N+1$, and take $2 ^ \lambda = \frac{\nu}{2\cdot \mu \sqrt{N}} $, then the SV scheme provides $N /\lambda$ bits of security.
 
-\textbf{SWHE to FHE :} We recall that the authors of the scheme have proved that the multiplicative depth $d$ of SWHE scheme verifies: \begin{equation}d \cdot \mathrm{log}(2) \leq  \mathrm{log}\left( \mathrm{log}\left(\frac{\eta}{2\cdot \sqrt{N}}\right) \right) - \mathrm{log}\left(\mathrm{log}\left( N\mu\right)\right)\end{equation}
+\textbf{SWHE to FHE :} We recall that the authors have proved that the multiplicative depth $d$ of SWHE  verifies \[d \cdot \mathrm{log}(2) \leq  \mathrm{log}\left( \mathrm{log}\left(\frac{\nu}{2\cdot \sqrt{N}}\right) \right) - \mathrm{log}\left(\mathrm{log}\left( N\mu\right)\right)\]
 when $F(x)= x^N+1$.
-Turning the SWHE scheme to FHE scheme is achieved by recasting Gentry's method for the parameters of this scheme.
-To achieve this, authors define another algorithm \texttt{Recrypt} which takes a cipher-text $c$ and re-encrypts it to $c_{new}$, whilst at the same time removing some of the noise in $c$.
-This requires augmenting the encryption key with some additional information by extending the \texttt{KeyGen} algorithm.
-The FHE scheme now generates $s_1$ uniformly random integers $B_i$ in $[-p, \ldots, p]$ such that there exists a subset $S$ of $s_2$ elements with $\sum_{j \in S}{B_j}= B$ over integers.
-By defining $sk_i =1$ iff $i\in S$(else $sk_i=0$) and taking $c_i=\texttt{Encrypt}(sk_i,pk)$ we generate a new public key which contains hint of the secret key $sk$.
-The public key now comprises of \[(p, \alpha, s_1, s_2, \{c_i, B_i\}_{i=1}^{s1})\]
-To ensure that the hint does not provide any considerable advantage to an attacker, the underlying \textit{sparse subset-sum problem} SSSP must remain hard.
-If we take $s_1$ to be slightly greater than $\mathrm{log}_{2}(p)$, then we need to select $s_2$ such that $\sqrt {{s_1}  \choose {s_2} } > 2 ^{N/\epsilon}$ so as to ensure that SSSP difficulty is at least as difficult as the difficulty of the BDDP underlying the SWHE scheme.
+Turning the SWHE to FHE is achieved by recasting Gentr's method for the parameters of this scheme.
+To achive this the authors propose to generate $s_1$ uniformly random integers $B_i$ in $[-p, \ldots, p]$ such that there exists a subset $S$ of $s_2$ elements with $\sum_{j \in S}{B_j}= B$ over integers.
+By defining $sk_i =1$ iff $i\in S$ and taking $c_i=\texttt{Encrypt}(sk_i,pk)$ we generate a new public key which contains hint of the secret key $sk$.
+The public key now comprises of \[(p, \alpha, s_1, s_2, \{c_i, B_i\}_{i=1}^{s1})\].
+
+To ensure that the hint doesn't provide considerable advantage to an attacker, the underlying \textit{sparse subset-sum problem} SSSP must remain remain hard.
+If we take $s_1$ to be slightly greater than $p$, then we need to select $s_2$ such that $\sqrt {{s_1}  \choose {s_2} } \leq 2 ^{N/\lambda}$ so as to ensure that SSSP difficulty is at least as difficult as the difficulty of the BDDP underlying the SWHE scheme.
 
 \subsection{Considered Implementations}
-We used the open source implementation Scarab library \cite{hcrypt}  version $1.0.0$ of the SV scheme which is a part of \textsc{hcryptProject}.
+We used the open source implementation Scarab library \cite{hcrypt}  version $1.0.0$ of the Smart-Vercauteren scheme and is a part of \textsc{hcryptProject}.
 The implementation is in beta version.
-The software requires GMP(we tested with version $5.1.2$) \cite{gmp} : GNU Multiple Precision Arithmetic Library; FLINT version $1.6$ \cite{flint}: Fast Library for Number Theory; MPIR (we tested with $2.6.0$) \cite{mpir} : Multiple-Precision Integers and Rationals and MPFR (tested with version $3.1.2$) \cite{mpfr} :  Multiple-Precision Floating-point computations with correct Rounding.
+The software requires GMP(we tested with version $5.1.2$) \cite{gmp}, The GNU Multiple Precision Arithmetic Library; FLINT version $1.6$ \cite{flint} , Fast Library for Number Theory; MPIR (we tested with $2.6.0$) \cite{mpir}, Multiple Precision Integers and Rationals and MPFR (tested with version $3.1.2$) \cite{mpfr}  Multiple-Precision Floating-point computations with correct Rounding.
 Linux is supposed to be the only supported platform.
-The libraries are implemented in  C and an installation guide is provided with the package.
+The libraries are implemented in  C and the installation guide is provided with the package.
 
-\autoref{funs} presents the list of functions provided by Scarab with their description.
+\autoref{funs} presents the list of functions provided by the implementation with their description.
 The library provides a file \texttt{test.c} where a user can write his own functions to test different operations.
-It also provides a header file \texttt{parameters.h} to set the parameters $N, \eta, \mu, s_1$ and $ s_2$ of the cryptosystem.
-To simplify our computational circuit, we added two basic functions \texttt{or(mpz\_t res, mpz\_t a, mpz\_t b, fhe\_pk\_t pk);} and \texttt{not(mpz\_t res, mpz\_t a, fhe\_pk\_t pk);} which compute the logical \texttt{or}(denoted by $\vee$) of encrypted bits and the negation (denoted by $\neg$) of an encrypted bit respectively.
-In this article we denote logical \texttt{AND} using $\wedge$ and \texttt{XOR} using $\oplus$.
-
+It also provides a header file \texttt{parameters.h} to set the parameters $N, \nu, \mu, s_1$ and $ s_2$ of the cryptosystem.
 \begin{table*}
-\centering
-\caption{Functions available in Scarab}
+\caption{Function available in Scarab}
 \begin{tabular}{|l|l||}
@@
 \texttt{fhe\_recrypt(mpz\_t c, fhe\_pk\_t pk, fhe\_sk\_t sk); }	&Recrypt a cyphertext ( ``refreshing'' it) \\
-\texttt{fhe\_add(mpz\_t res, mpz\_t a, mpz\_t b, fhe\_pk\_t pk);} &	Add cypher-texts (= XOR) \\
-\texttt{fhe\_mul(mpz\_t res, mpz\_t a, mpz\_t b, fhe\_pk\_t pk);} &	Multiply cypher-texts (= AND) \\
+\texttt{fhe\_add(mpz\_t res, mpz\_t a, mpz\_t b, fhe\_pk\_t pk);} &	Add cyphertexts (= XOR) \\
+\texttt{fhe\_mul(mpz\_t res, mpz\_t a, mpz\_t b, fhe\_pk\_t pk);} &	Multiply cyphertexts (= AND) \\
 \texttt{fhe\_fulladd(mpz\_t sum, mpz\_t c\_out, mpz\_t a, mpz\_t b,} &	Add with carry in and carry out \\
@@
 
+To simplify our computational circuit, we added two basic functions \texttt{or(mpz\_t res, mpz\_t a, mpz\_t b, fhe\_pk\_t pk);} and \texttt{not(mpz\_t res, mpz\_t a, fhe\_pk\_t pk);} which compute the logical \texttt{or}(+) of encrypted bits and the negation ($\neg$) of an encrypted bit respectively.
+
 We time the various algorithms on two desktop machines.
-Both these machines were x86-64 platform running Linux kernel $3.2.0$-$45$-generic  and used GCC $4.6.3$ C compiler.
-The first machine housed Intel Core i3 M330 (2.13GHz x 4) processor and will be referred in this article as machine M1 while the other housed Intel Core i5 M2430 (2.40GHz x 4) processor and will be referred as M2.
-During the experiments these machines were not connected to any network and were running only the most needed applications.
+Both these machines were x86-64 platform running linux kernel $3.2.0$-$45$-generic  and used GCC $4.6.3$ C compiler.
+The first machine housed Intel Core i3 M330 (2.13GHz x 4) processor and will be referred in this article as machine M1 while the other used  housed Intel Core i5 M2430 (2.40GHz x 4) processor and will be referred as machine M2.
+During the experiments these machines were not connected to any network and were executing the inevitable applications to support them.
 
-\subsection{Cost of the Cryptosystem}
- In the SV scheme, performing any operation on encrypted bits requires  \texttt{KeyGen}, \texttt{Encrypt}, \texttt{Add},\texttt{ Mult}, \texttt{Recrypt}, \texttt{Decrypt}, and hence we measure their performance in terms of run time.
-These measurements are done by varying the parameter $N$(keeping all other parameters fixed) that determines the degree of all intermediate polynomials of the cryptosystem.
-The measurements in this section were taken on M2.
-From \autoref{common cost}, we can infer that the cost of these functions increase with the increase of the degree of the polynomial $F(x)$.
-Futhermore, we observe that the size of the public key is increasing linearly with $n$  where $N=2^n$.
+\subsection{Intial set-up cost}
+Measurements taken are CPU time and Wall Time by varying the input size  and the algorithmic parameters. Noise reduction threshold.\\
+Here we estimate the performance of this program in terms of run time for KeyGen, Encrypt, Decrypt and the Min-Max algorithm.
 
-\begin{table}[htb]
-  \centering
-  \caption{Run time (ms)}
-\resizebox{9 cm}{!}{
-\begin{tabular}{|c|c|c|c|c|c|c|c||}
-  \hline
-  \multicolumn{8}{|c||}{$\mu = 4$ , $\eta = 2^{384}$} \\
-  \hline
-  $N=2^{n}$ & $log_{2}(p)$ & KeyGen & Encrypt & Add & Mult & Recrypt & Decrypt \\
-  \hline
-  $2^{1}$ & 764 & 99 & 0.057 & 0.0 & 2.372 & 2.371 & 0.0 \\
-  $2^{2}$ & 1535 & 221 & 0.072 & 0.0 & 	3.012 & 3.023 & 0.001\\
-  $2^{3}$ & 3077 & 1131 & 0.079 & 0.001 & 3.396 & 3.380 & 0.004 \\
-  $2^{4}$ & 6155 & 8560 & 0.135 & 0.002 & 5.881 & 5.889 & 0.012\\
-  $2^{5}$ & 12329 & 852849 & 0.477 & 0.005 & 20.230 & 20.057 & 0.028\\
-  \hline
-\end{tabular}
-\normalsize
-\label{common cost}
-}
-\end{table}
-
-\autoref{fig:image_f2} measures execution time for \texttt{KeyGen} for fixed values of parameters: $N=8$ and $\eta = 2^{384}$.
-It shows a variation from 0.2 s to 14.41 s with a very high density in the interval [0.2s, 2s].
-
+\textbf{KeyGen}\\
+The measured time execution for KeyGen($N, \mu$)  for fixed values of parameters: $N=8$ and $\mu = 4$ show a variation from 0.2 s to 14.41 s with big density at the interval [0.2s, 1s].
+\begin{comment}
 \begin{figure}[!h] %on ouvre l'environnement figure
 \centering
-\includegraphics[width=5cm, height=4.5cm]{f3.pdf} 
+\includegraphics[width=5cm]{f3.eps} 
 \caption{Run time of KeyGen(ms)} 
-\label{fig:image_f2} %l'étiquette pour faire référence à cette image
+\label{image_f2} %l'étiquette pour faire référence à cette image
 \end{figure}
+\end{comment}
 
-As the time taken by \texttt{KeyGen} depends on how fast the prime $p$ is found, its cost is related with the density of primes i.e.
-$\frac{1}{\mathrm{log(n)}}$.
-\autoref{fig:image_f2} is in accordance with the density of primes over $\mathbb{N}$.
-
-\subsection{Security }
-
-Using (1), and (2), we calculate the theoretical security level and the depth provided by the cryptosystem, and we find that the security level increases with increase in $N$ and for $\mu =4$ and $\eta=2^{384}$ fixed.
-\autoref{common cost} asserts that  \texttt{KeyGen} takes 15mins for $N=2^5$.
-We note that for $N \geq 2^6$, \texttt{KeyGen} takes hours.
-Hence, we choose $N=8$ for our experiments which provides $1.01472$ level of security and we vary $\mu$ and $\eta$.
-Due to some erroneous results provided by the decryption function for $d<5.3$, we choose $\mu$ and $\eta$ to ensure that the depth is greater than the threshold value $5.9$.
-
-\begin{table}[htb]
-  \centering
-  \caption{Security, Depth}
-\begin{tabular}{|c|c|c||}
-  \hline
-  \multicolumn{3}{|c||}{$\mu = 4$ , $\eta = 2^{384}$} \\
-  \hline
-  $N=2^{n}$ &  $2^{\frac{N}{\epsilon}}$ & d \\
-  \hline
-  $2^{1}$ &  1.00365 & 6.99 \\
-  $2^{2}$ &  1.00732 & 6.57\\
-  $2^{3}$ &  1.01472 & 6.25\\
-  $2^{4}$ &  1.02969 & 5.98\\
-  $2^{5}$ & 1.06035 & 5.76\\
-  \hline
-\end{tabular}
-\normalsize
-\label{tab:securitytab}
-\end{table}
-
-\autoref{tab:tradeofftab1} presents the security-cost trade-off for 10000 multiplications as a function of $\eta$.
-We remark that : decreasing $\eta$ with other parameters fixed increases the security of the system at the cost of decreasing the depth.
-We further note that increasing the value of $\eta$ increases the computational cost.
-On the contrary, \autoref{tab:tradeofftab2} presents the security-cost tradeoff for 10000 multiplications as a function of $\mu$.
-Here, increasing $\mu$ with other parameters fixed increases the security of the system at the cost of decreasing the depth.
-However, in this case the cost does not vary much.
-Hence it is profitable to increase $\mu$ to increase the security of the system.
-
-\begin{table}[htb]
-  \centering
-  \caption{Trade-off for 10000 multiplications}
-\begin{tabular}{|c|c|c|c||}
-  \hline
-  \multicolumn{4}{|c||}{$\mu = 4$ , $N=8$} \\
-  \hline
-  $\eta$ &  time(in s)  & depth & $2^{\frac{N}{\epsilon}}$ \\
-  \hline
-  $2^{600}$ & 619  & 6.90 & 1.009 \\
-  $2^{400}$ &  580 & 6.31 & 1.014 \\
-  $2^{200}$ &  509 & 5.03 & 1.028 \\
-  $2^{100}$ &  490 & 4.28 & 1.059 \\
-   \hline
-\end{tabular}
-\normalsize
-\label{tab:tradeofftab1}
-\end{table}
-
-\begin{table}[htb]
-  \centering
-  \caption{Trade-off for 10000 multiplications}
-\begin{tabular}{|c|c|c|c||}
-  \hline
-  \multicolumn{4}{|c||}{$\eta = 2^{300}$ , $N=8$} \\
-  \hline
-  $\mu$ &  time(in s)  & depth & $2^{\frac{N}{\epsilon}}$ \\
-  \hline
-  $2$ & 527  & 6.90 & 1.01887 \\
-  $4$ & 526 & 5.89 & 1.01894 \\
-  $8$ & 528  & 5.63 & 1.01900 \\
-  $16$ & 529  & 5.40 & 1.01907 \\
-   \hline
-\end{tabular}
-\normalsize
-\label{tab:tradeofftab2}
-\end{table}
+\textbf{Encryption and Decryption}\\
 
 \section{Circuit Transformation}
-As previously discussed, a user sends his program which runs on unencrypted data and his encrypted input to the cloud.
-The cloud then performs the demanded computation and returns the encrypted result.
+As previously discussed, a user sends his program which works on unencrypted data and his encrypted input to the cloud.
+The cloud then performs the demanded computation and returns the result.
 However, the program in the same form cannot always be used for computations on encrypted data.
 
-\textbf{Non-secret branching}: We consider a scenario where a user wants to compute the \texttt{xor} of an $n$ bit sequence $a_0,a_1,\ldots,$ \\ $a_{n-1}$. A program on the unencrypted bits would be :
-
- \phantom{x} \texttt{res=0, i=0;}
-\newline \phantom{x} \texttt{do\{ }
-\newline \phantom{x} \hspace{9ex} \texttt{res=res$\oplus$a\_i;}
-\newline \phantom{x} \hspace{9ex} \texttt{i++;} 
-\newline   \phantom{x} \} \texttt{while(i < n);} 
-\newline  \phantom{x} \texttt{return res;}\\
-
-This program can directly be used by the cloud, as it only has to check \texttt{if(i<n)} where $i$ and $n$ are unencrypted integers.
-
-\subsection{Secret Branching}
-
-Consider a program which involves the following test on two inputs : \texttt{if(a > b) instruction\_1; else instruction\_2;} If the cloud could know how to perform \texttt{if(a' > b') instruction\_1; else instruction\_2;} (where \texttt{a'} and \texttt{b'} are the encryptions of \texttt{a} and \texttt{b}) without executing both the instructions, he would know the decryption of the comparison \texttt{a'>b'}, which means that he would have information on \texttt{a} and \texttt{b}.
-The cloud transforms the actual program into : \texttt{test(a'> b')$\wedge$} \texttt{instruction\_1 +}$\neg$\texttt{test(a'> b')$\wedge$ } \\ \texttt{instruction\_2}, where \texttt{test()}  is a function on encrypted inputs \texttt{a'}, \texttt{b'} and returns an encryption of $1$ iff \texttt{a > b}.
-Hence, if the program used has branching i.e.
-it involves \texttt{if(cond\_0)} \texttt{\{inst\_0\} else if(cond\_1)\{inst\_1\}} \texttt{ ...else if(cond\_n-2) \{inst\_n-2\}} \texttt{else\{inst\_n-1 \}}; the cloud has to perform all the $n$ instructions i.e.
+Consider a program involves the following test on two inputs : \texttt{if(a > b) instruction\_1; else instruction\_2;}.
+As the cloud does not know the result of the test\texttt{ a' > b'} where \texttt{a'} and \texttt{b'} are the encryptions of \texttt{a} and \texttt{b}, he does not know which of the instructions he has perform.
+In fact he performs both the instrunctions by transforming the actual program into : \texttt{test(a'> b')*} \texttt{instruction\_1 +}$\neg$\texttt{test(a'> b')*instruction\_2}, where \texttt{test()}  is a function on encrypted inputs \texttt{a'}, \texttt{b'} and returns an encryption of $1$ iff \texttt{a > b}.
+Hence, if the program used has braching i.e.
+it involves \texttt{if(cond\_0)} \texttt{\{inst\_0\} else if(cond\_1)\{inst\_1\}}\linebreak \texttt{ ...else if(cond\_n-2) \{inst\_n-2\}} \texttt{else\{inst\_n-1 \}}; the cloud has to perform all the $n$ instructions i.e.
 the size of the circuit changes from a constant size to a size linear in the number of tests.
@@
 
-\subsection{Secret Conditional Stopping}
-We consider the following program that a cloud receives where \texttt{f} is a boolean function. : \\
+\textbf{Another transformation}: We consider the following program that a cloud receives : \\
  \phantom{x} \texttt{i=0, res=0;}
@@
 \newline  \phantom{x} \texttt{res = f(i)};\\
-In this case, the cloud needs to transform a loop with conditional stopping into a loop with unconditional branching. We propose the following transformation : \\
- \phantom{x} \texttt{cont=1', res=0', i=0;}
+In this case, the cloud needs to transform a loop with condititonal stopping into a loop with unconditional branching. We propose the following possible transformation : \\
+ \phantom{x} \texttt{endLoop=0', res=0', i=0;}
 \newline \phantom{x} \texttt{do\{ }
-\newline \phantom{x} \hspace{6ex} \texttt{res = res$\vee$(cont$\wedge$f(i)$\wedge\neg$cond\_i);}
-\newline \phantom{x} \hspace{6ex} \texttt{cont = cont$\wedge$cond\_i;}
+\newline \phantom{x} \hspace{6ex} \texttt{endLoop = $\neg$cond\_i;}
+\newline \phantom{x} \hspace{6ex} \texttt{res = $\neg$endLoop*f(i)+($\neg$cond\_i)*res;}
 \newline \phantom{x} \hspace{6ex} \texttt{i++;} 
 \newline   \phantom{x} \} \texttt{while(i < n);}
-\newline \phantom{x} \texttt{res=($\neg$(cond\_i)$\wedge$res)$\vee$(f(n)$\wedge$cond\_i);}
-\newline 
-\textbf{Correctness of the code :} We consider the following three cases :
 
-1. \texttt{cond\_i} \textbf{is always} \texttt{true}: res equals $f(n)$ after the end of the loop.\newline
-\phantom{x} 2.
-\texttt{cond\_i} is \texttt{true} for $i<t$ and \texttt{false} afterwards: \texttt{res} is \texttt{false} and \texttt{cont}=\texttt{true} for $i<t$.
-At $i=t$, \texttt{cond\_i}=\texttt{false}, so \texttt{res = f(t)}.
-For $i>t$ \texttt{cont}=\texttt{false} and so hence \texttt{res} retains its value till the end of the loop.
-\newline
-\phantom{x} 3.
-\texttt{cond\_i} is \texttt{false} for the first time at $i=t_1$ and becomes \texttt{true} at $i=t_2$ with $t_1<t_2$ : With the previous argument, \texttt{res=f(t\_1)}$\; \forall i<t_2$.
-At $i=t_2$, \texttt{$\neg$(cond\_i)}=\texttt{false} hence \texttt{res} retains the value \texttt{f(t\_1)} till the end of the loop.
+\textbf{Correctness of the code :} If \texttt{cond\_i} is always \texttt{true}, \texttt{endLoop} is always false hence the \texttt{res=f(n)}.
+If at the $t^{th}$iteration, \texttt{cond\_i} is \texttt{false}, \texttt{endLoop} becomes \texttt{false} and hence \texttt{res} contains its previous value $f(t-1)$.
 
@@
 \label{sec:ex}
-Suppose that a user wants to find the maximum and the minimum of two $n$-bit sequences $a = (a_0,a_1,\ldots, a_{n-1})$, $b=(b_0,b_1,\ldots, b_{n-1})$ where $a_0$ is the highest significant bit.
+
+We suppose that a user wants to find the maximum and the minimum of two $n$-bit sequences $a = (a_0,a_1,\ldots, a_{n-1})$, $b=(b_0,b_1,\ldots, b_{n-1})$.
 He provides the following algorithm to the cloud :
@@
 \newline \phantom{x} \texttt{do\{ }
-\newline \phantom{x} \hspace{6ex} \texttt{aIsGreater = a\_i$ \wedge \neg$(b\_i);} 
+\newline \phantom{x} \hspace{6ex} \texttt{ if(a[i]==1 \&\& b[i]==0) 
+\newline \phantom{x} \hspace{14ex}aIsGreater = 1;}
 \newline \phantom{x} \hspace{7ex} \texttt{i++;} 
-\newline   \phantom{x} \} \texttt{while(i<n \&\& (a\_i$\wedge$b\_i) $\vee$ ($\neg$(a\_i)$\wedge \neg$(b\_i));}
-\newline \newline
-where \texttt{ (a\_i$\wedge$b\_i) $\vee$ ($\neg$(a\_i)$\wedge \neg$(b\_i)} tests the equality of the bits.
+\newline   \phantom{x} \} \texttt{while(i < n);}
 
-We propose the transformed algorithm \autoref{Code:algo} of the abov
-e program.
-It recasts the same ideas used for the previous example.
-The algorithm inspects the relative magnitude of pairs of bits, starting from the most significant bit and gradually proceeding towards lower significant bits until an inequality is found.
+We note that, we do not know how an optimized version :  using \texttt{break} to exit the loop once \texttt{aIsGreater} is set to \texttt{true}, could be transformed into a program for the cloud.
+We believe that the possibility to quit the loop would mean that the cloud knows the result of the \texttt{if(condition)}.
 
-\newtheorem{theorem}{Lemma}
-\begin{theorem}
-Algorithm \autoref{Code:algo} returns the maximum and the minimum of the input bit sequences. 
-\end{theorem}
-
-\begin{proof}
-
-  Consider $x_{-1}=1$ and $x_i = (a_i'\wedge b_i)'\vee (\neg(a_i')\wedge\neg(b_i')) $ in line 5.
-$x_i$ is $1$ iff $a_i'$ and $b_i'$ are equal.
-We denote by $bitEqual_{t}$ the value of $bitEqual$ at $i=t$ before assignment at line 5.
-In fact, $bitEqual_{t} = \bigwedge_{i<t}{x_i} $ at this stage and it is $1$ iff $a_i'=b_i'$ for all $i < t$.
-
-The term $\neg(b_i')\wedge a_i'$ at line 4 is $1$ iff $a_i'=1$ and $b_i'=0$.
-Hence at the iteration $i=t$, the algorithm using $bitEqual$ tests if $a'_i = b'_i \;\forall i<t$, while using $\neg(b_t')\wedge a_t'$, the algorithm tests if $a_t>b_t$.
-Hence $aIsGreater$ at $i=t$ is set to $1$ if all the bits till $i<t$ are equal and $a_t>b_t$.
-Once $aIsGreater$ is set to 1, it retains its value till the end of the loop.
-
-Max and Min regenerate $a_i$ and $b_i$ and hence contain the correct result.  
-\end{proof}
+We propose the transformed algorithm \autoref{Code:algo} of the above program.
+It inspects the relative magnitude of pairs of bits, starting from the most significant bit and gradually proceeding towards lower significant bits until an inequality is found.
 
@@
 
-     $aIsGreater \leftarrow aIsGreater \vee (\neg(b_i')\wedge a_i'\wedge bitEqual$) \;
-     $bitEqual \leftarrow bitEqual\wedge((a_i'\wedge b_i')\vee(\neg(a_i)'\wedge\neg(b_i')))$		       	
+     $aIsGreater \leftarrow (aIsGreater +\neg(b_i')a_i') bitEqual$ \;
+     $bitEqual \leftarrow bitEqual(a_i'b_i' + \neg(a_i)'\neg(b_i'))$		       	
  }
@@
 
-     $Max_i \leftarrow (aIsGreater \wedge a_i') \vee (b_i'\wedge \neg(aIsGreater))$ \;
+     $Max_i \leftarrow aIsGreater\cdot a_i' + \neg(aIsGreater)b_i'$ \;
 
-     $Min_i \leftarrow  (a_i' \wedge \neg(aIsGreater) ) \vee (aIsGreater \wedge b_i')$ \;
+     $Min_i \leftarrow  \neg(aIsGreater)a_i' + aIsGreater \cdot b_i'$ \;
 
@@
 
- \caption{Min-Max on cipher-text \label{Code:algo}}
+ \caption{Min-Max on ciphertext \label{Code:algo}}
 
@@
 
-\textbf{Theoretical Cost :} Algorithm \autoref{Code:algo} uses $5n$ \texttt{AND} gates, $2n$ \texttt{OR} gates and $2n$ \texttt{NOT} gates to find the larger of the two bit sequences and then to regenerate the maximum and the minimum $4n$ \texttt{AND} gates and $2n$ \texttt{NOT} and \texttt{OR} gates.
+\newtheorem{theorem}{Lemma}
+\begin{theorem}
+Algorithm \autoref{Code:algo} returns the maximum and the minimum of the input bit sequences. 
+\end{theorem}
+
+\begin{proof}
+
+Consider $x_i = a_ib_i+\neg(a_i)\neg(b_i) $.
+$x_i$ is $1$ iff $a_i$ and $b_i$ are equal.
+We note that, $bitEqual$ is the product of $x_i$ and is $1$ at the $t^{th}$ iteration iff $a_i=b_i$ for $i < t$.
+The term $\neg(b_i)a_i$ is $1$ iff $a_i=1$ and $b_i =0$.
+Hence at the $t^{th}$ iteration, the algorithm using $bitEqual$ tests if the previous bits were equal.
+Hence, $aIsGreater$ is $1$ iff at any stage  $a_t\neg(b_t)=1$ and the previous bits were equal.
+
+Max and Min regenerate $a_i$ and $b_i$ and hence contain the correct result.  
+\end{proof}
+\textbf{Theoretical Cost:} Algorithm \autoref{Code:algo} uses $n$ \texttt{AND} gates, $n$ \texttt{OR} gates and $n$ \texttt{NOT} gates to find the larger of the two bit sequences and then to regenerate the maximum and the minuimum $4n$ \texttt{AND} gates and $2n$ \texttt{NOT} and \texttt{OR} gates.
 We note that reconstruction of Max and  Min is not required when working on non-encrypted data.
@@
 
-\textbf{Experimental Analysis :} We measure the run time to perform min-max by varying $n=1$ to $32$ bits, \autoref{image_f2}. We find a linear cost which confirms the $\theta(n)$ complexity.
-
+\textbf{Experimental Analysis :} We measure the run time from $n=1$ to $32$ bits, we find a linear cost which confirms the $\theta(n)$ complexity.
+During these measures the result of Min-Max is correct.
+\begin{comment} 
 \begin{figure}[!h] %on ouvre l'environnement figure
 \centering
-\includegraphics[width=5cm,height=4cm]{f2.pdf} 
+\includegraphics[width=5cm]{f2.eps} 
 \caption{Run time(ms)} 
@@
 \end{figure}
+\end{comment}
+The cost of this algorithm on ciphertext is linear with bit number, like  the algorithm on plaintext, the extra cost in this case is encryption-decryption cost and especially the code generation which is very inpreductible and take often a long time in the SV scheme.
 
@@
 We propose a set of benchmark functions to evaluate the implementations.
-These functions can be categorized into three classes : functions operating on bits, functions operating on block of bits and functions where branching is usually required i.e \texttt{if-then-else} condition is evaluated.
+These functions can be categorized into three classes : functions operating on bits, \textcolor{orange}{functions operating directly on integers or block of bits} and functions where branching is usually required i.e \texttt{if-then-else} condition is evaluated.
 
-Functions operating on bits provide information on the security-cost trade-off for bit-wise operations.
-The first two categories of functions have straight-line programs on non-encrypted data and hence can directly be translated to operate on encrypted bits.
-For others, evaluation of \texttt{if-then-else} condition on encrypted data is chosen.
+Functions operating on bits provide information on the security-cost tradeoff for bitwise operations, \textcolor{orange}{while when operating directly on integers}, the tradeoff is obtained as a function of the size of integers.
+The first two categories of functions with straight-line programs on non-encrypted data can directly be translated to operate on encrypted bits.
+For others, evaluation of \texttt{if-then-else} condition on encrypted data is choosen.
 In this case, a circuit(program) transformation is required and which often makes the size longer than the one on non-encrypted data.
-Hence, this provides information on the increase in size of the circuit(when passing from non-encrypted to encrypted data) and the associated trade-off.
-We study the security-cost trade-off for the following problems : \newline
+Hence, this provides information on increase in size of the circuit(when passing from non-encrypted to enrypted data) and the associated trade-off.
+We study the security-cost tradeoff for the following problems :
+
 1. \textbf{XOR of an $n$-bit sequence}\\
-2. \textbf{Majority bit of an $n$-bit sequence} \\
-3. \textbf{Sum of :}  a) two unsigned integers of $32$ bits  \newline 
-\phantom{x}\hspace{12ex} b) two unsigned integers of arbitrary  \newline \phantom{x}\hspace{15ex} number of bits  \newline
-4. \textbf{Product of two $n\times n$ boolean matrices} \\
-5. \textbf{Sorting of $n$ sequences of $nbit$ using :} \newline\noindent
-\phantom{x}\hspace{3ex} a) Insertion sort \phantom{x}\hspace{2ex} b) Bitonic sort \\
-	\phantom{x}\hspace{3ex} 	     c) Odd-Even Merge sort
+2. \textbf{Sum of :}  
+\newline\noindent
+\phantom{x}\hspace{3ex} a) integers having $n$ bits 
+ \textcolor{orange}{b) integers having arbitrary
+\newline \phantom{x}\hspace{6ex}  number of bits}\\ 
+3. \textbf{Majority bit of an $n$-bit sequence} \\
+4. \textbf{Product of two $n\times n$ matrices} \\
+5. \textbf{Sorting of $n$ sequences of $nbits$: } \newline\noindent
+\phantom{x}\hspace{3ex} a) Insertion sort c) Bitonic sort \\
+	\phantom{x}\hspace{3ex} 	     b) Odd-Even Merge sort
 
@@
 \subsection{Size of Evaluation Circuit}
-As the implementation(\autoref{funs}) provides addition and multiplication of cipher-texts,  size in terms of \texttt{XOR} and \texttt{AND} gates are provided for each problem. \newline \newline
-\textbf{XOR of $n$-bits :} \texttt{XOR} of $n$-bits requires $n-1$ \texttt{XOR} gates. \newline \newline
-\textbf{Majority of $n$-bits :} Majority bit is evaluated by obtaining the sum of the bits and then returning the result of the comparison of the sum and $n/2$.
-The comparison is done using algorithm \autoref{Code:algo}.
-This operation is interesting in the sense that if the same program is evaluated on the user's side, he has to store the sum of the bits, hence  needs $\mathrm{\lfloor\log_{2}n \rfloor +1}$ bits of memory.
+As the implementations provide addition and multiplicaion of ciphertexts,  size in terms of \texttt{XOR} and \texttt{AND} gates are provided for each problem.
+
+\textbf{XOR of $n$-bits :} \texttt{XOR} of $n$-bits requires $n-1$ \texttt{XOR} gates. \newline
+\textbf{Sum of integers of $n$-bits :} Sum of two integers is performed using an $n$ \texttt{full-adder} circuits.
+The cost of a full adder circuit is $2$ \texttt{XOR} to calculate the sum and $2$ \texttt{AND}, $1$ \texttt{XOR} and $1$ \texttt{OR} for the carry.
+Hence the total complexity is $3n$ \texttt{AND}, $5n$ \texttt{XOR}.
+\newline
+\textcolor{orange}{\textbf{Sum of arbitrary integers}} \newline
+\textbf{Majority of $n$-bits :} Majority bit is evaluated by obtaining the sum of the bits and then returning the result of the comparision of the sum and $n/2$.
+This operation is interesting in the sense that if the same program is evaluated on the user's side, he has to store the sum of the bits, hence  needs $\mathrm{\lfloor\log_{2}n \rfloor +1}$ bits.
 However, if he performs the operation remotely on a cloud, he only requires a constant number of bits to retrieve the result.
 \newline \newline
-\textbf{Sum of two unsigned integers of $32$ bits :} It is a sum of two $n$-bits sequences such as $n<32$ and it is performed using $n$ \texttt{full-adder} circuits (provided as \texttt{fhe\_fulladd(...)} function in the Scarab library).
-The cost of a full adder circuit is $2$ \texttt{XOR} to calculate the sum and $2$ \texttt{AND}, $1$ \texttt{XOR} and $1$ \texttt{OR} for the carry.
-Hence the total complexity is $3n$ \texttt{AND}, $5n$ \texttt{XOR}.
+\textbf{Product of two $n\times n$ matrices}: This requires $n^3$ \texttt{AND} gates and \texttt{$n^2(n-1)$} \texttt{XOR} gates. \newline \newline
+\textbf{Sorting} Several straight-line programs for sorting have have been proposed in litterature \cite{dk}, \cite{Batcher:1968:SNA:1468075.1468121}.
+These programs use a comparator gate : a logical gate with two inputs and two ouputs, that computes the minimum and maximum of two $n$ bit sequences.
+Algorithm \autoref{Code:algo} implements a comparator gate.
+Hence we do not need to perform any transformation for these algorithms.
 \newline \newline
-\textbf{Sum of two unsigned integers :} This program selects the first $32$-bits sequences of the $2$ integers and does the sum of them exactly like the previous algorithm and then perform the sum with next $32$-bits sequences with the carry from the previous addition until there is no sequence left.
-So this program has approximately the same linear cost as the previous one.
-\newline \newline
-\textbf{Product of two $n\times n$ matrices :} Thes standard two loops algorithm requires $n^3$ \texttt{AND} gates and \texttt{$n^2(n-1)$} \texttt{XOR} gates. \newline \newline
-\textbf{Sorting :} Several straight-line programs for sorting have have been proposed in literature \cite{dk}, \cite{Batcher:1968:SNA:1468075.1468121}.
-These programs use a comparator gate : a logical gate with two inputs and two outputs, that computes the minimum and maximum of two $n$ bit sequences.
-Algorithm \autoref{Code:algo} implements such a comparator gate.
-We do not need to perform any transformation for these algorithms.
-The algorithms used for Bitonic and Odd-Even merge sort are provided in the appendix.
-They accept $n$ which are powers of $2$.
-
-\textbf{Insertion sort :} When allowing for parallel comparators, bubble sort and insertion sort are identical. Hence $n(n-1)/2$ comparator gates are used for insertion sort.
-
-\textbf{Bitonic Sort :} The standard algorithm uses $n\mathrm{log}(n)·(\mathrm{log}(n)+1)/4$ comparator gates.
-
-\textbf{Odd-Even Merge sort :} Odd-Even merge sort requires  $n(\mathrm{log}^{2}(n)-1)/2 + 1 $ comparator gates.
+\textbf{Insertion sort :} When allowing for parallel comparators, bubble sort and insertion sort are identical. Hence $n(n-1)/2$ comparator gates are used for insertion sort.\newline \newline
+\textbf{Bitonic Sort :} \autoref{bitsort} and \autoref{bitmerge} are used to perform Bitonic Sort. The algorithm use $log(n) · (log(n)+1) / 2 $ gates are required. \newline \newline
+\textbf{Odd-Even Merge sort :} \autoref{oesort} and \autoref{oemerge} are used to perform Odd-Even merge sort and hence  $n/2(log(n)-1) + 1 $ comparator gates are required.\newline
 We note that the sorting programs used do not increase the size of the circuit operating on encrypted input bit sequences.
 
-\section{Experimental evaluation \\ and results}
+\lstset{                                    % line wrapping on
+  language=C,
+  frame=lines,
+  captionpos=b
+ }
+
+\renewcommand{\lstlistingname}{Code}
+
+\section{Experimental evaluation \\ and analysis}
 \label{Sec:Eval}
-We execute the implementations of the above programs, and we measure their wall time and compare the cost with the theoretical complexity depending on the sizes of the input data.
-For each test, $5-10$ random samples were taken.
-These were generated using the Unix \texttt{rand()} function by setting the seed using \texttt{srand(time(NULL))}.
 
- \autoref{fig:image_sf7} represents minimum and maximum wall time of \texttt{XOR}.
-We can see that the wall time increases linearly with number of bits which confirm the theoretical cost.
-We notice the same complexity for both \texttt{Bit Majority} \autoref{fig:image_sf0bis} and \texttt{sum of integers} \autoref{fig:image_sf1}.
-We further confirm the $O(n^{3})$ complexity for the \texttt{matrix product} \autoref{fig:image_sf2}.
-These experiments were performed on M2.
+\begin{comment}
+\begin{figure}[!h] %on ouvre l'environnement figure
+\centering
+\includegraphics[width=8cm]{./Insertion_sort_CPU.jpg} 
+\caption{Run time of } 
+\label{image_f2} %l'étiquette pour faire référence à cette image
+\end{figure}
+\end{comment}
+\begin{comment}
+\begin{figure}
 
-\begin{figure}[!H]%on ouvre l'environnement figure
-\centering
-\includegraphics[width=5cm, height=4cm]{f4.pdf} 
-\caption{Wall time for XOR} 
-\label{fig:image_sf0} %l'étiquette pour faire référence à cette image
+\includegraphics{/home/kumaram/Bureau/Measurements/PARAMS1/figures/InsertionSort/Insertion\_sort\_min-max\_4bits.jpg}
+ \label{fig:insernbit4}
+ \caption{Wall time for Insertion sort}
 \end{figure}
-
-\begin{figure}%on ouvre l'environnement figure
-\centering
-\includegraphics[width=5cm, height=4cm]{f8.pdf} 
-\caption{Wall time for bit majority} 
-\label{fig:image_sf0bis} %l'étiquette pour faire référence à cette image
-\end{figure}
-\begin{figure}%on ouvre l'environnement figure
-\centering
-\includegraphics[width=5cm, height=4cm]{f8.pdf} 
-\caption{Wall time for sum} 
-\label{fig:image_sf1} %l'étiquette pour faire référence à cette image
-\end{figure}
-
-\begin{figure}%on ouvre l'environnement figure
-\centering
-\includegraphics[width=5cm, height=4cm]{f9.pdf} 
-\caption{Wall time for matrix product} 
-\label{fig:image_sf2} %l'étiquette pour faire référence à cette image
-\end{figure}
-
+\end{comment}
  \textbf{Sorting :} 
-The experiments on the sorting algorithms were performed on machine M1. 
-Initially, the cryptographic parameters were set to $(N = 8, \nu = 2^{384}, \mu = 4, s_1 = 8, s_2 = 5)$ which is the default setting in the software.
-We measured CPU time and Wall time by varying the sequence length(nbit) and the number of sequences(n).
-We plot maximum and minimum time in minutes for nbit=6, \autoref{fsort8.pdf}.
-
-\begin{figure} %on ouvre l'environnement figure
-\centering
-\includegraphics[width=6cm, height=6cm]{fsort8.pdf} 
-\caption{CPU time for Insertion sort, nbit=6} 
-\label{fig:image_sf8} %l'étiquette pour faire référence à cette image
-\end{figure}
-
- \autoref{fig:image_sf3},\autoref{fig:image_sf4}, \autoref{fig:image_sf5}, \autoref{fig:image_sf6}, \\ \autoref{fig:image_sf8}, \autoref{fig:image_sf7} and \autoref{fig:image_sf2} show the variation of CPU time and Wall time with the increase in the number of sequences to sort and the number of bits.
-These experiments were done for Insertion Sort algorithm.
-\autoref{fig:image_sf1} presents a  curve fitting plot that verifies the quadratic complexity of this algorithm.
+The experiments on the sorting methods were done on the machine M1.
+For each test 5 random samples were taken.
+These were generated using the Unix \texttt{rand} function by setting the seed using \texttt{srand(time(NULL))}.
+Intially the cryptographic parameters were set to $(N = 8, \nu = 2^{384}, \mu = 4, s_1 = 8, $  and $ s_2 = 5)$which is the default setting in the software.
+The above figures show how the CPU time and Wall time vary with the increase in the number of sequences to sort and the number of bits.
+These experiments were done for Insertion Sorting algorithm.
+We also present a  curve fitting plot that verifies quadratic nature of the complexity of this algorithm.
 
 \begin{table}
-\caption{Wall time for Bitonic Sort}
+\caption{CPU time for Bitonic Sort}
 \resizebox{8cm}{!}{
@@
   \hline
-  (Number of sequences,  & Maximum time (in ms) & Minimum time (in ms) \\
-  Number of bits) &  &    \\
+  (Number of bits,  & Maximum time (in ms) & Minimum time (in ms) \\
+  Number of sequences) &  &    \\
   \hline
-  (4,4)  &  34584 & 32759\\
+  (4, 4) & 		 34584 & 32759\\
   (8,4)  & 	  	 189685  & 130157\\
@@
   (32,4) &	 	 1315663 &  1313082\\
-  (4,6)  &  49668 & 49038 \\
-  (8,6)  & 197853 & 196183 \\
-  (16,6) & 667521 & 656369 \\
-  (32,6) & 1976534 & 1946724 \\ 
+
 \hline
@@
 \begin{table}
-\caption{Wall time for Odd-Even Merge Sort}
+\caption{CPU time for Odd-Even Sort}
 \resizebox{8cm}{!}{
@@
   \hline
-  (Number of sequences,  & Maximum time (in ms) & Minimum time (in ms) \\
-  Number of bits) &  &    \\
+  (Number of bits,  & Maximum time (in ms) & Minimum time (in ms) \\
+  Number of sequences) &  &    \\
   \hline
-  (4, 4) & 28363 & 27321  \\
-  (8, 4)  & 158674 & 120868 \\
-  (16,4) & 459895  & 340981  \\
-  (32,4) & 1043093 &  1041674 \\
-  (4,6) & 41350 & 41204 \\
-  (8,6) & 158272  &156721 \\
-  (16,6) & 543735 & 520719 \\
-  (32,6) & 1638711 & 1594432 \\
+  (4, 4) & 		 27958 & 27455\\
+  (8,4)  & 	  	 108197  & 103683\\
+  (16,4) & 	 	 354188 &  341522\\
+  (32,4) &	 	 1587427 &  1044640\\
+
 \hline
 \end{tabular}
-\label{OddEvensort1}
+\label{OddEvensort}
 }
@@
 
-\autoref{bitonicsort}, \autoref{OddEvensort1} justify the fact that Odd-Even Merge algorithm performs better than the Bitonic sort(even though they have the same worst case complexity) as it uses less number of comparator gates.
-We further remark that for small values, Insertion sort performs better than Bitonic, but we estimate that for $32$ sequences of $4$ bits each, Bitonic search would be faster.
-This estimate comes from the fact that the insertion sort would cost $16$ times the cost of sorting only $8$ such sequences i.e.
-around $3000000$ ms.
-This is experimentally confirmed by the obtained value : 3639429 which is thrice the time = 1315663 taken by Bitonic sort.
+When we increase the security of the system by setting the parameters to  $(N = 256, \nu = 16, \mu = 2, s_1 = 5000, s_2 = 5)$ which ensures $25$ bits of security, we obtain the following results for Odd-Even Sorting algorithm.
 
 \begin{table}
-\caption{Wall time for Odd-Even Merge Sort with increased security}
+\caption{CPU time for Odd-Even Sort}
 \resizebox{8cm}{!}{
@@
   \hline
-  (Number of sequences,  & Maximum time (in ms) & Minimum time (in ms) \\
-  Number of bits) &  &    \\
+  (Number of bits,  & Maximum time (in ms) & Minimum time (in ms) \\
+  Number of sequences) &  &    \\
   \hline
   (4, 4) & 		 27958 & 27455\\
-  (8, 4)  &    108197  & 103683\\
+  (8,4)  & 	  	 108197  & 103683\\
   (16,4) & 	 	 354188 &  341522\\
   (32,4) &	 	 1587427 &  1044640\\
-  (32,6) &   1629722 & 1610464\\
+
 \hline
 \end{tabular}
-\label{OddEvensort2}
+\label{OddEvensort}
 }
@@
 
-When we increase the security of the system by setting the parameters to  $(N = 256,\eta  = 16, \mu = 2, s_1 = 5000, s_2 = 5)$(as suggested in \cite{cryptoeprint:2009:571}) which ensures $25$ bits of security, the Odd-Even sorting algorithm on  $4$ sequences, each of $4$ bits takes hours.
-By lowering the security level to only $16$ bits using the parameters :$(N = 16, \eta = 32, \mu = 2, s_1 = 85, s_2 = 5)$, the result did not decrypt to the desired output; which confirms to the theory that $\epsilon$ must be greater than 1 for correct decryption.
-Lowering the security even further to only $2$ bits using the parameters: $(N = 8, \eta = 2^8, \mu = 4, s_1 = 65, s_2 = 5)$, and testing odd-even sorting for $32$ sequences of $6$ bits each took more than an hour.
-However, increasing $\mu$ also increases security, and setting the parameters to :  $(N = 8, \eta = 2^{384}, \mu = 8, s_1 = 8, s_2 = 5)$ we obtained the results as in \autoref{OddEvensort2}.
-The results show that this set of parameters provide a better security(than the default parameters) and at almost no extra cost.
-For this result to be conclusive, we need to perform tests for large $n$.
-For our last test, we set the parameters to  $(N = 8, \eta = 2^{200}, \mu = 8, s_1 = 8, s_2 = 5)$ which gave us incorrect decryption.
-We note that decryption fails in case the depth is too small for re-crypt to function.
+\section{Conclusion}
 
-\section{Conclusion}
-With the examples and the programs discussed, we conclude that the transformation of a non-straight-line program on unencrypted data(with branching) into a straight line program on encrypted data increases the circuit complexity.
-We experimentally measured the cost of different operations on encrypted data and the security-cost trade-off for certain operations.
-The existing implementation of Smart-Vercauteren scheme remains practical only for very low level of security, when a user wants to apply a sorting algorithm on encrypted bit sequences of short length.
+%\begin{figure*}
 
-As the sorting algorithms used can be parallelized to obtain better results, it would be interesting to perform computations on GPU.
+%  \incudegraphics{"/home/honey/Documents/Mosig\_1/ProjSpec/Measurements\Insertion\_sort\_CPU.jpg"}
+
+%\end{figure*}
 
@@
 \bibliography{article}
+
+%\begin{comment}
+\newpage
+\section{Appendix}
+
+ The programs used for Odd-Even Merge sort and Bitonic sort are provided below :
+
+\begin{figure}[h]
+\begin{lstlisting}[label = oesort ]
+
+ OddEvenMergeSort(int lo, int n)
+if (n > 1)
+        {
+            int m = n/2;
+            oddEvenMergeSort(lo, m);
+            oddEvenMergeSort(lo + m, m);
+            oddEvenMerge(lo, n, 1);
+        }
+
+\end{lstlisting}
+\caption{Odd-Even Merge Sort : sort from index lo to n }
+\end{figure}
+
+\begin{figure}
+\begin{lstlisting}[label = oemerge ]
+
+oddEvenMerge(int lo, int n, int r)
+    {
+        int m = r*2;
+        if (m < n)
+        {
+	    //even subsequence ;		
+            oddEvenMerge(lo, n, m); 
+            //odd subsequence ;
+	    oddEvenMerge(lo+r, n, m); 
+	    int i = lo+r;   
+            for (;i + r < lo + n;){
+		compare(i, i + r);
+		i += m;
+	    }
+        }
+        else
+            compare(lo, lo + r);
+    }
+
+\end{lstlisting} 
+\caption{Odd-Even Merge Sort : merging function}
+\end{figure}
+
+\begin{figure}
+\begin{lstlisting}[label=bitsort]
+
+sortup( int m, int n) {//from m to m+n
+    if (n == 1) return;
+    sortup(m, n/2);
+    sortdown(m + n/2, n/2);
+    mergeup(m, n/2);
+}
+ sortdown(int m, int n) {//from m to m+n
+    if (n == 1) return;
+    sortup(m, n/2);
+    sortdown(m + n/2, n/2);
+    mergedown(m, n/2);
+}
+\end{lstlisting}
+\caption{Bitonic Sort : sort form m to n}
+\end{figure}
+
+\begin{figure}[t]
+\begin{lstlisting}[label=bitmerge]
+mergeup(int m, int n) {  
+    if (n == 0) return;
+
+    for (i = 0 : n)
+        // Increasing Comparator
+	 compare(m + i,m + i + n);
+    mergeup(m, n/2);
+    mergeup(m + n,n/2);
+}
+
+mergedown( int m,  int n) { 
+    if (n == 0) return;
+    for (i = 0 : n) 
+        // Decreasing Comparator
+	compare(m + i, m + i + n); 
+    mergedown(m, n/2);
+    mergedown(m + n, n/2);
+}
+\end{lstlisting}
+\caption{Bitonic Merge} 
+\end{figure} 
+%\begin{comment}
+
+% sigproc.bib is the name of the Bibliography in this case
+% You must have a proper ".bib" file
+%  and remember to run:
+% latex bibtex latex latex
+% to resolve all references
+%
+% ACM needs 'a single self-contained file'!
+%
+%APPENDICES are optional
+%\balancecolumns
 \balancecolumns

### 2013-06-18 Report/article.tex
gg

--- 2013-06-18 Report/article.tex
@@
 Futhermore, we observe that the size of the public key is increasing with the increase of $N$ which can be explained by the fact that the resultant of 2 polynomials increases with the increase of the degree which makes the prime number $p$ harder to be found and so it increases the duration of key generation.
+The same thing for encrypt which evaluate a polynomial of degree $N$ so it take more time for bigger $N$ and it generates bigger ciphertexts.
+The decryption function also increases in duration because $p$ and the cpiphertext become bigger with increasing $N$.
+And for the other functions, the increase in duration is explained by the increase of the size of ciphertexts which makes the addition and multiplication more difficult.
 

### 2013-06-18 Report/article.tex
j
ci

--- 2013-06-18 Report/article.tex
@@
 Futhermore, we observe that the size of the public key is increasing with the increase of $N$ which can be explained by the fact that the resultant of 2 polynomials increases with the increase of the degree which makes the prime number $p$ harder to be found and so it increases the duration of key generation.
+The same thing happend to \texttt{Encrypt} which evaluate a polynomial of bigger degree.
+And as for the rest of function they depend on the size of ciphertext which become bigger because $p$ become bigger.
 
@@
 However, for larger values, the cost increases considerably and this is due to the fact that, the coefficients of the random polynomial in \texttt{Encrypt} increase  which is reflected in the size of the ciphertexts.
-Hence it is profitable to increase $\mu$ to increase the security of the system when $\mu$ is not too large
+Hence it is profitable to increase $\mu$ to increase the security of the system when $\mu$ is not too large.
 
-.
 \begin{table}[htb]
@@
   $16$ & 529  & 5.40 & 1.01907 \\
-  $32$ & 801  & 5.40 & 1.01913 \\
-  $64$ & 824  & 5.40 & 1.01920 \\
+  $32$ & 801  & 5.21 & 1.01913 \\
+  $64$ & 824  & 5.04 & 1.01920 \\
 

### 2013-06-18 Report/article.tex
Present

@@
 From \autoref{common cost}, we can infer that the cost of these functions increase with the increase of the degree of the polynomial $F(x)$.
-Futhermore, we observe that the size of the public key is increasing with the increase of $N$ which can be explained by the fact that the resultant of 2 polynomials increases with the increase of the degree which makes the prime number $p$ harder to be found and so it increases the duration of key generation.
-The same thing happend to \texttt{Encrypt} which evaluate a polynomial of bigger degree.
-And as for the rest of function they depend on the size of ciphertext which become bigger because $p$ become bigger.
+Futhermore, we observe that the size of the public key is increasing with $N$ which can be explained by the fact that the resultant of 2 polynomials increases with the degree which makes the prime number $p$ difficult to be found and hence it increases the duration of key generation.
+The reasoning extends to \texttt{Encrypt} which evaluates a polynomial of higher degree.
+As for the rest of functions they depend on the size of ciphertext which becomes bigger with $p$.
 
